### 2014-12-03 tensor/draft/draft-tensor-op.tex
added sub-folder <draft> with latex source and plots of paper draft

% vim: set sts=4 et :
\documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{listings}
\usepackage{xcolor}

\usepackage{textcomp}

\allowdisplaybreaks[1]

%%
%% Setup
%%
% Use the section number in equation tags
\renewcommand{\theequation}{\thesection.\arabic{equation}}
\numberwithin{equation}{section}
\setlength{\parindent}{15pt}

\lstset{
    basicstyle=\ttfamily,
    backgroundcolor=\color{lightgray}
}

%--------+---------+---------+---------+---------+---------+---------+---------+
%
%    Macros
%
%--------+---------+---------+---------+---------+---------+---------+---------+

% references to ...
\def \refeq#1{(\ref{#1})}
\def \refsec#1{sec.~\ref{#1}}
\def \refSec#1{Sec.~\ref{#1}}
\def \refapp#1{app.~\ref{#1}}
\def \reffig#1{fig.~\ref{#1}}
\def \reftab#1{tab.~\ref{#1}}

\def \nn{\nonumber\\}
\def \dis{\displaystyle}

%% tables
\newcommand\tabvsptop{\rule{0pt}{2.6ex}}
\newcommand\tabvspbot{\rule[-1.5ex]{0pt}{0pt}}

%%
%% Comments
%%
\newcommand{\danny}[1]{{\color{purple}{#1}}}
\newcommand{\christoph}[1]{{\color{red}{#1}}}
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{blue}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}

%% ----------------------------
%%  Physics, Math, Convenience
%% ----------------------------

% Physics
\newcommand{\wilson}[2][{}]{\mathcal{C}_{#2}^{\mathrm{#1}}}
\newcommand{\op}[1]{\mathcal{O}_{#1}}
\newcommand{\bra}[1]{\big\langle{#1}\big\vert}
\newcommand{\ket}[1]{\big\vert{#1}\big\rangle}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}

% Convenience
\renewcommand{\[}{\big[}
\renewcommand{\]}{\big]}
\renewcommand{\(}{\big(}
\renewcommand{\)}{\big)}
\newcommand{\dd}{{\rm d}}
\newcommand{\para}{\parallel}
\newcommand{\eps}{\varepsilon}
\newcommand{\GeV}{\ensuremath{\mathrm{GeV}}}
%\newcommand{\MeV}{{\si{\MeV}}
\newcommand{\msbar}{\ensuremath{\overline{\rm MS}}}

%% Physics
\newcommand{\alphas}{\alpha_\mathrm{s}}
\newcommand{\alphae}{\alpha_\mathrm{e}}
\newcommand{\gfermi}{G_\mathrm{F}}
\newcommand{\amp}[1]{\mathcal{A}\left({#1}\right)}

%--------------
% math symbols
%--------------

\renewcommand{\Im}[1]{{\rm Im}\left\lbrace{#1}\right\rbrace}
\renewcommand{\Re}[1]{{\rm Re}\left\lbrace{#1}\right\rbrace}

\def \ket#1{ \left| #1 \right\rangle}
\def \brac#1{\left\langle #1 \right|}
\def \averA#1{\left\langle #1 \right\rangle}
\def \aver#1{\langle #1 \rangle}
\def \abs#1{ \left| #1 \right| }
\def \order#1{ {\cal O} \left( #1 \right) }
\def \dslash#1{ #1\!\!\!/}
\def \re{\textrm{Re}}
\def \im{\textrm{Im}}
\def \eps{\varepsilon}
\def \LogGamma{\textrm{LogGamma}}
\def \Amoroso{\textrm{Amoroso}}
\def \vecth{\vec{\theta}}
\def \vecnu{\vec{\nu}}

%-------------
% caligraphic
%-------------

\def \cA{{\cal A}}
\def \cC{{\cal C}}
\def \cF{{\cal F}}
\def \cL{{\cal L}}

%
% effective Lagrangian, operators
%

\def \cLdB1{{{\cal L}_{\Delta B = 1}^{\rm EW}}} % Delta_B = 1 effective Lagrangian
\def \BR{{\cal B}}                               % branching ratio

\def \Op{{\cal O}}
\def \OpQ{{Q}}
\def \OpF{{O}}         % current operator of full theory (Delta_B = 1)
\def \OpE{{\cal O}}    % current operator of effective theory

\def \One{\leavevmode\hbox{\small1\kern-3.6pt\normalsize1}} % unit matrix

%-------------
% differential
%-------------

\newcommand\rmdx[1]{\mbox{d} \, #1 \,}

%--------------------------------
% couplings, scales, observables
%--------------------------------

\def \gS{g_s}              % strong coupling
\def \alS{\alpha_s}        % strong coupling
\def \alE{\alpha_e}        % electro-magnetic coupling
\def \GF{G_F}              % Fermi coupling
\def \LamConf{{\Lambda_{\rm QCD}}}    %  confinement scale
\def \LamConfS{{\Lambda^2_{\rm QCD}}} % (confinement scale)^2

\def \Gaml{{\Gamma_l}}
\def \Game{{\Gamma_e}}
\def \Gammu{{\Gamma_\mu}}

\def \BRl{{{\cal B}_l}}
\def \BRe{{{\cal B}_e}}
\def \BRmu{{{\cal B}_\mu}}

\def \BRll#1#2#3{{\BR(#1) |_{[#2] #3}}}

\def \AFBl{{A_{\rm FB}^l}}
\def \AFBmu{{A_{\rm FB}^\mu}}

\def \FHl{{F_H^l}}
\def \FHe{{F_H^e}}
\def \FHmu{{F_H^\mu}}

%--------
% angles
%--------

\def \thl {{\theta_\ell}}
\def \thK {{\theta_{K}}}
\def \barthl {{\bar{\theta}_l}}
\def \barthK {{\bar{\theta}_{K^*}}}

%--------
% decays
%--------

%
% B -> X + M
%
\def \BtoXM  {\bar{B} \to XM}
%
% b -> scc, B -> J/psi + ...
%
\def \cc{{\bar{c}c}}    % ccbar
\def \bscc   {b \to s + (c\bar{c})}

\def \BJpsiX {\bar{B} \to J/\psi X}
\def \BJpsiXs{\bar{B} \to J/\psi X_s}
\def \BJpsiK {\bar{B} \to J/\psi K}
%
% b -> clv
%
\def \bclv {b\to c l \bar\nu_l}
\def \BXclv  {\bar{B} \to X_c l \bar\nu_l}
%
% b -> s gamma
%
\def \bsgamma {b\to s \gamma}
\def \BXsgamma {\bar{B} \to X_s \gamma}
\def \BtoKastgamma{{ \bar{B} \to K^{\ast} \gamma}}
%
% bs -> ll, B_q -> ll
%
\def \Bstoll{{\bar{B}_s \to \bar{l}l}}
\def \Bstomm{{\bar{B}_s \to \bar{\mu}\mu}}
\def \Bqtomm{{\bar{B}_{d,s} \to \bar{\mu}\mu}}
%
% b -> sll
%
\def \bsll {b\to s \bar{l}l}
\def \BXsll{\bar{B} \to X_s \bar{l}l}

\def \BtoKast{{ \bar{B} \to K^{\ast}}}
\def \B0toK0ast{{ \bar{B}^0 \to K^{\ast 0}}}
%
% excl B->Kll
%
\def \BtoKll{{\bar{B} \to K \bar{l}l}}
\def \BtoKee{{\bar{B} \to K \bar{e}e}}
\def \BtoKmumu{{\bar{B} \to K \bar{\mu}\mu}}
\def \BptoKpll{{B^+ \to K^+ \bar{l}l}}
\def \BmtoKmll{{B^- \to K^- \bar{l}l}}
\def \BneutralKll{{\bar{B}^0 \to K^0 \bar{l}l}}
%%%\def \B0toK0ll{{\bar{B}^0 \to K^0 \bar{l}l}}
\def \BtoKastll{{\bar{B} \to K^\ast \bar{l}l}}
\def \BtoKastmumu{{\bar{B} \to K^\ast \bar{\mu} \mu}}

\def \BmtoKmmumu{{ B^- \to K^- \bar{\mu} \mu}}
\def \B0toK0mumu{{ \bar{B}^0 \to K^0 \bar{\mu} \mu}}
%
% excl B-> K^* (-> K pi) ll
%
\def \BtoKKpill{{ B \to K^\ast (\to K \pi) \bar{l}l}}
\def \BtoKKpimm{{ B \to K^\ast (\to K \pi) \bar{\mu}\mu}}
\def \barB0toKKpill{{ \bar{B}^0 \to \bar{K}^{\ast 0} (\to K^- \pi^+) \bar{l}l}}
\def \B0toKKpill{{ B^0 \to K^{\ast 0} (\to K^+ \pi^-) \bar{l}l}}
\def \BtoKastKpill{{ (\bar{B}^0, B^0)\to (K^{\ast 0},\bar{K}^{\ast 0}) (\to K^\mp \pi^\pm) \bar{l}l}}

%
% Scenario Names
%
\def \SMnu{SM($\nu$-only)}
\def \SM{SM}
\def \SMp{SM+SM$'$}
\def \SMpNine{SM+SM$'$$(9)$}

%--------+---------+---------+---------+---------+---------+---------+---------+
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+

\begin{document}

\title{Constraining tensorial and scalar couplings with 
  $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
}

\author{Frederik Beaujean}
\affiliation{
  C2PAP, Excellence Cluster Universe,\\
  Ludwig-Maximilians-Universit\"at M\"unchen,
  Garching, Germany
}

\author{Christoph Bobeth}
\affiliation{
  Institute for Advanced Study,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

\author{Stephan Jahn}
\affiliation{
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

\date{\today}

\preprint{EOS-2014-??, FLAVOUR(267104)-ERC-??}

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry $A_{\rm FB}^\ell$ and a flat
  term $F_H^\ell$ that are both suppressed in the standard model and very
  sensitive to nonstandard tensorial and scalar contributions. We use latest
  experimental results for $\ell = \mu$ in combination with $B_s\to \bar\mu\mu$
  to derive stronger model-independent constraints on tensorial and scalar 
  effective couplings and determine their impact on $B\to K^*\bar\mu\mu$ 
  angular observables. Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped 
  counterparts that are complementary to the once from the branching ratio 
  $B_s\to \bar\mu\mu$, which allows to put for the first time upper bounds
  on all four couplings.
\end{abstract}

%
%
%

\maketitle

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Introduction
}

With the first run of data taking by the LHCb Collaboration at the Large Hadron
Collider (LHC), $B$ physics has now also access to rather large samples of
rare $B$-meson decays with branching ratios below the $10^{-5}$. In consequence, 
angular analyses of three- and four-body final states can be used to measure
a larger number of additional observables. Namely rare $B$ decays that are driven
at parton level by flavor-changing neutral current (FCNC) transitions $b\to s
\bar\ell\ell$ constitute valuable probes of the standard model (SM) and provide
constraints on its extensions, especially $B\to K^*(\to K\pi) \bar\ell\ell$, but
also $B\to K \bar\ell\ell$.

The angular distribution of $B\to K \bar\ell\ell$ in the angle $\theta_\ell$
between the $B$ and $\ell^-$ as measured in the dilepton rest frame
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} & 
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell 
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,,
\end{align}
normalised to the width $\Gamma_\ell$, has been recently updated with 3 fb$^{-1}$
by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,
with unprecedented precision, and the first analysis of $B^0\to K_{S} \bar\mu\mu$
has been reported as well. It provides the lepton-forward-backward asymmetry 
$A_{\rm FB}^\mu$ and the flat term $F_H^\mu$ in CP-averaged form and integrated
over several bins in the dilepton invariant mass $q^2$. Similarly, the CP-averaged
branching ratios, ${\cal B}_\mu = \tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli}
and the rate CP asymmetry $A_{\rm CP}^\mu$ \cite{Aaij:2014bsa} are also
available from 3 fb$^{-1}$.

Both observables exihibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM 
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ 
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$ \cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details on the treatment of theory uncertainties are relegated to
appendices.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Effective Theory 
  \label{sec:EFT}
}

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory 
\begin{align}
  \label{eq:Heff}
  {\cal L}_{\rm eff} & =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, V_{tb}^{} V_{ts}^\ast
       \sum_{\ell = e, \mu,\tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i + \text{h.c.}
\end{align}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \bar\ell\ell$ are classified according to their chiral structure. 
There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$) operators 
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} & 
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} & 
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} & 
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} & 
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} & 
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} & 
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} & 
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at the typical
scale of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM predictions
in the presence of new physics.

The SM values $\wilson[\ell]{7,9,10}$ are obtained at NNLO \cite{Bobeth:2003at, 
Huber:2005ig} and depend on the fundamental parameters of the top-quark and
$W$-boson masses, as well as on the sine of the weak mixing angle. Moreover,
they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero: 
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim 
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. Beyond the SM,
lepton-flavor non-universal effects are possible in principle and have been 
discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa, 
Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

The Wilson coefficients of the four-quark current-current and QCD-penguin
operators as well as of the chromomagnetic dipole operators are set to their
NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$ \cite{Bobeth:2003at, Huber:2005ig}.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Observables and experimental input
  \label{sec:observables}
}

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective 
couplings
\begin{align}
  F_H^\ell(q^2)|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which in principle could also give additional $\cos\theta_\ell$ dependence
to the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background.

This picture does not change in the presence of new physics contributions to
vectorial and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
non-vanishing tensorial or scalar contributions are enhanced unless the 
dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensorial couplings whereas $A_{\rm FB}^\ell$ to
the interference of tensorial and scalar couplings.

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_CT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_CT.pdf}
  \caption{
    The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability. 
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9} 
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).
  }
  \label{fig:FHvsCT}
\end{figure*}

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial once 
present in the SM or their respective interference terms. These are $J_{6c}$ 
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ 
with explicit formulas given in \refapp{app:BKstarellell}. 
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto 
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T} 
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensorial and scalar operators,
  complementary to lepton forward-backward asymmetry of $B\to K \bar\ell\ell$} 
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto 
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5} 
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensorial contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensorial contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto 
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align} 
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensorial and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto 
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K 
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw, 
Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only 
constructively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times 
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
\refeq{eq:AFB-dependence} are measured in the angular
distribution \refeq{eq:ang-distr} of $B\to K \bar\ell\ell$ being normalised to the
decay width $\Gamma_\ell$, whereas $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$
appear in the unnormalised angular distribution of $B\to K^* \bar\ell\ell$.
Hence in the former, uncertainties due to form factors can cancel in part
\cite{Bobeth:2007dw, Bobeth:2012vn}. So-called ``optimised'' versions $S_1$, $M_1$ and
$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw} 
for $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, respectively.
In \refapp{app:BKstarellell} potential normalisations are discussed that
could serve to form optimised observables at high $q^2$ for special cases of
either vanishing chirality-flipped vectorial or tensorial or scalar couplings.
In the most general case, however, there are no optimised observables.
Although form factors do not cancel in this case, it might be
still advantageous to use normalisations, for example when the overall
normalisation of $B\to K^*$ form factors constitutes a major theoretical
uncertainty.

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}    
\\   
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\    
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements. 
  Lattice results of $B\to K$ form factors are used to constrain their parameters,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.  
}
\end{center}
\end{table*}

To illustrate the sensitivity of $F_H^\ell$ to tensorial couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of 
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa, 
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides 
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen, 
the sensitivity to tensorial couplings is highest for $F_H^\ell$ at high $q^2$, 
also due to a partial cancellation of form factors \cite{Bobeth:2012vn}, 
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensorial couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of 
tensorial couplings. Moreover, the dependence on vectorial couplings is such that 
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

Important additional constraints on scalar couplings come from
the branching ratio of $B_s \to \bar\mu\mu$ as given in \refeq{eq:Br-Bsmumu}.
It provides the most stringent constraints on the moduli $|\wilson{S} - \wilson{S'}|$
and $|\wilson{P} - \wilson{P'}|$ that are complementary to \refeq{eq:FH-dependence}
in $B\to K \bar\ell\ell$ and depends only on the further combination 
$(\wilson{10} - \wilson{10'})$.

We will also make use of the branching ratio of $B\to K^* \bar\mu\mu$ as it
allows us to $\ldots$
\todo{$A_{\rm CP}$ included.}

\todo{Find a place to cite \cite{Becirevic:2012fy}, perhaps in section on results
comparing our bounds to theirs in eq.(49): $|\wilson{S,\,S'}|Ê\lesssim 0.7$ and
$|\wilson{P,\,P'}|Ê\lesssim 1.0$ - what about \cite{Altmannshofer:2012az}
and \cite{Hurth:2012jn, Hurth:2013ssa} (this is only MFV, i.e. only one operator)?}.

In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
kinematically suppressed terms in observables, neither in the prediction of
yet not measured observables. The experimental input of these observables is 
listed in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
form factors. More details on the latter can be found in \refapp{app:theory:inputs}.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Fits and constraints
  \label{sec:results}
}

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section)
of $F_H^\mu$ and $A_{\rm FB}^\mu$ and their tiny SM predictions. Thus our main objective
is the derivation of stronger constraints on tensorial and scalar couplings, which
are enhanced in both observables compared to vectorial ones. For this purpose,
we will consider several model-independent scenarios, starting from rather
restricted to more general ones, in order to asses the effect of cancellations
among different contributions.

We will start with only tensorial couplings and see that they are well constrained
by $F_H^\mu$ alone. In a second step we consider only scalar couplings in order
to investigate the complementarity of $F_H^\mu$ and $B_s \to \bar\mu\mu$.
Eventually we will consider as a special scenario the SM augmented by dimension
six operators as an effective theory of new physics below some high scale
$\Lambda_{\rm NP}$, much larger than the typical scale of electroweak 
symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
as in the SM, i.e. $v \ll \Lambda_{\rm NP}$.

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensorial couplings \label{sec:tensor}}

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\ 
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$
  & $\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$
  & $\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)
  & $[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
  \\
  \hline 
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $< 0.35$ ($< 0.55$)
  & $< 0.25$ ($< 0.35$)
  & $< 0.30$ ($< 0.45$)
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized 
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $B_s \to \bar\mu\mu$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\wilson[NP]{i} \in [-3,\, 3]$.
  }
\end{table*}

In a scenario with only tensorial complex-valued couplings $\wilson{T,\, T5}$,
the experimental measurement of $F_H^\mu$ constrains the combination
$|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
$\wilson{T}$ with vectorial couplings $\wilson{7,\,7',\,9,\,9'}$. 
The according 65\% (95\%) 1D-marginalized probability intervals are listed in
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the branching ratio of $B\to K^{*} 
\bar\mu\mu$. The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that yield too high predictions compared
to the measurements~\cite{Horgan:2013pva}. Since tensorial couplings contribute
constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
constrained. In this scenario, the measurements of $A_{\rm FB}^\mu$ does not pose
constraints due to vanishing scalar couplings and we find that the rate 
CP-asymmetries $A_{\rm CP}$ of $B\to K^{(*)} \bar\mu\mu$ do not provide 
constraints, therefore omitting them.

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$,
($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
against destructive interference. In this case, $F_H^\mu$ by itself still provides 
bounds $|\wilson{T,\,T5}| < 0.5\,(0.8)$ at 68\% (95\%) probability that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and one recovers almost the same
constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ 
by a factor of two.

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Scalar couplings \label{sec:scalar}}

Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without 
kinematic suppression --- see \refeq{eq:FH-dependence} --- in the complementary
manner $(\wilson{i} + \wilson{i'})$, with $i = S,\, P$, to the branching ratio
$B_s\to \bar\mu\mu$, which provides only constraints on $(\wilson{i} - \wilson{i'})$.
Most notably, we find that the current measurement of $F_H^\mu$ does constrain 
the orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination with
$\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound for the first time the moduli of
all four couplings.

The according four-parameter fit for real-valued scalar couplings to the data of
$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
regions in the $(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
\reffig{fig:scalar}. The combination of $\overline{\cal B}(B_s \to \bar\mu\mu)$ 
and $F_H^\mu$ does not change when including the data of ${\cal B}$'s of $B\to 
K^{(*)}\bar\mu\mu$ --- remember that $A_{\rm FB}^\mu$ requires interference of
scalar with tensorial couplings. Quantitatively, the constraint from $\overline{\cal B}
(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor five
stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green) 
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson{10} \in [-1,\, 9]$, $\wilson{10'} \in [-5,\,5]$ (red) 
    at 68\% (darker) and 95\% (lighter) probability. The constraints on 
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
  }
  \label{fig:scalar}
\end{figure*}

Interference terms of $\wilson{P,\,P'}$ with vectorial couplings might weaken 
bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are 
$(\wilson{10} - \wilson{10'})$ --- compare \refeq{eq:Br-Bsmumu:time0} --- and
for $F_H^\ell$ similarly $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw},
which are suppressed by factors $m_\ell/M_{B_s}$ and $m_\ell/\sqrt{q^2}$,
respectively. However, due to the large SM contribution of $\wilson[SM]{10}
\simeq -4.2$, these terms are important for small pseudo-scalar couplings.
We compile constraints on complex-valued scalar couplings from $i)$ only
$F_H^\mu$, $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$
their combination, even allowing new physics in $\wilson{10,\, 10'}$ in
\reftab{tab:cSP:1-dimCLs}. Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
alone can bound all four complex-valued scalar couplings, however their
combination is capable to do so and moreover, the bounds are stable against
destructive interference with vectorial couplings. In the general case
of complex-valued couplings, $\overline{\cal B}(B_s \to \bar\mu\mu)$ does
not provide anymore constraints on sub-intervals in contrast to the
case of real-valued couplings. In consequence, for example the ring-like
structure in the $(\wilson{S}-\wilson{S'}) - (\wilson{P}-\wilson{P'}) $-plane
of \reffig{fig:scalar} would turn into a filled circle.

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
  & all
  \\ 
  set of couplings
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'}$
  & $\wilson{S,\,S',\,P,\,P'\,10,\,10'}$
  \\
  \hline \hline
  $\mbox{Re}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  \\
  $\mbox{Im}(\wilson{S} - \wilson{S'})$
  & $\quad$ $-$ $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
  \\[0.1cm]
  $\mbox{Re}(\wilson{S} + \wilson{S'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)
  \\
  $\mbox{Im}(\wilson{S} + \wilson{S'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)
  & $[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)
  \\
  $\mbox{Im}(\wilson{P} - \wilson{P'})$
  & $-$
  & $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)
  & $[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)
  \\[0.1cm]
  $\mbox{Re}(\wilson{P} + \wilson{P'})$
  & $[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\
  $\mbox{Im}(\wilson{P} + \wilson{P'})$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  & $-$
  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cSP:1-dimCLs}
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized 
     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
     \reftab{tab:observables} allowing also for new physics contributions to 
     $\wilson{10,\,10'}$ with uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$.
  }
\end{table*}

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{SM-EFT-constrained scalar couplings}

In the following we consider a model-independent scenario as predicted by the SM
augmented by dimension six operators that respect the SM gauge group and are
composed out of SM fields. After the discovery of a scalar resonance at the LHC
that complies currently with all requirements of the Higgs particle in the SM
and the steadily rising lower bounds on new particle masses towards higher energies 
from ATLAS and CMS such a scenario becomes more and more viable.

A non-redundant set of dimension six operators of
this effective theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
matching to the effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the
scale $\mu \sim m_W$ of the order of the $W$-boson mass in \cite{D'Ambrosio:2002ex}
for vectorial couplings $\wilson{7,\,9,\,10}$. The matching for tensor
\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators 
\cite{Alonso:2014csa} shows that SM gauge groups impose the relations
\begin{align}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensorial couplings to be
suppressed to the level of dimension eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm NP} \ll 1$
where $v^2$ denotes the scale of electroweak symmetry breaking and $\Lambda_{\rm NP}$
a high energy scale at which new physics generates these operators.

The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (neglecting
terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$) \cite{Alonso:2014csa}
\begin{equation}
\begin{aligned}
  \overline{\cal B}(B_s\to \bar\ell\ell) & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2 
\\[0.2cm]
  - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re} 
  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right]
\end{aligned}
\end{equation}
and almost similarly (neglecting terms of order $m_\ell^2/q^2$
and $m_s/m_b$)
\begin{equation}
\begin{aligned}
  F_H^\ell & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2 
\\[0.2cm] 
  & - \frac{4 m_\ell\, m_b}{q^2} \mbox{Re} 
  \left[ (\wilson{S} - \wilson{S'})(\wilson{10} + \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}

The SM gauge groups do not impose constraints on the operators of the SM-EFT that
imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
are in general additional independent parameters. Here we find that destructive
interference with contributions involving $\wilson{10,\, 10'}$ do not change
much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. However,
for the most general case of complex-valued couplings destructive interference
constrains (4 parameters)

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensorial, scalar and vectorial couplings and
  predictions for $B\to K^* \bar\ell\ell$}

We start with the scenario of the combination of tensorial and scalar couplings
$\wilson{S,S',P,P',T,T5}$, i.e. the combination of the preceding
two sections. In this scenario there are only small changes on the bounds, in fact
they tend to be even more stringent, because tensorial and scalar couplings
can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. Furthermore we find that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts. In this case, the constraints are even a bit tighter and strong correlations
arise as before among real parts of $\wilson{i}$ and $\wilson{i'}$ for $i = S,P$,
and in addition similarly among their imaginary parts.  
\todo{Check this with EOS}

In the remainder we discuss the influence of non-standard $\wilson{10,\, 10'}$,
that play an important role in $\overline{\cal B}(B_s \to \bar\mu\mu)$ ...

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{Conclusions}

We have derived to date most stringent constraints on tensorial and scalar
couplings that mediate $b\to s\bar\mu\mu$ utilising the latest measurements
of angular observables $F_H^\mu$ and the lepton forward-backward asymmetry
$A_{\rm FB}^\mu$ in $B^+\to K^+ \bar\mu\mu$ from LHCb \cite{Aaij:2014tfa},
supplemented by measurements of the branching ratios of $B_s\to \bar\mu\mu$ and
$B\to K^{(*)} \bar\mu\mu$. Both observables, $F_H^\mu$ and $A_{\rm FB}^\mu$,
belong to a class in which vectorial and dipole couplings that arise also in
the standard model (SM) are suppressed (mostly kinematically by $m_\ell / 
\sqrt{q^2}$) w.r.t tensorial and scalar couplings. We provide predictions for
analogous but not yet measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ .

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensorial couplings $|{\cal C}_{T,\,T5}^\mu|
  < 0.35\, (0.55)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
  (0.45)$, even in the presence of non-standard contributions in vectorial
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar 
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vectorial couplings
  $|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
  0.1\, (0.2)$ for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
  strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
  Future measurements at LHCb and Belle II might change this, especially for 
  $\ell = e$. 
\item SM-EFT $\ldots$
\end{enumerate}
In all cases these constraints are weakened only slightly in the presence of
new physics in vectorial couplings from destructive interference.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS} and Chris Bouchard for communications concerning $B\to K$
  form factors \cite{Bouchard:2013eph}.
  C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR'' 
  (267104).
\end{acknowledgments}

%--------+---------+---------+---------+---------+---------+---------+---------+
%
%  Appendix
%
%--------+---------+---------+---------+---------+---------+---------+---------+

\appendix

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Angular observables in $B\to K^* \bar\ell\ell$
  \label{app:BKstarellell}
}

Here we present those angular observables $J_i$ in $B\to K^* \bar\ell\ell$
in which tensorial and scalar contributions are kinematically enhanced by a factor
$\sqrt{q^2}/m_\ell$ over vectorial once present in the SM or their respective 
interference terms using results and notation from \cite{Bobeth:2012vn}.

For convenience, we split the time-like transversity amplitude into
\begin{align}
  A_t & 
  = \tilde{A}_t - \frac{1}{2} \frac{\sqrt{q^2}}{m_\ell} A_P
\end{align}
that depend on the Wilson coefficients $i = 10, 10', P, P'$ and the scalar
$B\to K^*$ form factor $A_0(q^2)$, a normalisation factor $N$ and the 
K{\"a}ll{\'e}n-function $\lambda$ (see \cite{Bobeth:2012vn})
\begin{equation}
\begin{aligned}
  \tilde{A}_t & = 2 N \frac{\sqrt{\lambda}}{\sqrt{q^2}}
    (\wilson[]{10} - \wilson[]{10'}) A_0\,,
\\
  A_P & = - 2 N\sqrt{\lambda} \frac{(\wilson[]{P} - \wilson[]{P'})}{(m_b+m_s)} A_0\,.
\end{aligned}
\end{equation}
The lepton-flavor index $\ell$ at Wilson coefficients is omitted for
brevity throughout this section.

In full generality angular observables in $B\to K^* \bar\ell\ell$ depend on
seven transversity amplitudes with vectorial and dipole contributions 
$A_{0,\,\perp,\,\parallel}^{L,R}$, and $\tilde{A}_t$, one scalar and one
pseudoscalar amplitude $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$, 
and six tensorial amplitudes: $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto 
\wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$. 
The interesting combinations are

\begin{widetext}
\begin{align}
  \frac{4}{3} J_{6c} & =
  4\, \beta_\ell\, \mbox{Re} \bigg[ 2\, (A_{t0}^{} A_S^* - A_{\parallel\perp}^{} A_P^*) + 
      \frac{m_\ell}{\sqrt{q^2}} \big[(A_0^L + A_0^R) A_S^* 
           + 4\, A_{\parallel\perp}^{} \tilde{A}_t^* \big] \bigg],
\\
  \frac{4}{3}\(J_{1c} + J_{2c}\) & =
    \Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2
   + \Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2 + \beta_\ell^2\, |A_S|^2
   + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2,
\\[0.2cm]
  \frac{4}{3}\(J_{1s} - 3\, J_{2s}\) &  =
    \Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\perp^L + A_\perp^R) + 4\, A_{t\perp} \Bigg|^2
  + \Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\parallel^L + A_\parallel^R) + 4\, A_{t\parallel} \Bigg|^2.
\end{align}
\end{widetext}
Above $\beta_\ell^2 = 1 - 4 m_\ell^2/q^2 \to 1$ for $m_\ell \ll \sqrt{q^2}$.
The condition is well fulfilled for $\ell = e$ and $1\, \mbox{GeV}^2\lesssim q^2$,
provided that tensorial and scalar Wilson coefficients do not receive additional 
suppression factors. For $\ell = \mu$ the value of $q^2$ should not be too low,
whereas in the case $\ell = \tau$, these observables are not anymore dominated by 
tensorial and/or scalar contributions alone, and the full lepton-mass dependence has
to be taken into account.

Finally, we note that the term
\begin{widetext}
\begin{align}
  \Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
  + \beta_\ell^2\, |A_S|^2  & = 
  4 N^2 \lambda A_0^2 \Bigg\{ 
    \beta_\ell^2 \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2 
  + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{q^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2 
    \Bigg\}
\end{align}
entering $(J_{1c} + J_{2c})$, resembles very much the branching ratio of the rare
decays $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
\begin{equation}
\label{eq:Br-Bsmumu:time0}
\begin{aligned}
  {\cal B}(B_s \to \bar\ell\ell) & = 
    \frac{G_F^2 \alpha_e^2 |V_{tb}^{} V_{ts}^*|^2}{64\, \pi^3} 
    M_{B_s}^5 f_{B_s}^2 \tau_{B_s} \beta_\ell(q^2 = M_{B_s}^2) 
\\
   & \hskip0.5cm \times \Bigg\{ 
    \beta_\ell^2(q^2 = M_{B_s}^2) \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2 
  + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
     + \frac{2 m_\ell}{M_{B_s}^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2 
    \Bigg\}\,.
\end{aligned}
\end{equation}
\end{widetext}
Hence there is some complementarity among $(J_{1c} + J_{2c})$ in $B \to K^*
\bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$, however former depends also
on tensorial couplings and vectorial couplings. The helicity suppression
factor $4\,m_\ell^2/q^2$ of vector couplings is weaker in 
$B \to K^* \bar\ell\ell$ decays than the corresponding factor 
$4\,m_\ell^2/M_{B_s}^2$ in $B_s \to \bar\ell\ell$.

Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0} 
corresponds to the unintegrated branching ratio at time $t=0$. Due to the non-vanishing
decay width $\Delta\Gamma_s$, experiments measure the average 
time-integrated branching ratio --- denoted by $\overline{\cal B}$ --- 
and both are related as \cite{DeBruyn:2012wk} 
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) & 
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$. 
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot 
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba} 
and NNLO QCD corrections \cite{Hermann:2013kca}.

Finally we discuss the possibility of suitable normalisations of $J_{6c}$,  
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
optimised observables. For this purpose we use form factor relations at leading
order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
notation and expressions derived in \cite{Bobeth:2012vn},
\begin{equation}
\begin{aligned}
  J_{1s} - 3\, J_{2s} & = \frac{3}{2}\, \rho_1^T (f_\perp^2 + f_\parallel^2) \,,
\\[0.1cm]
  J_{1c} + J_{2c} & = 3\, \rho_1^T f_0^2 
     + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\ 
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
\\[0.1cm]
  \frac{4}{3} J_{6c} & = \todo{???}
\end{aligned}
\end{equation}
Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
the $\rho_1^\pm$ depends on vectorial couplings and $\rho_1^T \propto 
(|\wilson{T}|^2 + |\wilson{T5}|^2)$.

Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalisations,
unless chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ vanish, because then
$\rho_1^+ = \rho_1^-$ holds. There are three potential normalisations
\begin{equation}
\begin{aligned}
  \frac{4}{3} & J_{1s} =
    (3 \rho_1^+ + \rho_1^T) f_\perp^2 +  (3 \rho_1^- + \rho_1^T) f_\parallel^2 \,,
\\
  \frac{8}{3} & J_{2s} =
    (\rho_1^+ - \rho_1^T) f_\perp^2 +
    (\rho_1^- - \rho_1^T) f_\parallel^2 \,,
\\[0.1cm]
  & J_{1s} + 2 J_{2s} =
    3 (\rho_1^+ f_\perp^2 + \rho_1^- f_\parallel^2) \,
\end{aligned}
\end{equation}
where the last one depends only on vectorial couplings, i.e., is free of
tensorial and scalar ones. In the $J_{1s}$ and $J_{2s}$, tensorial couplings
contribute either cumulative or destructive to vectorial couplings in 
$\rho_1^\pm$.

A similar situation arises for $(J_{1c} + J_{2c})$, where no appropriate
normalisation exists, unless scalar couplings vanish. In this special
case, either $J_{1c}$ and also $J_{2c} = -3/2 (\rho_1^- - \rho_1^T) f_0^2$ will
depend only on $f_0$ and can be used as normalisation. In the general case, 
$J_{2c}$ still depends only on tensorial couplings and was used at low $q^2$  
\cite{Matias:2012xw}. Finally we note that
\begin{equation}
\begin{aligned}
  J_{1c} - J_{2c} & = 3\,\rho_1^- f_0^2 + \frac{3 N^2 \lambda}{(m_b+m_s)^2} A_0^2
\\ 
   & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,. 
\end{aligned}
\end{equation}
is free of tensorial couplings at high $q^2$ and would provide access to
$\rho_1^-$ provided scalar couplings vanish.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Theoretical Inputs
  \label{app:theory:inputs}
}

Here we describe the theoretical treatment of observables and collect numerical
input of the most relevant parameters. The software package {\tt EOS} \cite{Bobeth:2011gi,
Bobeth:2011nj, EOS} is used for predictions of observables in $B_s\to \bar\mu\mu$
and $B\to K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt pypmc},
which incorporates the algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj}
and in addition an implementation of the variational Bayes algorithm.

The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ depend on 
$B\to K^{(*)}$ form factors and do not receive any other long-distance contribution,
i.e., they factorize naively. These amplitudes are implemented in {\tt EOS} for 
$B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as given in \cite{Bobeth:2007dw}
and \cite{Bobeth:2012vn}, respectively, and without the use of form factor relations
at large and low recoil.

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters and according values, whose uncertainties
are negligible. \todo{Check for updated values for $y_s$ of $B_s$?} Further, we 
adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
given in \cite{Beaujean:2013soa}.

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34^{+0.05}_{-0.02}$  &  --    &  \cite{Khodjamirian:2010vf}\\
  $f_T(0)$    &  $0.39^{+0.05}_{-0.03}$  &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

The most important change in the treatment of $B\to K$ form factors is the consistent
use of correlations available from lattice \cite{Bouchard:2013eph} for all three form
factors  $f_{+,T,0}$ in the construction of their prior. We use the $z$-parameterization
\cite{Khodjamirian:2010vf}, such that only five nuisance parameters --- see
\reftab{tab:hadronic:nuisance} --- arise due to the kinematical relation 
$f_0(0) = f_+(0)$.

\begin{table}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccc}
        \hline
        $q^2$ [\GeV] & $17$            & $20$            & $23$\\
        \hline
        $f_0(q^2)$   & $0.62 \pm 0.03$ & $0.72 \pm 0.03$ & $0.87 \pm 0.04$\\
        $f_+(q^2)$   & $1.13 \pm 0.05$ & $1.63 \pm 0.07$ & $2.68 \pm 0.13$\\
        $f_T(q^2)$   & $1.02 \pm 0.06$ & $1.47 \pm 0.08$ & $2.42 \pm 0.18$\\        
        \hline
    \end{tabular}\\
    \renewcommand{\arraystretch}{1.0}
    \vspace{2\smallskipamount}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{c|ccccccccc}
        \hline
        $q^2$ [\GeV]
             & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
        \hline
   $f_0(17)$ & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010 & 0.048 \\
   $f_0(20)$ & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093 & 0.075 \\
   $f_0(23)$ & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046 & 0.058 \\
   $f_+(17)$ & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21  & 0.051 \\
   $f_+(20)$ & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26  & 0.20  \\
   $f_+(23)$ & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14  & 0.22  \\
   $f_T(17)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79  & 0.46  \\
   $f_T(20)$ & --    & --   & --   & --   & --   & --   & --    & 1.00  & 0.85  \\
   $f_T(23)$ & --    & --   & --   & --   & --   & --   & --    & --    & 1.00  \\    
        \hline
    \end{tabular}
    \renewcommand{\arraystretch}{1.0}
    \caption{Reproduction of mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        vector form factors $f_{0,+,T}(q^2)$ in $B\to K$ transitions.
        \label{tab:btok-lattice}
      }
\end{table}

For $B\to K$ we have modified the prior of the nuisance parameter $f_+(0)$ of
the $f_+$ form factor parametrization w.r.t our previous analysis but kept the
slope parameter $b_1^+$ as is. This change accounts for both LCSR results
\cite{Khodjamirian:2010vf,Ball:2004ye} that use the same approach of
$B$-interpolating currents and on-shell $K$-mesons. As a result the prior on
$f_+(0)$ is wider and the tension between the SM prediction of the $B\to K
\ell\bar\ell$ branching ratio at $q^2 \in[1, 6]$~GeV$^2$~\cite{Khodjamirian:2012rm}
and the LHCb measurement \cite{Aaij:2012vr} is
reduced. Moreover, the recent lattice predictions \cite{Bouchard:2013eph} of the
form factor $f_+$ at high $q^2$ are included in our analysis as part of the
likelihood for technical reasons. For this purpose we reproduced lattice
predictions at three values
of $q^2 = 17,\, 20,\, 23$~GeV$^2$ as well as their correlation matrix based on
the parametrization given in \cite{Bouchard:2013eph}, see
\reftab{tab:btok-lattice}.  (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$). This
constraint is included in the likelihood by means of a multivariate Gaussian.

The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching
ratio of $B_s\to \bar\mu\mu$. We adopt recent updates of the $N_f = (2 + 1)$
FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}. 
More recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and
$N_f = 2$ \cite{Carrasco:2013zta} are consistent with these averages.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Standard model predictions
  \label{app:SM:predictions}
}

%--------+---------+---------+---------+---------+---------+---------+---------+
%
%  References
%
%--------+---------+---------+---------+---------+---------+---------+---------+

\bibliographystyle{apsrev4-1}
\bibliography{references.bib}

\end{document}

### 2014-12-05 tensor/draft/draft-tensor-op.tex
[tensor...draft.tex] 1) everything to be checked with EOS now in red color 2) preliminary final version of app B

@@
 \newcommand{\danny}[1]{{\color{purple}{#1}}}
-\newcommand{\christoph}[1]{{\color{red}{#1}}}
+\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
 \newcommand{\fred}[1]{{\color{green}{#1}}}
@@
   \caption{
-    The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
+    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
     \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
@@
     For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9} 
-    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).
+    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
   }
@@
   $\mbox{Re}\,\wilson{T}$
-  & $\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$
-  & $\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$
-  & $\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$
+  & \eos{$\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$}
+  & \eos{$\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$}
+  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
   \\
   $\mbox{Im}\,\wilson{T}$
-  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
-  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
-  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
+  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
+  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
+  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
   \\[0.1cm]
   $\mbox{Re}\,\wilson{T5}$
-  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
-  & $[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)
-  & $[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)
+  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
+  & \eos{$[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)}
+  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
   \\
   $\mbox{Im}\,\wilson{T5}$
-  & $[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)
-  & $[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)
-  & $[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)
+  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
+  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
+  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
   \\
@@
   $|\wilson{T}|$, $|\wilson{T5}|$
-  & $< 0.35$ ($< 0.55$)
-  & $< 0.25$ ($< 0.35$)
-  & $< 0.30$ ($< 0.45$)
+  & \eos{$< 0.35$ ($< 0.55$)}
+  & \eos{$< 0.25$ ($< 0.35$)}
+  & \eos{$< 0.30$ ($< 0.45$)}
   \\
@@
      also new physics contributions to $\wilson{9,\,10}$ with uniform prior
-     $\wilson[NP]{i} \in [-3,\, 3]$.
+     \eos{$\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-3,\, 3]$}.
   }
@@
 $\wilson{T}$ with vectorial couplings $\wilson{7,\,7',\,9,\,9'}$. 
-The according 65\% (95\%) 1D-marginalized probability intervals are listed in
+The according 68\% (95\%) 1D-marginalized probability intervals are listed in
 \reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
@@
 Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
-by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$,
+by allowing uniform priors for \eos{$\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$},
 ($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
 against destructive interference. In this case, $F_H^\mu$ by itself still provides 
-bounds $|\wilson{T,\,T5}| < 0.5\,(0.8)$ at 68\% (95\%) probability that are
+bounds \eos{$|\wilson{T,\,T5}| < 0.5\,(0.8)$} at 68\% (95\%) probability that are
 weakened by a factor of two since $F_H^\mu$ does not pose constraints on
@@
 3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ 
-by a factor of two.
+by a \eos{factor of two}.
 
@@
 scalar with tensorial couplings. Quantitatively, the constraint from $\overline{\cal B}
-(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor five
+(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor five}
 stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
@@
   \caption{
+    \eos{
     Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
@@
     [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
+    }
   }
@@
   & $\quad$ $-$ $\quad$
-  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
-  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
   \\
@@
   & $\quad$ $-$ $\quad$
-  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
-  & $\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
   \\[0.1cm]
   $\mbox{Re}(\wilson{S} + \wilson{S'})$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   & $-$
-  & $[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)
+  & \eos{$[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)}
   \\
   $\mbox{Im}(\wilson{S} + \wilson{S'})$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   & $-$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   \\[0.1cm]
@@
   & $-$
-  & $[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)
-  & $[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)
+  & \eos{$[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)}
+  & \eos{$[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)}
   \\
@@
   & $-$
-  & $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)
-  & $[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)
+  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
+  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
   \\[0.1cm]
   $\mbox{Re}(\wilson{P} + \wilson{P'})$
-  & $[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)
+  & \eos{$[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)}
   & $-$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   \\
   $\mbox{Im}(\wilson{P} + \wilson{P'})$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   & $-$
-  & $[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
   \\
@@
      \reftab{tab:observables} allowing also for new physics contributions to 
-     $\wilson{10,\,10'}$ with uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
-     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$.
+     $\wilson{10,\,10'}$ with \eos{uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
+     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$}.
   }
@@
 \begin{enumerate}
-\item imposes by itself constraints on tensorial couplings $|{\cal C}_{T,\,T5}^\mu|
-  < 0.35\, (0.55)$ at 68\% (95\%) probability, superseding previous bounds.
+\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}^\mu|
+  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
   In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
-  (0.45)$, even in the presence of non-standard contributions in vectorial
+  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\, 
+  (0.45)$}, even in the presence of non-standard contributions in vectorial
   couplings.
@@
   Even when taking into account destructive interference with vectorial couplings
-  $|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
-  0.1\, (0.2)$ for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
+  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
+  0.1\, (0.2)$} for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
   strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
@@
 \end{enumerate}
-In all cases these constraints are weakened only slightly in the presence of
+In all cases these \eos{constraints are weakened only slightly} in the presence of
 new physics in vectorial couplings from destructive interference.
@@
 
+Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
+the compilation of nuisance parameters and according values, whose uncertainties
+are negligible. Further, we 
+adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
+matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
+and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
+given in \cite{Beaujean:2013soa}.
+
 The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ depend on 
@@
 
-Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
-the compilation of nuisance parameters and according values, whose uncertainties
-are negligible. \todo{Check for updated values for $y_s$ of $B_s$?} Further, we 
-adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
-matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
-and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
-given in \cite{Beaujean:2013soa}.
-
 \begin{table}
@@
 
-The most important change in the treatment of $B\to K$ form factors is the consistent
-use of correlations available from lattice \cite{Bouchard:2013eph} for all three form
-factors  $f_{+,T,0}$ in the construction of their prior. We use the $z$-parameterization
-\cite{Khodjamirian:2010vf}, such that only five nuisance parameters --- see
-\reftab{tab:hadronic:nuisance} --- arise due to the kinematical relation 
-$f_0(0) = f_+(0)$.
+As we do not make use of form factor relations for tensorial and scalar amplitudes
+in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
+set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the 
+$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters 
+(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematical relation 
+$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
+are adopted and supplemented with lattice determinations \cite{Bouchard:2013eph}.
+The lattice results are given within a slightly different parameterisation necessitating
+a conversion to the parameterisation used here. For this purpose, we generate the
+form factors from the parameterisation \cite{Bouchard:2013eph}, including full
+correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
+compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
+such that the correlation of neighboring points does not exceed $80\%$.)
+Subsequently, these ``data'' of the form factors is included in the likelihood
+by means of a multivariate Gaussian in addition to experimental measurements.
 
@@
 
-For $B\to K$ we have modified the prior of the nuisance parameter $f_+(0)$ of
-the $f_+$ form factor parametrization w.r.t our previous analysis but kept the
-slope parameter $b_1^+$ as is. This change accounts for both LCSR results
-\cite{Khodjamirian:2010vf,Ball:2004ye} that use the same approach of
-$B$-interpolating currents and on-shell $K$-mesons. As a result the prior on
-$f_+(0)$ is wider and the tension between the SM prediction of the $B\to K
-\ell\bar\ell$ branching ratio at $q^2 \in[1, 6]$~GeV$^2$~\cite{Khodjamirian:2012rm}
-and the LHCb measurement \cite{Aaij:2012vr} is
-reduced. Moreover, the recent lattice predictions \cite{Bouchard:2013eph} of the
-form factor $f_+$ at high $q^2$ are included in our analysis as part of the
-likelihood for technical reasons. For this purpose we reproduced lattice
-predictions at three values
-of $q^2 = 17,\, 20,\, 23$~GeV$^2$ as well as their correlation matrix based on
-the parametrization given in \cite{Bouchard:2013eph}, see
-\reftab{tab:btok-lattice}.  (The $q^2$ values and number of points are chosen
-such that the correlation of neighboring points does not exceed $80\%$). This
-constraint is included in the likelihood by means of a multivariate Gaussian.
-
 The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching

### 2014-12-08 plot/samplingOutput.py
(wip) transfer to laptop

@@ -7,8 +7,7 @@ import priors as priorDistributions
 
 import h5py
 import numpy as np
-import os
-import sys
+import os, sys
 
 # todo rename to description
 class ParameterDefinition(object):
@@ -938,13 +937,16 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         #adjust which range is drawn, default: full range
         if self.skip_initial > 0:
             self.select[0] = int(self.skip_initial * full_length)
+        if self.select[0] is None:
+            self.select[0] = 0
         if self.select[1] is None:
-            self.select[1] = full_length - 1
+            self.select[1] = full_length
 
-        reduced_length = self.select[1] - self.select[0]
+        print(self.select[1], self.select[0])
+        self.reduced_length = self.select[1] - self.select[0]
 
-        merged_chains = np.empty((len(chains) * reduced_length, chain.shape[1]), dtype='float64')
-        merged_chains[:reduced_length] = hdf5_file[prefix + '/chain #' + first_chain][self.select[0]:self.select[1]]
+        merged_chains = np.empty((len(chains) * self.reduced_length, chain.shape[1]), dtype='float64')
+        merged_chains[:self.reduced_length] = hdf5_file[prefix + '/chain #' + first_chain][self.select[0]:self.select[1]]
         n_chains_parsed = 1
 
         par_defs, priors = read_descriptions(hdf5_file,
@@ -956,7 +958,7 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         for chain in chains[1:]:
             c = hdf5_file[prefix + '/chain #%d' % chain]
             assert len(c) == full_length, 'Length of chain %d (%d) differs from length of chain %s (%d)' % (chain, len(c), first_chain, full_length)
-            merged_chains[n_chains_parsed * reduced_length:(n_chains_parsed + 1) * reduced_length] = c[self.select[0]:self.select[1]]
+            merged_chains[n_chains_parsed * self.reduced_length:(n_chains_parsed + 1) * self.reduced_length] = c[self.select[0]:self.select[1]]
             n_chains_parsed += 1
 
         hdf5_file.close()
@@ -970,3 +972,7 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         self.samples = merged_chains
         self.par_defs = par_defs
         self.priors = priors
+
+    def individual_chains(self):
+        '''Return list of individual chains.'''
+        return [self.samples[i * self.reduced_length:(i+1) * self.reduced_length] for i in range(len(self.samples) // self.reduced_length)]

### 2014-12-09 py-eos/vb.py
[py-eos] add missing vb.py

@@ -1,0 +1,102 @@
+#! /usr/bin/env python
+
+"""Provide an interface to variational Bayes with pypmc"""
+from __future__ import print_function, division
+
+import eos
+from make_analysis import make_analysis
+from pypmc.mix_adapt.r_value import make_r_gaussmix
+from pypmc.mix_adapt.variational import GaussianInference
+
+import argparse
+import h5py
+import numpy as np
+import os, sys
+
+sys.path.append(os.path.realpath('../plot'))
+import samplingOutput
+
+def read_chains(file_name, **kwargs):
+    '''Read mcmc chains and return a list of arrays'''
+    output = samplingOutput.EOS_PYPMC_MCMC(file_name, **kwargs)
+
+    # TODO check if analysis agrees
+
+    # number of chains
+#     assert len(output.samples) % output.reduced_length == 0, "chains not of same size"
+#     K = len(output.samples // output.reduced_length)
+    chains = output.individual_chains()
+    print(len(chains))
+    print(len(chains[0]))
+    return chains
+
+class VB(object):
+    def __init__(self, analysis, args):
+        self.analysis = analysis
+        output = samplingOutput.EOS_PYPMC_MCMC(args.mcmc_input,
+                                               chains=args.chains,
+                                               skip_initial=args.skip_initial)
+
+        print("R value grouping")
+        long_patches = make_r_gaussmix(output.individual_chains(),
+                                       K_g=args.components_per_group,
+                                       indices=self.indices(args))
+
+        self.vb = GaussianInference(output.samples, initial_guess=long_patches, W0=np.diag([1e20] * len(analysis.priors)))
+
+    def indices(self, args):
+        '''Indices of parameters to compute R value for'''
+        if args.indices:
+            indices = args.indices
+        elif args.group_nuisance:
+            # all parameters
+            indices = list(range(len(self.analysis.priors)))
+        else:
+            # find non-nuisance parameters
+            indices = []
+            for i, p in enumerate(self.analysis.priors):
+                if not p.nuisance:
+                    indices.append(i)
+
+        print('R group parameter indices', indices)
+        return indices
+
+    def run(self):
+        self.vb.run(verbose=True)
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description="Run MCMC on EOS analysis from python")
+    parser.add_argument("--analysis-from",
+                        help="Specify where the `eos.Analysis` instance shall be read off. " \
+                        "Either specify a python module (for example `module.analysis`) or `env` " \
[…]

### 2014-12-11 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added figures for the SM-EFT scenario

@@
 \cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
-test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$ \cite{Bobeth:2012vn}.
+test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.
 
@@
     and their combination with other data in \reftab{tab:observables} as well as
-    $\wilson{10} \in [-1,\, 9]$, $\wilson{10'} \in [-5,\,5]$ (red) 
+    $\wilson[NP]{10} \in [-1,\, 9]$, $\wilson[NP]{10'} \in [-5,\,5]$ (red) 
     at 68\% (darker) and 95\% (lighter) probability. The constraints on 
@@
 
+\begin{figure*}
+  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
+  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
+  \caption{
+    \eos{
+    Constraints on real-valued [left] and complex-valued [right] scalar couplings 
+    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to 
+    \bar\mu\mu)$ (blue) and 
+    all data in \reftab{tab:observables} (green) marginalising over non-zero 
+    $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
+    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$, 
+    or all data but $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
+    at 68\% (darker) and 95\% (lighter) probability. 
+    }
+  }
+  \label{fig:scalar:SM-EFT}
+\end{figure*}
+
 %
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\section{
-  Standard model predictions
-  \label{app:SM:predictions}
-}
+%\section{
+%  Standard model predictions
+%  \label{app:SM:predictions}
+%}
 

### 2014-12-12 plot/samplingOutput.py
[samplingOutput] change EOS_MCMC output, start IS reading

@@ -907,6 +907,10 @@ class UncertaintyPropagation(IS_Output):
 
         hdf5_file.close()
 
+class EOS_PYPMC_IS(SamplingOutput):
+    def _read(self, *args, **kwargs):
+        pass
+
 class EOS_PYPMC_MCMC(SamplingOutput):
 
     def _read(self, *args, **kwargs):
@@ -942,7 +946,6 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         if self.select[1] is None:
             self.select[1] = full_length
 
-        print(self.select[1], self.select[0])
         self.reduced_length = self.select[1] - self.select[0]
 
         merged_chains = np.empty((len(chains) * self.reduced_length, chain.shape[1]), dtype='float64')
@@ -962,6 +965,8 @@ class EOS_PYPMC_MCMC(SamplingOutput):
             n_chains_parsed += 1
 
         hdf5_file.close()
+
+        print('Merged %d chains, total number of samples: %d' % (n_chains_parsed, len(merged_chains)))
 
         ###
         # assign members

### 2014-12-12 py-eos/hdf5_io.py
[py-eos] add hdf5_io to bundle io to hdf5
o cut analysis io from mcmc.py

@@ -1,0 +1,128 @@
+'''Input/output to HDF5'''
+
+import pypmc
+import h5py
+import numpy as np
+import os
+
+def save_analysis(file, analysis, intermediate=''):
+    """Store analysis in human-readable format in hdf5 file.
+
+    ``intermediate`` is a string to distinguish such as ``chain #1``
+     if multiple chains are to be stored. A separate group
+     ``/descriptions/$intermediate`` will be created.
+
+    Example:
+    $ h5ls -r file.hdf5
+    /                        Group
+    /descriptions            Group
+    /descriptions/constraints Dataset {3}
+    /descriptions/parameters Dataset {15}
+
+    $ h5ls -d file.hdf5/descriptions/constraints
+    constraints              Dataset {3}
+    Data:
+        (0) "B->K::f_0+f_++f_T@HPQCD-2013A",
+
+    $ h5ls -d file.hdf5/descriptions/parameters
+    parameters               Dataset {15}
+    Data:
+        (0) "Parameter: Re{cT}, prior type: flat, range: [-1,1], value = 0.981878",
+
+    """
+
+    desc  = 'descriptions'
+    const = 'constraints'
+    param = 'parameters'
+
+    group = file.create_group(desc)
+    if intermediate:
+        group = file[desc].create_group(intermediate)
+
+    # variable-length ASCII string
+    dt = h5py.special_dtype(vlen=bytes)
+    ds_const = group.create_dataset(const, (len(analysis.constraints),), dtype=dt)
+    dt = np.dtype({'names': ['name', 'min', 'max', 'nuisance', 'info'],
+                   'formats': [dt, np.float64, np.float64, np.uint8, dt]})
+    ds_param = group.create_dataset(param, (len(analysis.priors),), dtype=dt)
+
+    for i, c in enumerate(analysis.constraints):
+        ds_const[i] = c.name
+
+    ana_str = repr(analysis)
+
+    # index where a line with parameter info starts
+    line_start = ana_str.find('Parameter: ')
+    i = 0
+    while line_start != -1:
+        end = ana_str.find(', value = ', line_start)
+        line = ana_str[line_start:end]
+        p = analysis.priors[i]
+        ds_param[i] = (p.name, p.range_min, p.range_max, p.nuisance, line)
+        i += 1
+        # search forward in next line
+        line_start = ana_str.find('Parameter: ', end)
+
+    assert i == len(analysis.priors)
+
+def save_mixture(file, directory, mixture):
+    '''Support Gauss and Students't mixtures'''
[…]

### 2014-12-12 py-eos/mcmc.py

@@ -6,70 +6,11 @@ from __future__ import print_function, division
 import eos
 from make_analysis import make_analysis
 import pypmc
+import hdf5_io
 
 import argparse
 import h5py
 import numpy as np
-
-def save_analysis(file, analysis, intermediate=''):
-    """Store analysis in human-readable format in hdf5 file.
-
-    ``intermediate`` is a string to distinguish such as ``chain #1``
-     if multiple chains are to be stored. A separate group
-     ``/descriptions/$intermediate`` will be created.
-
-    Example:
-    $ h5ls -r file.hdf5
-    /                        Group
-    /descriptions            Group
-    /descriptions/constraints Dataset {3}
-    /descriptions/parameters Dataset {15}
-
-    $ h5ls -d file.hdf5/descriptions/constraints
-    constraints              Dataset {3}
-    Data:
-        (0) "B->K::f_0+f_++f_T@HPQCD-2013A",
-
-    $ h5ls -d file.hdf5/descriptions/parameters
-    parameters               Dataset {15}
-    Data:
-        (0) "Parameter: Re{cT}, prior type: flat, range: [-1,1], value = 0.981878",
-
-    """
-
-    desc  = 'descriptions'
-    const = 'constraints'
-    param = 'parameters'
-
-    group = file.create_group(desc)
-    if intermediate:
-        group = file[desc].create_group(intermediate)
-
-    # variable-length ASCII string
-    dt = h5py.special_dtype(vlen=bytes)
-    ds_const = group.create_dataset(const, (len(analysis.constraints),), dtype=dt)
-    dt = np.dtype({'names': ['name', 'min', 'max', 'nuisance', 'info'],
-                   'formats': [dt, np.float64, np.float64, np.uint8, dt]})
-    ds_param = group.create_dataset(param, (len(analysis.priors),), dtype=dt)
-
-    for i, c in enumerate(analysis.constraints):
-        ds_const[i] = c.name
-
-    ana_str = repr(analysis)
-
-    # index where a line with parameter info starts
-    line_start = ana_str.find('Parameter: ')
-    i = 0
-    while line_start != -1:
-        end = ana_str.find(', value = ', line_start)
-        line = ana_str[line_start:end]
-        p = analysis.priors[i]
-        ds_param[i] = (p.name, p.range_min, p.range_max, p.nuisance, line)
-        i += 1
-        # search forward in next line
-        line_start = ana_str.find('Parameter: ', end)
-
[…]

### 2014-12-12 py-eos/is.py
[py-eos] Add importance sampling with mpi

@@ -1,0 +1,90 @@
+#! /usr/bin/env python
+
+"""Provide an interface to variational Bayes with pypmc"""
+from __future__ import print_function, division
+
+import eos
+import hdf5_io
+
+import vb
+from make_analysis import make_analysis
+import pypmc
+from pypmc.mix_adapt.r_value import make_r_gaussmix
+from pypmc.mix_adapt.variational import GaussianInference
+from pypmc.tools import plot_mixture
+from pypmc.tools.parallel_sampler import MPISampler
+
+import argparse
+import h5py
+import numpy as np
+import os, sys
+
+from mpi4py.MPI import COMM_WORLD
+rank = COMM_WORLD.Get_rank()
+master = (rank == 0)
+
+hdf5_directory = '/importance_samples'
+
+class IS(object):
+    def __init__(self, analysis, args):
+        self.analysis = analysis
+        self.dim = len(analysis.priors)
+
+        # make sure that every process has a different random number generator seed
+        np.random.seed(args.seed + rank)
+
+        # parse mixture
+        mixture = hdf5_io.read_mixture(args.input, vb.hdf5_directory)
+#         from matplotlib import pyplot
+#         plot_mixture(mixture)
+#         pyplot.show()
+#
+#         hyper = hdf5_io.read_vb_hyperparameters(args.input, vb.hdf5_directory)
+#         print(hyper['m'])
+
+        # same number of n_samples in each process
+        self.n_samples = args.samples // COMM_WORLD.Get_size()
+
+        # define the importance sampler
+        SequentialIS = pypmc.sampler.importance_sampling.DeterministicIS
+        self.parallel_sampler = MPISampler(SequentialIS, target=analysis, proposal=mixture, prealloc=self.n_samples)
+
+    def run(self):
+        self.parallel_sampler.run(self.n_samples)
+        if master:
+            hdf5_io.save_is_samples(args.output, args.primary_group + hdf5_directory, self.parallel_sampler.history_list)
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description="Run MCMC on EOS analysis from python")
+    parser.add_argument("--analysis-from",
+                        help="Specify where the `eos.Analysis` instance shall be read off. " \
+                        "Either specify a python module (for example `module.analysis`) or `env` " \
+                        "[default] for reading off the environement variables.",
+                        type=str, default='env')
+    parser.add_argument("--analysis-info", help='Print constraints, parameters, and observables',
+                        type=int, default=False)
[…]

### 2014-12-14 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] cleaned up scalar operator section, comparing with lit, other small changes

@@
 
-Important additional constraints on scalar couplings come from
-the branching ratio of $B_s \to \bar\mu\mu$ as given in \refeq{eq:Br-Bsmumu}.
-It provides the most stringent constraints on the moduli $|\wilson{S} - \wilson{S'}|$
+Important additional constraints on scalar couplings come from the branching
+ratio of $B_s \to \bar\mu\mu$ as given in \refeq{eq:Br-Bsmumu}. It provides
+the most stringent constraints on the moduli $|\wilson{S} - \wilson{S'}|$
 and $|\wilson{P} - \wilson{P'}|$ that are complementary to \refeq{eq:FH-dependence}
@@
 
-We will also make use of the branching ratio of $B\to K^* \bar\mu\mu$ as it
-allows us to $\ldots$
-\todo{$A_{\rm CP}$ included.}
-
-\todo{Find a place to cite \cite{Becirevic:2012fy}, perhaps in section on results
-comparing our bounds to theirs in eq.(49): $|\wilson{S,\,S'}|Ê\lesssim 0.7$ and
-$|\wilson{P,\,P'}|Ê\lesssim 1.0$ - what about \cite{Altmannshofer:2012az}
-and \cite{Hurth:2012jn, Hurth:2013ssa} (this is only MFV, i.e. only one operator)?}.
+Eventually we also explore the behaviour of derived constraints with respect
+to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
+this purpose we include also the branching ratio and the rate CP asymmetry
+of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
+of vectorial couplings.
 
 In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
-kinematically suppressed terms in observables, neither in the prediction of
-yet not measured observables. The experimental input of these observables is 
-listed in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
-form factors. More details on the latter can be found in \refapp{app:theory:inputs}.
+kinematically suppressed terms in predictions of measured observables as well
+as when predicting not yet measured observables. The experimental input of these
+observables is listed in \reftab{tab:observables} together with input for the 
+$B\to K^{(*)}$ form factors. More details on the latter can be found in 
+\refapp{app:theory:inputs}.
 
@@
 of \reffig{fig:scalar} would turn into a filled circle.
+
+Our results improve and extend previous constraints in the literature to
+the most general case of complex-valued couplings. For example they are
+a factor \eos{two to three} more stringent then \cite{Becirevic:2012fy} and
+\eos{comparable} to \cite{Altmannshofer:2012az} once restricting to scenarios
+considered there.
 
@@
 for the most general case of complex-valued couplings destructive interference
-constrains (4 parameters)
+constrains (4 parameters) \todo{finish, describe \reffig{fig:scalar:SM-EFT}}
 
@@
     $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to 
-    \bar\mu\mu)$ (blue) and 
-    all data in \reftab{tab:observables} (green) marginalising over non-zero 
-    $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
-    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$, 
-    or all data but $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
+    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green) 
+    at 68\% (darker) and 95\% (lighter) probability when marginalising
+    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
+    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
+    For comparison the according constraints from all data when keeping
+    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
     at 68\% (darker) and 95\% (lighter) probability. 
@@
 
+\begin{table*}
+  \renewcommand{\arraystretch}{1.3}
+  %\resizebox{\textwidth}{!}{
+  \begin{tabular}{cc|cc}
+  \hline
+    observable
+  & $q^2$-bin [GeV$^2$]
+  & SM
+  & NP
+  \\
+  \hline \hline
+  \multirow{2}{*}{$J_{6c}$}
+  & $[1.1,\, 6]$
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  & $[15,\, 19]$
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  \hline
+  \multirow{2}{*}{$J_{1c} + J_{2c}$}
+  & $[1.1,\, 6]$
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  & $[15,\, 19]$
+  & $[ ,\, ]$ ($[ ,\, ]$) 
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  \hline
+  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
+  & $[1.1,\, 6]$
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  & $[15,\, 19]$
+  & $[ ,\, ]$ ($[ ,\, ]$) 
+  & $[ ,\, ]$ ($[ ,\, ]$)
+  \\
+  \hline 
+  \end{tabular}
+%}
+  \renewcommand{\arraystretch}{1.0}
+  \caption{
+     \label{tab:predictions}
+     \todo{predictions for $B\to K^*\bar\ell\ell$}
+  }
+\end{table*}
+
 %
@@
   \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
-  0.1\, (0.2)$} for $i = S,P$. Currently, the bounds from $F_H^\mu$ are not as
-  strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by a factor four.
-  Future measurements at LHCb and Belle II might change this, especially for 
-  $\ell = e$. 
+  0.1\, (0.2)$} for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds 
+  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
+  by a factor four. In the future, measurements at LHCb and Belle II will 
+  further tighten the bounds. Moreover, measurements of $F_H^e$ ($\ell = e$)
+  will provide constraints on scalar couplings in the electron channel in
+  the lack of measurements of $B_s \to \bar{e}e$. 
 \item SM-EFT $\ldots$

### 2014-12-16 py-eos/vb.py
[py-eos, tensor] Add --init-method to choose between random and ... for vb

@@ -14,6 +14,7 @@ import argparse
 import h5py
 import numpy as np
 import os, sys
+from argparse import ArgumentError
 
 sys.path.append(os.path.realpath('../plot'))
 import samplingOutput
@@ -41,7 +42,7 @@ class VB(object):
         elif args.is_input:
             self.init_is(args)
         else:
-            raise KeyError('No input file specified')
+            raise ArgumentError('No input file specified')
 
     def init_is(self, args):
         pass
@@ -63,8 +64,17 @@ class VB(object):
             samples = output.samples[::args.thin]
         else:
             samples = output.samples
-        self.vb = GaussianInference(samples, initial_guess='random', components=len(long_patches),
-                                    W0=np.diag([1e20] * len(analysis.priors)))
+
+
+        if args.init_method == 'random':
+            initial_guess = args.init_method
+        elif args.init_method == 'long-patches':
+            initial_guess = long_patches
+        else:
+            raise ArgumentError('Invalid initialization method: "%s"' % args.init_method)
+
+        self.vb = GaussianInference(samples, initial_guess=initial_guess, components=len(long_patches),
+                                    W0=np.diag([1e20] * len(self.analysis.priors)))
 
     def indices(self, args):
         '''Indices of parameters to compute R value for'''
@@ -105,6 +115,7 @@ if __name__ == '__main__':
                         type=int, default=0)
     parser.add_argument('--indices', help="Use only the specified parameters for R value grouping. Example: --indices 0 2 5",
                         type=int, nargs='+', metavar=('index0', 'index1'))
+    parser.add_argument("--init-method", help="Method to initialize variational Bayes", const='random', nargs='?')
     parser.add_argument("--is-input", help='File name that has the input from importance sampling', const='', nargs='?')
     parser.add_argument("--mcmc-input", help='File name that has the Markov chains', const='', nargs='?')
     parser.add_argument("--output", help="Output file name")

### 2014-12-16 plot/plotScript.py
(wip) vb->is->vb chain almost finished

@@ -1666,6 +1666,8 @@ def factory(cmd_line=None):
     else:
         if args.i.endswith('.npy'):
             OutputClass = JahnISOutput
+        elif args.pypmc:
+            OutputClass = EOS_PYPMC_IS
         else:
             OutputClass = PMC_Output
 

### 2014-12-16 plot/samplingOutput.py

@@ -7,7 +7,7 @@ import priors as priorDistributions
 
 import h5py
 import numpy as np
-import os, sys
+import os, re, sys
 
 # todo rename to description
 class ParameterDefinition(object):
@@ -909,7 +909,46 @@ class UncertaintyPropagation(IS_Output):
 
 class EOS_PYPMC_IS(SamplingOutput):
     def _read(self, *args, **kwargs):
-        pass
+        self.crop_outliers = kwargs.get('crop_outliers', 0)
+        self.equal_weights = kwargs.get('equal_weights', False)
+        self.step = kwargs.get('step', None)
+
+        with h5py.File(self.input_file_name, 'r') as hdf5_file:
+            prefix = '/importance_samples'
+            if self.step is not None:
+                prefix = '/step_%d' % self.step + prefix
+            else:
+                # find last step
+                groups = list(hdf5_file['/'].keys())
+                steps = sorted(filter(lambda x:re.search(r'^step', x), groups))
+                if steps:
+                    prefix = steps[-1] + prefix
+                # or don't update prefix if no group name step_* exists
+
+            samples = hdf5_file[prefix + '/samples'][self.select[0]:self.select[1]]
+
+            if self.equal_weights:
+                weights = np.ones(len(samples))
+            else:
+                weights = hdf5_file[prefix + '/weights'][self.select[0]:self.select[1]]
+
+            print(weights)
+
+            if self.crop_outliers > 0:
+                crop(weights, self.crop_outliers)
+
+            par_defs, priors = read_descriptions(hdf5_file,
+                                                 data_set='/descriptions/parameters',
+                                                 npar=len(samples[0]),
+                                                 samples=samples)
+
+        # assign members
+        self.weights = weights
+        self.samples = samples
+        self.par_defs = par_defs
+        self.priors = priors
+        self.stats = None
+        self.components = None
 
 class EOS_PYPMC_MCMC(SamplingOutput):
 
@@ -922,49 +961,47 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         if hasattr(self.chains, '__len__') and len(self.chains) == 1:
             self.single_chain = str(self.chains[0])
 
-        hdf5_file = h5py.File(self.input_file_name, 'r')
+        with h5py.File(self.input_file_name, 'r') as hdf5_file:
 
-        prefix = '/samples'
+            prefix = '/samples'
 
-        # select all chains
-        if self.chains:
-            chains = self.chains
-        else:
-            chains = range(len(list(hdf5_file[prefix])))
[…]

### 2014-12-16 py-eos/hdf5_io.py

@@ -5,12 +5,8 @@ import h5py
 import numpy as np
 import os
 
-def save_analysis(file, analysis, intermediate=''):
+def save_analysis(file, directory, analysis):
     """Store analysis in human-readable format in hdf5 file.
-
-    ``intermediate`` is a string to distinguish such as ``chain #1``
-     if multiple chains are to be stored. A separate group
-     ``/descriptions/$intermediate`` will be created.
 
     Example:
     $ h5ls -r file.hdf5
@@ -35,35 +31,38 @@ def save_analysis(file, analysis, intermediate=''):
     const = 'constraints'
     param = 'parameters'
 
-    group = file.create_group(desc)
-    if intermediate:
-        group = file[desc].create_group(intermediate)
+    print('save_analysis', file)
+    with h5py.File(file, 'a') as file:
+        if desc in file[directory]:
+            return
 
-    # variable-length ASCII string
-    dt = h5py.special_dtype(vlen=bytes)
-    ds_const = group.create_dataset(const, (len(analysis.constraints),), dtype=dt)
-    dt = np.dtype({'names': ['name', 'min', 'max', 'nuisance', 'info'],
-                   'formats': [dt, np.float64, np.float64, np.uint8, dt]})
-    ds_param = group.create_dataset(param, (len(analysis.priors),), dtype=dt)
+        group = file[directory].create_group(desc)
 
-    for i, c in enumerate(analysis.constraints):
-        ds_const[i] = c.name
+        # variable-length ASCII string
+        dt = h5py.special_dtype(vlen=bytes)
+        ds_const = group.create_dataset(const, (len(analysis.constraints),), dtype=dt)
+        dt = np.dtype({'names': ['name', 'min', 'max', 'nuisance', 'info'],
+                       'formats': [dt, np.float64, np.float64, np.uint8, dt]})
+        ds_param = group.create_dataset(param, (len(analysis.priors),), dtype=dt)
 
-    ana_str = repr(analysis)
+        for i, c in enumerate(analysis.constraints):
+            ds_const[i] = c.name
 
-    # index where a line with parameter info starts
-    line_start = ana_str.find('Parameter: ')
-    i = 0
-    while line_start != -1:
-        end = ana_str.find(', value = ', line_start)
-        line = ana_str[line_start:end]
-        p = analysis.priors[i]
-        ds_param[i] = (p.name, p.range_min, p.range_max, p.nuisance, line)
-        i += 1
-        # search forward in next line
[…]

### 2014-12-16 py-eos/is.py

@@ -23,7 +23,7 @@ from mpi4py.MPI import COMM_WORLD
 rank = COMM_WORLD.Get_rank()
 master = (rank == 0)
 
-hdf5_directory = '/importance_samples'
+hdf5_subdirectory = '/importance_samples'
 
 class IS(object):
     def __init__(self, analysis, args):
@@ -34,13 +34,12 @@ class IS(object):
         np.random.seed(args.seed + rank)
 
         # parse mixture
-        mixture = hdf5_io.read_mixture(args.input, vb.hdf5_directory)
+        mixture = hdf5_io.read_mixture(args.input, args.primary_group + vb.hdf5_subdirectory)
 #         from matplotlib import pyplot
 #         plot_mixture(mixture)
 #         pyplot.show()
 #
-#         hyper = hdf5_io.read_vb_hyperparameters(args.input, vb.hdf5_directory)
-#         print(hyper['m'])
+        hyper = hdf5_io.read_vb_hyperparameters(args.input, args.primary_group + vb.hdf5_subdirectory)
 
         # same number of n_samples in each process
         self.n_samples = args.samples // COMM_WORLD.Get_size()
@@ -49,10 +48,12 @@ class IS(object):
         SequentialIS = pypmc.sampler.importance_sampling.DeterministicIS
         self.parallel_sampler = MPISampler(SequentialIS, target=analysis, proposal=mixture, prealloc=self.n_samples)
 
+        hdf5_io.save_analysis(args.output, '/', self.analysis)
+
     def run(self):
         self.parallel_sampler.run(self.n_samples)
         if master:
-            hdf5_io.save_is_samples(args.output, args.primary_group + hdf5_directory, self.parallel_sampler.history_list)
+            hdf5_io.save_is_samples(args.output, args.primary_group + hdf5_subdirectory, self.parallel_sampler.history_list)
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(description="Run MCMC on EOS analysis from python")
@@ -68,7 +69,7 @@ if __name__ == '__main__':
     parser.add_argument("--samples", type=int,
                         help='Total number of importance n_samples; i.e. for the combination of all processes')
     parser.add_argument("--seed", type=int)
-    parser.add_argument("--step", type=int, default=None)
+    parser.add_argument("--step", type=int, default=None, const=None, nargs='?')
 
     args = parser.parse_args()
 
@@ -81,7 +82,7 @@ if __name__ == '__main__':
     if args.step is None:
[…]

### 2014-12-16 py-eos/mcmc.py

@@ -63,7 +63,7 @@ class MCMC_Sampler(object):
         self.sample_dset = '/samples/chain #0'
         file.create_dataset(self.sample_dset, (self.samples, self.dim), 'float64')
 
-        hdf5_io.save_analysis(file, self.analysis, intermediate='chain #0')
+        hdf5_io.save_analysis(file, self.analysis)
         file.close()
 
     def draw_uniform_in_support(self):

### 2014-12-16 py-eos/vb.py

@@ -19,7 +19,7 @@ from argparse import ArgumentError
 sys.path.append(os.path.realpath('../plot'))
 import samplingOutput
 
-hdf5_directory = '/vb'
+hdf5_subdirectory = '/vb'
 
 def read_chains(file_name, **kwargs):
     '''Read mcmc chains and return a list of arrays'''
@@ -44,10 +44,41 @@ class VB(object):
         else:
             raise ArgumentError('No input file specified')
 
+        if args.prune:
+            self.prune = float(args.prune)
+        else:
+            # Stephan's rule of thumb, reduce components agressively
+            self.prune = 0.5 * self.vb.N / self.vb.K
+
+        hdf5_io.save_analysis(args.output, '/', self.analysis)
+
     def init_is(self, args):
-        pass
+        # parse samples and weights
+        output = samplingOutput.EOS_PYPMC_IS(args.is_input, args.step)
+
+        # use MCMC results as prior
+        hyperpar = hdf5_io.read_vb_hyperparameters(args.is_input, args.primary_group + hdf5_subdirectory)
+        hyperpar_prior = self.posterior2prior(hyperpar)
+
+        # but ignore weights from MCMC
+        if args.step == 0:
+            hyperpar_prior['alpha0'][:] = 1e-5
+
+        # now combine both dicts
+        hyperpar.update(hyperpar_prior)
+
+        initial_guess = hdf5_io.read_mixture(args.is_input, args.primary_group + hdf5_subdirectory)
+
+        self.vb = GaussianInference(output.samples, components=len(hyperpar['alpha']), **hyperpar)
+
+    def posterior2prior(self, hyperpar):
+        '''Convert posterior hyperparameter values into priors.
+        Important to make independent copies so values can be changed inside GaussianInference.'''
+        return dict(alpha0=hyperpar['alpha'].copy(), beta0=hyperpar['beta'].copy(), m0=hyperpar['m'].copy(),
+                    nu0=hyperpar['nu'].copy(), W0=hyperpar['W'].copy())
 
     def init_mcmc(self, args):
+        print(args.mcmc_input)
         output = samplingOutput.EOS_PYPMC_MCMC(args.mcmc_input,
                                                chains=args.chains,
                                                skip_initial=args.skip_initial)
@@ -56,7 +87,7 @@ class VB(object):
         long_patches = make_r_gaussmix(output.individual_chains(),
                                        K_g=K_g, critical_r=args.R_value,
[…]

### 2015-01-13 tensor/draft/draft-tensor-op.tex
[tensor/draft] add hyperref, fix plot file names

@@
-% vim: set sts=4 et :
 \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{listings}
 \usepackage{multirow}
-\usepackage{listings}
 \usepackage{xcolor}
@@
 \begin{figure*}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_CT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_CT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_CT.pdf}
+  \includegraphics[width=.24\textwidth]{plots/pdf/FH_1_6_vs_cT}
+  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
+  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
   \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
 \\
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_CT.pdf}
+  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
   \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_CT.pdf}
+  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
   \caption{

### 2015-01-13 tensor/draft/draft-tensor-op.tex
[tensor/draft] fix another file-name error, add comment

@@
 \begin{figure*}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH_1_6_vs_cT}
+  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT}
   \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
@@
 to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
-this purpose we include also the branching ratio and the rate CP asymmetry
+this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
 of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli

### 2015-01-13 py-eos/vb.py
[py-eos/vb] change default step to 0

@@ -162,7 +162,7 @@ if __name__ == '__main__':
     parser.add_argument('--skip-initial', help="Allows to skip the first fraction of iterations", type=float, default=0.0)
     parser.add_argument('--thin', help='Select only every N-th sample from the chains to reduce autocorrelation',
                         type=int, default=0)
-    parser.add_argument("--step", type=int, default=1, help='Select a step: used to identify input/output')
+    parser.add_argument("--step", type=int, default=0, help='Select a step: used to identify input/output')
 
     args = parser.parse_args()
 

### 2015-01-13 py-eos/is.py
[py-eos/is] Switch from DeterministicIS to Regular IS

@@ -38,14 +38,15 @@ class IS(object):
 #         from matplotlib import pyplot
 #         plot_mixture(mixture)
 #         pyplot.show()
-#
-        hyper = hdf5_io.read_vb_hyperparameters(args.input, args.primary_group + vb.hdf5_subdirectory)
+
+        # todo why used here?
+#         hyper = hdf5_io.read_vb_hyperparameters(args.input, args.primary_group + vb.hdf5_subdirectory)
 
         # same number of n_samples in each process
         self.n_samples = args.samples // COMM_WORLD.Get_size()
 
         # define the importance sampler
-        SequentialIS = pypmc.sampler.importance_sampling.DeterministicIS
+        SequentialIS = pypmc.sampler.importance_sampling.ImportanceSampler
         self.parallel_sampler = MPISampler(SequentialIS, target=analysis, proposal=mixture, prealloc=self.n_samples)
 
         hdf5_io.save_analysis(args.output, '/', self.analysis)
@@ -60,7 +61,7 @@ if __name__ == '__main__':
     parser.add_argument("--analysis-from",
                         help="Specify where the `eos.Analysis` instance shall be read off. " \
                         "Either specify a python module (for example `module.analysis`) or `env` " \
-                        "[default] for reading off the environement variables.",
+                        "[default] for reading off the environment variables.",
                         type=str, default='env')
     parser.add_argument("--analysis-info", help='Print constraints, parameters, and observables',
                         type=int, default=False)
@@ -79,10 +80,8 @@ if __name__ == '__main__':
     analysis = make_analysis(args.analysis_from)
     if args.analysis_info:
         print(analysis)
-    if args.step is None:
-        args.primary_group = ''
-    else:
-        args.primary_group = '/step_%d' % args.step
+
+    args.primary_group = '' if args.step is None else '/step_%d' % args.step
 
     ###
     # take action

### 2015-01-13 py-eos/mcmc.py
[py-eos/mcmc] Store log posterior values for each sample

@@ -12,6 +12,8 @@ import argparse
 import h5py
 import numpy as np
 
+hdf5_subdirectory = '/chain #0'
+
 class MCMC_Sampler(object):
     def __init__(self, analysis, args):
         self.analysis = analysis
@@ -49,7 +51,8 @@ class MCMC_Sampler(object):
             start[:] = self.draw_uniform_in_support()
 
         self.chain = pypmc.sampler.markov_chain.AdaptiveMarkovChain(self.analysis, local_prop, start,
-                                                                      indicator=ind, prealloc=args.samples)
+                                                                    save_target_values=True,
+                                                                    indicator=ind, prealloc=args.samples)
 
         self.burn_in = args.burn_in
 
@@ -58,13 +61,14 @@ class MCMC_Sampler(object):
 
         self.file_name = args.output
 
-        file = h5py.File(self.file_name, 'w')
-        # one row per sample, store parameter values and log(posterior)
-        self.sample_dset = '/samples/chain #0'
-        file.create_dataset(self.sample_dset, (self.samples, self.dim), 'float64')
+        with h5py.File(self.file_name, 'w') as file:
+            # one row per sample, store parameter values and log(posterior)
+            self.sample_dset = hdf5_subdirectory + '/samples'
+            file.create_dataset(self.sample_dset, (self.samples, self.dim), 'float64')
+            self.target_dset = hdf5_subdirectory + '/log_posterior'
+            file.create_dataset(self.target_dset, (self.samples, 1), 'float64')
 
-        hdf5_io.save_analysis(file, self.analysis)
-        file.close()
+        hdf5_io.save_analysis(self.file_name, hdf5_subdirectory, self.analysis)
 
     def draw_uniform_in_support(self):
         ''' draw initial points'''
@@ -105,9 +109,10 @@ class MCMC_Sampler(object):
     def save_samples(self, iterations):
         '''Save batch of samples. File is closed to ensure flush to disk.'''
 
-        file = h5py.File(self.file_name, 'r+')
-        file[self.sample_dset][iterations:iterations + self.update] = self.chain.history[:]
-        file.close()
+        with h5py.File(self.file_name, 'r+') as file:
+            file[self.target_dset][iterations:iterations + self.update] = self.chain.target_values[:]
+            file[self.sample_dset][iterations:iterations + self.update] = self.chain.history[:]
+
         self.chain.clear()
 
 if __name__ == '__main__':

### 2015-01-13 plot/samplingOutput.py
[plot/samplingOutput] Read pypmc mcmc files
add more generic extract_chain modes()

@@ -298,6 +298,51 @@ class MCMC_Output(SamplingOutput):
         else:
             return 'All chains'
 
+def extract_chain_modes(output):
+        """
+        Find the mode of each Markov chain and display it
+
+        Assume that each chain of same length. Designed for use with EOS_PYPMC_MCMC
+        """
+        print("There are %d chains" % output.n_chains)
+        output._modes = []
+
+        global_max = -np.inf
+        global_max_index = None
+
+        for i in range(output.n_chains):
+            mode = []
+
+            index = np.argmax(output.log_posterior[i * output.reduced_length : (i + 1) * output.reduced_length])
+            for j in range(output.npar):
+                mode.append(output.samples[i * output.reduced_length + index][j])
+            max = output.log_posterior[i * output.reduced_length + index]
+
+            if max > global_max:
+                global_max_index = i
+
+            # special case: only one chain
+            if output.single_chain is not None:
+                i = int(output.single_chain)
+            print("Mode of chain %d with log posterior = %.16f is at:" % (i, max))
+
+            # print in a format friendly for eos-scan-mc
+            w = sys.stdout.write
+
+            # all on one line
+            w('"{ ')
+            for p in mode:
+                w("%+.16f " % p)
+            w('}"\n')
+            sys.stdout.flush()
+
+            output._modes.append(np.array(mode))
+
+        # global mode
+        output.global_mode_index = global_max_index
+        if output.single_chain is None:
+            print("Global mode found in chain %d" % output.global_mode_index)
+
 def crop(weights, n):
     '''Set the `n` highest elements in `weights` to zero. Modify in place.'''
     print('\033[91m' + 'WARNING: filtering highest %d weights' % n + '\033[0m')
@@ -951,6 +996,17 @@ class EOS_PYPMC_IS(SamplingOutput):
         self.components = None
 
 class EOS_PYPMC_MCMC(SamplingOutput):
+    '''The structure in the HDF5 file is supposed to be
+
+    /                        Group
+    /chain\ #0               Group
+    /chain\ #0/descriptions  Group
+    /chain\ #0/descriptions/constraints Dataset {1}
+    /chain\ #0/descriptions/parameters Dataset {13}
+    /chain\ #0/log_posterior Dataset {30000, 1}
+    /chain\ #0/samples       Dataset {30000, 13}
+
+    '''
 
     def _read(self, *args, **kwargs):
[…]

### 2015-03-11 plot/merge.py
[merge.py] Use --cut-off option with pypmc chain output

@@ -17,10 +17,13 @@ def natural_sort_key(key):
     import re
     return [int(t) if t.isdigit() else t for t in re.split(r'(\d+)', key)]
 
-def invalid_chain(file, chain, cut_off=None):
+def invalid_chain(file, chain, cut_off=None, format='eos'):
     """Check if mode larger than cut off"""
-    # last value of the last mode is the best found in all updates sequences
-    mode = file['/prerun/chain #%d/stats/mode' % chain][-1][-1]
+    if format == 'eos':
+        # last value of the last mode is the best found in all updates sequences
+        mode = file['/prerun/chain #%d/stats/mode' % chain][-1][-1]
+    elif format == 'pypmc':
+        mode = file['/chain #%d' % chain + '/log_posterior'][:].max()
 
     if cut_off is None:
         print('chain %d has mode %g' % (chain, mode))
@@ -81,7 +84,7 @@ def merge_preruns(output_file_name, search='*.hdf5', input_files=None,
 
         # copy data
         for i in range(nchains_in_file):
-            if invalid_chain(input_file, i, cut_off):
+            if invalid_chain(input_file, i, cut_off, format='eos'):
                 continue
             for g in groups:
                 input_file.copy(g + "/chain #%d" % i, output_file, name=g + "/chain #%d" % nchains_copied)
@@ -92,7 +95,8 @@ def merge_preruns(output_file_name, search='*.hdf5', input_files=None,
 
     output_file.close()
 
-def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None):
+def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
+                cut_off=None):
     '''
     Merge Markov chains from eos-to-pypmc interface.
     '''
@@ -126,6 +130,8 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None):
             np.testing.assert_equal(input_file['/chain #%d/descriptions/constraints' % i][:], constraints)
             assert len(input_file['/chain #%d/samples' % i]) == n_samples
 
+            if invalid_chain(input_file, i, cut_off, format='pypmc'):
+                continue
             # copy data
             for g in groups:
                 input_file.copy('/chain #%d' % i + g, output_file, name='/chain #%d' % nchains_copied + g)
@@ -243,7 +249,7 @@ def main():
         merge_sm_unc(output_file_name=args.output, input_files=input_files)
     elif args.pypmc:
[…]

### 2015-03-11 py-eos/vb.py
[py-eos/vb] Don't group by R value for 'random' initialization

@@ -90,29 +90,27 @@ class VB(object):
         output = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input,
                                                chains=self.args.chains,
                                                skip_initial=self.args.skip_initial)
-
         K_g = self.args.components_per_group
-        long_patches = make_r_gaussmix(output.individual_chains(),
-                                       K_g=K_g, critical_r=self.args.R_value,
-                                       indices=self._indices())
         print("K_g:", K_g)
-        print('Found %d groups with a total of %d patches' %
-              (len(long_patches) // K_g, len(long_patches)))
+
+        if self.args.init_method == 'random':
+            initial_guess = self.args.init_method
+        elif self.args.init_method == 'long-patches':
+            long_patches = make_r_gaussmix(output.individual_chains(),
+                                           K_g=K_g, critical_r=self.args.R_value,
+                                           indices=self._indices())
+            print('Found %d groups with a total of %d patches' %
+                  (len(long_patches) // K_g, len(long_patches)))
+            initial_guess = long_patches
+        else:
+            raise ArgumentError('Invalid initialization method: "%s"' % self.args.init_method)
 
         if self.args.thin:
             samples = output.samples[::self.args.thin]
         else:
             samples = output.samples
 
-
-        if self.args.init_method == 'random':
-            initial_guess = self.args.init_method
-        elif self.args.init_method == 'long-patches':
-            initial_guess = long_patches
-        else:
-            raise ArgumentError('Invalid initialization method: "%s"' % self.args.init_method)
-
-        self.vb = GaussianInference(samples, initial_guess=initial_guess, components=len(long_patches),
+        self.vb = GaussianInference(samples, initial_guess=initial_guess, components=K_g,
                                     W0=np.diag([1e20] * len(self.analysis.priors)))
 
     def _indices(self):

### 2015-03-11 plot/plotScript.py
[plot] Plot VB proposal w/o any samples

@@ -322,7 +322,8 @@ class MarginalDistributions:
                  projection=False):
 
         self.out = sampling_output
-        print('data shape:', self.out.samples.shape)
+        if self.out.samples:
+            print('data shape:', self.out.samples.shape)
 
         #alternatively use KDE
         self.use_histogram = not use_KDE
@@ -442,6 +443,9 @@ class MarginalDistributions:
         """
         self.min = np.empty((self.out.npar,))
         self.max = np.empty((self.out.npar,))
+
+        if self.out.samples is None:
+            return
 
         for index in range(self.min.shape[0]):
             self.min[index] = np.min(self.out.samples.T[index])

### 2015-03-11 plot/samplingOutput.py

@@ -1060,7 +1060,10 @@ class EOS_PYPMC_IS(IS_Output):
                     samples = None
 
                 if self.equal_weights:
-                    weights = np.ones(len(samples)) if weights is not None else None
+                    try:
+                        weights = np.ones(len(samples))
+                    except TypeError:
+                        weights = None
                 else:
                     if len(samples) > 0:
                         weights = hdf5_file[prefix + '/weights'][self.select[0]:self.select[1]]
@@ -1072,7 +1075,7 @@ class EOS_PYPMC_IS(IS_Output):
 
             par_defs, priors = read_descriptions(hdf5_file,
                                                  data_set='/descriptions/parameters',
-                                                 npar=len(samples[0]),
+                                                 npar=len(hdf5_file['/descriptions/parameters']),
                                                  samples=samples)
 
             # get proposal

### 2015-03-11 tensor/paper_plots.py
[tensor] Add SP_FH fit

@@ -247,6 +247,7 @@ class MarginalContours(object):
             # then zoom will work correctly
             density, xrange, yrange = self.__density_cache[(i, j, s, solution)]
             line = bool(k)
+            line=False
             artist = self.margs[s].contours_two(xrange, yrange, density,
                                                 color=self.scen[s].c, line=line, grid=True,
                                                 desired_levels=desired_levels)
@@ -403,31 +404,40 @@ class Spring2015(object):
         # scenarios
         ###
         s = 'scSP_Bsmumu'
-        scenarios = [s]
-
-        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_scSP_Bsmumu.hdf5'), 'OrangeRed',
+        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), 'OrangeRed',
                                 nbins=300)
 #                                         local_mode=[[-0.348441713,   3.787226592, -4.420530192],
 #                                                     [ 0.5021320352, -4.568457245,  4.25129282]])
+        marg.scen[s].set_bandwidth(0, 2, 0.015)
+        marg.scen[s].set_bandwidth(2, 6, 0.008)
+
+        s = 'scSP_FH'
+        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), 'Blue',
+                                nbins=300)
+#                                         local_mode=[[-0.348441713,   3.787226592, -4.420530192],
+#                                                     [ 0.5021320352, -4.568457245,  4.25129282]])
+        marg.scen[s].set_bandwidth(0, 2, 0.025)
+        marg.scen[s].set_bandwidth(2, 6, 0.015)
 
         marg.read_data()
-        m = marg.margs[s]
-        data = m.out.samples
+        scenarios = marg.scen.keys()
 
         ###
         # transformations
         ###
-        transform(data, 0, 2)
-        transform(data, 4, 6)
+        for s in scenarios:
+            data = marg.margs[s].out.samples
+            transform(data, 0, 2)
+            transform(data, 4, 6)
 
+        ###
+        # plot settings
+        ###
[…]

### 2015-03-13 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added predictions for B->K* ll angular observables

--- 2015-01-13 tensor/draft/draft-tensor-op.tex
@@
+% vim: set sts=4 et :
 \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
@@
 \usepackage{graphicx}
-\usepackage{hyperref}
+\usepackage{multirow}
 \usepackage{listings}
-\usepackage{multirow}
 \usepackage{xcolor}
@@
 
-Both observables exihibit strong suppression factors for vectorial and dipole
+Both observables exhibit strong suppression factors for vectorial and dipole
 couplings present in the SM, thereby enhancing their sensitivity to tensorial and
@@
 \begin{figure*}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH_1_6_vs_cT}
+  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT.pdf}
   \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
@@
     & $A_{\rm FB}^\mu$
-    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
+    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
     & $F_{H}^\mu$
@@
     & $A_{\rm CP}^\mu$
-    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
+    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 19.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
 \\    
@@
   $\mbox{Re}\,\wilson{T}$
-  & \eos{$\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$}
-  & \eos{$\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$}
+  & $\quad$ $[-0.31,\, 0.16]$ ($[-0.51,\, 0.34]$) $\quad$
+  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
   & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
@@
   $\mbox{Im}\,\wilson{T}$
-  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
-  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
+  & $[-0.23,\, 0.24]$ ($[-0.43,\, 0.43]$)
+  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
   & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
@@
   $\mbox{Re}\,\wilson{T5}$
-  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
-  & \eos{$[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)}
+  & $[-0.24,\, 0.25]$ ($[-0.43,\, 0.44]$)
+  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
   & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
@@
   $\mbox{Im}\,\wilson{T5}$
-  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
-  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
+  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
+  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
   & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
@@
   $|\wilson{T}|$, $|\wilson{T5}|$
-  & \eos{$< 0.35$ ($< 0.55$)}
+  & $[0.13,\, 0.42]$ ($[0.04,\, 0.56]$)
   & \eos{$< 0.25$ ($< 0.35$)}
@@
      measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
-     \reftab{tab:observables} (except $B_s \to \bar\mu\mu$), and $iii)$ allowing
+     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
      also new physics contributions to $\wilson{9,\,10}$ with uniform prior
-     \eos{$\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-3,\, 3]$}.
+     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
   }
@@
 Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
-by allowing uniform priors for \eos{$\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$},
+by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-7,\, 7]$,
 ($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{SM-EFT-constrained scalar couplings}
+\subsection{SM-EFT-constrained scalar couplings \label{sec:SM-EFT}}
 
@@
 
-The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (neglecting
-terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$) \cite{Alonso:2014csa}
+The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (omitting
+for the sake of the argument terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$) 
+\cite{Alonso:2014csa}
 \begin{equation}
@@
 \end{equation}
-and almost similarly (neglecting terms of order $m_\ell^2/q^2$
+and almost similarly (omitting terms of order $m_\ell^2/q^2$
 and $m_s/m_b$)
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{Tensorial, scalar and vectorial couplings and
-  predictions for $B\to K^* \bar\ell\ell$}
+\subsection{Tensorial, scalar and vectorial couplings \label{sec:tensor:scalar}}
 
 We start with the scenario of the combination of tensorial and scalar couplings
-$\wilson{S,S',P,P',T,T5}$, i.e. the combination of the preceding
+$\wilson{S,S',P,P',T,T5, 10,10'}$ \todo{(extend this discussion right away to include
+also $\wilson{10,\, 10'}$)}, i.e. the combination of the preceding
 two sections. In this scenario there are only small changes on the bounds, in fact
@@
 
-In the remainder we discuss the influence of non-standard $\wilson{10,\, 10'}$,
-that play an important role in $\overline{\cal B}(B_s \to \bar\mu\mu)$ ...
+%
+%
+%--------+---------+---------+---------+---------+---------+---------+---------+
+\subsection{ for $B\to K^* \bar\ell\ell$}
 
 \begin{table*}
-  \renewcommand{\arraystretch}{1.3}
+  \renewcommand{\arraystretch}{1.5}
   %\resizebox{\textwidth}{!}{
-  \begin{tabular}{cc|cc}
+  \begin{tabular}{cc|c|ccc}
   \hline
@@
   & SM
-  & NP
+  & $9,10,T,T5$
+  & $10^{(')},S^{(')},P^{(')}$    
+  & $10^{(')},S^{(')},P^{(')},T,T5$
   \\
@@
   & $[1.1,\, 6]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $\simeq 0$
+  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
+  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
+  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
   \\
   & $[15,\, 19]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & $\simeq 0$
+  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
+  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
+  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
   \\
@@
   & $[1.1,\, 6]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
+  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
+  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
+  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
   \\
   & $[15,\, 19]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$} 
+  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
+  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
+  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
   \\
@@
   & $[1.1,\, 6]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
+  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
+  & \eos{SM}
+  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
   \\
   & $[15,\, 19]$
-  & $[ ,\, ]$ ($[ ,\, ]$)
-  & $[ ,\, ]$ ($[ ,\, ]$)
+  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$} 
+  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
+  & \eos{SM}
+  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
   \\
@@
   \caption{
-     \label{tab:predictions}
-     \todo{predictions for $B\to K^*\bar\ell\ell$}
+     \label{tab:postdictions}
+     The 68\% probability intervals of not yet measured angular observables in 
+     $B\to K^*\bar\mu\mu$ integrated over
+     $q^2$ bins at low- and high-$q^2$ for several new physics scenarios respecting
+     all the considered experimental constraints. The SM prediction with respective
+     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
+     approximation, see text for more explanations.
   }
 \end{table*}
+
+Eventually, we present the yet allowed ranges due to non-standard tensorial
+and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
+$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$
+in order to explore the potential of their future measurements in fits of the kind
+pursued in this work.
+The 68\% probability intervals are collected in \reftab{tab:postdictions} 
+for the various general scenarios, i.e. allowing for interference with non-zero
+vectorial couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}, 
+\refsec{sec:SM-EFT} and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities 
+in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ 
+GeV$^2$, respectively. Their posterior distributions have been obtained from the
+final posterior samples as explained in~\cite{Beaujean:2012uj}.
+
+For comparison, the SM estimates are also given in \reftab{tab:postdictions}.
+At low-$q^2$ they are of order ${\cal O}(10^{-21})$ for $(J_{1s} - 3\, J_{2s})$ and
+$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-23})$ at high-$q^2$ 
+due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical 
+magnitude of vectorial couplings, note that for example the decay width of 
+$B\to K^*\bar\ell\ell$
+\begin{align}
+  \frac{{\rm d}\Gamma}{{\rm d}q^2} & =
+    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c}) 
+\end{align}
+is numerically of the order ${\cal O}(10^{-19})$ in the SM
+\begin{equation}
+\begin{aligned}
+  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
+  \eos{\left(1.07_{-0.25}^{+0.28} \right) \cdot 10^{-19}} \,,
+\\
+  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[\eos{16},\, 19]} & =
+  \eos{\left(0.63_{-0.17}^{+0.20} \right) \cdot 10^{-19}} \,,
+\end{aligned}
+\end{equation}
+when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
+is strictly zero for the approximation adopted here. Non-zero contributions
+can be generated by QED corrections or potentially from higher-dimensional
+($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
+suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
+suppression must be compared to potential suppression present for tensorial
+and scalar contributions in particular NP models in order to decide their
+relevance. Our model-independent fits are still in a realm where such
+considerations insignificant since current experimental measurements, in
+combination with theory uncertainties, do not impose yet too stringent
+constraints on tensorial and scalar couplings.
+
+Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in all considered
+scenarios. Concerning $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, substantial
+deviations from the SM prediction are possible only in the presence of non-zero
+tensorial couplings up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also
+at low-$q^2$ in the case of $(J_{1s} - 3\, J_{2s})$.
 
@@
 analogous but not yet measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
-and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ .
+and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$.
 
@@
 \begin{enumerate}
-\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}^\mu|
+\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}|
   < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
   In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\,
+  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}| < 0.30\, 
   (0.45)$}, even in the presence of non-standard contributions in vectorial
-  couplings.
+  couplings $(\wilson{9,10}\neq 0)$.
 \item allows for the first time to bound all four scalar and pseudo-scalar 
@@
   Even when taking into account destructive interference with vectorial couplings
+  $(\wilson{10,10'}\neq 0)$, we find
   \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| < 
@@
 \end{enumerate}
-In all cases these \eos{constraints are weakened only slightly} in the presence of
-new physics in vectorial couplings from destructive interference.
+In all cases these \eos{constraints are weakened only slightly} in the presence
+of new physics in vectorial couplings from destructive interference.
+
+In the future this might change once measurements start to probe the SM expectation,
+as in this case constraints on the tensorial and scalar couplings become so
+stringent that the formal suppression of vectorial couplings by $m_\ell / \sqrt{q^2}$ 
+is overcome. Our study of angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
+and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ shows that
 
@@
 are adopted and supplemented with lattice determinations \cite{Bouchard:2013eph}.
+\eos{Contrary to \cite{}, we do not adapt a log-gamma prior for the asymmetric
+uncertainty but rather $\ldots$ .}
 The lattice results are given within a slightly different parameterisation necessitating

### 2015-03-13 tensor/draft/draft-tensor-op.tex

@@
     & $A_{\rm CP}^\mu$
-    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 19.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
+    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
 \\
@@
   In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}| < 0.30\, 
+  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\,
   (0.45)$}, even in the presence of non-standard contributions in vectorial
-  couplings $(\wilson{9,10}\neq 0)$.
+  couplings.
 \item allows for the first time to bound all four scalar and pseudo-scalar
@@
   Even when taking into account destructive interference with vectorial couplings
-  $(\wilson{10,10'}\neq 0)$, we find
   \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| <
@@
 \end{enumerate}
+
 In all cases these \eos{constraints are weakened only slightly} in the presence

### 2015-03-24 py-eos/unc.py
[py-eos, tensor] Add unc.py for uncertainty propagation with eos-evaluate

@@ -1,0 +1,92 @@
+#! /usr/bin/env python
+
+'''Uncertainty propagation with `eos-evaluate`.'''
+
+from __future__ import print_function, division
+
+import argparse
+import h5py
+import numpy as np
+import commands, os, sys
+
+sys.path.append(os.path.realpath('../plot'))
+import samplingOutput
+
+hdf5_subdirectory = '/unc'
+class Unc(object):
+    def __init__(self, args):
+        self.args = args
+
+        # read MCMC input file
+        select = [int(x) for x in args.input_range]
+        self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input,
+                                                   select=select)
+
+        self.fixed_name = args.parameter[0]
+        self.fixed_values = np.linspace(*tuple([float(x) for x in args.parameter[1:]]))
+
+        self.results = np.empty((len(self.input.samples), len(self.fixed_values)))
+
+        desc = 'descriptions'
+        with h5py.File(args.output, 'w') as output_file:
+            with h5py.File(args.mcmc_input, 'r') as input_file:
+                # todo Don't hardcode chain id!
+                input_file.copy('/chain #0/' + desc, output_file, name=desc)
+
+            ds_fixed = output_file.create_dataset(desc + '/fixed parameter', data=self.fixed_values)
+            ds_fixed.attrs['name'] = self.fixed_name
+
+            ds_par = output_file[desc + '/parameters']
+            ds_par.attrs['input file'] = self.args.mcmc_input
+            ds_par.attrs['min sample index'] = select[0]
+            ds_par.attrs['max sample index'] = select[1]
+
+    def run(self):
+        for n, x in enumerate(self.input.samples):
+            for i, par in enumerate(self.fixed_values):
+                cmd = self.build_cmd(x, par)
+                status, output = commands.getstatusoutput(cmd)
+                self.results[n, i] = float(output.splitlines()[-1].split()[0])
+
+        # dump results
+        with h5py.File(args.output, 'a') as output_file:
+            ds_obs = output_file.create_dataset('/observable', data=self.results)
+            ds_obs.attrs['name'] = self.args.observable
+
+    def build_cmd(self, x, par):
+        cmd = 'eos-evaluate --precision 16'
+        for i, p in enumerate(self.input.par_defs):
+            cmd += ' --parameter "' + p.name + '" %.16f' % x[i]
+        cmd += ' --parameter "' + self.fixed_name + '" %.16f' % par
+        cmd += ' ' + self.args.extra_args
[…]

### 2015-03-24 py-eos/vb.py
[py-eos/vb] remove old code

@@ -146,13 +146,9 @@ class VB(object):
         print(kwargs)
         self.vb.run(**kwargs)
 
-        # todo code dublication
         mix = self.vb.make_mixture()
         hdf5_io.save_mixture(self.args.output, output_directory, mix)
         hdf5_io.save_vb_hyperparameters(self.args.output, output_directory, self.vb)
-        # plot_mixture(mix, 0, 2)
-        # from matplotlib import pyplot as plt
-        # plt.savefig('/tmp/vb.pdf')
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(description="Run MCMC on EOS analysis from python")

### 2015-03-25 plot/plotScript.py
[plot] --select overrides --skip-initial

@@ -1537,7 +1537,7 @@ def factory(cmd_line=None):
     parser.add_argument('--single-2D', help="Plot only the 2D marginal distribution of parameters i,j, i<j, i,j=0...N-1", nargs=2, type=int, action='append')
     parser.add_argument('--single-ext', help="File extension for single plots, e.g 'pdf'[default] or 'png'", action='store')
     parser.add_argument('--select', help="Select a range of samples from each chain", action='store',nargs=2, default=(None, None))
-    parser.add_argument('--skip-initial', help="Allows to skip the first fraction of iterations", action='store', default=0)
+    parser.add_argument('--skip-initial', help="Allows to skip the first fraction of iterations. Ignored if --seelect MIN MAX given.", action='store', default=0)
     parser.add_argument('--uncertainty-propagation', help="Parse uncertainty-propagation data", action='store_true')
     parser.add_argument('--use-data-range', help="Determine the parameter ranges from data, instead of from definition in HDF5. ", action='store', default=0.0)
     parser.add_argument('--use-KDE',  help='Use kernel density estimation instead of histograms', action='store_true')

### 2015-03-25 plot/samplingOutput.py

@@ -199,8 +199,13 @@ class MCMC_Output(SamplingOutput):
         full_length = len(hdf5_file[prefix + '/chain #' + first_chain + "/samples"])
 
         #adjust which range is drawn, default: full range
-        if self.skip_initial > 0:
-            self.select[0] = int(self.skip_initial * full_length)
+        if self.select[0] is None:
+            if self.skip_initial > 0:
+                self.select[0] = int(self.skip_initial * full_length)
+            else:
+                self.select[0] = 0
+        if self.select[1] is None:
+            self.select[1] = self.chain_length
 
         merged_chains = hdf5_file[prefix + '/chain #' + first_chain + "/samples"][self.select[0]:self.select[1]]
         n_chains_parsed += 1
@@ -1172,14 +1177,16 @@ class EOS_PYPMC_MCMC(SamplingOutput):
             self.chain_length = len(samples)
 
             #adjust which range is drawn, default: full range
-            if self.skip_initial > 0:
-                self.select[0] = int(self.skip_initial * self.chain_length)
             if self.select[0] is None:
-                self.select[0] = 0
+                if self.skip_initial > 0:
+                    self.select[0] = int(self.skip_initial * self.chain_length)
+                else:
+                    self.select[0] = 0
             if self.select[1] is None:
                 self.select[1] = self.chain_length
 
             self.reduced_length = self.select[1] - self.select[0]
+            assert self.reduced_length > 0, "Invalid selection: " + str(self.select)
 
             source_slice = np.s_[self.select[0]:self.select[1]]
             destination_slice = np.s_[0:self.reduced_length]

### 2015-03-25 plot/merge.py
[plot/merge.py] Create samples below 'chain #0' for single chain output

@@ -107,11 +107,12 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
     # hdf5 groups
     groups = ['/samples', '/descriptions', '/log_posterior']
+    first = '/chain #0'
 
     with h5py.File(input_files[0], 'r') as f:
-        par = f['/chain #0/descriptions/parameters'][:]
-        constraints = f['/chain #0/descriptions/constraints'][:]
-        n_samples = len(f['/chain #0/samples'])
+        par = f[first + '/descriptions/parameters'][:]
+        constraints = f[first + '/descriptions/constraints'][:]
+        n_samples = len(f[first + '/samples'])
 
     # count chains copied
     nchains_valid = 0
@@ -148,21 +149,22 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
             print("Select %d samples from each chain" % new_samples)
 
             # predefine data sets large enough to hold everything
-            grp = output_file.create_group('/chain #0')
+            grp = output_file.create_group(first)
             data_groups = [('/samples', (n_samples_total, len(par))), ('/log_posterior', (n_samples_total,))]
-            data_sets = [grp.create_dataset(g[0], g[1]) for g in data_groups]
+            data_sets = [output_file.create_dataset(first + g[0], g[1]) for g in data_groups]
 
             # loop over valid input files
+            nchain = 0
             for j, file_name in enumerate(valid_files):
                 with h5py.File(file_name, 'r') as input_file:
                     # copy descriptions only once
                     if j == 0:
-                        s = '/chain #0/descriptions'
+                        s = first + '/descriptions'
                         input_file.copy(s, output_file, name=s)
                     # loop over chains
                     for i, c in enumerate(input_file['/'].iterkeys()):
                         for g, ds in zip(data_groups, data_sets):
-                            old_length = len(ds)
+                            old_length = nchain * new_samples
                             data = input_file[c + g[0]][first_index::thin]
 
                             # 1D versus 2D assignment
@@ -170,6 +172,7 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
                                 ds[old_length:old_length + new_samples] = data
                             else:
                                 ds[old_length:old_length + new_samples, :] = data
+                    nchain += 1
 
     print("Merged %d chains from %d files" % (nchains_valid, len(input_files)))
 

### 2015-03-25 py-eos/unc.py
[py-eos,tensor,unc] pass kinematics separately, fix loadleveler submission

@@ -19,7 +19,7 @@ class Unc(object):
 
         # read MCMC input file
         select = [int(x) for x in args.input_range]
-        self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input,
+        self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input, skip_initial=0.0,
                                                    select=select)
 
         self.fixed_name = args.parameter[0]
@@ -46,6 +46,10 @@ class Unc(object):
             for i, par in enumerate(self.fixed_values):
                 cmd = self.build_cmd(x, par)
                 status, output = commands.getstatusoutput(cmd)
+                if status:
+                    print(cmd)
+                    print(output)
+                    exit(status)
                 self.results[n, i] = float(output.splitlines()[-1].split()[0])
 
         # dump results
@@ -58,17 +62,17 @@ class Unc(object):
         for i, p in enumerate(self.input.par_defs):
             cmd += ' --parameter "' + p.name + '" %.16f' % x[i]
         cmd += ' --parameter "' + self.fixed_name + '" %.16f' % par
-        cmd += ' ' + self.args.extra_args
+        for k,v in self.args.kinematics.iteritems():
+            cmd += ' --kinematics %s %s' % (k, v)
         cmd += ' --observable "' + self.args.observable + '"'
         return cmd
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(description=__doc__)
 
-    parser.add_argument("--extra-args", const='', nargs='?',
-                        help='''passed on as extra argument when calling `eos-evaluate`.
-                        Use it to define kinematics or other options.
-                        Example: --extra-args "--kinematics s_min 1 --kinematics s_max 6" ''')
+    parser.add_argument("--kinematics", nargs='*',
+                        help='''Use it to define kinematics or other options.
+                        Example: --kinematics s_min 1 s_max 6''')
     parser.add_argument("--input-range", help='The range of input samples used. Example: --input-range 3800 4100', nargs=2)
     parser.add_argument("--mcmc-input", help='File name with MCMC samples. Only `chain #0` is used!')
     parser.add_argument('--observable',
@@ -84,6 +88,13 @@ if __name__ == '__main__':
     ###
     # validate and use arguments
     ###
+    # keyword and value stored after one another
+    if len(args.kinematics) % 2 == 1:
[…]

### 2015-03-25 py-eos/unc.py
[py-eos] Adjust unc.py to new `eos-evaluate` interface

@@ -23,18 +23,13 @@ class Unc(object):
                                                    select=select)
 
         self.fixed_name = args.parameter[0]
-        self.fixed_values = np.linspace(*tuple([float(x) for x in args.parameter[1:]]))
 
-        self.results = np.empty((len(self.input.samples), len(self.fixed_values)))
+        self.results = np.empty((len(self.input.samples), int(args.parameter[-1])))
 
         desc = 'descriptions'
         with h5py.File(args.output, 'w') as output_file:
             with h5py.File(args.mcmc_input, 'r') as input_file:
-                # todo Don't hardcode chain id!
                 input_file.copy('/chain #0/' + desc, output_file, name=desc)
-
-            ds_fixed = output_file.create_dataset(desc + '/fixed parameter', data=self.fixed_values)
-            ds_fixed.attrs['name'] = self.fixed_name
 
             ds_par = output_file[desc + '/parameters']
             ds_par.attrs['input file'] = self.args.mcmc_input
@@ -43,25 +38,30 @@ class Unc(object):
 
     def run(self):
         for n, x in enumerate(self.input.samples):
-            for i, par in enumerate(self.fixed_values):
-                cmd = self.build_cmd(x, par)
-                status, output = commands.getstatusoutput(cmd)
-                if status:
-                    print(cmd)
-                    print(output)
-                    exit(status)
-                self.results[n, i] = float(output.splitlines()[-1].split()[0])
+            cmd = self.build_cmd(x)
+            status, output = commands.getstatusoutput(cmd)
+            if status:
+                print(cmd)
+                print(output)
+                exit(status)
+            # ignore first two lines, then extract second column
+            arr = np.loadtxt(output.splitlines()[2:])
+            self.results[n] = arr.T[1]
 
         # dump results
         with h5py.File(args.output, 'a') as output_file:
             ds_obs = output_file.create_dataset('/observable', data=self.results)
             ds_obs.attrs['name'] = self.args.observable
 
-    def build_cmd(self, x, par):
+            # fixed values always the same, only use from last output
+            ds_fixed = output_file.create_dataset('/descriptions/fixed parameter', data=arr.T[0])
+            ds_fixed.attrs['name'] = self.fixed_name
+
+    def build_cmd(self, x):
         cmd = 'eos-evaluate --precision 16'
         for i, p in enumerate(self.input.par_defs):
[…]

### 2015-03-26 plot/merge.py
[plot,tensor] Merge uncertainty output from parallel run

@@ -176,7 +176,63 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
     print("Merged %d chains from %d files" % (nchains_valid, len(input_files)))
 
-def merge_sm_unc(output_file_name, input_files):
+def merge_unc_pypmc(output_file_name, search='unc*.hdf5', input_files=None):
+    if not input_files:
+        input_files = search_files(search, output_file_name)
+
+
+    with h5py.File(output_file_name, "w") as output_file:
+        # check if files agree with first input file
+        with h5py.File(input_files[0], 'r') as f:
+            constraints = f['/descriptions/constraints'][:]
+
+            par_ds = f['/descriptions/parameters']
+            parameters = par_ds[:]
+            sample_input_file = par_ds.attrs['input file']
+
+            fixed_par_ds = f['/descriptions/fixed parameter']
+            fixed_par = fixed_par_ds[:]
+            fixed_par_name = fixed_par_ds.attrs['name']
+
+            obs_ds = f['observable']
+            obs_name = obs_ds.attrs['name']
+
+            print("Definining data format from %s" % os.path.split(input_files[0])[1])
+
+            # copy meta data to output file
+            f.copy('/descriptions', output_file)
+
+            # create observable data set and initialize with first input file
+            obs_ds = output_file.create_dataset('/observable', data=obs_ds[:], maxshape=(None, obs_ds.shape[1]))
+            obs_ds.attrs['name'] = obs_name
+
+        for file_name in input_files[1:]:
+            with h5py.File(file_name, 'r') as input_file:
+                # check agreement
+                np.testing.assert_equal(input_file['/descriptions/constraints'][:], constraints)
+
+                par_ds = input_file['/descriptions/parameters']
+                np.testing.assert_equal(par_ds[:], parameters)
+                assert par_ds.attrs['input file'] == sample_input_file
+
+                fixed_par_ds = input_file['/descriptions/fixed parameter']
+                np.testing.assert_equal(fixed_par_ds[:], fixed_par)
+                assert fixed_par_ds.attrs['name'] == fixed_par_name
+
+                in_obs_ds = input_file['/observable']
+                assert in_obs_ds.attrs['name'] == obs_name
+
+                print("merging %s" % os.path.split(file_name)[1])
+                old_length = obs_ds.len()
+                obs_ds.resize(old_length + in_obs_ds.len(), axis=0)
+                obs_ds[old_length:old_length + in_obs_ds.len()] = in_obs_ds[:]
+
[…]

### 2015-03-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added new prior average of BZ and KMPW LCSR results for plus and tensor FF and text rephrasinng

@@
   constraints on (pseudo-)scalar couplings and their chirality-flipped
-  counterparts that are complementary to the once from the branching ratio
-  $B_s\to \bar\mu\mu$, which allows to put for the first time upper bounds
-  on all four couplings.
+  counterparts that are complementary to the ones from the branching ratio
+  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously 
+  upper bounds on all four couplings.
 \end{abstract}
@@
 
-Both observables exhibit strong suppression factors for vectorial and dipole
+Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
+factors for vectorial and dipole
 couplings present in the SM, thereby enhancing their sensitivity to tensorial and
@@
 are presented for several model-independent scenarios in \refsec{sec:results}.
-Technical details on the treatment of theory uncertainties are relegated to
-appendices.
+Technical details of the angular observables in $B\to K^* \bar\ell\ell$ and the
+treatment of theory uncertainties are relegated to appendices.
 
@@
 the most general dimension-six flavor-changing operators $\Op_i$ mediating
-$b\to s \bar\ell\ell$ are classified according to their chiral structure.
-There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$) operators
+$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
+chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$) 
+operators
 \begin{equation}
@@
 also used frequently in the literature. Their respective short-distance couplings,
-the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at the typical
-scale of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM predictions
-in the presence of new physics.
-
-The SM values $\wilson[\ell]{7,9,10}$ are obtained at NNLO \cite{Bobeth:2003at,
-Huber:2005ig} and depend on the fundamental parameters of the top-quark and
-$W$-boson masses, as well as on the sine of the weak mixing angle. Moreover,
-they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
+the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
+the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
+predictions in the presence of new physics.
+
+The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
+(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
+of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
+Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
 All other Wilson coefficients are numerically suppressed or zero:
@@
 \begin{align}
-  F_H^\ell(q^2)|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
-  A_{\rm FB}^\ell|_{\rm SM} & = 0 \,.
+  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
+  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
 \end{align}
@@
 \bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
-are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial once
+are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial ones
 present in the SM or their respective interference terms. These are $J_{6c}$
@@
 \intertext{is sensitive to the interference of tensorial and scalar operators,
-  complementary to lepton forward-backward asymmetry of $B\to K \bar\ell\ell$}
+  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
   \label{eq:AFB-dependence}
@@
 Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only
-constructively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
+constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
 Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
 \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
-by $m_\ell/\sqrt{q^2}$, but can become relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$
+by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
 and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
@@
 The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
-\refeq{eq:AFB-dependence} are measured in the angular
-distribution \refeq{eq:ang-distr} of $B\to K \bar\ell\ell$ being normalised to the
-decay width $\Gamma_\ell$, whereas $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$
-appear in the unnormalised angular distribution of $B\to K^* \bar\ell\ell$.
-Hence in the former, uncertainties due to form factors can cancel in part
-\cite{Bobeth:2007dw, Bobeth:2012vn}. So-called ``optimised'' versions $S_1$, $M_1$ and
-$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw}
-for $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, respectively.
-In \refapp{app:BKstarellell} potential normalisations are discussed that
-could serve to form optimised observables at high $q^2$ for special cases of
-either vanishing chirality-flipped vectorial or tensorial or scalar couplings.
-In the most general case, however, there are no optimised observables.
-Although form factors do not cancel in this case, it might be
-still advantageous to use normalisations, for example when the overall
+\refeq{eq:AFB-dependence} are measured in the angular distribution \refeq{eq:ang-distr}
+of $B\to K \bar\ell\ell$ being normalised to the decay width $\Gamma_\ell$, such
+that uncertainties due to form factors can cancel in part \cite{Bobeth:2007dw, 
+Bobeth:2012vn}. On the other hand, $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and 
+$(J_{1c} + J_{2c})$ appear in the unnormalised angular distribution of 
+$B\to K^* \bar\ell\ell$ and so-called ``optimised'' versions $S_1$, $M_1$ and 
+$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw}, 
+respectively, where form factors cancel in the limit of $m_b \to \infty$. 
+For the high-$q^2$ region potential normalisations are discussed in 
+\refapp{app:BKstarellell}, which could serve to form optimised observables for
+special scenarios of either vanishing chirality-flipped vectorial or tensorial
+or scalar couplings. In the most general case, however, there are no optimised
+observables at high-$q^2$. Although form factors do not cancel in this case, it
+might be still advantageous to use normalisations, for example when the overall
 normalisation of $B\to K^*$ form factors constitutes a major theoretical
@@
   respective kinematics and experiments that provide the measurements.
-  Lattice results of $B\to K$ form factors are used to constrain their parameters,
+  Lattice results of $B\to K$ form factors are used to constrain parameters
+  of their $q^2$-dependence,
   and theoretical constraints on $B\to K^*$ form factors are included. For
@@
 this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
-of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
-of vectorial couplings.
+of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the 
+imaginary parts of vectorial couplings.
 
@@
 As a matter of the fact there are no discrepancies between the latest measurements
-for $\ell = \mu$ (throughout this section)
-of $F_H^\mu$ and $A_{\rm FB}^\mu$ and their tiny SM predictions. Thus our main objective
-is the derivation of stronger constraints on tensorial and scalar couplings, which
-are enhanced in both observables compared to vectorial ones. For this purpose,
-we will consider several model-independent scenarios, starting from rather
-restricted to more general ones, in order to asses the effect of cancellations
-among different contributions.
-
-We will start with only tensorial couplings and see that they are well constrained
-by $F_H^\mu$ alone. In a second step we consider only scalar couplings in order
-to investigate the complementarity of $F_H^\mu$ and $B_s \to \bar\mu\mu$.
-Eventually we will consider as a special scenario the SM augmented by dimension
-six operators as an effective theory of new physics below some high scale
-$\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
+for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ and
+their tiny SM predictions. Thus our main objective is the derivation of stronger
+constraints on tensorial and scalar couplings, taking advantage of their enhancement
+in both observables over vectorial ones. For this purpose, we will consider several
+model-independent scenarios, starting from rather restricted to more general ones,
+in order to asses the effect of cancellations due to interference of various
+contributions.
+
+We will start with the scenario of only tensorial couplings and see that they are
+well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
+couplings in order to investigate the complementarity of $F_H^\mu$ and 
+$B_s \to \bar\mu\mu$. Here we find that for the first time all scalar couplings
+can be bounded simultaneously by the combination of both measurements. Eventually
+we will consider as a special scenario the SM
+augmented by dimension six operators as an effective theory of new physics below
+some high scale $\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
 symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
-as in the SM, i.e. $v \ll \Lambda_{\rm NP}$.
+as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
+also interference effects with new physics in vectorial couplings. Finally, we
+conclude this section with postdictions of the allowed ranges of the yet not
+measured angular observables in $B\to K^*\bar\mu\mu$ given all other experimental
+constraints. 
+\todo{Perhaps give also postdictions for $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$}
 
@@
 in order to explore the potential of their future measurements in fits of the kind
-pursued in this work.
+pursued in this work. \todo{Find nice place to cite method of moments paper.}
 The 68\% probability intervals are collected in \reftab{tab:postdictions} 
 for the various general scenarios, i.e. allowing for interference with non-zero
-vectorial couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}, 
-\refsec{sec:SM-EFT} and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities 
+vectorial couplings, in \refsec{sec:tensor}, \refsec{sec:scalar} 
+and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities 
 in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ 
@@
 relevance. Our model-independent fits are still in a realm where such
-considerations insignificant since current experimental measurements, in
+considerations are insignificant since current experimental measurements, in
 combination with theory uncertainties, do not impose yet too stringent
@@
 
-Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in all considered
-scenarios. Concerning $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, substantial
+Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in scenarios
+involving tensorial couplings and only ${\cal O}(10^{-23})$ in their absence. 
+Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
 deviations from the SM prediction are possible only in the presence of non-zero
-tensorial couplings up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also
-at low-$q^2$ in the case of $(J_{1s} - 3\, J_{2s})$.
+tensorial couplings. In this case enhancement by two orders of magnitude are
+possible up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also at low-$q^2$ in
+the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
+experimental constraints in \reftab{tab:observables}. In view of current
+experimental precision of \eos{$20\%$} branching ratio measurements corresponding
+to the \eos{${\cal O}(10^{-20})$} one can indeed hope for some sensitivity to
+such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ in future
+measurements.
 
@@
 \hline
-  $f_+(0)$    &  $0.34^{+0.05}_{-0.02}$  &  --    &  \cite{Khodjamirian:2010vf}\\
-  $f_T(0)$    &  $0.39^{+0.05}_{-0.03}$  &  --    &  \cite{Khodjamirian:2010vf}\\
+  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
+  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
   $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
@@
 $f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
-are adopted and supplemented with lattice determinations \cite{Bouchard:2013eph}.
-\eos{Contrary to \cite{}, we do not adapt a log-gamma prior for the asymmetric
-uncertainty but rather $\ldots$ .}
+and \cite{Ball:2004ye} have been averaged (see \reftab{tab:hadronic:nuisance} and
+cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}. 
+Contrary to \cite{Beaujean:2013soa}, we do not adapt a
+log-gamma prior for the asymmetric uncertainties but rather a continuous, but
+asymmetric gaussian distribution.
 The lattice results are given within a slightly different parameterisation necessitating

### 2015-03-26 plot/translator.py
[plot] translate BSZ parameter names to tex

@@ -90,6 +90,18 @@ class EOS_Translator:
                   "B->K^*::b^A1_1@KMPW2010":r"$b^{A_1}_1$",
                   "B->K^*::F^A2(0)@KMPW2010":r"$A_2(0)$",
                   "B->K^*::b^A2_1@KMPW2010":r"$b^{A_2}_1$",
+                  "B->K^*::alpha^A0_0@BSZ2015":r"$\alpha^{A_0}_0$",
+                  "B->K^*::alpha^A0_1@BSZ2015":r"$\alpha^{A_0}_1$",
+                  "B->K^*::alpha^A0_2@BSZ2015":r"$\alpha^{A_0}_2$",
+                  "B->K^*::alpha^A1_0@BSZ2015":r"$\alpha^{A_1}_0$",
+                  "B->K^*::alpha^A1_1@BSZ2015":r"$\alpha^{A_1}_1$",
+                  "B->K^*::alpha^A1_2@BSZ2015":r"$\alpha^{A_1}_2$",
+                  "B->K^*::alpha^A12_0@BSZ2015":r"$\alpha^{A_{12}}_0$",
+                  "B->K^*::alpha^A12_1@BSZ2015":r"$\alpha^{A_{12}}_1$",
+                  "B->K^*::alpha^A12_2@BSZ2015":r"$\alpha^{A_{12}}_2$",
+                  "B->K^*::alpha^V_0@BSZ2015":r"$\alpha^{V}_0$",
+                  "B->K^*::alpha^V_1@BSZ2015":r"$\alpha^{V}_1$",
+                  "B->K^*::alpha^V_2@BSZ2015":r"$\alpha^{V}_2$",
                   #subleading uncertainties
                   "B->Pll::Lambda_pseudo@LowRecoil":r"SL$(B \to P l^+ l^- \mathrm{@ low recoil}): \Lambda$",
                   "B->Pll::sl_phase_pseudo@LowRecoil":r"SL$(B \to P l^+ l^- \mathrm{@ low recoil}): \varphi$",

### 2015-03-27 plot/merge.py
[plot] pypmc unc merge takes 'search' argument

@@ -347,7 +347,8 @@ def main():
 
     if args.unc:
         if args.pypmc:
-            merge_unc_pypmc(output_file_name=args.output, input_files=input_files)
+            merge_unc_pypmc(output_file_name=args.output, input_files=input_files,
+                            search=args.search)
         else:
             merge_unc(output_file_name=args.output, input_files=input_files)
     else:

### 2015-03-27 plot/plotScript.py
[plot] Plot pypmc unc output

@@ -1581,8 +1581,13 @@ def factory(cmd_line=None):
         OutputClass = EmceeOutput
     elif args.nest:
         OutputClass = MultinestOutput
-    elif args.uncertainty_propagation:
-        OutputClass = UncertaintyPropagation
+    elif args.uncertainty_propagation or 'unc_' in args.i or '_unc' in args.i:
+        # correlations not meaningful if computed from the same random numbers
+        args.__dict__['1D_only'] = True
+        if args.pypmc:
+            OutputClass = EOS_PYPMC_UNC
+        else:
+            OutputClass = UncertaintyPropagation
     else:
         if args.i.endswith('.npy'):
             OutputClass = JahnISOutput

### 2015-03-27 plot/samplingOutput.py

@@ -1231,3 +1231,22 @@ class EOS_PYPMC_MCMC(SamplingOutput):
     def individual_chains(self):
         '''Return list of individual chains.'''
         return [self.samples[i * self.reduced_length:(i+1) * self.reduced_length] for i in range(len(self.samples) // self.reduced_length)]
+
+class EOS_PYPMC_UNC(SamplingOutput):
+    '''Read samples of a single observable computed from parameter samples.'''
+
+    def _read(self, *args, **kwargs):
+        with h5py.File(self.input_file_name) as input_file:
+            obs_ds = input_file['/observable']
+            self.samples = obs_ds[:]
+            self.weights = np.ones(len(self.samples))
+            fixed_ds = input_file['/descriptions/fixed parameter']
+            fixed_name = fixed_ds.attrs['name']
+            fixed_values = fixed_ds[:]
+            self.par_defs = []
+            for i in range(len(fixed_values)):
+                # get everything up to '@' to remove lengthy options
+                name = obs_ds.attrs['name']
+                name = name[:name.find('@')] + '@' + fixed_name + '= %g' % fixed_values[i]
+                self.par_defs.append(ParameterDefinition(name, np.min(self.samples.T[i]), np.max(self.samples.T[i])))
+            self.priors = [None] * len(fixed_values)

### 2015-03-27 plot/plotScript.py
[plot] Clean up plotScript
* remove discrete parameters
* unify 1D contour plotting
* store 1D marginal summary statistics

@@ -411,6 +411,14 @@ class MarginalDistributions:
         self.minimum_probability = None
 
         ###
+        # Summary of 1D marginals stored as np.array
+        # credibilities:  par index => 1sigma: [min, max, width], 2sigma: [min, max, width]
+        # marginal_modes: par index => [modes]
+        ###
+        self.credibilities = {}
+        self.marginal_modes = {}
+
+        ###
         # Marginalization options
         ###
         if projection:
@@ -570,7 +578,7 @@ class MarginalDistributions:
         self.nBins[index] = int(( self.max[index] - self.min[index])/bandwidth)
         return bandwidth
 
-    def contours_one(self, x, densities, level, specifier, mode, **kwargs):
+    def contours_one(self, x, densities, level, specifier, hist=True, **kwargs):
         """
         Plot contours and output intervals for one dim. distributions of parameter x.
         args:
@@ -578,16 +586,18 @@ class MarginalDistributions:
         densities = the estimate of the probability density
         level = the desired credibility level
         specifier = label used for text output, e.g. 'one sigma'
-        mode = if hist, use traditional plotting.
+        hist = if `True`, plot with histogram bars, else interpolate smoothly
         **kwargs are passed to the plotting routine of pylab.fill_between
         """
-        if mode == 'hist':
-            #draw 95% bins in yellow, 68% in green
+        if hist:
             for i in range(len(x)-1):
                 if densities[i] > level:
                     P.fill_between( (x[i], x[i+1]), 0, densities[i], **kwargs)
                     continue
 
+            return
+        else:
+            P.fill_between(x, densities, 0, interpolate=True, where=densities > level, **kwargs)
             return
 
         high_points = densities >= level
@@ -708,7 +718,7 @@ class MarginalDistributions:
         print("Maxima of 68 %% contours at = %s " % np.array(maxima_68))
         """
 
-    def __extract_smallest_intervals(self, x, prob_density, level_68, level_95):
+    def __extract_smallest_intervals(self, x, prob_density, level_68, level_95, index=None):
         """
         Extract set of smallest intervals in 1D
         """
@@ -718,17 +728,19 @@ class MarginalDistributions:
         runs = find_runs(points_95, True)
 
         # print intervals
-        intervals_95 = []
+        intervals95 = []
         local_modes = []
         for run in runs:
-            intervals_95.append([x[run[0]], x[run[1] - 1]])
-            intervals_95[-1].append(intervals_95[-1][1] - intervals_95[-1][0])
[…]

### 2015-03-27 plot/samplingOutput.py

@@ -18,18 +18,17 @@ def open_hdf5(name, mode='r'):
 class ParameterDefinition(object):
     """Properties of a fit parameter"""
 
-    def __init__(self, name, min, max, nuisance=False, discrete=False, index=None):
+    def __init__(self, name, min, max, nuisance=False, index=None):
         self.name = name
         self.min = min
         self.max = max
         self.nuisance = nuisance
-        self.discrete = discrete
         self.range = (min, max)
         self.i = index
 
     def __repr__(self):
-        return "{Name: %s, min: %g, max: %g, nuisance: %d, discrete: %d}" % \
-                ( self.name, self.min, self.max, self.nuisance, self.discrete)
+        return "{Name: %s, min: %g, max: %g, nuisance: %d}" % \
+                ( self.name, self.min, self.max, self.nuisance)
 
 class SamplingOutput(object):
     """
@@ -974,7 +973,7 @@ class UncertaintyPropagation(IS_Output):
             sm_predictions[o] = dset.attrs['SM prediction']
             pd = ParameterDefinition(observable_names[o] + str(kinematics.get(o, '')),
                                      self.samples[:,o].min(), self.samples[:, o].max(),
-                                     nuisance=False, discrete=False, index=o)
+                                     nuisance=False, index=o)
             self.par_defs.append(pd)
             self.priors.append(None)
 

### 2015-03-30 py-eos/optimize.py
[py-eos, tensor] Implement optimization

@@ -93,6 +93,8 @@ if __name__ == '__main__':
     parser.add_argument("--algorithm", required=True)
     parser.add_argument("--analysis-from", help="Specify where the `eos.Analysis` instance shall be read off. Either specify a python module (for example `module.analysis`) or `env` (default) for reading off the environement variables.",
                         type=str, action='store', default='env')
+    parser.add_argument("--analysis-info", help='Print constraints, parameters, and observables',
+                        type=int, default=False)
     parser.add_argument("--initial-guess", nargs='*', help="Vector to seed the optimization (minus signs must be replaced by `n` if notation `0.3e-3` is used). Ex: { 0.1 n0.3e-3 -0.5 }")
     parser.add_argument("--local-algorithm", nargs='?', default=None)
     parser.add_argument("--max-evaluations", type=int, action='store')
@@ -102,7 +104,7 @@ if __name__ == '__main__':
 
     # validate arguments
     args = parser.parse_args()
-    assert len(args.initial_guess) > 2, "invalid specification of the initial guess:" + str(args.initial_guess)
+    assert len(args.initial_guess) > 2, "invalid specification of the initial guess: " + str(args.initial_guess)
 
     ana = make_analysis(args.analysis_from)
     target_density = NLOPT_Wrapper(ana)
@@ -113,7 +115,8 @@ if __name__ == '__main__':
         local_opt = make_opt(target_density, args.local_algorithm, maxeval=args.max_evaluations_local, tol=args.tolerance_local)
         opt.set_local_optimizer(local_opt)
 
-    print target_density.analysis
+    if args.analysis_info:
+        print target_density.analysis
 
     start = np.array([float(x.replace('n','-')) for x in args.initial_guess[1:-1]])
     print "Starting", print_opt(opt), " with f =", target_density.analysis(start), "at"

### 2015-03-31 plot/samplingOutput.py
[plot,tensor] fix sampling on c2pap

@@ -1172,9 +1172,12 @@ class EOS_PYPMC_MCMC(SamplingOutput):
             first_chain = str(chains[0])
 
             #read data
-            samples = hdf5_file['/chain #' + first_chain + '/samples']
+            ds = '/chain #' + first_chain + '/samples'
+            samples = hdf5_file[ds]
             self.chain_length = len(samples)
+            assert self.chain_length > 0, "No samples found in " + ds
 
+            print(self.select, samples.shape)
             #adjust which range is drawn, default: full range
             if self.select[0] is None:
                 if self.skip_initial > 0:

### 2015-03-31 plot/plotScript.py
[plot] bugfix credibility intervals

@@ -727,11 +727,14 @@ class MarginalDistributions:
         # find connected regions
         runs = find_runs(points_95, True)
 
+        # assume fix bin width!
+        bin_width = x[1] - x[0]
+
         # print intervals
         intervals95 = []
         local_modes = []
         for run in runs:
-            intervals95.append([x[run[0]], x[run[1] - 1]])
+            intervals95.append([x[run[0]] - 0.5 * bin_width, x[run[1] - 1] + 0.5 * bin_width ])
             intervals95[-1].append(intervals95[-1][1] - intervals95[-1][0])
             mode_index = run[0] + np.argmax(prob_density[run[0]:run[1]])
             local_modes.append((x[mode_index] + x[mode_index + 1]) / 2.0)
@@ -753,7 +756,8 @@ class MarginalDistributions:
         # print intervals
         intervals68 = []
         for run in runs:
-            intervals68.append([x[run[0]], x[run[1] - 1]])
+            # minimum interval = one bin width
+            intervals68.append([x[run[0]] - 0.5 * bin_width, x[run[1] - 1] + 0.5 * bin_width])
             intervals68[-1].append(intervals68[-1][1] - intervals68[-1][0])
 
         intervals68 = np.array(intervals68)

### 2015-03-31 tensor/paper_plots.py
[tensor] begin unc plot

@@ -57,7 +57,7 @@ def adjust_subplot(fig=None, equal=True):
 class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
                  bandwidth_default=None, two_sigma_color=None, queue_output=True,
-                 crop_outliers=200, local_mode=None, defs={}):
+                 crop_outliers=200, local_mode=None, defs={}, file_type='mcmc'):
         self.f = file
         self.c = color
         self.prob = {}
@@ -72,6 +72,7 @@ class Scenario(object):
         self.local_mode = local_mode
         # dictionary of name:ParameterDefinition
         self.defs = defs
+        self.file_type = file_type
 
     def get_bandwidth(self, par1, par2):
         try:
@@ -172,8 +173,13 @@ class MarginalContours(object):
         cmd_template += ' --2D-bins %d' % scenario.nbins
         if self.max_samples is not None:
             cmd_template += ' --select 0 %d' % self.max_samples
-        cmd_template += ' --contours'
-        cmd_template += ' --mcmc --pypmc --skip-init 0.2'
+        cmd_template += ' --contours  --pypmc'
+        if scenario.file_type == 'mcmc':
+            cmd_template += ' --mcmc --skip-init 0.2'
+        elif scenario.file_type == 'unc':
+            cmd_template += ' --unc'
+        else:
+            raise Exception('Unknown file type' + scenario.file_type)
 
         for p in scenario.defs:
             cmd_template += ' --cut %d %s %s' % (p.i, p.min, p.max)
@@ -186,7 +192,7 @@ class MarginalContours(object):
         for k in self.scen.keys():
             self.margs[k] = plotScript.factory(self.command_template(self.scen[k]))
 
-    def compute_marginal(self, def1, def2, scenario, solution=0):
+    def compute_marginal2D(self, def1, def2, scenario, solution=0):
         # parameter index
         i = def1.i
         j = def2.i
@@ -240,7 +246,7 @@ class MarginalContours(object):
 
         # compute and cache densities
         for s in scenarios:
-            self.compute_marginal(def1, def2, s, solution)
+            self.compute_marginal2D(def1, def2, s, solution)
 
         for k, s in enumerate(scenarios):
             # retrieve original range used to create prob_density
@@ -351,6 +357,10 @@ class MarginalContours(object):
[…]

### 2015-04-01 tensor/paper_plots.py
[tensor/paper_plots] Compute 1D marginal for unc prop

@@ -80,8 +80,17 @@ class Scenario(object):
         except KeyError:
             return self.__bandwidth_default
 
+    def get_bandwidth(self, par1):
+        try:
+            return self.__bandwidth[par1]
+        except KeyError:
+            return self.__bandwidth_default
+
     def set_bandwidth(self, par1, par2, value):
         self.__bandwidth[(par1, par2)] = value
+
+    def set_bandwidth(self, par1, value):
+        self.__bandwidth[par1] = value
 
 class ScenarioComparison(object):
     """Store parameter definitions and bandwidths to compare
@@ -170,14 +179,15 @@ class MarginalContours(object):
         # input file
         cmd_template += ' %s' % scenario.f
 #         cmd_template += ' --pmc-crop-outliers %d' % scenario.crop_outliers
-        cmd_template += ' --2D-bins %d' % scenario.nbins
         if self.max_samples is not None:
             cmd_template += ' --select 0 %d' % self.max_samples
         cmd_template += ' --contours  --pypmc'
         if scenario.file_type == 'mcmc':
             cmd_template += ' --mcmc --skip-init 0.2'
+            cmd_template += ' --2D-bins %d' % scenario.nbins
         elif scenario.file_type == 'unc':
             cmd_template += ' --unc'
+            cmd_template += ' --1D-bins %d' % scenario.nbins
         else:
             raise Exception('Unknown file type' + scenario.file_type)
 
@@ -191,6 +201,24 @@ class MarginalContours(object):
         self.margs = {}
         for k in self.scen.keys():
             self.margs[k] = plotScript.factory(self.command_template(self.scen[k]))
+
+    def compute_marginal1D(self, def1, scenario):
+        i = def1.i
+        m = self.margs[scenario]
+        if m.marginal_modes.has_key(i):
+            return
+
+        bandwidth = self.scen[scenario].get_bandwidth(i)
+        if bandwidth is None:
+            m.use_histogram = True
+        else:
+            m.use_histogram = False
+            m.kde_bandwidth = bandwidth
+
+        if def1.min != def1.max:
+            m.cuts[i] = def1.range
+        m.one_dimensional(i)
+        assert len(m.credibilities[0][0]) == 1, "Found disconnected 1sigma interval\n" + str(m.credibilities[0][0])
 
[…]

### 2015-04-01 plot/plotScript.py
[plotScript] bugfix output of 1D marginal with disconnected interval

@@ -764,7 +764,7 @@ class MarginalDistributions:
         print("Minimal 1 sigma intervals:")
         print(intervals68)
 
-        if len(local_modes) == 1:
+        if len(local_modes) == 1 and len(intervals68) == 1:
             print('x +a -b:')
             print('%g +%g -%g' % (local_modes[0], intervals68[0][1] - local_modes[0], local_modes[0] - intervals68[0][0]))
 

### 2015-04-01 plot/samplingOutput.py
[plot] Add parameter index to ParameterDefinition

@@ -145,12 +145,13 @@ def read_descriptions(file, data_set, npar=None, samples=None):
             priors.append(None)
             par_defs.append(ParameterDefinition('par%d' % i,
                                                 np.min(samples.T[i]),
-                                                np.max(samples.T[i])))
+                                                np.max(samples.T[i]),
+                                                index=i))
     # output from an Analysis includes parameters and their priors
     else:
         f = priorDistributions.PriorFactory()
-        for row in descriptions:
-            par_defs.append(ParameterDefinition(row[0], row[1], row[2], row[3], False))
+        for i, row in enumerate(descriptions):
+            par_defs.append(ParameterDefinition(row[0], row[1], row[2], row[3], index=i))
 
             try:
                 prior_name, prior = f.create(row[4])
@@ -1250,5 +1251,7 @@ class EOS_PYPMC_UNC(SamplingOutput):
                 # get everything up to '@' to remove lengthy options
                 name = obs_ds.attrs['name']
                 name = name[:name.find('@')] + '@' + fixed_name + '= %g' % fixed_values[i]
-                self.par_defs.append(ParameterDefinition(name, np.min(self.samples.T[i]), np.max(self.samples.T[i])))
+                self.par_defs.append(ParameterDefinition(name, np.min(self.samples.T[i]), np.max(self.samples.T[i]),
+                                                         index=i))
             self.priors = [None] * len(fixed_values)
+            self.fixed_values = fixed_values

### 2015-04-01 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex, references] added treatment of B->K* form factors to appendix B and new references for LCSR and lattice calculations

@@
   more details see the text and \refapp{app:theory:inputs}.
+  \todo{update $B\to K^*$ form factors}
 }
@@
   We are grateful to Danny van Dyk for helpful discussions and his support on
-  EOS \cite{EOS} and Chris Bouchard for communications concerning $B\to K$
-  form factors \cite{Bouchard:2013eph}.
+  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
+  Bouchard and Matthew Wingate for communications on their results of $B\to K$
+  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors, 
+  respectively. We thank also David Straub for his support with LCSR results of
+  $B\to K^*$ form factors \cite{Straub:2015ica}.
   C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR''
@@
 the compilation of nuisance parameters and according values, whose uncertainties
-are negligible. Further, we
-adopt the same values for common nuisance parameters of $i)$ the CKM quark-mixing
-matrix, $ii)$ the charm and bottom quark masses in the $\overline{\rm MS}$ scheme,
-and $iii)$ the parameterisation of subleading corrections in $1/m_b$ as
-given in \cite{Beaujean:2013soa}.
-
-The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ depend on
-$B\to K^{(*)}$ form factors and do not receive any other long-distance contribution,
-i.e., they factorize naively. These amplitudes are implemented in {\tt EOS} for
-$B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as given in \cite{Bobeth:2007dw}
-and \cite{Bobeth:2012vn}, respectively, and without the use of form factor relations
-at large and low recoil.
+are negligible. Further, we adopt the same values for common nuisance parameters of
+$i)$ the CKM quark-mixing matrix, $ii)$ the charm and bottom quark masses in the 
+$\overline{\rm MS}$ scheme, and $iii)$ the parameterisation of subleading corrections
+in $1/m_b$ as given in \cite{Beaujean:2013soa}.
+
+The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching
+ratio of $B_s\to \bar\mu\mu$. We adopt recent updates of the $N_f = (2 + 1)$
+FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
+averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.
+More recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and
+$N_f = 2$ \cite{Carrasco:2013zta} are consistent with these averages.
+
+The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
+i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
+are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
+given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively. In the case
+of $B\to K\bar\ell\ell$, we refrain from using respective form factor relations at
+large and low recoil for the tensor and scalar form factors, $f_T$ and $f_0$ in the
+corresponding amplitudes. In the case of $B\to K^*\bar\ell\ell$, we use the scalar
+form factor $A_0$ in the scalar and time-like amplitudes, but apply form factor
+relations in tensor amplitudes for the tensor form factors $T_{1,2,3}$.
 
@@
   Quantity & Prior & Unit & Reference\\
+\hline
+  \multicolumn{4}{c}{$B_s$ decay constant}
+\\
+\hline
+  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
 \hline
@@
 \hline
-  \multicolumn{4}{c}{$B_s$ decay constant}
-\\
-\hline
-  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
+  \multicolumn{4}{c}{$B\to K^*$ form factors}\\
 \hline
@@
 cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}. 
-Contrary to \cite{Beaujean:2013soa}, we do not adapt a
-log-gamma prior for the asymmetric uncertainties but rather a continuous, but
-asymmetric gaussian distribution.
+Contrary to \cite{Beaujean:2013soa}, we do not adapt anymore a log-gamma prior for
+the asymmetric uncertainties but rather a continuous, but asymmetric gaussian distribution.
 The lattice results are given within a slightly different parameterisation necessitating
@@
         \hline
-        $q^2$ [\GeV] & $17$            & $20$            & $23$\\
+        $q^2$ [\GeV$^2$] & $17$            & $20$            & $23$\\
         \hline
@@
         \hline
-        $q^2$ [\GeV]
+        $q^2$ [\GeV$^2$]
              & $17$  & $20$ & $23$ & $17$ & $20$ & $23$ & $17$  & $20$   & $23$ \\
@@
         information (bottom) of lattice points \cite{Bouchard:2013eph} for the
-        vector form factors $f_{0,+,T}(q^2)$ in $B\to K$ transitions.
+        $B\to K$ form factors $f_{0,+,T}(q^2)$.
         \label{tab:btok-lattice}
@@
 
-The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching
-ratio of $B_s\to \bar\mu\mu$. We adopt recent updates of the $N_f = (2 + 1)$
-FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
-averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.
-More recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and
-$N_f = 2$ \cite{Carrasco:2013zta} are consistent with these averages.
+We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
+work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
+(SSE) \cite{Bharucha:2010im}
+\begin{align}
+  \label{eq:SSE-FF-parameterization}
+  F_i(q^2) & =
+  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
+\end{align}
+with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}$
+and two ($k=1,2$) for $i= A_{12}$. The parameters $\alpha_0^i$ correspond to
+$F_i(q^2 = 0)$ and the kinematic constraint
+\begin{align}
+  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,,
+\end{align}
+is used to eliminate $\alpha_0^{A_{12}}$, where the kinematic factor 
+${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
+$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
+given in \cite{Straub:2015ica}.
+
+This parameterization allows us to combine consistently available results
+of form factors from different non-perturbative approaches, namely LCSR's at
+large recoil and lattice at low recoil and implement simultaneously additional
+kinematic constraints. We determine the parameters $\alpha_i^k$
+in a combined fit to form factor predictions of $V, A_{0,1,12}$ from the LCSR  
+\cite{Straub:2015ica} and lattice \cite{Horgan:2013hoa, Horgan:2015vla} calculations,
+including their correlations. Further, we implement the second kinematic constraint 
+\begin{align}
+  \label{eq:A12-constraint-q2max}
+  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
+\end{align}
+at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
+are chosen for all $\alpha_k^i$
+\begin{align}
+  \alpha_0^i & \in [0,\, 1] \,, &
+  \alpha_{1,2}^i & \in [-10,\, 10].
+\end{align}
+The results of the LCSR predictions of the form factors have been provided to us
+directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
+12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12}$, including their $16\times16$
+correlation matrix. In the case of lattice predictions, we proceed as in our
+previous work \cite{Beaujean:2013soa} by generating form factor values of
+$V,\, A_{0,1,12}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
+\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
+see \reftab{tab:btokstar-lattice}.
+
+We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
+versus two parameters only and found that in the latter case lattice form factor
+results influence the fit such that form factors tend to be higher than LCSR
+predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
+setup as it accommodates better LCSR and lattice results.
+
+\begin{table}
+    \renewcommand{\arraystretch}{1.3}
+    \begin{tabular}{c|cc}
+        \hline
+        $q^2$ [\GeV$^2$] & $15$            & $19.21$ \\
+        \hline
+        $V(q^2)$         & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
+        $A_0(q^2)$       & $0.62 \pm 0.03$ & $0.72 \pm 0.03$\\
+        $A_1(q^2)$       & $1.13 \pm 0.05$ & $1.63 \pm 0.07$\\
+        $A_{12}(q^2)$    & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
+        \hline
+    \end{tabular}\\
+    \renewcommand{\arraystretch}{1.0}
+    \vspace{2\smallskipamount}
+    \renewcommand{\arraystretch}{1.3}
+    \begin{tabular}{c|ccccccccc}
+        \hline
+        $q^2$ [\GeV$^2$]
+                & $15$  & $19$ & $15$ & $19$ & $15$ & $19$ & $15$  & $19$ \\
+        \hline
+   $V(15)$      & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010\\
+   $V(19)$      & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093\\
+   $A_0(15)$    & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046\\
+   $A_0(19)$    & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21 \\
+   $A_1(15)$    & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26 \\
+   $A_1(19)$    & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14 \\
+   $A_{12}(15)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79 \\
+   $A_{12}(19)$ & --    & --   & --   & --   & --   & --   & --    & 1.00 \\
+        \hline
+    \end{tabular}
+    \renewcommand{\arraystretch}{1.0}
+    \caption{Reproduction of mean values, uncertainties (top) and correlation
+        information (bottom) of lattice points \cite{Horgan:2015vla} for the
+        $B\to K^*$ form factors $V(q^2)$ and $A_{0,1,12}(q^2)$.
+        \todo{Enter correct numbers from constraint.cc}
+        \label{tab:btokstar-lattice}
+      }
+\end{table}
 

### 2015-04-01 tensor/paper_plots.py
[tensor] first working version of uncertainty plot

@@ -57,7 +57,8 @@ def adjust_subplot(fig=None, equal=True):
 class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
                  bandwidth_default=None, two_sigma_color=None, queue_output=True,
-                 crop_outliers=200, local_mode=None, defs={}, file_type='mcmc'):
+                 crop_outliers=200, local_mode=None, defs={}, file_type='mcmc',
+                 unc_label=''):
         self.f = file
         self.c = color
         self.prob = {}
@@ -73,6 +74,7 @@ class Scenario(object):
         # dictionary of name:ParameterDefinition
         self.defs = defs
         self.file_type = file_type
+        self.unc_label = unc_label
 
     def get_bandwidth(self, par1, par2):
         try:
@@ -91,6 +93,18 @@ class Scenario(object):
 
     def set_bandwidth(self, par1, value):
         self.__bandwidth[par1] = value
+
+class Measurement(object):
+    '''Store info to plot x +a -b for a measurement.'''
+    def __init__(self, lower, central, upper, central_style=dict(), one_sigma_style=None, label=''):
+        self.central = central
+        self.lower = lower
+        self.upper = upper
+        self.central_style = central_style
+        self.one_sigma_style = one_sigma_style
+        if one_sigma_style is None:
+            self.one_sigma_style = self.central_style
+        self.label = label
 
 class ScenarioComparison(object):
     """Store parameter definitions and bandwidths to compare
@@ -386,10 +400,57 @@ class MarginalContours(object):
 
                     P.savefig(self.out('overlay_%d_%d_%s' % (i, self.pars.index(p1) + j + 1, k)))
 
-    def prediction(self, scen):
+    def prediction(self, scen, one_sigma_style={}, two_sigma_style=None):
         '''Plot uncertainty band for one observable'''
+        m = self.margs[scen]
+
         # compute uncertainties
-        pass
+        lower_one_sigma = np.empty(len(m.out.par_defs))
+        upper_one_sigma = np.empty_like(lower_one_sigma)
+        lower_two_sigma = np.empty_like(lower_one_sigma)
+        upper_two_sigma = np.empty_like(lower_one_sigma)
+        mode = np.empty_like(lower_one_sigma)
+        for def1 in m.out.par_defs:
[…]

### 2015-04-01 plot/plotScript.py
[plotScript] guess data format from file name

@@ -1520,6 +1520,22 @@ def factory(cmd_line=None):
                   deterministic_mixture=args.deterministic_mixture)
 
     OutputClass = None
+
+    # try to guess data type from file name
+    types = [args.mcmc, args.emcee, args.nest, args.uncertainty_propagation]
+    matched_types = []
+    if not any(types):
+        matches = 0
+        if 'mcmc' in args.i:
+            matched_types.append(args.mcmc)
+        if 'unc' in args.i:
+            matched_types.append(args.uncertainty_propagation)
+
+        if len(matched_types) > 1:
+            print("Cannot autodetermine the file type from its name")
+        elif len(matched_types) == 1:
+            matched_types[0] = True
+
     if args.mcmc:
         if args.i.endswith('.npy'):
             OutputClass = JahnMCMCOutput

### 2015-04-01 py-eos/unc.py
[tensor,py-eos] rewrite uncertainty propagation
Instructions in `readme.md`!

@@ -22,9 +22,9 @@ class Unc(object):
         self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input, skip_initial=0.0,
                                                    select=select)
 
-        self.fixed_name = args.parameter[0]
+        self.fixed_name = args.fix[0]
 
-        self.results = np.empty((len(self.input.samples), int(args.parameter[-1])))
+        self.results = np.empty((len(self.input.samples), int(args.fix[-1])))
 
         desc = 'descriptions'
         with h5py.File(args.output, 'w') as output_file:
@@ -59,42 +59,53 @@ class Unc(object):
 
     def build_cmd(self, x):
         cmd = 'eos-evaluate --precision 16'
+        if args.eos_integration_points:
+            cmd += ' --integration-points %d' % args.eos_integration_points
         for i, p in enumerate(self.input.par_defs):
             cmd += ' --parameter "' + p.name + '" %.16f' % x[i]
-        cmd += ' --parameter-range %s %s %s %s' % tuple(self.args.parameter)
+        cmd += ' --parameter-range %s %s %s %s' % tuple(self.args.fix)
         for k,v in self.args.kinematics.iteritems():
             cmd += ' --kinematics %s %s' % (k, v)
+        for k,v in self.args.parameter.iteritems():
+            cmd += ' --parameter %s %s' % (k, v)
         cmd += ' --observable "' + self.args.observable + '"'
         return cmd
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(description=__doc__)
 
-    parser.add_argument("--kinematics", nargs='*',
-                        help='''Use it to define kinematics or other options.
-                        Example: --kinematics s_min 1 s_max 6''')
+    parser.add_argument("--eos-integration-points", type=int)
+    parser.add_argument('--fix', nargs=4,
+                        help='EOS parameter name, min, max, npoints. Includes end point!. Example: "Re{cT} -1 1 11')
     parser.add_argument("--input-range", help='The range of input samples used. Example: --input-range 3800 4100', nargs=2)
+    parser.add_argument("--kinematics", nargs='*',
+                        help='''Use it to define kinematics.
+                        Example: --kinematics s_min 1 s_max 6''')
     parser.add_argument("--mcmc-input", help='File name with MCMC samples. Only `chain #0` is used!')
     parser.add_argument('--observable',
[…]

### 2015-04-01 tensor/paper_plots.py
[tensor/paper_plots] First plot of K_FH uncertainty

@@ -425,7 +425,7 @@ class MarginalContours(object):
                        **one_sigma_style)
         P.xlim(m.out.fixed_values[0], m.out.fixed_values[-1])
 
-    def stack_prediction(self, scenarios, measurement, xlabel='', ylabel=''):
+    def stack_prediction(self, scenarios, measurement, xlabel='', ylabel='', legendpos='best'):
         legend_patches = []
         for scen in scenarios:
             s = self.scen[scen]
@@ -433,7 +433,7 @@ class MarginalContours(object):
             two_sigma_style = dict(one_sigma_style)
             two_sigma_style['alpha'] = 0.2
             self.prediction(scen, one_sigma_style, two_sigma_style)
-            legend_patches.append((matplotlib.patches.Patch(color=one_sigma_style['color']),s.unc_label))
+            legend_patches.append((matplotlib.patches.Patch(color=one_sigma_style['color'], alpha=one_sigma_style['alpha']), s.unc_label))
 
         x_range = P.gca().get_xlim()
 
@@ -446,7 +446,7 @@ class MarginalContours(object):
         # http://stackoverflow.com/q/14534130/987623
         patches = [p[0] for p in legend_patches]
         labels = [p[1] for p in legend_patches]
-        P.legend(patches, labels)
+        P.legend(patches, labels, loc=legendpos)
 
         P.xlabel(xlabel)
         P.ylabel(ylabel)
@@ -583,10 +583,11 @@ class Spring2015(object):
             m.one_dimensional(data.shape[1]-1)
             P.savefig(marg.out(s+'_Betrag_' + name))
 
-    def fig_pred(self, file_name):
+    def fig_pred(self, scenarios, measurement, xlabel, ylabel, legendpos='best'):
         '''Plot predictions/postdictions with uncertainty varying one parameter over a fixed range.'''
 
         marg = MarginalContours(self.input_base, self.output_base, max_samples=self.max_samples)
+        '''
         s = 'sm_unc_Bsmumu'
         marg.scen[s] = Scenario(file_name, 'Blue', nbins=25, file_type='unc', bandwidth_default=None,
                                 unc_label=r'$C_9^{NP}=0$')
@@ -600,9 +601,23 @@ class Spring2015(object):
                               xlabel=r'$C_{10}$',
                               ylabel=r'$\mathcal{B}(B_s \to \mu^+ \mu^-)$')
[…]

### 2015-04-02 plot/samplingOutput.py
[samplingOutput] consistently open hdf files read only

@@ -1121,7 +1121,7 @@ class EOS_PYPMC_IS(IS_Output):
     def read_mixture(file, directory):
         import pypmc
 
-        with h5py.File(file, 'r') as file:
+        with open_hdf5(file) as file:
             means = file[directory + '/means'][:]
             covs = file[directory + '/covariances'][:]
             weights = file[directory + '/weights'][:]
@@ -1239,7 +1239,7 @@ class EOS_PYPMC_UNC(SamplingOutput):
     '''Read samples of a single observable computed from parameter samples.'''
 
     def _read(self, *args, **kwargs):
-        with h5py.File(self.input_file_name) as input_file:
+        with open_hdf5(self.input_file_name) as input_file:
             obs_ds = input_file['/observable']
             self.samples = obs_ds[:]
             self.weights = np.ones(len(self.samples))

### 2015-04-02 tensor/paper_plots.py
[tensor] polish uncertainty plots

@@ -31,7 +31,7 @@ def run_command(com):
 def square_figure(size=6):
     return P.figure(figsize=(size, size))
 
-def wide_figure(x_size=8, ratio=4/3.0, left=0.08, right=0.95, top=0.95, bottom=0.15):
+def wide_figure(x_size=8, ratio=4/3.0, left=0.165, right=0.95, top=0.95, bottom=0.145):
     """
     Create a figure with aspect ratio 4:3 and sufficient room for margins
     """
@@ -58,7 +58,7 @@ class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
                  bandwidth_default=None, two_sigma_color=None, queue_output=True,
                  crop_outliers=200, local_mode=None, defs={}, file_type='mcmc',
-                 unc_label=''):
+                 unc_label='', histogram=True):
         self.f = file
         self.c = color
         self.prob = {}
@@ -75,6 +75,7 @@ class Scenario(object):
         self.defs = defs
         self.file_type = file_type
         self.unc_label = unc_label
+        self.histogram = histogram
 
     def get_bandwidth(self, par1, par2):
         try:
@@ -202,8 +203,11 @@ class MarginalContours(object):
         elif scenario.file_type == 'unc':
             cmd_template += ' --unc'
             cmd_template += ' --1D-bins %d' % scenario.nbins
+            cmd_template += ' --use-data-range 0.05'
         else:
             raise Exception('Unknown file type' + scenario.file_type)
+        if not scenario.histogram:
+            cmd_template += ' --use-KDE'
 
         for p in scenario.defs:
             cmd_template += ' --cut %d %s %s' % (p.i, p.min, p.max)
@@ -223,16 +227,22 @@ class MarginalContours(object):
             return
 
         bandwidth = self.scen[scenario].get_bandwidth(i)
-        if bandwidth is None:
-            m.use_histogram = True
+        if m.use_histogram and bandwidth is None:
+                pass
         else:
             m.use_histogram = False
-            m.kde_bandwidth = bandwidth
+            if bandwidth:
+                m.kde_bandwidth = bandwidth
 
         if def1.min != def1.max:
             m.cuts[i] = def1.range
         m.one_dimensional(i)
         assert len(m.credibilities[0][0]) == 1, "Found disconnected 1sigma interval\n" + str(m.credibilities[0][0])
+
[…]

### 2015-04-02 tensor/draft/draft-tensor-op.tex
[tensor/draft] use new plots

@@
 
+%
+% useful variable for multiple same-size plots
+%
+\newlength{\relwidth}
 %--------+---------+---------+---------+---------+---------+---------+---------+
@@
 \begin{figure*}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
+  \setlength{\relwidth}{0.31\textwidth}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
+  \\
+  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
   \\

### 2015-04-02 tensor/paper_plots.py
[tensor] finish unc plot polishing

@@ -593,7 +593,7 @@ class Spring2015(object):
             m.one_dimensional(data.shape[1]-1)
             P.savefig(marg.out(s+'_Betrag_' + name))
 
-    def fig_pred(self, scen_obs, measurement, xlabel, ylabel, yrange=None, legendpos='best'):
+    def fig_pred(self, scen_obs, measurement, xlabel, ylabel, yrange=None, legendpos='upper center'):
         '''Plot predictions/postdictions with uncertainty varying one parameter over a fixed range.'''
 
         marg = MarginalContours(self.input_base, self.output_base, max_samples=self.max_samples)
@@ -617,7 +617,7 @@ class Spring2015(object):
         one_sigma_style = dict(color='grey', alpha=1)
         if not measurement.has_key('sigma_lower'):
             measurement['sigma_lower'] = measurement['sigma_upper']
-        measurement = Measurement(label=r'$\mathrm{LHCb}$',
+        measurement = Measurement(label=r'$\mathrm{LHCb \; 2014}$',
                                   central_style=central_style,
                                   one_sigma_style=one_sigma_style,
                                   central=measurement['central'],
@@ -634,41 +634,38 @@ class Spring2015(object):
         P.savefig(marg.out(scenario_names[0]))
 
     def np_label(self, value):
-        return r'$C_9^{\mathrm{NP}}=' + str(value) + '$'
+        return r'$\Delta C_9=' + str(value) + '$'
 
     def fig_1(self):
         xlabel = r'$C_{T}$'
-        ylabel=r'$\langle F_H \rangle'
-#         FH_yrange = (-0.1, 0.9)
-#         self.fig_pred(scen_obs=[dict(name='ct_K_FH1to6', unc_label=self.np_label(0)),
-#                                 dict(name='ct_c9_1dot1_K_FH1to6', unc_label=self.np_label(-1.1))],
-#                       measurement=dict(central=0.03, sigma_upper=0.036),
-#                       xlabel=xlabel,
-#                       ylabel=ylabel + r'_{[1,6]}$', yrange=FH_yrange,
-#                        legendpos='upper center')
-#
-#         self.fig_pred(scen_obs=[dict(name='ct_K_FH15to22', unc_label=self.np_label(0)),
-#                                 dict(name='ct_c9_1dot1_K_FH15to22', unc_label=self.np_label(-1.1))],
[…]

### 2015-04-29 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] removed comments on R_K measurement, updated first row in scTT5_FH, appendix: no FF-relations in tensor amplitudes of B->K* ll

@@
 $\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
-{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. Beyond the SM,
-lepton-flavor non-universal effects are possible in principle and have been
-discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
-Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
-connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
-$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
-from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
+{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. 
+%Beyond the SM,
+%lepton-flavor non-universal effects are possible in principle and have been
+%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
+%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
+%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
+%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
+%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
 
@@
   \caption{
-    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
-    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
-    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
+    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
+    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
+    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
     coupling $\wilson{T}$. The bands represent the theory uncertainties at
     68\% probability.
-    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
-    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
+    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
+    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
   }
@@
   $\mbox{Re}\,\wilson{T}$
-  & $\quad$ $[-0.31,\, 0.16]$ ($[-0.51,\, 0.34]$) $\quad$
+  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
   & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
@@
   $\mbox{Im}\,\wilson{T}$
-  & $[-0.23,\, 0.24]$ ($[-0.43,\, 0.43]$)
+  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
   & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
@@
   $\mbox{Re}\,\wilson{T5}$
-  & $[-0.24,\, 0.25]$ ($[-0.43,\, 0.44]$)
+  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
   & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
@@
   $\mbox{Im}\,\wilson{T5}$
-  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
+  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
   & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
@@
   $|\wilson{T}|$, $|\wilson{T5}|$
-  & $[0.13,\, 0.42]$ ($[0.04,\, 0.56]$)
+  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
   & \eos{$< 0.25$ ($< 0.35$)}
@@
   & $\wilson{S,\,S',\,P,\,P'}$
-  & $\wilson{S,\,S',\,P,\,P'\,10,\,10'}$
+  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
   \\
@@
    & \quad \times \left(|\wilson{S}-\wilson{S'}|^2 + |\wilson{P}-\wilson{P'}|^2\right)\,.
-\\[0.1cm]
-  \frac{4}{3} J_{6c} & = \todo{???}
+%\\[0.1cm]
+%  \frac{4}{3} J_{6c} & = \todo{???}
 \end{aligned}
@@
 are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
-given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively. In the case
-of $B\to K\bar\ell\ell$, we refrain from using respective form factor relations at
-large and low recoil for the tensor and scalar form factors, $f_T$ and $f_0$ in the
-corresponding amplitudes. In the case of $B\to K^*\bar\ell\ell$, we use the scalar
-form factor $A_0$ in the scalar and time-like amplitudes, but apply form factor
-relations in tensor amplitudes for the tensor form factors $T_{1,2,3}$.
+given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively and we refrain from
+using respective form factor relations at large and low recoil for the tensor and scalar
+$B\to K$ and $B\to K^*$ form factors.
 

### 2015-04-29 plot/plotScript.py
[plotScript] refine 1D marginal console output

@@ -840,7 +840,7 @@ class MarginalDistributions:
             parameter_name = "par"+str(index)
 
         print('')
-        print("%s: x_range = [%g, %g], bins = %d" % (parameter_name, x_min, x_max, self.nBins[index]))
+        print("%d: %s in [%g, %g] with %d bins" % (index, parameter_name, x_min, x_max, self.nBins[index]))
 
         # general array, either from histogramming or from KDE
         probability_array = None

### 2015-04-29 tensor/paper_plots.py
[tensor/paper_plots] switch to libertine font

@@ -684,6 +684,10 @@ if __name__ == '__main__':
     matplotlib.rcParams['text.usetex'] = True
     matplotlib.rcParams['text.latex.unicode'] = True
     matplotlib.rcParams['font.size'] = 22
+    matplotlib.rcParams['text.latex.preamble'] = r'''
+    \usepackage[proportional]{libertine}
+    \usepackage[libertine]{newtxmath}
+    '''
 
     # enlarge ticks
     major = dict(size=8, width=1.4, pad=10)
@@ -696,6 +700,6 @@ if __name__ == '__main__':
 
     f = Spring2015()
     f.figSP()
-#    f.figTT5()
+#     f.figTT5()
 #     f.fig_1()
 #    f.all()

### 2015-04-30 plot/plotScript.py
[plotScript] bugfix in local mode at right boundary

@@ -751,7 +751,7 @@ class MarginalDistributions:
             intervals95.append([x[run[0]] - 0.5 * bin_width, x[run[1] - 1] + 0.5 * bin_width ])
             intervals95[-1].append(intervals95[-1][1] - intervals95[-1][0])
             mode_index = run[0] + np.argmax(prob_density[run[0]:run[1]])
-            local_modes.append((x[mode_index] + x[mode_index + 1]) / 2.0)
+            local_modes.append(x[mode_index] + bin_width / 2.0)
         intervals95 = np.array(intervals95)
         local_modes = np.array(local_modes)
         print("Minimal 2 sigma intervals:")

### 2015-04-30 tensor/draft/draft-tensor-op.tex
[tensor] Unc. prop. for B->K* observables
* update plot script and add plots to draft

@@
   \\
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
-  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
+  \\
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
+  \\
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
+  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
   \caption{

### 2015-04-30 tensor/paper_plots.py

@@ -230,7 +230,7 @@ class MarginalContours(object):
         if m.marginal_modes.has_key(i):
             return
 
-        bandwidth = self.scen[scenario].get_bandwidth(i)
+        bandwidth = self.scen[scenario].get_bandwidth1D(i)
         if m.use_histogram and bandwidth is None:
                 pass
         else:
@@ -440,9 +440,10 @@ class MarginalContours(object):
         # plot measurement first and below the patches
         m = self.margs[scenarios[0]]
         x_range = m.out.fixed_values[0], m.out.fixed_values[-1]
-        P.fill_between(x_range, [measurement.lower] * 2, [measurement.upper] * 2, **measurement.one_sigma_style)
-        P.plot(x_range, [measurement.central] * 2, **measurement.central_style)
-        legend_patches.append((matplotlib.patches.Patch(**measurement.one_sigma_style), measurement.label))
+        if measurement:
+            P.fill_between(x_range, [measurement.lower] * 2, [measurement.upper] * 2, **measurement.one_sigma_style)
+            P.plot(x_range, [measurement.central] * 2, **measurement.central_style)
+            legend_patches.append((matplotlib.patches.Patch(**measurement.one_sigma_style), measurement.label))
 
         for scen in scenarios:
             s = self.scen[scen]
@@ -599,7 +600,7 @@ class Spring2015(object):
             m.one_dimensional(data.shape[1]-1)
             P.savefig(marg.out(s+'_Betrag_' + name))
 
-    def fig_pred(self, scen_obs, measurement, xlabel, ylabel, yrange=None, legendpos='upper center'):
+    def fig_pred(self, scen_obs, measurement, ylabel, xlabel=r'$C_{T}$', yrange=None, legendpos='upper center'):
         '''Plot predictions/postdictions with uncertainty varying one parameter over a fixed range.'''
 
         marg = MarginalContours(self.input_base, self.output_base, max_samples=self.max_samples)
@@ -621,14 +622,15 @@ class Spring2015(object):
         central_style = dict(color='black', linewidth=matplotlib.rcParams['axes.linewidth'],
                              linestyle='solid', alpha=1)
         one_sigma_style = dict(color='grey', alpha=1)
-        if not measurement.has_key('sigma_lower'):
[…]

### 2015-04-30 plot/merge.py
[merge.py] fix bug with single chain and cut off

@@ -116,13 +116,14 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
     # count chains copied
     nchains_valid = 0
-    valid_files = []
+    valid_file_chains = []
 
     with h5py.File(output_file_name, "w") as output_file:
         for file_name in input_files:
             print("merging %s" % file_name)
             with h5py.File(file_name, 'r') as input_file:
                 nchains_in_file = len(input_file['/'].keys())
+                valid_chains = []
 
                 for i in range(nchains_in_file):
                     # check agreement
@@ -132,13 +133,16 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
                     if invalid_chain(input_file, i, cut_off, format='pypmc'):
                         continue
+                    else:
+                        valid_chains.append(i)
 
                     # copy data
                     for g in groups:
                         if not single_chain:
                             input_file.copy('/chain #%d' % i + g, output_file, name='/chain #%d' % nchains_valid + g)
                     nchains_valid += 1
-                valid_files.append(file_name)
+                if valid_chains:
+                    valid_file_chains.append((file_name, valid_chains))
 
         # compress into one big chain
         if single_chain:
@@ -155,17 +159,17 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
             # loop over valid input files
             nchain = 0
-            for j, file_name in enumerate(valid_files):
+            for j, (file_name, chains) in enumerate(valid_file_chains):
                 with h5py.File(file_name, 'r') as input_file:
                     # copy descriptions only once
                     if j == 0:
                         s = first + '/descriptions'
                         input_file.copy(s, output_file, name=s)
                     # loop over chains
-                    for i, c in enumerate(input_file['/'].iterkeys()):
+                    for c in chains:
                         for g, ds in zip(data_groups, data_sets):
                             old_length = nchain * new_samples
-                            data = input_file[c + g[0]][first_index::thin]
+                            data = input_file['chain #%d/' % c + g[0]][first_index::thin]
 
                             # 1D versus 2D assignment
                             if g[0] == '/log_posterior':

### 2015-05-05 plot/plotScript.py
[plotScript] add whitespace

@@ -837,7 +837,7 @@ class MarginalDistributions:
         # extract parameter name
         parameter_name = self.tr.to_tex(self.out.par_defs[index].name)
         if parameter_name == '':
-            parameter_name = "par"+str(index)
+            parameter_name = "par" + str(index)
 
         print('')
         print("%d: %s in [%g, %g] with %d bins" % (index, parameter_name, x_min, x_max, self.nBins[index]))

### 2015-05-05 tensor/draft/draft-tensor-op.tex
[tensor/draft] Update uncertainty plots
* rescale J_* by B meson lifetime
* increase font size
* expand figure caption

@@
   \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
-  \caption{
-    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
-    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
-    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
-    coupling $\wilson{T}$. The bands represent the theory uncertainties at
-    68\% probability.
-    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
-    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
-  }
+  \caption{ \eos{The sensitivity to the tensorial coupling
+      $\wilson{T}$ of $F_H$ [first row], ${\cal B}$ [second row] for
+      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
+      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ for $B^0 \to K^{*0}
+      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
+      last two rows, the observables are normalized by the lifetime of
+      the $B$ meson for easier comparison with the branching
+      rations. The bands represent the theory uncertainties at 68\%
+      and 95\% probability.  For comparison, two sets of bands are
+      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
+      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
+      latest 68\% uncertainty reported by LHCb (grey) if a measurement
+      is available.}  }
   \label{fig:FHvsCT}

### 2015-05-05 tensor/paper_plots.py

@@ -213,8 +213,9 @@ class MarginalContours(object):
         if not scenario.histogram:
             cmd_template += ' --use-KDE'
 
-        for p in scenario.defs:
-            cmd_template += ' --cut %d %s %s' % (p.i, p.min, p.max)
+        if not scenario.file_type == 'unc':
+            for p in scenario.defs:
+                cmd_template += ' --cut %d %s %s' % (p.i, p.min, p.max)
 
         return cmd_template.split()
 
@@ -238,8 +239,8 @@ class MarginalContours(object):
             if bandwidth:
                 m.kde_bandwidth = bandwidth
 
-        if def1.min != def1.max:
-            m.cuts[i] = def1.range
+        # if def1.min != def1.max:
+        #     m.cuts[i] = def1.range
         m.one_dimensional(i)
         assert len(m.credibilities[0][0]) == 1, "Found disconnected 1sigma interval\n" + str(m.credibilities[0][0])
 
@@ -600,7 +601,8 @@ class Spring2015(object):
             m.one_dimensional(data.shape[1]-1)
             P.savefig(marg.out(s+'_Betrag_' + name))
 
-    def fig_pred(self, scen_obs, measurement, ylabel, xlabel=r'$C_{T}$', yrange=None, legendpos='upper center'):
+    def fig_pred(self, scen_obs, measurement, ylabel, xlabel=r'$C_{T}$', yrange=None,
+                 legendpos='upper center', rescale=None):
         '''Plot predictions/postdictions with uncertainty varying one parameter over a fixed range.'''
 
         marg = MarginalContours(self.input_base, self.output_base, max_samples=self.max_samples)
@@ -616,6 +618,15 @@ class Spring2015(object):
             marg.scen[name] = Scenario(self.input('unc_' + name + '.hdf5'), **kw)
             scenario_names.append(name)
         marg.read_data()
+
+        # rescale every sample by a constant
+        # this requires updating cached min/max values, too.
+        if rescale:
+            for k,v in marg.margs.iteritems():
+                v.out.samples *= rescale
+                v.min *= rescale
+                v.max *= rescale
+
         marg.compute_marginal1D_all(scenario_names)
[…]

### 2015-05-19 tensor/lattice-synthetic-data/parse.py
[tensor] update lattice parse

@@ -70,6 +70,15 @@ def match_qsquared(indices, qsquared):
         res[v] = qsquared[k[pos1 + 4:]]
     return res
 
+def kinematics(qsquared):
+    s = '{{ '
+    for i, qsq in enumerate(qsquared):
+        if i > 0 and ((i % 3) == 0):
+            s += '\n'
+        s += 'Kinematics{{ "s", ' + str(qsq) + ' }}, '
+    s += ' }},'
+    return s
+
 def eosify(arr):
     '''Return string representation easier for pasting into eos'''
     s = repr(arr)
@@ -111,7 +120,7 @@ def plot_ff(tensor=False):
 
     # output data
     print('q^2')
-    print(repr(qsquared))
+    print(kinematics(qsquared))
     print('mean')
     print(eosify(mean))
     print("std_dev with systematic uncertainty")

### 2015-05-19 plot/plotScript.py
[plotScript] add `--par-indices` to select subset of parameters
* no more matplotlib rcparam setting
* `tight_layout` for 1D plots

@@ -15,9 +15,6 @@ import matplotlib.pyplot as P
 import numpy as np
 import priors as priorDistributions
 
-matplotlib.rcParams['text.usetex'] = False #not bool(commands.getstatusoutput('which latex')[0]) #requires LaTex installation
-matplotlib.rcParams['text.latex.unicode'] = True
-
 #get the figtree module, assume its directory is in the python path
 try:
     import figtree
@@ -1325,7 +1322,7 @@ class MarginalDistributions:
         ###
         # perplexity. Avoid NaN due to log(0) by log(1)=0
         ###
-        entr = - np.sum( w * np.log(w.filled(1.0)))
+        entr = -np.sum( w * np.log(w.filled(1.0)))
         perp = np.exp(entr) / n
 
         ###
@@ -1346,7 +1343,8 @@ class MarginalDistributions:
         P.xlabel('weight')
         self.pdf_file.savefig()
 
-    def plot(self):
+    def plot(self, index_list=None):
+        '''index_list: If given, choose which parameters to plot'''
 
         # output file name
         ext = ''
@@ -1387,6 +1385,7 @@ class MarginalDistributions:
                 for x in self.single_1D:
                     P.figure()
                     one_dim(x)
+                    P.tight_layout()
                     if n_single_plots > 1:
                         pdf_file.savefig()
                         P.close()
@@ -1413,7 +1412,8 @@ class MarginalDistributions:
         nCols = len(self.out.par_defs)
 
         #take indices only from this list
-        index_list = np.arange(nCols, dtype='int')
+        if index_list is None:
+            index_list = np.arange(nCols, dtype='int')
 
         #filter out nuisance parameters
         if not self.use_nuisance:
@@ -1427,7 +1427,8 @@ class MarginalDistributions:
         print("Plotting %d 1D marginal distributions" % len(index_list))
         for column in index_list:
                 P.figure()
-                if one_dim(column):
+                if one_dim(column) is not False:
+                    P.tight_layout()
                     self.pdf_file.savefig()
                 P.close()
         if self.one_dimensional_only:
@@ -1442,9 +1443,8 @@ class MarginalDistributions:
 
                 #aspect ratio 1/1
                 P.figure(figsize=(6,6))
-                plotted = two_dim(par1, par2)
-                P.tight_layout()
-                if plotted is not False:
+                if two_dim(par1, par2) is not False:
+                    P.tight_layout()
                     print("plot #%d" % counter)
[…]

### 2015-05-19 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] updates concerning B->K* form factor treatments

--- 2015-04-30 tensor/draft/draft-tensor-op.tex
@@
   \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
-  \caption{
-    \eos{The sensitivity of $F_H^\mu$ [upper row], ${\cal B}(B^+ \to K^+
-    \bar\mu\mu)$ [middle row] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
-    [lower row] integrated over low- and high-$q^2$ bins to the tensorial
-    coupling $\wilson{T}$. The bands represent the theory uncertainties at
-    68\% probability.
-    For comparison two values of $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9}
-    = -1.1$ (red) are shown together with the 68\% measurements of LHCb (grey).}
-  }
+  \caption{ The sensitivity to the tensorial coupling
+      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
+      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
+      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
+      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
+      last two rows, the observables are normalized by the lifetime of
+      the $B$ meson for easier comparison with the branching
+      ratios. The bands represent the theory uncertainties at 68\%
+      and 95\% probability.  For comparison, two sets of bands are
+      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
+      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
+      latest 68\% uncertainty reported by LHCb (grey) if a measurement
+      is available. }
   \label{fig:FHvsCT}
@@
     & $A_{\rm FB}^\mu$
-    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
+    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
     & $F_{H}^\mu$
@@
 \hline
-\multirow{3}{*}{${B\to K^*}$ {form factors}}
-    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
-    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
-    & $V$, $A_1$, $A_{12}$
-              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
+\multirow{2}{*}{${B\to K^*}$ {form factors}}
+    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
+    & $V,\,A_{0,1,2},\, T_{1,2,3}$
+    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
 \hline
@@
 \renewcommand{\arraystretch}{1.0}
-\caption{\label{tab:observables} List of all observables in the various
-  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
-  respective kinematics and experiments that provide the measurements.
-  Lattice results of $B\to K$ form factors are used to constrain parameters
-  of their $q^2$-dependence,
-  and theoretical constraints on $B\to K^*$ form factors are included. For
-  more details see the text and \refapp{app:theory:inputs}.
-  \todo{update $B\to K^*$ form factors}
+\caption{\label{tab:observables} List of all observables of the various
+  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
+  and experiments that provide the measurements. LCSR and lattice results of
+  $B\to K^{(*)}$ form factors are used to constrain parameters of their
+  $q^2$-dependence.
+  For more details see the text and \refapp{app:theory:inputs}.
 }
@@
 
-Eventually we also explore the behaviour of derived constraints with respect
-to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
-this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
+Eventually we also explore the behaviour of derived constraints with respect to
+destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
+For this purpose we include also the branching ratio and the rate CP asymmetry
 of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the
@@
   \\
+  \hline \hline
+  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
+  & 1
+  &
+  & SM
+  &
+  \\
   \hline
@@
      The 68\% probability intervals of not yet measured angular observables in
-     $B\to K^*\bar\mu\mu$ integrated over
-     $q^2$ bins at low- and high-$q^2$ for several new physics scenarios respecting
-     all the considered experimental constraints. The SM prediction with respective
+     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$ 
+     for several new physics scenarios respecting all the considered experimental
+     constraints. The SM prediction with respective
      uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
@@
   Quantity & Prior & Unit & Reference\\
-\hline
+\hline \hline
   \multicolumn{4}{c}{$B_s$ decay constant}
@@
   $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
-\hline
+\hline \hline
   \multicolumn{4}{c}{$B\to K$ form factors}\\
@@
   $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
-\hline
+\hline \hline
   \multicolumn{4}{c}{$B\to K^*$ form factors}\\
@@
     \renewcommand{\arraystretch}{1.0}
-    \caption{Reproduction of mean values, uncertainties (top) and correlation
+    \caption{Mean values, uncertainties (top) and correlation
         information (bottom) of lattice points \cite{Bouchard:2013eph} for the
@@
 \end{align}
-with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}$
-and two ($k=1,2$) for $i= A_{12}$. The parameters $\alpha_0^i$ correspond to
-$F_i(q^2 = 0)$ and the kinematic constraint
+with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1}, 
+T_{1,23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
+correspond to $F_i(q^2 = 0)$ and the kinematic constraints
 \begin{align}
-  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,,
+  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,, &
+  T_1(0) & = T_2(0)
 \end{align}
-is used to eliminate $\alpha_0^{A_{12}}$, where the kinematic factor
+are used to eliminate $\alpha_0^{A_{12}, T_2}$, where the kinematic factor
 ${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
@@
 of form factors from different non-perturbative approaches, namely LCSR's at
-large recoil and lattice at low recoil and implement simultaneously additional
+large recoil and lattice at low recoil and implement simultaneously the
 kinematic constraints. We determine the parameters $\alpha_i^k$
-in a combined fit to form factor predictions of $V, A_{0,1,12}$ from the LCSR
-\cite{Straub:2015ica} and lattice \cite{Horgan:2013hoa, Horgan:2015vla} calculations,
+in a combined fit to form factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the
+LCSR \cite{Straub:2015ica} and of $V, A_{0,1,12},T_{1,2,23}$ from the lattice
+\cite{Horgan:2013hoa, Horgan:2015vla} calculations,
 including their correlations. Further, we implement the second kinematic constraint
@@
   \alpha_0^i & \in [0,\, 1] \,, &
-  \alpha_{1,2}^i & \in [-10,\, 10].
+  \alpha_{1}^i & \in [-2,\, 2]  \,, &
+  \alpha_{2}^i & \in [-3,\, 3] \,.
 \end{align}
@@
 directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
-12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12}$, including their $16\times16$
-correlation matrix. In the case of lattice predictions, we proceed as in our
+12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12},\, T_{1,2,3}$, including their $28\times 28$
+covariance matrix. \todo{In the case of lattice predictions, we proceed as in our
 previous work \cite{Beaujean:2013soa} by generating form factor values of
-$V,\, A_{0,1,12}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
+$V,\, A_{0,1,12},\, T_{1,2,3}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
 \cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
-see \reftab{tab:btokstar-lattice}.
-
-We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
+see \reftab{tab:btokstar-lattice}.}
+
+\todo{We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
 versus two parameters only and found that in the latter case lattice form factor
@@
 predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
-setup as it accommodates better LCSR and lattice results.
-
-\begin{table}
-    \renewcommand{\arraystretch}{1.3}
-    \begin{tabular}{c|cc}
-        \hline
-        $q^2$ [\GeV$^2$] & $15$            & $19.21$ \\
-        \hline
-        $V(q^2)$         & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
-        $A_0(q^2)$       & $0.62 \pm 0.03$ & $0.72 \pm 0.03$\\
-        $A_1(q^2)$       & $1.13 \pm 0.05$ & $1.63 \pm 0.07$\\
-        $A_{12}(q^2)$    & $1.02 \pm 0.06$ & $1.47 \pm 0.08$\\
-        \hline
-    \end{tabular}\\
-    \renewcommand{\arraystretch}{1.0}
-    \vspace{2\smallskipamount}
-    \renewcommand{\arraystretch}{1.3}
-    \begin{tabular}{c|ccccccccc}
-        \hline
-        $q^2$ [\GeV$^2$]
-                & $15$  & $19$ & $15$ & $19$ & $15$ & $19$ & $15$  & $19$ \\
-        \hline
-   $V(15)$      & 1.00  & 0.93 & 0.73 & 0.58 & 0.48 & 0.23 & 0.13  & 0.010\\
-   $V(19)$      & --    & 1.00 & 0.87 & 0.41 & 0.45 & 0.24 & 0.059 & 0.093\\
-   $A_0(15)$    & --    & --   & 1.00 & 0.28 & 0.34 & 0.32 & 0.010 & 0.046\\
-   $A_0(19)$    & --    & --   & --   & 1.00 & 0.78 & 0.30 & 0.36  & 0.21 \\
-   $A_1(15)$    & --    & --   & --   & --   & 1.00 & 0.71 & 0.22  & 0.26 \\
-   $A_1(19)$    & --    & --   & --   & --   & --   & 1.00 &-0.025 & 0.14 \\
-   $A_{12}(15)$ & --    & --   & --   & --   & --   & --   & 1.00  & 0.79 \\
-   $A_{12}(19)$ & --    & --   & --   & --   & --   & --   & --    & 1.00 \\
-        \hline
-    \end{tabular}
-    \renewcommand{\arraystretch}{1.0}
-    \caption{Reproduction of mean values, uncertainties (top) and correlation
-        information (bottom) of lattice points \cite{Horgan:2015vla} for the
-        $B\to K^*$ form factors $V(q^2)$ and $A_{0,1,12}(q^2)$.
-        \todo{Enter correct numbers from constraint.cc}
-        \label{tab:btokstar-lattice}
-      }
-\end{table}
+setup as it accommodates better LCSR and lattice results.}
 

### 2015-05-20 plot/plotScript.py
[plotScript] Add `--trace` and `--2D-with-others` options
* revive trace plot in favor of `evolution`
* plot 1 parameter against all others
* reformat according to PEP8 with pycharm

@@ -1,7 +1,7 @@
 #!/usr/bin/env python
 # -*- coding: utf-8 -*-
 
-from __future__ import print_function
+from __future__ import print_function, division
 
 import commands
 import matplotlib
@@ -15,7 +15,7 @@ import matplotlib.pyplot as P
 import numpy as np
 import priors as priorDistributions
 
-#get the figtree module, assume its directory is in the python path
+# get the figtree module, assume its directory is in the python path
 try:
     import figtree
 except:
@@ -39,14 +39,14 @@ def histOutline(dataIn, *args, **kwargs):
     (histIn, binsIn) = np.histogram(dataIn, *args, **kwargs)
     stepSize = binsIn[1] - binsIn[0]
 
-    bins = np.zeros(len(binsIn)*2 + 2, dtype=np.float)
-    data = np.zeros(len(binsIn)*2 + 2, dtype=np.float)
+    bins = np.zeros(len(binsIn) * 2 + 2, dtype=np.float)
+    data = np.zeros(len(binsIn) * 2 + 2, dtype=np.float)
     for bb in range(len(binsIn)):
-        bins[2*bb + 1] = binsIn[bb]
-        bins[2*bb + 2] = binsIn[bb] + stepSize
+        bins[2 * bb + 1] = binsIn[bb]
+        bins[2 * bb + 2] = binsIn[bb] + stepSize
         if bb < len(histIn):
-            data[2*bb + 1] = histIn[bb]
-            data[2*bb + 2] = histIn[bb]
+            data[2 * bb + 1] = histIn[bb]
+            data[2 * bb + 2] = histIn[bb]
 
     bins[0] = bins[1]
     bins[-1] = bins[-2]
@@ -54,6 +54,7 @@ def histOutline(dataIn, *args, **kwargs):
     data[-1] = 0
 
     return ((bins, data), (binsIn, histIn))
+
 
 def find_hist_level(histo):
     """
@@ -85,6 +86,7 @@ def find_hist_level(histo):
     level_95 = bin_counts[index]
 
     return (level_68, level_95)
+
 
 def find_credibility_region_indices(histo, alpha):
     """
@@ -134,16 +136,9 @@ def find_credibility_region_indices(histo, alpha):
 
     return indices
 
-#    print(max_count, max_index)
-#    print(h)
-#    print(h[indices])
-#    print(sum(h[indices]))
[…]

### 2015-05-20 py-eos/mcmc.py
[py-eos/mcmc] Bugfix: log posterior was identical for all samples in batch

@@ -116,7 +116,7 @@ class MCMC_Sampler(object):
 
             # history has rank 2 but 2nd rank can be ignored
             file[self.target_dset].resize(new_length, axis=0)
-            file[self.target_dset][iterations:new_length] = self.chain.target_values[:][0,:]
+            file[self.target_dset][iterations:new_length] = self.chain.target_values[:][:,0]
 
             file[self.sample_dset].resize(new_length, axis=0)
             file[self.sample_dset][iterations:new_length] = self.chain.history[:]

### 2015-05-21 plot/plotScript.py
[plotScript] bugfix gof off-by-one error when point at right edge
* remove debug gof output

@@ -561,10 +561,8 @@ class MarginalDistributions:
         (prob_overcover, prob_undercover) = self.find_hist_limits(probability_array, density=posterior_level)
         sigmas_overcover = Gaussian.ppf((prob_overcover + 1) / 2.0)  #, location=0, scale=1)
         sigmas_undercover = Gaussian.ppf((prob_undercover + 1) / 2.0)  #, location=0, scale=1)
-        print(value, prob_overcover * 100, prob_undercover * 100, sigmas_overcover, sigmas_undercover)
-        print(
-            "GoF: point (%s) at most at the %g%% level (at least at the %g%% level). On the Gaussian scale, that's at %g [%g] sigmas" %
-            (value, prob_overcover * 100, prob_undercover * 100, sigmas_overcover, sigmas_undercover))
+        print("GoF: point (%s) at most at the %g%% level [at least: %g%%]. " % (value, prob_overcover * 100, prob_undercover * 100, ) +
+              "On the Gaussian scale, that's at %g [%g] sigmas." % (sigmas_overcover, sigmas_undercover))
 
     def __bandwidth(self, samples, index):
         """
@@ -852,9 +850,16 @@ class MarginalDistributions:
                                                       normed=True, range=(x_min, x_max))
             P.plot(hist_outline[0], hist_outline[1], label=legend_label, **marginal_style)
 
+            # this would be the code to replace the workaround
+            # `histOutline` but I don't know how to turn off filling
+            # of the histogram with old versions of matplotlib
+            # y_values, x_values, _ = P.hist(samples, bins=self.nBins[index], weights=self.out.weights,
+            #                                normed=True, range=(x_min, x_max), label=legend_label, **marginal_style)
+            # x_values, y_values = np.asanyarray(x_values), np.asanyarray(y_values)
+
             # data for contours
             x_values, y_values = hist_normal
-
+            assert len(x_values) == len(y_values) + 1, "x values (%d) and y values (%d) should differ in length by one" % (len(x_values), len(y_values))
         else:  #use KDE
             mesh_points = np.linspace(x_min, x_max, self.nBins[index])
 
@@ -902,12 +907,11 @@ class MarginalDistributions:
             except KeyError:
                 pass
             else:
-                # calculate index of bin containing the point
-                bin_index = np.floor((value - x_min) / (x_max - x_min) * len(x_values))
-                # special case: value at right edge
-                bin_index = min(bin_index, len(x_values) - 1)
-
-                posterior_level = y_values[bin_index]
[…]

### 2015-05-21 plot/plotScript.py
[plotScript] Switch colors of global mode and gof, beautify trace
global mode, gof:

* gof in salmon not well visible with `gist_heat_r` map
* surveyed various sequential color maps, `gist_heat_r` remains the most appealing

trace plot:
* bugfix color cycle: wasn't used before
* add horizontal line for gof if given

@@ -916,12 +916,12 @@ class MarginalDistributions:
                 self.print_gof(value, y_values, posterior_level)
 
                 # indicate GOF point
-                P.scatter(value, 0, marker='*', s=200, color='salmon')
+                P.scatter(value, 0, marker='*', s=200, color='blue')
 
         # plot global mode for single chains
         global_mode_index = self.out.get('global_mode_index')
         if global_mode_index is not None:
-            P.scatter(self.out._modes[global_mode_index][index], 0, marker='^', s=200)
+            P.scatter(self.out._modes[global_mode_index][index], 0, marker='^', s=200, color='salmon')
 
         # plot the prior in the same plot
         if self.plot_prior and self.out.priors[index] is not None:
@@ -1149,7 +1149,7 @@ class MarginalDistributions:
                 posterior_level = orig_probability_array[bin_index]
                 self.print_gof(value, probability_array, posterior_level)
 
-                P.plot(value[0], value[1], marker='+', color='salmon', markersize=15, markeredgewidth=3)
+                P.plot(value[0], value[1], marker='+', color='blue', markersize=15, markeredgewidth=4)
 
         #set labels, avoid empty parameter names
         x_label = self.tr.to_tex(self.out.par_defs[par1].name)
@@ -1194,7 +1194,6 @@ class MarginalDistributions:
         # use a "qualitative colormap" from http://matplotlib.org/users/colormaps.html
         cmap = P.get_cmap('spectral')
         color_cycle = [cmap(i) for i in np.linspace(0, 1, n_chains)]
-        ax.set_color_cycle(color_cycle)
 
         def save():
             ax.set_xscale(scale)
@@ -1208,6 +1207,7 @@ class MarginalDistributions:
         #print out mode info
         for par in index_list:
             ax.clear()
+            ax.set_color_cycle(color_cycle)
 
             #set labels, avoid empty parameter names
             y_label = self.tr.to_tex(self.out.par_defs[par].name)
@@ -1234,9 +1234,20 @@ class MarginalDistributions:
 
             ax.set_ylim(y_min, y_max)
 
+            if self.gof_point is not None:
+
+                try:
+                    # read out value in this this dimension
+                    value = self.gof_point[par]
+                except KeyError:
+                    pass
+                else:
+                    P.axhline(value, linestyle='--', color='black', label='gof')
+
             save()
         # posterior
         ax.clear()
+        ax.set_color_cycle(color_cycle)
         ax.set_ylabel('log posterior')
 
         for c in range(n_chains):

### 2015-06-22 plot/samplingOutput.py
[samplingOutput] select more than one chain for mcmc parses correctly

@@ -1212,12 +1212,12 @@ class EOS_PYPMC_MCMC(SamplingOutput):
             n_chains_parsed = 1
 
             # read all remaining chains
-            for chain in chains[1:]:
+            for i, chain in enumerate(chains[1:]):
                 c = hdf5_file['/chain #%d' % chain + '/samples']
-                destination_slice = np.s_[destination_slice.stop:destination_slice.stop + self.reduced_lengths[chain]]
-                c.read_direct(merged_chains, slices[chain], destination_slice)
-                tau[chain, :] = autocorrelation(merged_chains[destination_slice])
-                hdf5_file['/chain #%d' % chain + "/log_posterior"].read_direct(merged_posteriors, slices[chain], destination_slice)
+                destination_slice = np.s_[destination_slice.stop:destination_slice.stop + self.reduced_lengths[i + 1]]
+                c.read_direct(merged_chains, slices[i + 1], destination_slice)
+                tau[i + 1, :] = autocorrelation(merged_chains[destination_slice])
+                hdf5_file['/chain #%d' % chain + "/log_posterior"].read_direct(merged_posteriors, slices[i + 1], destination_slice)
                 n_chains_parsed += 1
 
         print('Merged %d chains, total number of samples: %d' % (n_chains_parsed, len(merged_chains)))

### 2015-06-22 plot/plotScript.py
[plotScript] add --thin argument for MCMC

@@ -1608,6 +1608,8 @@ def factory(cmd_line=None):
     parser.add_argument('--skip-initial',
                         help="Allows to skip the first fraction of iterations. Ignored if --seelect MIN MAX given.",
                         action='store', default=0)
+    parser.add_argument('--thin',
+                        help="Thin every chain by selecting only every Nth sample", default=1)
     parser.add_argument('--trace', help="Trace plot of individual chains, either on the 'log' or 'linear' scale",
                         action='store_true')
     parser.add_argument('--uncertainty-propagation', help="Parse uncertainty-propagation data", action='store_true')
@@ -1636,6 +1638,7 @@ def factory(cmd_line=None):
         select=[int(x) if x is not None else x for x in args.select],
         # mcmc
         chains=args.chains, prerun=args.prerun, skip_initial=float(args.skip_initial),
+        thin=int(args.thin),
         # pmc
         queue_output=args.pmc_queue_output, crop_outliers=int(args.pmc_crop_outliers),
         equal_weights=args.pmc_equal_weights or args.pmc_proposal,

### 2015-06-22 plot/samplingOutput.py

@@ -1155,6 +1155,7 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         self.chains = kwargs.get('chains', None)
         self.prerun = kwargs.get('prerun', True)
         self.skip_initial = kwargs.get('skip_initial', 0.2)
+        self.thin = kwargs.get('thin', 1)
 
         self.single_chain = None
         if hasattr(self.chains, '__len__') and len(self.chains) == 1:
@@ -1182,8 +1183,8 @@ class EOS_PYPMC_MCMC(SamplingOutput):
                     c = hdf5_file['/chain #%d' % chain + '/samples']
                 except KeyError:
                     raise KeyError('"chain #%d' % chain + '/samples" not found')
-                slices.append(self.source_slice(c))
-                self.reduced_lengths.append(slices[-1].stop - slices[-1].start)
+                slices.append(self.source_slice(c, self.thin))
+                self.reduced_lengths.append((slices[-1].stop - slices[-1].start) // slices[-1].step)
                 assert self.reduced_lengths[-1] > 0, "Empty chain %d" % chain
 
             #read data
@@ -1236,7 +1237,7 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         # S = np.cov(self.samples, rowvar=0)
         # np.savetxt('Kstar-FF-cov.txt', S, header=par_defs[0].name + ' ' + par_defs[-1].name)
 
-    def source_slice(self, chain):
+    def source_slice(self, chain, thin):
         #adjust which range is drawn, default: full range
         first, last = None, None
         if self.select[0] is None:
@@ -1251,7 +1252,7 @@ class EOS_PYPMC_MCMC(SamplingOutput):
         else:
             last = min(self.select[1], len(chain))
 
-        return slice(first, last)
+        return np.s_[first:last:thin]
 
     def individual_chains(self):
         '''Return list of individual chains.'''

### 2015-06-22 plot/plotScript.py
[plotScript, samplingOutput] fix bug with nonaligned thinning

@@ -1609,7 +1609,7 @@ def factory(cmd_line=None):
                         help="Allows to skip the first fraction of iterations. Ignored if --seelect MIN MAX given.",
                         action='store', default=0)
     parser.add_argument('--thin',
-                        help="Thin every chain by selecting only every Nth sample", default=1)
+                        help="Thin every chain by selecting only every Nth sample", default=1, type=int)
     parser.add_argument('--trace', help="Trace plot of individual chains, either on the 'log' or 'linear' scale",
                         action='store_true')
     parser.add_argument('--uncertainty-propagation', help="Parse uncertainty-propagation data", action='store_true')
@@ -1638,7 +1638,7 @@ def factory(cmd_line=None):
         select=[int(x) if x is not None else x for x in args.select],
         # mcmc
         chains=args.chains, prerun=args.prerun, skip_initial=float(args.skip_initial),
-        thin=int(args.thin),
+        thin=args.thin,
         # pmc
         queue_output=args.pmc_queue_output, crop_outliers=int(args.pmc_crop_outliers),
         equal_weights=args.pmc_equal_weights or args.pmc_proposal,

### 2015-06-22 plot/samplingOutput.py

@@ -2,7 +2,7 @@
 Provide consistent interface to parsing sampling output from various algorithms, and in various formats.
 
 """
-from __future__ import print_function
+from __future__ import division, print_function
 
 import priors as priorDistributions
 
@@ -1184,7 +1184,8 @@ class EOS_PYPMC_MCMC(SamplingOutput):
                 except KeyError:
                     raise KeyError('"chain #%d' % chain + '/samples" not found')
                 slices.append(self.source_slice(c, self.thin))
-                self.reduced_lengths.append((slices[-1].stop - slices[-1].start) // slices[-1].step)
+                # for 250 samples and thin = 100, take 3 samples at indices 0, 100, 200 => ceil(2.5) = 3
+                self.reduced_lengths.append(int(np.ceil((slices[-1].stop - slices[-1].start) / (slices[-1].step))))
                 assert self.reduced_lengths[-1] > 0, "Empty chain %d" % chain
 
             #read data

### 2015-06-22 py-eos/vb.py
[vb] Use new thinning option of plotScript

@@ -86,7 +86,8 @@ class VB(object):
     def _init_mcmc(self):
         output = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input,
                                                chains=self.args.chains,
-                                               skip_initial=self.args.skip_initial)
+                                               skip_initial=self.args.skip_initial,
+                                               thin=int(self.args.thin) if self.args.thin else 1)
         K_g = self.args.components_per_group
         print("K_g:", K_g)
 
@@ -102,12 +103,7 @@ class VB(object):
         else:
             raise ArgumentError('Invalid initialization method: "%s"' % self.args.init_method)
 
-        if self.args.thin:
-            samples = output.samples[::self.args.thin]
-        else:
-            samples = output.samples
-
-        self.vb = GaussianInference(samples, initial_guess=initial_guess, components=K_g,
+        self.vb = GaussianInference(output.samples, initial_guess=initial_guess, components=K_g,
                                     W0=np.diag([1e20] * len(self.analysis.priors)))
 
     def _indices(self):

### 2015-06-23 tensor/paper_plots.py
[tensor/paper_plots] Format code according to PEP8 with pycharm

@@ -19,6 +19,7 @@ sys.path.append(os.path.realpath('../plot'))
 import plotScript
 from plotScript import ParameterDefinition
 
+
 def run_command(com):
     import commands
 
@@ -28,10 +29,12 @@ def run_command(com):
 
     return output
 
+
 def square_figure(size=6):
     return P.figure(figsize=(size, size))
 
-def wide_figure(x_size=8, ratio=4/3.0, left=0.165, right=0.95, top=0.95, bottom=0.145):
+
+def wide_figure(x_size=8, ratio=4 / 3.0, left=0.165, right=0.95, top=0.95, bottom=0.145):
     """
     Create a figure with aspect ratio 4:3 and sufficient room for margins
     """
@@ -45,6 +48,7 @@ def wide_figure(x_size=8, ratio=4/3.0, left=0.165, right=0.95, top=0.95, bottom=
 
     return ax
 
+
 def adjust_subplot(fig=None, equal=True):
     # 1:1 aspect ratio, but only if called before adjusting edges
     if equal:
@@ -53,6 +57,7 @@ def adjust_subplot(fig=None, equal=True):
     if fig is None:
         fig = P.gcf()
     fig.subplots_adjust(left=0.2, right=0.95, bottom=0.15)
+
 
 class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
@@ -79,7 +84,7 @@ class Scenario(object):
 
     def get_bandwidth(self, par1, par2):
         try:
-            return self.__bandwidth[(par1,par2)]
+            return self.__bandwidth[(par1, par2)]
         except KeyError:
             return self.__bandwidth_default
 
@@ -95,8 +100,10 @@ class Scenario(object):
     def set_bandwidth1D(self, par1, value):
         self.__bandwidth[par1] = value
 
+
 class Measurement(object):
     '''Store info to plot x +a -b for a measurement.'''
+
     def __init__(self, lower, central, upper, central_style=dict(), one_sigma_style=None, label=''):
         self.central = central
         self.lower = lower
@@ -106,6 +113,7 @@ class Measurement(object):
         if one_sigma_style is None:
             self.one_sigma_style = self.central_style
         self.label = label
+
 
 class ScenarioComparison(object):
     """Store parameter definitions and bandwidths to compare
@@ -118,6 +126,7 @@ class ScenarioComparison(object):
     Could be a sequence of (pairs of) ParameterDefinition. Pairs would be
     used for a comparison of individual modes
     """
+
[…]

### 2015-06-23 py-eos/mcmc.py
[mcmc] simplify initialization

@@ -113,27 +113,17 @@ class MCMC_Sampler(object):
         valid_args = ['uniform', 'fixed']
         assert args.initial_values[0] in valid_args, \
         '--initial-values must begin with one of ' + str(valid_args) + ': ' + str(args.initial_values)
-        err = ValueError('Invalid argument for choosing initial values: ' + str(args.initial_values))
-        if len(args.initial_values) == 1:
-            if args.initial_values[0] == 'uniform':
-                start = self.draw_uniform_in_support()
-                # log_target(start) must not be -inf!
-                while self.analysis(start) == -np.inf:
-                    start[:] = self.draw_uniform_in_support()
-            elif args.initial_values[0] == 'fixed':
-                start = self.fixed_initial_values(args)
-            else:
-                raise err
+
+        if args.initial_values[0] == 'uniform':
+            start = self.draw_uniform_in_support()
+            # log_target(start) must not be -inf!
+            while self.analysis(start) == -np.inf:
+                start[:] = self.draw_uniform_in_support()
+        elif args.initial_values[0] == 'fixed':
+            start = self.fixed_initial_values(args)
         else:
-            # expect list
-            assert isinstance(args.initial_values, list)
+            ValueError('Invalid argument for choosing initial values: ' + str(args.initial_values))
 
-            if args.initial_values[0] == 'fixed':
-                start = self.fixed_initial_values(args)
-            else:
-                raise err
-
-        print('initial values (' + args.initial_values[0] + '):')
         for i, (prior, v) in enumerate(zip(self.analysis.priors, start)):
             print(i,":", prior.name, v)
             assert (v >= prior.range_min) and (v <= prior.range_max),\
@@ -214,8 +204,8 @@ class MCMC_Sampler(object):
             total_accept += last_accept
             last_accept_rate = last_accept / self.update
             total_accept_rate = total_accept / (iterations + self.update)
-            print("Acceptance rate in chunk %d: %4.2f%%, in total:  %4.2f%%" %
-                  (i, last_accept_rate * 100, total_accept_rate * 100))
+            print("Acceptance rate in chunk %d: %4.2f%%, in total:  %4.2f%%. Covar. scale factor: %g" %
+                  (i, last_accept_rate * 100, total_accept_rate * 100, self.chain.covar_scale_factor))
             try:
                 self.chain.adapt()
             except np.linalg.LinAlgError:
@@ -275,7 +265,7 @@ if __name__ == '__main__':
[…]

### 2015-06-23 tensor/draft/draft-tensor-op.tex
[tensor/draft] updated values for tensor and scalar scenario, added A_FB's for B->K* ll, other small changes

@@
 \affiliation{
+  \todo{neue Adresse}
   Excellence Cluster Universe,
@@
   The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
-  provides a lepton-forward-backward asymmetry $A_{\rm FB}^\ell$ and a flat
-  term $F_H^\ell$ that are both suppressed in the standard model and very
-  sensitive to nonstandard tensorial and scalar contributions. We use latest
-  experimental results for $\ell = \mu$ in combination with $B_s\to \bar\mu\mu$
-  to derive stronger model-independent constraints on tensorial and scalar
-  effective couplings and determine their impact on $B\to K^*\bar\mu\mu$
-  angular observables. Most notably, the measurement of $F_H^\mu$ provides
+  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
+  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
+  nonstandard tensorial and scalar contributions are enhanced with respect
+  to vectorial ones. We use latest experimental results for $\ell = \mu$ in
+  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent 
+  constraints on tensorial and scalar effective couplings and determine their 
+  impact on not yet measured angular observables in 
+  $B\to K^*\bar\mu\mu$, which feature the same suppression of vectorial couplings. 
+  Most notably, the measurement of $F_H^\mu$ provides
   constraints on (pseudo-)scalar couplings and their chirality-flipped
@@
 are presented for several model-independent scenarios in \refsec{sec:results}.
-Technical details of the angular observables in $B\to K^* \bar\ell\ell$ and the
+Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
+branching fraction of $B_s\to \bar\mu\mu$ and the
 treatment of theory uncertainties are relegated to appendices.
@@
 In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
-\begin{align}
+\begin{equation}
   \label{eq:Heff}
-  {\cal L}_{\rm eff} & =
-   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, V_{tb}^{} V_{ts}^\ast
-       \sum_{\ell = e, \mu,\tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i + \text{h.c.}
-\end{align}
+\begin{aligned}
+  {\cal L}_{\rm eff}  =
+   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
+      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
+ \\ & +
+       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
+\end{aligned}
+\end{equation}
 the most general dimension-six flavor-changing operators $\Op_i$ mediating
@@
 
-The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
+The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
 (NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
@@
 All other Wilson coefficients are numerically suppressed or zero:
-$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
-{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$.
+$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
+{\cal O}(m_b^2/m_W^2)$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
 %Beyond the SM,
@@
 of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
-which in principle could also give additional $\cos\theta_\ell$ dependence
-to the angular distribution~\refeq{eq:ang-distr}, however, currently there is
-no solid estimate available for this source of SM background.
+which will modify the simple $\cos\theta_\ell$ dependence
+of the angular distribution~\refeq{eq:ang-distr}, however, currently there is
+no solid estimate available for this source of SM background\footnote{The leading
+QED corrections to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
+corresponding effects in $B\to K \bar\ell\ell$.}.
 
@@
     & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
+    & $A_{\rm FB}^\mu$
+    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
     & $A_{\rm CP}^\mu$
@@
 it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
-\bar\ell\ell$, integrated over low and high $q^2$. The details of the numerical
+\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
 input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
@@
 destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
-For this purpose we include also the branching ratio and the rate CP asymmetry
-of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the
-imaginary parts of vectorial couplings.
+For this purpose we include also the branching ratio, the lepton forward-backward
+asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
+additional constraints on the real and imaginary parts of vectorial couplings.
 
@@
 As a matter of the fact there are no discrepancies between the latest measurements
-for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ and
+for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in 
+$B^+ \to K^+ \bar\mu\mu$ and
 their tiny SM predictions. Thus our main objective is the derivation of stronger
@@
 also interference effects with new physics in vectorial couplings. Finally, we
-conclude this section with postdictions of the allowed ranges of the yet not
-measured angular observables in $B\to K^*\bar\mu\mu$ given all other experimental
-constraints.
-\todo{Perhaps give also postdictions for $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$}
+conclude this section with postirior predictions of the allowed ranges of the yet
+not measured angular observables in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in 
+$B_s\to\bar\mu\mu$ given all other experimental constraints.
+
+\todo{Explain special initialisation of Markov chains at fixed point in parameter
+space in order to avoid other local modes in subspace of nuisance parameters.
+What would be appropriate place to do so?}
 
@@
   & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
-  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
+  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
   \\
@@
   & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
-  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
+  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
   \\[0.1cm]
@@
   & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
-  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
+  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
   \\
@@
   & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
-  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
+  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
   \\
@@
   & \eos{$< 0.25$ ($< 0.35$)}
-  & \eos{$< 0.30$ ($< 0.45$)}
+  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
   \\
@@
      \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
-     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
-     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
+     also complex-valud new physics contributions to $\wilson{9,\,10}$.
   }
@@
 the constraints become tighter when utilising all observables in
-\reftab{tab:observables}, mainly due to the branching ratio of $B\to K^{*}
-\bar\mu\mu$. The latter stronger bounds are driven by the new lattice
+\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio of $B\to K^{*}
+\bar\mu\mu$ to tensorial couplings (see also \reffig{fig:FHvsCT}). The latter 
+stronger bounds are driven by the new lattice
 results of $B\to K^*$ form factors that yield too high predictions compared
@@
 constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
-constrained. In this scenario, the measurements of $A_{\rm FB}^\mu$ does not pose
-constraints due to vanishing scalar couplings and we find that the rate
-CP-asymmetries $A_{\rm CP}$ of $B\to K^{(*)} \bar\mu\mu$ do not provide
-constraints, therefore omitting them.
+constrained. In this scenario, the measurements of $A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$ 
+does not pose constraints due to vanishing scalar couplings.
 
 Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
-by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-7,\, 7]$,
-($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
+by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$,
+($i = 9,10$) in order to access the stability of the bounds
 against destructive interference. In this case, $F_H^\mu$ by itself still provides
-bounds \eos{$|\wilson{T,\,T5}| < 0.5\,(0.8)$} at 68\% (95\%) probability that are
+bounds on $|\wilson{T,\,T5}|$ that are
 weakened by a factor of two since $F_H^\mu$ does not pose constraints on
@@
 are taken into account, the potential destructive effects of new physics
-in $\wilson{9,\,10}$ become reduced and one recovers almost the same
-constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
+in $\wilson{9,\,10}$ become reduced and almost the same constraints on $\wilson{T,\,T5}$
+are recovered, as shown in \reftab{tab:cTT5:1-dimCLs}.
 In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
@@
 \subsection{Scalar couplings \label{sec:scalar}}
-
-Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
-kinematic suppression --- see \refeq{eq:FH-dependence} --- in the complementary
-manner $(\wilson{i} + \wilson{i'})$, with $i = S,\, P$, to the branching ratio
-$B_s\to \bar\mu\mu$, which provides only constraints on $(\wilson{i} - \wilson{i'})$.
-Most notably, we find that the current measurement of $F_H^\mu$ does constrain
-the orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination with
-$\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound for the first time the moduli of
-all four couplings.
-
-The according four-parameter fit for real-valued scalar couplings to the data of
-$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
-regions in the $(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
-\reffig{fig:scalar}. The combination of $\overline{\cal B}(B_s \to \bar\mu\mu)$
-and $F_H^\mu$ does not change when including the data of ${\cal B}$'s of $B\to
-K^{(*)}\bar\mu\mu$ --- remember that $A_{\rm FB}^\mu$ requires interference of
-scalar with tensorial couplings. Quantitatively, the constraint from $\overline{\cal B}
-(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor five}
-stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
 
@@
   \caption{
-    \eos{
-    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$
-    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green)
-    and their combination with other data in \reftab{tab:observables} as well as
-    $\wilson[NP]{10} \in [-1,\, 9]$, $\wilson[NP]{10'} \in [-5,\,5]$ (red)
+    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
+    from $i)$ only $F_H^\mu$~(blue), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ 
+    (green) and $iii)$ their combination with other data in \reftab{tab:observables} 
+    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red)
     at 68\% (darker) and 95\% (lighter) probability. The constraints on
-    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
-    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
-    }
+    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$, 
+    apart from a small shift of the contours by $(+0.2,\, +0.15)$.
   }
@@
 
+\begin{table*}
+  \renewcommand{\arraystretch}{1.3}
+%\resizebox{\textwidth}{!}{
+  \begin{tabular}{c|ccc}
+  \hline
+  data set
+  & only $F_H^\mu$
+  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
+  & all
+  \\
+  set of couplings
+  & $\wilson{S,\,S',\,P,\,P'}$
+  & $\wilson{S,\,S',\,P,\,P'}$
+  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
+  \\
+  \hline \hline
+  $\mbox{Re}(\wilson{S} - \wilson{S'})$
+  & $\quad$ $-$ $\quad$
+  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
+  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
+  \\
+  $\mbox{Im}(\wilson{S} - \wilson{S'})$
+  & $\quad$ $-$ $\quad$
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
+  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
+  \\[0.1cm]
+  $\mbox{Re}(\wilson{S} + \wilson{S'})$
+  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
+  & $-$
+  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
+  \\
+  $\mbox{Im}(\wilson{S} + \wilson{S'})$
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $-$
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  \\[0.1cm]
+  $\mbox{Re}(\wilson{P} - \wilson{P'})$
+  & $-$
+  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
+  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
+  \\
+  $\mbox{Im}(\wilson{P} - \wilson{P'})$
+  & $-$
+  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
+  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
+  \\[0.1cm]
+  $\mbox{Re}(\wilson{P} + \wilson{P'})$
+  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
+  & $-$
+  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
+  \\
+  $\mbox{Im}(\wilson{P} + \wilson{P'})$
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $-$
+  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  \\
+  \hline
+  \end{tabular}
+%}
+  \renewcommand{\arraystretch}{1.0}
+  \caption{
+     \label{tab:cSP:1-dimCLs}
+     The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
+     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
+     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
+     \reftab{tab:observables} and additional new physics contributions to 
+     $\wilson{9,\, 9',\, 10,\,10'}$.
+  }
+\end{table*}
+
+Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
+kinematic suppression --- see \refeq{eq:FH-dependence} --- in the complementary
+manner $(\wilson{i} + \wilson{i'})$ to the branching ratio
+$\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only $(\wilson{i} - \wilson{i'})$,
+where $i = S,\, P$.
+Most notably, we find that the current measurement of $F_H^\mu$ does constrain
+the orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of $F_H^\mu$ and
+$\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound for the first time the moduli of
+all four couplings.
+
+The according four-parameter fit for complex-valued scalar couplings to the data of
+$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
+regions in the $\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
+\reffig{fig:scalar} and similarly for $\mbox{Im}(\wilson{i} \pm \wilson{i'})$. These 
+bounds do not change when including all other data in \reftab{tab:observables}, since
+the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensorial
+couplings and other observables are not very sensitive to scalar
+couplings. Quantitatively, the constraint from $\overline{\cal B}
+(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor four to five}
+stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
+
 Interference terms of $\wilson{P,\,P'}$ with vectorial couplings might weaken
-bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
+these bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
 $(\wilson{10} - \wilson{10'})$ --- compare \refeq{eq:Br-Bsmumu:time0} --- and
 for $F_H^\ell$ similarly $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw},
-which are suppressed by factors $m_\ell/M_{B_s}$ and $m_\ell/\sqrt{q^2}$,
+which are suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
 respectively. However, due to the large SM contribution of $\wilson[SM]{10}
@@
 $F_H^\mu$, $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$
-their combination, even allowing new physics in $\wilson{10,\, 10'}$ in
-\reftab{tab:cSP:1-dimCLs}. Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
+their combination with all the other observables in \reftab{tab:observables}, 
+even allowing new physics in vectorial couplings 
+$\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
+\todo{uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$}. 
+Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
 alone can bound all four complex-valued scalar couplings, however their
@@
 
-\begin{table*}
-  \renewcommand{\arraystretch}{1.3}
-  %\resizebox{\textwidth}{!}{
-  \begin{tabular}{c|ccc}
-  \hline
-  data set
-  & only $F_H^\mu$
-  & only $\overline{\cal B}(B_s \to \bar\mu\mu)$
-  & all
-  \\
-  set of couplings
-  & $\wilson{S,\,S',\,P,\,P'}$
-  & $\wilson{S,\,S',\,P,\,P'}$
-  & $\wilson{S,\,S',\,P,\,P',\,9,\,9',\,10,\,10'}$
-  \\
-  \hline \hline
-  $\mbox{Re}(\wilson{S} - \wilson{S'})$
-  & $\quad$ $-$ $\quad$
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
-  \\
-  $\mbox{Im}(\wilson{S} - \wilson{S'})$
-  & $\quad$ $-$ $\quad$
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
-  \\[0.1cm]
-  $\mbox{Re}(\wilson{S} + \wilson{S'})$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  & $-$
-  & \eos{$[-0.3,\, 0.4]$ ($[-0.6,\, 0.7]$)}
-  \\
-  $\mbox{Im}(\wilson{S} + \wilson{S'})$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  & $-$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  \\[0.1cm]
-  $\mbox{Re}(\wilson{P} - \wilson{P'})$
-  & $-$
-  & \eos{$[0.06,\, 0.20]$  ($[0.02,\, 0.25]$)}
-  & \eos{$[-0.10,\, 0.10]$ ($[-0.18,\, 0.18]$)}
-  \\
-  $\mbox{Im}(\wilson{P} - \wilson{P'})$
-  & $-$
-  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
-  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
-  \\[0.1cm]
-  $\mbox{Re}(\wilson{P} + \wilson{P'})$
-  & \eos{$[-0.2,\, 0.6]$ ($[-0.5,\, 0.9]$)}
-  & $-$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  \\
-  $\mbox{Im}(\wilson{P} + \wilson{P'})$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  & $-$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
-  \\
-  \hline
-  \end{tabular}
-%}
-  \renewcommand{\arraystretch}{1.0}
+\begin{figure*}
+  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
+  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
   \caption{
-     \label{tab:cSP:1-dimCLs}
-     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ --- 1D-marginalized
-     at 65\% (95\%) probability --- when using measurements of $i)$ only $F_H^\mu$,
-     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
-     \reftab{tab:observables} allowing also for new physics contributions to
-     $\wilson{10,\,10'}$ with \eos{uniform prior $\mbox{Re}\,\wilson[NP]{10} \in [-1,\, 9]$,
-     $\mbox{Im}\,(\wilson[NP]{10})$ and $\mbox{Re},\mbox{Im}\,(\wilson[NP]{10'}) \in [-5,\, 5]$}.
-  }
-\end{table*}
+    \eos{
+    Constraints on real-valued [left] and complex-valued [right] scalar couplings
+    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
+    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
+    at 68\% (darker) and 95\% (lighter) probability when marginalising
+    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
+    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
+    For comparison the according constraints from all data when keeping
+    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
+    at 68\% (darker) and 95\% (lighter) probability.
+    }
+  }
+  \label{fig:scalar:SM-EFT}
+\end{figure*}
 
@@
 constrains (4 parameters) \todo{finish, describe \reffig{fig:scalar:SM-EFT}}
-
-\begin{figure*}
-  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
-  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
-  \caption{
-    \eos{
-    Constraints on real-valued [left] and complex-valued [right] scalar couplings
-    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
-    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
-    at 68\% (darker) and 95\% (lighter) probability when marginalising
-    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
-    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
-    For comparison the according constraints from all data when keeping
-    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
-    at 68\% (darker) and 95\% (lighter) probability.
-    }
-  }
-  \label{fig:scalar:SM-EFT}
-\end{figure*}
 

### 2015-06-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added missing numbers to table for TT5 scenario

@@
 
-\preprint{EOS-2014-??, FLAVOUR(267104)-ERC-??}
+\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-??}
 
@@
   & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
-  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
+  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
   & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
@@
   & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
-  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
+  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
   & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
@@
   & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
-  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
+  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
   & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
@@
   & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
-  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
+  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
   & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
@@
   & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
-  & \eos{$< 0.25$ ($< 0.35$)}
+  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
   & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
@@
      for several new physics scenarios respecting all the considered experimental
-     constraints. The SM prediction with respective
-     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
+     constraints. The SM prior predictives are given too, where ``$\simeq 0$'' 
+     indicates zero in the considered
      approximation, see text for more explanations.

### 2015-06-26 tensor/draft/draft-tensor-op.tex
[plot,tensor] Replace scSP plots in draft
* contour_two accepts linestyle
* each scenario gets different linestyle

--- 2015-05-19 tensor/draft/draft-tensor-op.tex
@@
 \begin{figure*}
-  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
-%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
-  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
-  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
+  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,2}
+%  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
+  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
+  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
   \caption{

### 2015-06-26 plot/plotScript.py

@@ -623,7 +623,7 @@ class MarginalDistributions:
         print(np.array(local_modes))
 
     def contours_two(self, x_range, y_range, densities, desired_levels=None,
-                     color='blue', grid=True, line=False,
+                     color='blue', grid=True, line=None,
                      alpha=(1, 0.5, 0.3, 0.1, 0.05)):
         """
         Plot several filled 2D contours
@@ -649,7 +649,7 @@ class MarginalDistributions:
             Bool; superimpose grid a major locators.
 
         :param line:
-            Bool; ``True`` only plots contour line, ``False`` fills the contour.
+            String; ``None`` fills the contour, anything else considered a matplotlib linestyle
 
         :param alpha:
             Transparency of multiple contours. With default values,
@@ -682,9 +682,7 @@ class MarginalDistributions:
         extent = [x_range[0], x_range[1], y_range[0], y_range[1]]
 
         artist = None
-        if line:
-            artist = P.contour(densities, levels[1:-1], colors=color, extent=extent)
-        else:
+        if line is None:
             # give all colors explicitly
             colors = [color] * (len(levels) - 1)
             colors.append('white')
@@ -696,6 +694,8 @@ class MarginalDistributions:
 
             for i, zc in enumerate(reversed(artist.collections[1:])):
                 P.setp(zc, alpha=alpha[i])
+        else:
+            artist = P.contour(densities, levels[1:-1], colors=color, extent=extent, linestyles=line)
 
         # add grid lines for easier visual comparison
         P.grid(grid)

### 2015-06-26 tensor/paper_plots.py

@@ -56,14 +56,14 @@ def adjust_subplot(fig=None, equal=True):
 
     if fig is None:
         fig = P.gcf()
-    fig.subplots_adjust(left=0.2, right=0.95, bottom=0.15)
+    fig.subplots_adjust(left=0.25, right=0.95, bottom=0.15)
 
 
 class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
                  bandwidth_default=None, two_sigma_color=None, queue_output=True,
-                 crop_outliers=200, local_mode=None, defs={}, file_type='mcmc',
-                 unc_label='', histogram=True):
+                 crop_outliers=200, local_mode=None, defs={},
+                 unc_label='', histogram=True, linestyle='solid'):
         self.f = file
         self.c = color
         self.prob = {}
@@ -78,9 +78,9 @@ class Scenario(object):
         self.local_mode = local_mode
         # dictionary of name:ParameterDefinition
         self.defs = defs
-        self.file_type = file_type
         self.unc_label = unc_label
         self.histogram = histogram
+        self.linestyle = linestyle
 
     def get_bandwidth(self, par1, par2):
         try:
@@ -206,23 +206,26 @@ class MarginalContours(object):
         cmd_template = ''
         # input file
         cmd_template += ' %s' % scenario.f
-        #         cmd_template += ' --pmc-crop-outliers %d' % scenario.crop_outliers
         if self.max_samples is not None:
             cmd_template += ' --select 0 %d' % self.max_samples
         cmd_template += ' --contours  --pypmc'
-        if scenario.file_type == 'mcmc':
+        if 'mcmc' in scenario.f:
             cmd_template += ' --mcmc --skip-init 0.2'
             cmd_template += ' --2D-bins %d' % scenario.nbins
-        elif scenario.file_type == 'unc':
+        elif 'unc' in scenario.f:
             cmd_template += ' --unc'
             cmd_template += ' --1D-bins %d' % scenario.nbins
             cmd_template += ' --use-data-range 0.05'
+        elif 'vb' in scenario.f:
+            cmd_template += ' --pmc-crop-outliers %d' % scenario.crop_outliers
+            cmd_template += ' --2D-bins %d' % scenario.nbins
+            cmd_template += ' --determ'
         else:
-            raise Exception('Unknown file type' + scenario.file_type)
[…]

### 2015-06-26 tensor/draft/draft-tensor-op.tex
[tensor] Add scSP plots with new colors and b&w compatibility

@@
 \begin{figure*}
-  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,2}
+  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
 %  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
@@
     The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
-    from $i)$ only $F_H^\mu$~(blue), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ 
-    (green) and $iii)$ their combination with other data in \reftab{tab:observables} 
-    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red)
+    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
+    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
+    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
     at 68\% (darker) and 95\% (lighter) probability. The constraints on

### 2015-06-26 tensor/paper_plots.py

@@ -344,9 +344,9 @@ class MarginalContours(object):
             density, xrange, yrange = self.__density_cache[(par_indices_i[k], par_indices_j[k], s, solution)]
             for line in [None, self.scen[s].linestyle]:
                 artist = self.margs[s].contours_two(xrange, yrange, density,
-                                                    color=self.scen[s].c, line=line, grid=True,
+                                                    color=self.scen[s].c if line is None else 'black', line=line, grid=True,
                                                     desired_levels=desired_levels,
-                                                    alpha=self.contour_alpha)
+                                                    alpha=self.contour_alpha if line is None else 0.8)
 
         if SM_point:
             P.plot(self.sm_point.get(def1.name, 0.), self.sm_point.get(def2.name, 0.), **self.sm_point_style)
@@ -561,20 +561,8 @@ class Spring2015(object):
         # scenarios
         ###
 
-        s = 'scSP_Bsmumu'
-        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), '#006600',
-                                nbins=300, linestyle='dashed')
-        #                                         local_mode=[[-0.348441713,   3.787226592, -4.420530192],
-        #                                                     [ 0.5021320352, -4.568457245,  4.25129282]])
-        marg.scen[s].set_bandwidth(0, 2, 0.015)
-        marg.scen[s].set_bandwidth(2, 6, 0.008)
-        marg.scen[s].set_bandwidth(4, 6, 0.015)
-
-        # indices of S,S' and P,P'
-        marg.scen[s].spind = [(0, 2), (4, 6)]
-
         s = 'scSP_FH'
-        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), '#2966B8',
+        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), '#848484',
                                 nbins=300, linestyle='dotted')
         #                                         local_mode=[[-0.348441713,   3.787226592, -4.420530192],
         #                                                     [ 0.5021320352, -4.568457245,  4.25129282]])
@@ -585,8 +573,20 @@ class Spring2015(object):
         # indices of S,S' and P,P'
[…]

### 2015-06-26 tensor/paper_plots.py
[tensor] analyse imaginary parts in scSP*

@@ -571,7 +571,8 @@ class Spring2015(object):
         marg.scen[s].set_bandwidth(4, 6, 0.025)
 
         # indices of S,S' and P,P'
-        marg.scen[s].spind = [(0, 2), (4, 6)]
+        marg.scen[s].spind = [(0, 2), (4, 6)] # real
+        # marg.scen[s].spind = [(1, 3), (5, 7)] # imaginary
 
         s = 'scSP_Bsmumu'
         marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), '#2E64FE',
@@ -583,13 +584,16 @@ class Spring2015(object):
         marg.scen[s].set_bandwidth(4, 6, 0.015)
 
         # indices of S,S' and P,P'
-        marg.scen[s].spind = [(0, 2), (4, 6)]
+        marg.scen[s].spind = [(0, 2), (4, 6)] # real
+        # marg.scen[s].spind = [(1, 3), (5, 7)] # imaginary
 
         s = 'sc910SP_K_KstarBR_Bsmumu'
         marg.scen[s] = Scenario(os.path.join(marg.input_base, 'vb_' + s + '.hdf5'), '#FE2E2E',
                                 nbins=300, crop_outliers=500)
         # indices of S,S' and P,P'
-        marg.scen[s].spind = [(8, 10), (12, 14)]
+        marg.scen[s].spind = [(8, 10), (12, 14)] # real
+        # marg.scen[s].spind = [(9, 11), (13, 15)] # imaginary
+
         marg.scen[s].set_bandwidth(marg.scen[s].spind[0][0], marg.scen[s].spind[0][1], 0.025) # +-
         marg.scen[s].set_bandwidth(marg.scen[s].spind[0][0], marg.scen[s].spind[1][0], 0.055) # ++
         marg.scen[s].set_bandwidth(marg.scen[s].spind[0][1], marg.scen[s].spind[1][1], 0.015) # --
@@ -631,7 +635,7 @@ class Spring2015(object):
                 ind_in_file = v.spind[i // 2][i % 2]
                 m.fixed_1D_binning = False
                 m.use_histogram = False
-                m.kde_bandwidth = 0.01
+                m.kde_bandwidth = 0.05
                 m.nBins[ind_in_file] = 200
 
                 m.one_dimensional(ind_in_file)

### 2015-07-02 plot/merge.py
[plot] Fix merge with thinning

@@ -1,7 +1,7 @@
 #! /usr/bin/env python
 '''Merge multiple input files into one output file.'''
 
-from __future__ import print_function
+from __future__ import division, print_function
 import commands
 import glob
 import h5py
@@ -116,8 +116,8 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
     # count chains copied
     nchains_valid = 0
-    n_samples_total = 0
     valid_file_chains = []
+    n_samples_total = 0
 
     with h5py.File(output_file_name, "w") as output_file:
         for file_name in input_files:
@@ -125,6 +125,7 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
             with h5py.File(file_name, 'r') as input_file:
                 nchains_in_file = len(input_file['/'].keys())
                 valid_chains = []
+                n_samples = []
 
                 for i in range(nchains_in_file):
                     # check agreement
@@ -134,7 +135,9 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
                         continue
                     else:
                         valid_chains.append(i)
-                        n_samples_total += int( (1 - skip_initial) * input_file['/chain #%d/samples' % i].len())
+                        # for 250 samples and thin = 100, take 3 samples at indices 0, 100, 200 => ceil(2.5) = 3
+                        n_samples.append(int(np.ceil(int( (1 - skip_initial) * input_file['/chain #%d/samples' % i].len()) / thin)))
+                        n_samples_total += n_samples[-1]
 
                     # copy data
                     for g in groups:
@@ -142,7 +145,7 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
                             input_file.copy('/chain #%d' % i + g, output_file, name='/chain #%d' % nchains_valid + g)
                     nchains_valid += 1
                 if valid_chains:
-                    valid_file_chains.append((file_name, valid_chains))
+                    valid_file_chains.append((file_name, valid_chains, n_samples))
 
         # compress into one big chain
         if single_chain:
@@ -155,17 +158,16 @@ def merge_pypmc(output_file_name, search='mcmc_*.hdf5', input_files=None,
 
             # loop over valid input files
             old_length = 0
-            for j, (file_name, chains) in enumerate(valid_file_chains):
+            for j, (file_name, chains, n_samples) in enumerate(valid_file_chains):
                 with h5py.File(file_name, 'r') as input_file:
                     # copy descriptions only once
[…]

### 2015-07-02 py-eos/unc.py
[py-eos,tensor] unc.py now accepts importance samples in addition to MCMC

@@ -16,31 +16,39 @@ hdf5_subdirectory = '/unc'
 class Unc(object):
     def __init__(self, args):
         self.args = args
-
-        # read MCMC input file
-        select = [int(x) for x in args.input_range]
-        self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.mcmc_input, skip_initial=0.0,
-                                                   select=select)
-
         self.fixed_name = args.fix[0]
 
+        select = [int(x) for x in args.input_range]
+
+        # read input file
+        if 'mcmc' in args.input:
+            self.input = samplingOutput.EOS_PYPMC_MCMC(self.args.input, skip_initial=0.0,
+                                                   select=select)
+            path_to_descriptions = '/chain #0'
+        else:
+            self.input = samplingOutput.EOS_PYPMC_IS(self.args.input, select=select,
+                                                     deterministic_mixture=True)
+            path_to_descriptions = ''
+
+        self.par_attributes(path_to_descriptions, select)
         self.results = np.empty((len(self.input.samples), int(args.fix[-1])))
 
-        desc = 'descriptions'
-        with h5py.File(args.output, 'w') as output_file:
-            with h5py.File(args.mcmc_input, 'r') as input_file:
-                input_file.copy('/chain #0/' + desc, output_file, name=desc)
-
-            ds_par = output_file[desc + '/parameters']
-            ds_par.attrs['input file'] = self.args.mcmc_input
-            ds_par.attrs['min sample index'] = select[0]
-            ds_par.attrs['max sample index'] = select[1]
+    def par_attributes(self, path_to_descriptions, select):
+        with h5py.File(self.args.output, 'w') as output_file:
+            with h5py.File(self.args.input, 'r') as input_file:
+                desc = 'descriptions'
+                input_file.copy(path_to_descriptions + '/' + desc, output_file, name=desc)
+                ds_par = output_file[desc + '/parameters']
+                ds_par.attrs['input file'] = self.args.input
+                ds_par.attrs['min sample index'] = select[0]
+                ds_par.attrs['max sample index'] = select[1]
 
     def run(self):
         for n, x in enumerate(self.input.samples):
             cmd = self.build_cmd(x)
             status, output = commands.getstatusoutput(cmd)
             if status:
+                print("Error in calling eos-evaluate (escape `'` or `\"` in parameter names?):")
                 print(cmd)
                 print(output)
                 exit(status)
@@ -81,7 +89,8 @@ if __name__ == '__main__':
[…]

### 2015-07-02 plot/merge.py
[plot] plot and merg unc. with importance weights

@@ -2,13 +2,14 @@
 '''Merge multiple input files into one output file.'''
 
 from __future__ import division, print_function
+
 import commands
 import glob
 import h5py
-import os
-import shutil
-
 import numpy as np
+import os
+import samplingOutput
+import shutil
 
 # solution from http://stackoverflow.com/a/341730
 def natsorted(strings):
@@ -215,6 +216,19 @@ def merge_unc_pypmc(output_file_name, search='unc_*.hdf5', input_files=None):
             obs_ds = output_file.create_dataset('/observable', data=obs_ds[:], maxshape=(None, obs_ds.shape[1]))
             obs_ds.attrs['name'] = obs_name
 
+            # check if input from importance sampling, then get weights
+            with h5py.File(sample_input_file, 'r') as original_input_file:
+                try:
+                    original_input_file['/step #0/vb/weights']
+                except KeyError:
+                    weights = None
+                else:
+                    weights = True
+                if weights:
+                    weights = samplingOutput.EOS_PYPMC_IS(sample_input_file, deterministic_mixture=True).weights
+                    weights_ds = output_file.create_dataset('/weights', maxshape=(None,),
+                                                             data=weights[par_ds.attrs['min sample index']:par_ds.attrs['max sample index']])
+
         for file_name in input_files[1:]:
             with h5py.File(file_name, 'r') as input_file:
                 # check agreement
@@ -236,8 +250,16 @@ def merge_unc_pypmc(output_file_name, search='unc_*.hdf5', input_files=None):
 
                 print("merging %s" % os.path.split(file_name)[1])
                 old_length = obs_ds.len()
+                output_slice = slice(old_length, old_length + in_obs_ds.len())
+
+                # add more observables
                 obs_ds.resize(old_length + in_obs_ds.len(), axis=0)
-                obs_ds[old_length:old_length + in_obs_ds.len()] = in_obs_ds[:]
+                obs_ds[output_slice] = in_obs_ds[:]
+
+                # add more weights
+                if weights is not None:
+                    weights_ds.resize(old_length + in_obs_ds.len(), axis=0)
+                    weights_ds[output_slice] = weights[par_ds.attrs['min sample index']:par_ds.attrs['max sample index']]
 
                 # reset max. There may be holes in the range of min to max
                 s = 'max sample index'

### 2015-07-02 plot/samplingOutput.py

@@ -1271,7 +1271,10 @@ class EOS_PYPMC_UNC(SamplingOutput):
         with open_hdf5(self.input_file_name) as input_file:
             obs_ds = input_file['/observable']
             self.samples = obs_ds[:]
-            self.weights = np.ones(len(self.samples))
+            try:
+                self.weights = input_file['/weights'][:]
+            except KeyError:
+                self.weights = np.ones(len(self.samples))
             fixed_ds = input_file['/descriptions/fixed parameter']
             fixed_name = fixed_ds.attrs['name']
             try:

### 2015-07-02 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] finished bounds on scalar scenario, added posterior predictive except for most general scenario

@@
 \begin{figure*}
-  \setlength{\relwidth}{0.31\textwidth}
+  \setlength{\relwidth}{0.33\textwidth}
   \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
@@
   \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
-  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
+  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
   \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
@@
       latest 68\% uncertainty reported by LHCb (grey) if a measurement
-      is available. }
+      is available. 
+      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$ 
+            or even $\in [-0.5, +0.5]$?}}
   \label{fig:FHvsCT}
@@
   & $\quad$ $-$ $\quad$
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
-  & \eos{$\quad$ $[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$) $\quad$}
+  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.11,\, 0.12]$) $\quad$
+  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.12,\, 0.11]$) $\quad$
   \\[0.1cm]
@@
   $\mbox{Im}(\wilson{S} + \wilson{S'})$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $[-0.37,\, 0.35]$ ($[-0.68,\, 0.66]$)
   & $-$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $[-0.25,\, 0.41]$ ($[-0.57,\, 0.64]$)
   \\[0.1cm]
@@
   & $-$
-  & \eos{$[-0.08,\, 0.08]$ ($[-0.12,\, 0.12]$)}
-  & \eos{$[-0.10,\, 0.10]$ ($[-0.20,\, 0.20]$)}
+  & $[-0.07,\, 0.08]$ ($[-0.12,\, 0.12]$)
+  & $[-0.07,\, 0.09]$ ($[-0.14,\, 0.16]$)
   \\[0.1cm]
@@
   $\mbox{Im}(\wilson{P} + \wilson{P'})$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $[-0.36,\, 0.37]$ ($[-0.67,\, 0.67]$)
   & $-$
-  & \eos{$[-0.4,\, 0.4]$ ($[-0.7,\, 0.7]$)}
+  & $[-0.37,\, 0.29]$ ($[-0.68,\, 0.57]$)
   \\
@@
 $\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
-\todo{uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$}.
+uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$.
 Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
@@
 and the steadily rising lower bounds on new particle masses towards higher energies
-from ATLAS and CMS such a scenario becomes more and more viable.
+from ATLAS and CMS such a scenario becomes more and more viable\footnote{\todo{
+comment on Cata/Jung \cite{Cata:2015ltad}.}}.
 
@@
   & SM
-  & $9,10,T,T5$
-  & $10^{(')},S^{(')},P^{(')}$
-  & $10^{(')},S^{(')},P^{(')},T,T5$
+  & $T,\,T5,\,9,\,10,$
+  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
+  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
   \\
   \hline \hline
-  \multirow{2}{*}{$J_{6c}$}
+  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
   & $[1.1,\, 6]$
   & $\simeq 0$
-  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
-  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
+  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
+  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
   & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
@@
   & $\simeq 0$
-  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
-  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
+  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
+  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
   & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
@@
   \hline
-  \multirow{2}{*}{$J_{1c} + J_{2c}$}
+  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
   & $[1.1,\, 6]$
-  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
-  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
-  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
+  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
+  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
+  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
   & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
@@
   & $[15,\, 19]$
-  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
-  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
-  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
+  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
+  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
+  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
   & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
@@
   \hline
-  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
+  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
   & $[1.1,\, 6]$
-  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
-  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
-  & \eos{SM}
+  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
+  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
+  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
   & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
@@
   & $[15,\, 19]$
-  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
-  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
-  & \eos{SM}
+  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
+  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
+  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
   & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
@@
   \hline \hline
-  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
+  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
   & 1
-  &
   & SM
-  &
+  & $[-1,\, 1]$
+  & \eos{???}
   \\
@@
 
-For comparison, the SM estimates are also given in \reftab{tab:postdictions}.
-At low-$q^2$ they are of order ${\cal O}(10^{-21})$ for $(J_{1s} - 3\, J_{2s})$ and
-$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-23})$ at high-$q^2$
+For comparison, the SM estimates are also given in \reftab{tab:postdictions}
+multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
+At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
+$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
 due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
-magnitude of vectorial couplings, note that for example the decay width of
+magnitude of vectorial couplings, note that for example the branching ratio of
 $B\to K^*\bar\ell\ell$ 
 \begin{align}
-  \frac{{\rm d}\Gamma}{{\rm d}q^2} & =
+  \frac{1}{\tau_{B^0}} \frac{{\rm d}\BR}{{\rm d}q^2} & =
     \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c})
@@
 is numerically of the order ${\cal O}(10^{-19})$ in the SM 
+\todo{check large SM uncertainty of 30\% at low-$q^2$}
 \begin{equation}
 \begin{aligned}
-  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
-  \eos{\left(1.07_{-0.25}^{+0.28} \right) \cdot 10^{-19}} \,,
-\\
-  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[\eos{16},\, 19]} & =
-  \eos{\left(0.63_{-0.17}^{+0.20} \right) \cdot 10^{-19}} \,,
+  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
+  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
+\\
+  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
+  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
 \end{aligned}

### 2015-07-02 plot/plotScript.py
[plotScript] add `--rescale-samples`

@@ -1597,6 +1597,7 @@ def factory(cmd_line=None):
     parser.add_argument('--prerun', help="Use prerun instead of main", action='store_true')
     parser.add_argument('--prior', help="Plot the prior in 1D distributions.", action='store_true')
     parser.add_argument('--pypmc', help="Output file format from eos->pypmc interface.", action='store_true')
+    parser.add_argument('--rescale-samples', help="Scale every sample by a constant.", type=float)
     parser.add_argument('--single-1D', help="Plot only the 1D marginal distribution of the ith parameter, i=0...N-1",
                         type=int, nargs='+')
     parser.add_argument('--single-2D',
@@ -1698,6 +1699,12 @@ def factory(cmd_line=None):
     if args.nest:
         assert input_source == input_source_default
         input_source = 'multinest'
+
+    if args.rescale_samples is not None:
+        output.samples *= args.rescale_samples
+        for d in output.par_defs:
+            d.min *= args.rescale_samples
+            d.max *= args.rescale_samples
 
     #had some trouble getting the second argument out-of the namepace, so use the dictionary directly
     marg = MarginalDistributions(output, args.__dict__['use_KDE'], output_dir=args.__dict__['output_dir'],

### 2015-07-02 plot/samplingOutput.py
[samplingOutput] PYPMC_UNC can crop weights

@@ -1268,11 +1268,16 @@ class EOS_PYPMC_UNC(SamplingOutput):
     '''Read samples of a single observable computed from parameter samples.'''
 
     def _read(self, *args, **kwargs):
+        self.crop_outliers = kwargs.get('crop_outliers', 0)
+
         with open_hdf5(self.input_file_name) as input_file:
             obs_ds = input_file['/observable']
             self.samples = obs_ds[:]
             try:
                 self.weights = input_file['/weights'][:]
+                if self.crop_outliers > 0:
+                    crop(self.weights, self.crop_outliers)
+
             except KeyError:
                 self.weights = np.ones(len(self.samples))
             fixed_ds = input_file['/descriptions/fixed parameter']

### 2015-07-02 tensor/paper_plots.py
[tensor] fix paper_plot + unc

@@ -713,7 +713,7 @@ class Spring2015(object):
 
         marg = MarginalContours(self.input_base, self.output_base, max_samples=self.max_samples)
 
-        scen_kw = dict(nbins=200, file_type='unc', histogram=False)
+        scen_kw = dict(nbins=200, histogram=False)
         colors = ['blue', 'red']
         scenario_names = []
         for i, d in enumerate(scen_obs):
@@ -872,7 +872,7 @@ if __name__ == '__main__':
     matplotlib.rcParams['axes.linewidth'] = major['width']
 
     f = Spring2015()
-    f.figSP()
+    # f.figSP()
     # f.figTT5()
-    # f.fig_1()
+    f.fig_1()
     # f.all()

### 2015-07-06 py-eos/vb.py
[py-eos,tensor] Change default to not prune components

@@ -175,8 +175,8 @@ if __name__ == '__main__':
                         help="Output file name. If left empty, the output is written to 'vb.hdf5'" \
                         " in the same directory as the input file."
                         "For the special name 'APPEND', the output is written to the input file.")
-    parser.add_argument('--prune', help="Components responsible for less than this value are removed.",
-                        default=None, const=None, nargs='?')
+    parser.add_argument('--prune', default=None, const=None, nargs='?',
+                        help="Components responsible for less than this value are removed. If left blank, a rule of thumb based on the number of samples, N,  is used; i.e., the prune threshold is chosen as 0.5 * N / K, where K is the number of components.",)
     parser.add_argument('--rel-tol', type=float, default=None, const=None, nargs='?',
                         help="Relative tolerance to determine convergence of variational Bayes")
     parser.add_argument('--R-value', help="Critical R value used in grouping of chains", type=float)

### 2015-07-06 plot/samplingOutput.py
[samplingOutput] Require `natsort` package to fix IS with 10 or more steps

@@ -10,6 +10,12 @@ import h5py
 import numpy as np
 import os, re, sys
 
+try:
+    from natsort import natsorted
+except ImportError:
+    "Please install the natsort package using for example `pip install --user natsort`"
+    raise
+
 def open_hdf5(name, mode='r'):
     print('Opening ' + name)
     return h5py.File(name, mode)
@@ -995,7 +1001,7 @@ class EOS_PYPMC_IS(IS_Output):
         with open_hdf5(self.input_file_name) as hdf5_file:
             # find last step
             groups = list(hdf5_file['/'].keys())
-            steps = sorted(filter(lambda x:re.search(r'^step #', x), groups))
+            steps = natsorted(filter(lambda x:re.search(r'^step #', x), groups))
             # extract 3 from 'step #3'
             last_step = int(steps[-1][steps[-1].find('#')+1:]) if steps else 0
 
@@ -1016,7 +1022,7 @@ class EOS_PYPMC_IS(IS_Output):
 
                 # read samples
                 group = hdf5_file['/step #%d/combination' % step]
-                combinations = sorted(filter(lambda x:re.search(r'^weights #', x), group.keys()))
+                combinations = natsorted(filter(lambda x:re.search(r'^weights #', x), group.keys()))
                 assert combinations, 'No deterministic-mixture weights found'
                 assert len(combinations) == len(steps), \
                 "samples (%d) and combined weights (%d) don't match" % (len(steps), len(combinations))
@@ -1114,9 +1120,7 @@ class EOS_PYPMC_IS(IS_Output):
 
     def _n_combined_weights(self, hdf5_group):
         n = []
-#         elements = hdf5_group.keys()
-        weights = sorted(filter(lambda x:re.search(r'^weights #', x), hdf5_group.keys()))
-        print(weights)
+        weights = natsorted(filter(lambda x:re.search(r'^weights #', x), hdf5_group.keys()))
         for i, c in enumerate(weights):
             assert c == 'weights #%d' % i
             n.append(hdf5_group[c].len())

### 2015-07-06 plot/merge.py
[merge] use natsort package

@@ -6,19 +6,11 @@ from __future__ import division, print_function
 import commands
 import glob
 import h5py
+from natsort import natsorted
 import numpy as np
 import os
 import samplingOutput
 import shutil
-
-# solution from http://stackoverflow.com/a/341730
-def natsorted(strings):
-    "Sort strings the way humans are said to expect."
-    return sorted(strings, key=natural_sort_key)
-
-def natural_sort_key(key):
-    import re
-    return [int(t) if t.isdigit() else t for t in re.split(r'(\d+)', key)]
 
 def invalid_chain(file, chain, cut_off=None, format='eos'):
     """Check if mode larger than cut off"""

### 2015-07-06 py-eos/is.py
[tensor] Switch from IBM to Intel MPI
IBM MPI lead to spurious errors, each reproducible.

For example, with
create crash with IBM poe, eos-scripts@c7d9ca40 and
export EOS_IS_SAMPLES=20
./loadleveler-multistep.cmd ./sc910SPTT5-K_KstarBR_Bsmumu.bash 2 1

I get this stacktrace

rank 0: sampling completed
**** glibc detected *** python: free(): invalid pointer:
     0x0000000000619170 ***======== Backtrace:
     =========//lib64/libc.so.6(+0x76b18)[0x2b5d98df5b18]
/lib64/libc.so.6(cfree+0x6c)[0x2b5d98dfab5c]/opt/ibmhpc/pe1308/base/gnu/lib64/libpami.so(+0xacdd8)[0x2b5bc1293dd8]
/opt/ibmhpc/pe1308/

@@ -56,6 +56,7 @@ class IS(object):
 
     def run(self):
         self.parallel_sampler.run(self.n_samples)
+        print("rank %d: sampling completed" % rank)
         if master:
             hdf5_io.save_is_samples(self.args.output, primary_group(self.args.step) + hdf5_subdirectory, self.parallel_sampler.history_list)
             # todo every process could do that, not just master

### 2015-07-07 tensor/paper_plots.py
[tensor] update readme, extract spTT5 marginal intervals

@@ -666,8 +666,10 @@ class Spring2015(object):
         ###
         # scenarios
         ###
+        scenarios = []
+        '''
         s = 'scTT5_FH'
-        scenarios = [s]
+        scenarios.append(s)
         marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_scTT5_FH.hdf5'), 'OrangeRed',
                                 nbins=300)
         # in python, we can add class members as we please, use with care!
@@ -685,6 +687,13 @@ class Spring2015(object):
         marg.scen[s] = Scenario(os.path.join(marg.input_base, 'mcmc_' + s + '.hdf5'), 'Green',
                                 nbins=300)
         marg.scen[s].ctind = [(4, 5), (6, 7)]
+        '''
+        s = 'sc910SPTT5_K_KstarBR_Bsmumu'
+        scenarios.append(s)
+        marg.scen[s] = Scenario(os.path.join(marg.input_base, 'vb_' + s + '.hdf5'), 'Green',
+                                nbins=300)
+        marg.scen[s].ctind = [(16, 17), (18, 19)]
+
 
         marg.read_data()
 
@@ -873,6 +882,6 @@ if __name__ == '__main__':
 
     f = Spring2015()
     # f.figSP()
-    # f.figTT5()
-    f.fig_1()
+    f.figTT5()
+    # f.fig_1()
     # f.all()

### 2015-07-07 plot/samplingOutput.py
[samplingOutput] fix natsort exception msg

@@ -12,9 +12,8 @@ import os, re, sys
 
 try:
     from natsort import natsorted
-except ImportError:
-    "Please install the natsort package using for example `pip install --user natsort`"
-    raise
+except:
+    raise ImportError("Please install the natsort package from the package manager or `pip install --user natsort`")
 
 def open_hdf5(name, mode='r'):
     print('Opening ' + name)

### 2015-07-07 plot/plotScript.py
[plotScript] fix several +1 index bugs with contours
* remove spline interpolation for KDE: it can negative
* don't use `interpolate` on `fill_between`, it creates a trapezoid at
  the end points rather than a vertical line
* KDE use half bins to interpolate linearly but credible regions are
  properly based on the actual output of KDE not the
  interpolation. Filling the contour correctly to match the output is
  nontrivial but done
* remove `find_limits`, it was unused
* overcovering now slightly more transparent

@@ -457,53 +457,6 @@ class MarginalDistributions:
             self.min[index] = np.min(self.out.samples.T[index])
             self.max[index] = np.max(self.out.samples.T[index])
 
-    def find_limits_1D(self, index, method='ECDF'):
-        """
-        Find the central limits using the empirical CDF
-        in 1D for the parameter identified by *index*
-        """
-
-        if method == 'ECDF':
-            #ascending order
-
-            #find multiplicity of multiple events
-            #it's in last column
-            order_statistics = filter_duplicates(np.sort(self.out.samples.T[index]))
-
-            #build cdf. normalize to unity
-            ecdf = np.cumsum(order_statistics.T[-1])
-            ecdf /= float(ecdf[-1])
-
-
-            #binary search for index next to CDF value,
-            #then extract physical parameter
-            #subtract/add one from index to overcover
-            limit_one_sigma = [order_statistics[max(0, np.searchsorted(ecdf, 0.15865525393145705) - 1), 0],
-                               order_statistics[
-                                   min(ecdf.shape[0] - 1, np.searchsorted(ecdf, 0.84134474606854293) + 1), 0]]
-            limit_two_sigma = [order_statistics[max(0, np.searchsorted(ecdf, 0.02275013194817919) - 1), 0],
-                               order_statistics[
-                                   min(ecdf.shape[0] - 1, np.searchsorted(ecdf, 0.97724986805182079) + 1), 0]]
-            return (limit_one_sigma, limit_two_sigma)
-
-        if method == 'histogram':
-            #bin the data
-            histo, edges = np.histogram(self.out.samples.T[index], self.nBins[index])
-
-            #build CDF
-            temp = np.cumsum(histo)
-            cdf = temp / float(temp[-1])
-
-            #binary search for index next to CDF value,
-            #then extract physical parameter
-            #subtract/add one from index to overcover
-            limit_one_sigma = [edges[max(0, np.searchsorted(cdf, 0.15865525393145705) - 1)],
-                               edges[min(cdf.shape[0] - 1, np.searchsorted(cdf, 0.84134474606854293) + 2)]]
-
-            limit_two_sigma = [edges[max(0, np.searchsorted(cdf, 0.02275013194817919) - 1)],
-                               edges[min(cdf.shape[0] - 1, np.searchsorted(cdf, 0.97724986805182079) + 2)]]
-            return (limit_one_sigma, limit_two_sigma)
-
     @staticmethod
[…]

### 2015-07-07 plot/plotScript.py
[plotScript] Fix even more index errors in histogram contour plots
* store estimates for bin centers for both histogram and KDE. Before
  hist credibility intervals were off by half a bin!
* check that histogram and KDE now agree on test data
* hist contour now with one call to `fill_between` to avoid rendering artefacts

@@ -529,61 +529,84 @@ class MarginalDistributions:
         self.nBins[index] = int(( self.max[index] - self.min[index]) / bandwidth)
         return bandwidth
 
-    def contours_one(self, x, densities, level, specifier, hist=True, **kwargs):
+    def __double_array(self, x, y):
         """
-        Plot contours and output intervals for one dim. distributions of parameter x.
+        Interpret ``y`` as an estimate of the density of a function in bins centered on ``x``. Assume uniform spacing
+        in ``x``. If ``x, y`` have length ``N``, then compute new arrays of length ``2 N + 1`` such that each point
+        in ``x`` gets a neighbor on either side. The values of ``y`` are used for linear interpolation for interior
+        points, and linear extrapolation for the two points at the boundary. If the extrapolation leads to negative
+        values, set it to zero instead.
+
+        :return: ``new_x, new_y``
+        """
+        # bin centers are given, assume uniform bin width
+        # and extrapolate linearly.
+        assert len(x) >= 2, 'Cannot determine bin width for less than two points'
+
+        # extend the array such that every original point has two neighbors
+        half_bin_width = (x[1] - x[0]) / 2
+        new_x = np.linspace(x[0] - half_bin_width, x[-1] + half_bin_width, 2 * len(x) + 1)
+        new_y = np.empty_like(new_x)
+
+        # interpolate interior points as mean value
+        for i in range(len(new_y))[1:-1]:
+            # values at odd index are the original values
+            if i % 2 == 1:
+                new_y[i] = y[i // 2]
+            else:
+                new_y[i] = (y[i // 2] + y[i // 2 - 1]) / 2
+
+        # first point: extrapolate backwards linearly
+        new_y[0] = max(1.5 * y[0] - 0.5 * y[1], 0.0)
+        # last point: extrapolate forward linearly
+        new_y[-1] = max(1.5 * y[-1] - 0.5 * y[-2], 0.0)
+
+        return new_x, new_y
+
+    def contours_one(self, x, y, level, doubled_arrays=None, **kwargs):
+        """
+        Plot contours for one dim. distributions of parameter x.
         args:
-        x = the ordinate
-        densities = the estimate of the probability density
-        level = the desired credibility level
-        specifier = label used for text output, e.g. 'one sigma'
-        hist = if `True`, plot with histogram bars, else interpolate smoothly
-        **kwargs are passed to the plotting routine of pylab.fill_between
+        x = the bin centers
+        y = the estimate of the probability density at x
[…]

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor/draft] vectorial -> vector, tensorial -> tensor
add Stephan's new address, modify title

@@
 
-\title{Constraining tensorial and scalar couplings with
+\title{Constraints on tensor and scalar couplings from
   $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$
@@
 \affiliation{
-  \todo{neue Adresse}
+  Max Planck institute for physics, Munich.\\
   Excellence Cluster Universe,
@@
   term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
-  nonstandard tensorial and scalar contributions are enhanced with respect
-  to vectorial ones. We use latest experimental results for $\ell = \mu$ in
+  nonstandard tensor and scalar contributions are enhanced with respect
+  to vector ones. We use latest experimental results for $\ell = \mu$ in
   combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent
-  constraints on tensorial and scalar effective couplings and determine their
+  constraints on tensor and scalar effective couplings and determine their
   impact on not yet measured angular observables in
-  $B\to K^*\bar\mu\mu$, which feature the same suppression of vectorial couplings.
+  $B\to K^*\bar\mu\mu$, which feature the same suppression of vector couplings.
   Most notably, the measurement of $F_H^\mu$ provides
@@
 Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
-factors for vectorial and dipole
-couplings present in the SM, thereby enhancing their sensitivity to tensorial and
+factors for vector and dipole
+couplings present in the SM, thereby enhancing their sensitivity to tensor and
 scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
-scalar couplings compared to helicity-suppressed vectorial couplings of the SM
+scalar couplings compared to helicity-suppressed vector couplings of the SM
 is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
@@
 allow to perform current angular analysis without the assumption of vanishing
-scalar and tensorial couplings in this decay mode. In the future also certain
+scalar and tensor couplings in this decay mode. In the future also certain
 angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
@@
 Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
-to derive stronger constraints then before on tensorial and scalar couplings in
+to derive stronger constraints then before on tensor and scalar couplings in
 various model-independent scenarios and study their impact on the yet not
@@
 model-independent fits are based on. We discuss the dependence of observables
-in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
+in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensor and scalar
 couplings in \refsec{sec:observables} and specify also the experimental input
-used in the fits. The constraints on tensorial and scalar couplings from the data
+used in the fits. The constraints on tensor and scalar couplings from the data
 are presented for several model-independent scenarios in \refsec{sec:results}.
@@
 $b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
-chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$)
+chiral structure. There are dipole ($i = 7,7')$ and vector ($i = 9,9',10,10'$)
 operators
@@
 
-The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
+The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
 couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
@@
 This picture does not change in the presence of new physics contributions to
-vectorial and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
-non-vanishing tensorial or scalar contributions are enhanced unless the
+vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
+non-vanishing tensor or scalar contributions are enhanced unless the
 dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
 for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
-$F_H^\ell$ is very sensitive to tensorial couplings whereas $A_{\rm FB}^\ell$ to
-the interference of tensorial and scalar couplings.
+$F_H^\ell$ is very sensitive to tensor couplings whereas $A_{\rm FB}^\ell$ to
+the interference of tensor and scalar couplings.
 
@@
   \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
-  \caption{ The sensitivity to the tensorial coupling
+  \caption{ The sensitivity to the tensor coupling
       $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
@@
 There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
-\bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
-are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial ones
+\bar\ell\ell$ with the same properties, i.e. tensor and scalar contributions
+are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones
 present in the SM or their respective interference terms. These are $J_{6c}$
@@
                 - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
-\intertext{is sensitive to the interference of tensorial and scalar operators,
+\intertext{is sensitive to the interference of tensor and scalar operators,
   complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
@@
 \end{align}
-i.e., with an interchange of tensorial contributions $T \leftrightarrow T5$.
+i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.
 We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
@@
 it has to compete with $J_{6s}$ in this observable, a separate measurement of
-$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensorial contributions enter
+$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensor contributions enter
 \begin{align}
@@
 where the dots indicate different kinematical and form factor dependences.
-On the other hand, tensorial and scalar contributions enter
+On the other hand, tensor and scalar contributions enter
 \begin{equation}
@@
 Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
-Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only
+Bobeth:2012vn} --- are such that tensor and scalar couplings contribute only
 constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
@@
 \refapp{app:BKstarellell}, which could serve to form optimised observables for
-special scenarios of either vanishing chirality-flipped vectorial or tensorial
+special scenarios of either vanishing chirality-flipped vector or tensor
 or scalar couplings. In the most general case, however, there are no optimised
@@
 
-To illustrate the sensitivity of $F_H^\ell$ to tensorial couplings, we compare
+To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we compare
 it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
@@
 $\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
-the sensitivity to tensorial couplings is highest for $F_H^\ell$ at high $q^2$,
+the sensitivity to tensor couplings is highest for $F_H^\ell$ at high $q^2$,
 also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
@@
 stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
-and has some impact on the constraints on tensorial couplings as will be
+and has some impact on the constraints on tensor couplings as will be
 discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
 high $q^2$ provides currently the most stringent constraints on the size of
-tensorial couplings. Moreover, the dependence on vectorial couplings is such that
+tensor couplings. Moreover, the dependence on vector couplings is such that
 $\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
@@
 Eventually we also explore the behaviour of derived constraints with respect to
-destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
+destructive interference with vector couplings $\wilson{9,\,9',\,10,\,10'}$.
 For this purpose we include also the branching ratio, the lepton forward-backward
 asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
-additional constraints on the real and imaginary parts of vectorial couplings.
+additional constraints on the real and imaginary parts of vector couplings.
 
@@
 their tiny SM predictions. Thus our main objective is the derivation of stronger
-constraints on tensorial and scalar couplings, taking advantage of their enhancement
-in both observables over vectorial ones. For this purpose, we will consider several
+constraints on tensor and scalar couplings, taking advantage of their enhancement
+in both observables over vector ones. For this purpose, we will consider several
 model-independent scenarios, starting from rather restricted to more general ones,
@@
 
-We will start with the scenario of only tensorial couplings and see that they are
+We will start with the scenario of only tensor couplings and see that they are
 well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
@@
 as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
-also interference effects with new physics in vectorial couplings. Finally, we
+also interference effects with new physics in vector couplings. Finally, we
 conclude this section with postirior predictions of the allowed ranges of the yet
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{Tensorial couplings \label{sec:tensor}}
+\subsection{Tensor couplings \label{sec:tensor}}
 
@@
 
-In a scenario with only tensorial complex-valued couplings $\wilson{T,\, T5}$,
+In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$,
 the experimental measurement of $F_H^\mu$ constrains the combination
 $|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
-$\wilson{T}$ with vectorial couplings $\wilson{7,\,7',\,9,\,9'}$.
+$\wilson{T}$ with vector couplings $\wilson{7,\,7',\,9,\,9'}$.
 The according 68\% (95\%) 1D-marginalized probability intervals are listed in
@@
 \reftab{tab:observables}, mainly due to the sensitivity of the branching ratio of $B\to K^{*}
-\bar\mu\mu$ to tensorial couplings (see also \reffig{fig:FHvsCT}). The latter
+\bar\mu\mu$ to tensor couplings (see also \reffig{fig:FHvsCT}). The latter
 stronger bounds are driven by the new lattice
 results of $B\to K^*$ form factors that yield too high predictions compared
-to the measurements~\cite{Horgan:2013pva}. Since tensorial couplings contribute
+to the measurements~\cite{Horgan:2013pva}. Since tensor couplings contribute
 constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
@@
 bounds do not change when including all other data in \reftab{tab:observables}, since
-the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensorial
+the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
 couplings and other observables are not very sensitive to scalar
@@
 
-Interference terms of $\wilson{P,\,P'}$ with vectorial couplings might weaken
+Interference terms of $\wilson{P,\,P'}$ with vector couplings might weaken
 these bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
@@
 their combination with all the other observables in \reftab{tab:observables},
-even allowing new physics in vectorial couplings
+even allowing new physics in vector couplings
 $\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
@@
 combination is capable to do so and moreover, the bounds are stable against
-destructive interference with vectorial couplings. In the general case
+destructive interference with vector couplings. In the general case
 of complex-valued couplings, $\overline{\cal B}(B_s \to \bar\mu\mu)$ does
@@
 scale $\mu \sim m_W$ of the order of the $W$-boson mass in \cite{D'Ambrosio:2002ex}
-for vectorial couplings $\wilson{7,\,9,\,10}$. The matching for tensor
+for vector couplings $\wilson{7,\,9,\,10}$. The matching for tensor
 \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
@@
 \end{align}
-on scalar and pseudo-scalar couplings and require tensorial couplings to be
+on scalar and pseudo-scalar couplings and require tensor couplings to be
 suppressed to the level of dimension eight operators. In consequence only two
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{Tensorial, scalar and vectorial couplings \label{sec:tensor:scalar}}
-
-We start with the scenario of the combination of tensorial and scalar couplings
+\subsection{Tensor, scalar and vector couplings \label{sec:tensor:scalar}}
+
+We start with the scenario of the combination of tensor and scalar couplings
 $\wilson{S,S',P,P',T,T5, 10,10'}$ \todo{(extend this discussion right away to include
@@
 two sections. In this scenario there are only small changes on the bounds, in fact
-they tend to be even more stringent, because tensorial and scalar couplings
+they tend to be even more stringent, because tensor and scalar couplings
 can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
@@
 
-Eventually, we present the yet allowed ranges due to non-standard tensorial
+Eventually, we present the yet allowed ranges due to non-standard tensor
 and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
@@
 for the various general scenarios, i.e. allowing for interference with non-zero
-vectorial couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
+vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
 and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities
@@
 due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
-magnitude of vectorial couplings, note that for example the branching ratio of
+magnitude of vector couplings, note that for example the branching ratio of
 $B\to K^*\bar\ell\ell$
@@
 suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
-suppression must be compared to potential suppression present for tensorial
+suppression must be compared to potential suppression present for tensor
 and scalar contributions in particular NP models in order to decide their
@@
 combination with theory uncertainties, do not impose yet too stringent
-constraints on tensorial and scalar couplings.
+constraints on tensor and scalar couplings.
 
 Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in scenarios
-involving tensorial couplings and only ${\cal O}(10^{-23})$ in their absence.
+involving tensor couplings and only ${\cal O}(10^{-23})$ in their absence.
 Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
 deviations from the SM prediction are possible only in the presence of non-zero
-tensorial couplings. In this case enhancement by two orders of magnitude are
+tensor couplings. In this case enhancement by two orders of magnitude are
 possible up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also at low-$q^2$ in
@@
 
-We have derived to date most stringent constraints on tensorial and scalar
+We have derived to date most stringent constraints on tensor and scalar
 couplings that mediate $b\to s\bar\mu\mu$ utilising the latest measurements
@@
 $B\to K^{(*)} \bar\mu\mu$. Both observables, $F_H^\mu$ and $A_{\rm FB}^\mu$,
-belong to a class in which vectorial and dipole couplings that arise also in
+belong to a class in which vector and dipole couplings that arise also in
 the standard model (SM) are suppressed (mostly kinematically by $m_\ell /
-\sqrt{q^2}$) w.r.t tensorial and scalar couplings. We provide predictions for
+\sqrt{q^2}$) w.r.t tensor and scalar couplings. We provide predictions for
 analogous but not yet measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
@@
 \begin{enumerate}
-\item imposes by itself constraints on tensorial couplings \eos{$|{\cal C}_{T,\,T5}|
+\item imposes by itself constraints on tensor couplings \eos{$|{\cal C}_{T,\,T5}|
   < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
@@
   $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\,
-  (0.45)$}, even in the presence of non-standard contributions in vectorial
+  (0.45)$}, even in the presence of non-standard contributions in vector
   couplings.
@@
   couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
-  Even when taking into account destructive interference with vectorial couplings
+  Even when taking into account destructive interference with vector couplings
   \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| <
@@
 In all cases these \eos{constraints are weakened only slightly} in the presence
-of new physics in vectorial couplings from destructive interference.
+of new physics in vector couplings from destructive interference.
 
 In the future this might change once measurements start to probe the SM expectation,
-as in this case constraints on the tensorial and scalar couplings become so
-stringent that the formal suppression of vectorial couplings by $m_\ell / \sqrt{q^2}$
+as in this case constraints on the tensor and scalar couplings become so
+stringent that the formal suppression of vector couplings by $m_\ell / \sqrt{q^2}$
 is overcome. Our study of angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
@@
 Here we present those angular observables $J_i$ in $B\to K^* \bar\ell\ell$
-in which tensorial and scalar contributions are kinematically enhanced by a factor
-$\sqrt{q^2}/m_\ell$ over vectorial once present in the SM or their respective
+in which tensor and scalar contributions are kinematically enhanced by a factor
+$\sqrt{q^2}/m_\ell$ over vector once present in the SM or their respective
 interference terms using results and notation from \cite{Bobeth:2012vn}.
@@
 In full generality angular observables in $B\to K^* \bar\ell\ell$ depend on
-seven transversity amplitudes with vectorial and dipole contributions
+seven transversity amplitudes with vector and dipole contributions
 $A_{0,\,\perp,\,\parallel}^{L,R}$, and $\tilde{A}_t$, one scalar and one
 pseudoscalar amplitude $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$,
-and six tensorial amplitudes: $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
+and six tensor amplitudes: $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
 \wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$.
@@
 The condition is well fulfilled for $\ell = e$ and $1\, \mbox{GeV}^2\lesssim q^2$,
-provided that tensorial and scalar Wilson coefficients do not receive additional
+provided that tensor and scalar Wilson coefficients do not receive additional
 suppression factors. For $\ell = \mu$ the value of $q^2$ should not be too low,
 whereas in the case $\ell = \tau$, these observables are not anymore dominated by
-tensorial and/or scalar contributions alone, and the full lepton-mass dependence has
+tensor and/or scalar contributions alone, and the full lepton-mass dependence has
 to be taken into account.
@@
 \bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$, however former depends also
-on tensorial couplings and vectorial couplings. The helicity suppression
+on tensor couplings and vector couplings. The helicity suppression
 factor $4\,m_\ell^2/q^2$ of vector couplings is weaker in
@@
 Here $f_{\perp, \parallel, 0}$ and $A_0$ denote $B\to K^*$ form factors, whereas
-the $\rho_1^\pm$ depends on vectorial couplings and $\rho_1^T \propto
+the $\rho_1^\pm$ depends on vector couplings and $\rho_1^T \propto
 (|\wilson{T}|^2 + |\wilson{T5}|^2)$.
@@
 \end{equation}
-where the last one depends only on vectorial couplings, i.e., is free of
-tensorial and scalar ones. In the $J_{1s}$ and $J_{2s}$, tensorial couplings
-contribute either cumulative or destructive to vectorial couplings in
+where the last one depends only on vector couplings, i.e., is free of
+tensor and scalar ones. In the $J_{1s}$ and $J_{2s}$, tensor couplings
+contribute either cumulative or destructive to vector couplings in
 $\rho_1^\pm$.
@@
 depend only on $f_0$ and can be used as normalisation. In the general case,
-$J_{2c}$ still depends only on tensorial couplings and was used at low $q^2$
+$J_{2c}$ still depends only on tensor couplings and was used at low $q^2$
 \cite{Matias:2012xw}. Finally we note that
@@
 \end{equation}
-is free of tensorial couplings at high $q^2$ and would provide access to
+is free of tensor couplings at high $q^2$ and would provide access to
 $\rho_1^-$ provided scalar couplings vanish.
@@
 
-The tensorial and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
+The tensor and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
 i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
@@
 
-As we do not make use of form factor relations for tensorial and scalar amplitudes
+As we do not make use of form factor relations for tensor and scalar amplitudes
 in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor] Add posterior predictions for sc910SPTT5 to draft
[draft-tensor-op.tex] updated IV.D

@@
 
-We start with the scenario of the combination of tensor and scalar couplings
-$\wilson{S,S',P,P',T,T5, 10,10'}$ \todo{(extend this discussion right away to include
-also $\wilson{10,\, 10'}$)}, i.e. the combination of the preceding
-two sections. In this scenario there are only small changes on the bounds, in fact
-they tend to be even more stringent, because tensor and scalar couplings
-can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
+The most general fit of complex-valued tensorial and scalar couplings 
+$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vectorial couplings
+$\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
+and \refsec{sec:scalar} with same prior ranges --- does not yield very different
+bounds. The changes are only small and in fact the bounds tend to be even more
+stringent, because tensor and scalar couplings can contribute to $F_H^{\mu}$
+only constructively --- see \refeq{eq:FH-dependence}.
 As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
-constraints on $\wilson{T,\, T5}$. Furthermore we find that even in the case
+constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
 of complex-valued couplings the data is able to constrain all real and imaginary
-parts. In this case, the constraints are even a bit tighter and strong correlations
-arise as before among real parts of $\wilson{i}$ and $\wilson{i'}$ for $i = S,P$,
-and in addition similarly among their imaginary parts.
-\todo{Check this with EOS}
+parts.
 
@@
   & $[-1,\, 1]$
-  & \eos{???}
+  & $[-1,\, 1]$
   \\

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] changed section IV.E, some changes in conclusion

@@
      \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
-     also complex-valud new physics contributions to $\wilson{9,\,10}$.
+     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
   }
@@
 augmented by dimension six operators that respect the SM gauge group and are
-composed out of SM fields. After the discovery of a scalar resonance at the LHC
+composed out of SM fields only. After the discovery of a scalar resonance at the LHC
 that complies currently with all requirements of the Higgs particle in the SM
 and the steadily rising lower bounds on new particle masses towards higher energies
-from ATLAS and CMS such a scenario becomes more and more viable\footnote{\todo{
-comment on Cata/Jung \cite{Cata:2015ltad}.}}.
+from ATLAS and CMS such a scenario becomes more and more viable.
 
@@
 matching to the effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the
-scale $\mu \sim m_W$ of the order of the $W$-boson mass in \cite{D'Ambrosio:2002ex}
+scale $\mu \sim m_W$ of the order of the $W$-boson mass in~\cite{D'Ambrosio:2002ex}
 for vector couplings $\wilson{7,\,9,\,10}$. The matching for tensor
 \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
-\cite{Alonso:2014csa} shows that SM gauge groups impose the relations
+\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the linear
+representation impose the relations
 \begin{align}
+  \label{eq:mEFT-constraints}
   \wilson{P}  & = -\wilson{S}\,, &
@@
 
+It must be noted that relations \refeq{eq:mEFT-constraints} are a consequence
+of embedding the Higgs in a weak doublet along with the Goldstone bosons.
+For example choosing a non-linear representation of the scalar sector allows
+for additional dimension six operators in the SM-EFT, such that $\wilson{S,S',P,P'}$
+are all independent and tensor operators have non-vanishing couplings already
+at dimension six \cite{Cata:2015lta}.
+
 %
@@
 
-The most general fit of complex-valued tensorial and scalar couplings 
-$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vectorial couplings
+The most general fit of complex-valued tensor and scalar couplings 
+$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vector couplings
 $\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
@@
 only constructively --- see \refeq{eq:FH-dependence}.
-As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
-constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
+As before branching-ratio measurements of $B\to K^{*}\bar\mu\mu$ help to strengthen
+the constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
 of complex-valued couplings the data is able to constrain all real and imaginary
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{ for $B\to K^* \bar\ell\ell$}
+\subsection{Angular observables in $B\to K^* \bar\ell\ell$}
 
@@
   & SM
-  & $T,\,T5,\,9,\,10,$
-  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
-  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
+  & $\quad T(5),\,9,\,10\quad$
+  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
+  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
   \\
@@
   & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
-  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
-  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
+  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-\todo{10}}$
+  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
   \\
@@
   & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
-  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
+  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
   \\
@@
   & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
-  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
+  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
   \\
@@
   & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
-  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
+  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
   \\
@@
   & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
-  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
+  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
   \\
@@
   & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
-  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
+  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
   \\
@@
 in order to explore the potential of their future measurements in fits of the kind
-pursued in this work. \todo{Find nice place to cite method of moments paper.}
+pursued in this work. 
 The 68\% probability intervals are collected in \reftab{tab:postdictions}
-for the various general scenarios, i.e. allowing for interference with non-zero
-vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
+for the various model-independent scenarios, allowing for interference with
+non-zero vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
 and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities
@@
 \begin{align}
-  \frac{1}{\tau_{B^0}} \frac{{\rm d}\BR}{{\rm d}q^2} & =
-    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c})
+  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
+    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c}) 
+  \right]
 \end{align}
-is numerically of the order ${\cal O}(10^{-19})$ in the SM
+is numerically of the order ${\cal O}(10^{-7})$ in the SM
 \todo{check large SM uncertainty of 30\% at low-$q^2$}
@@
 can be generated by QED corrections or potentially from higher-dimensional
-($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
+($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
 suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
@@
 
-Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in scenarios
-involving tensor couplings and only ${\cal O}(10^{-23})$ in their absence.
+Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in scenarios
+involving tensor couplings and only ${\cal O}(10^{-10})$ in their absence.
 Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
@@
 tensor couplings. In this case enhancement by two orders of magnitude are
-possible up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also at low-$q^2$ in
+possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
 the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
 experimental constraints in \reftab{tab:observables}. In view of current
-experimental precision of \eos{$20\%$} branching ratio measurements corresponding
-to the \eos{${\cal O}(10^{-20})$} one can indeed hope for some sensitivity to
-such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ in future
-measurements.
+experimental precision of $20\%$ of the branching ratio measurements at LHCb
+\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal O}(10^{-8})$, one can
+indeed hope for some sensitivity to such large effects in $(J_{1c} + J_{2c})$
+and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3 fb$^{-1}$ data set. 
+\todo{Would be a nice place to cite method of moments paper?}
 
@@
 \begin{enumerate}
-\item imposes by itself constraints on tensor couplings \eos{$|{\cal C}_{T,\,T5}|
-  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
+\item imposes by itself constraints on tensor couplings $|{\cal C}_{T,\,T5}|
+  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
   In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\,
-  (0.45)$}, even in the presence of non-standard contributions in vector
+  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}| < 0.33\,
+  (0.43)$, even in the presence of non-standard contributions in vector
   couplings.
@@
   Even when taking into account destructive interference with vector couplings
-  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| <
-  0.1\, (0.2)$} for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
+  $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| <
+  0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
   from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
-  by a factor four. In the future, measurements at LHCb and Belle II will
-  further tighten the bounds. Moreover, measurements of $F_H^e$ ($\ell = e$)
+  by about a factor four. In the future, measurements at LHCb and Belle II will
+  further tighten the bounds.
+
+  Moreover, measurements of $F_H^e$ ($\ell = e$)
   will provide constraints on scalar couplings in the electron channel in
-  the lack of measurements of $B_s \to \bar{e}e$.
+  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
 \item SM-EFT $\ldots$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor/draft] update all plots with identical colors
* replace Christoph's last figure
* rerun SM unc. predictions with new KDE contour computation and smaller
  range in cT

@@
 \begin{abstract}
-  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
-  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
-  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
-  nonstandard tensor and scalar contributions are enhanced with respect
-  to vector ones. We use latest experimental results for $\ell = \mu$ in
-  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent
-  constraints on tensor and scalar effective couplings and determine their
-  impact on not yet measured angular observables in
-  $B\to K^*\bar\mu\mu$, which feature the same suppression of vector couplings.
-  Most notably, the measurement of $F_H^\mu$ provides
-  constraints on (pseudo-)scalar couplings and their chirality-flipped
-  counterparts that are complementary to the ones from the branching ratio
-  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
-  upper bounds on all four couplings.
+  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
+  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
+  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
+  suppressed in the standard model. In both, nonstandard tensor and
+  scalar contributions are enhanced with respect to vector ones. We
+  use latest experimental results for $\ell = \mu$ in combination with
+  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
+  on tensor and scalar effective couplings and determine their impact
+  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
+  which feature the same suppression of vector couplings.  Most
+  notably, the measurement of $F_H^\mu$ provides constraints on
+  (pseudo-)scalar couplings and their chirality-flipped counterparts
+  that are complementary to the ones from the branching ratio $B_s\to
+  \bar\mu\mu$, which allows to put for the first time simultaneously
+  upper bounds on all four couplings. \fred{Try to shorten, add
+    sentence ``independent of deviations in vector-coupling dominated
+    observables''}
 \end{abstract}
@@
 \begin{figure*}
-  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
-  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
+  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
+  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
   \caption{

### 2015-07-08 tensor/paper_plots.py

@@ -19,6 +19,7 @@ sys.path.append(os.path.realpath('../plot'))
 import plotScript
 from plotScript import ParameterDefinition
 
+colors = dict(red='#FE2E2E', blue='#2E64FE', grey='#848484')
 
 def run_command(com):
     import commands
@@ -63,7 +64,8 @@ class Scenario(object):
     def __init__(self, file, color, nbins=200, alpha=0.4, sigma='2 sigma',
                  bandwidth_default=None, two_sigma_color=None, queue_output=True,
                  crop_outliers=200, local_mode=None, defs={},
-                 unc_label='', histogram=True, linestyle='solid'):
+                 unc_label='', histogram=True, linestyle='solid', fill=True,
+                 pred_range=None):
         self.f = file
         self.c = color
         self.prob = {}
@@ -81,6 +83,8 @@ class Scenario(object):
         self.unc_label = unc_label
         self.histogram = histogram
         self.linestyle = linestyle
+        self.fill = fill
+        self.pred_range = pred_range
 
     def get_bandwidth(self, par1, par2):
         try:
@@ -342,9 +346,15 @@ class MarginalContours(object):
             # retrieve original range used to create prob_density
             # then zoom will work correctly
             density, xrange, yrange = self.__density_cache[(par_indices_i[k], par_indices_j[k], s, solution)]
-            for line in [None, self.scen[s].linestyle]:
+            # fill contour only if desired but always draw contour line
+            fill = [self.scen[s].linestyle]
+            if self.scen[s].fill:
+                fill.append(None)
+                # color fill should come first
+                fill.reverse()
+            for line in fill:
                 artist = self.margs[s].contours_two(xrange, yrange, density,
-                                                    color=self.scen[s].c if line is None else 'black', line=line, grid=True,
+                                                    color=self.scen[s].c if (len(fill) == 1) or line is None else 'black', line=line, grid=True,
                                                     desired_levels=desired_levels,
[…]

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft] add note to describe Monte Carlo method

@@
   \caption{
-    \eos{
-    Constraints on real-valued [left] and complex-valued [right] scalar couplings
-    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
-    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
-    at 68\% (darker) and 95\% (lighter) probability when marginalising
-    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
-    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
-    For comparison the according constraints from all data when keeping
-    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
-    at 68\% (darker) and 95\% (lighter) probability.
-    }
+    Constraints (2D-marginalized) on complex-valued scalar couplings 
+    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in 
+    \reftab{tab:observables} (red) at 68\% (darker) and 95\% 
+    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
+    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
+    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
+    and $F_H^\mu$ \todo{What else?}
+    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
   }
@@
 interference with contributions involving $\wilson{10,\, 10'}$ do not change
-much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. However,
-for the most general case of complex-valued couplings destructive interference
-constrains (4 parameters) \todo{finish, describe \reffig{fig:scalar:SM-EFT}}
+much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. Since we
+consider here complex-valued couplings the allowed regions are circles rather
+than rings as for the case of real-valued couplings. The result of the simultaneous
+fit of complex-valued $\wilson{S,\,S',\,10,\,10'}$ is shown in 
+\reffig{fig:scalar:SM-EFT}.
 
@@
 
-Here we describe the theoretical treatment of observables and collect numerical
-input of the most relevant parameters. The software package {\tt EOS} \cite{Bobeth:2011gi,
-Bobeth:2011nj, EOS} is used for predictions of observables in $B_s\to \bar\mu\mu$
-and $B\to K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt pypmc},
-which incorporates the algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj}
-and in addition an implementation of the variational Bayes algorithm.
+Here we describe the theoretical treatment of observables and collect
+numerical input of the most relevant parameters. The software package
+{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
+predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
+K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
+  pypmc}, which incorporates the algorithm presented in
+\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
+implementation of the variational Bayes algorithm. \fred{Add, get DOI
+  for pypmc version}
 

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] changed caption of fig 3 and text in section IV.C

@@
 
-Here we describe the theoretical treatment of observables and collect
-numerical input of the most relevant parameters. The software package
-{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
-predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
-K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
-  pypmc}, which incorporates the algorithm presented in
-\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
-implementation of the variational Bayes algorithm. \fred{Add, get DOI
-  for pypmc version}
+Here we describe the theoretical treatment of observables and collect numerical
+input of the most relevant parameters. The software package {\tt EOS} \cite{Bobeth:2011gi,
+Bobeth:2011nj, EOS} is used for predictions of observables in $B_s\to \bar\mu\mu$
+and $B\to K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt pypmc},
+which incorporates the algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj}
+and in addition an implementation of the variational Bayes algorithm.
 

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[draft] corrections on introduction

--- 2015-07-08 tensor/draft/draft-tensor-op.tex
@@
     sentence ``independent of deviations in vector-coupling dominated
-    observables''}
+    observables''. There could be a bit of summary of outcome here, too}
 \end{abstract}
@@
 
-With the first run of data taking by the LHCb Collaboration at the Large Hadron
-Collider (LHC), $B$ physics has now also access to rather large samples of
-rare $B$-meson decays with branching ratios below the $10^{-5}$. In consequence,
-angular analyses of three- and four-body final states can be used to measure
-a larger number of additional observables. Namely rare $B$ decays that are driven
-at parton level by flavor-changing neutral current (FCNC) transitions $b\to s
-\bar\ell\ell$ constitute valuable probes of the standard model (SM) and provide
-constraints on its extensions, especially $B\to K^*(\to K\pi) \bar\ell\ell$, but
-also $B\to K \bar\ell\ell$.
-
-The angular distribution of $B\to K \bar\ell\ell$ in the angle $\theta_\ell$
-between the $B$ and $\ell^-$ as measured in the dilepton rest frame
+With the analysis of the data collected by the LHCb Collaboration
+during phase I at the Large Hadron Collider (LHC), we now have access
+to rather large samples of rare $B$ meson decays with branching ratios
+below $10^{-5}$. As a consequence, angular analyses of three- and
+four-body final states can be used to measure a larger number of
+observables than previously possible at the B factories BaBar and
+Belle. In this work we focus on rare $B$ decays driven at the parton
+level by the flavor-changing neutral-current (FCNC) transition $b\to s
+\bar\mu^+\mu^-$ that is well known to constitute a valuable probe of
+the standard model (SM) and to provide constraints on its extensions
+\fred{Here we need some references}.
+
+The angular distribution of $B\to K \bar\ell\ell$---normalized to the
+width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
+$\ell^-$ as measured in the dilepton rest frame is
 \begin{align}
@@
 \end{align}
-normalised to the width $\Gamma_\ell$, has been recently updated with 3 fb$^{-1}$
+ has been recently updated with 3 fb$^{-1}$
 by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,

### 2015-07-09 tensor/paper_plots.py
[tensor] Update prior predictive plots
* smaller C_T range, measurement with lines at 1 sigma
* compute moduli for SP

@@ -490,6 +490,17 @@ class MarginalContours(object):
         s = self.scen[scenarios[0]]
         x_range = m.out.fixed_values[s.pred_range][0], m.out.fixed_values[s.pred_range][-1]
         if measurement:
+            try:
+                linestyle = measurement.one_sigma_style.pop('linestyle')
+            except KeyError:
+                pass
+            else:
+                kwargs = dict(color=measurement.central_style.get('color', 'black'),
+                              linewidth=measurement.central_style.get('linewidth', 10),
+                              linestyle=linestyle)
+                P.axhline(measurement.lower, **kwargs)
+                P.axhline(measurement.upper, **kwargs)
+
             P.fill_between(x_range, [measurement.lower] * 2, [measurement.upper] * 2, **measurement.one_sigma_style)
             P.plot(x_range, [measurement.central] * 2, **measurement.central_style)
             legend_patches.append((matplotlib.patches.Patch(**measurement.one_sigma_style), measurement.label))
@@ -646,7 +657,30 @@ class Spring2015(object):
 
         square_figure(self.fig_size)
         matplotlib.rcParams['font.size'] = 20
+        '''
+        # absolute values
+        m = marg.margs[s]
+        data = m.out.samples
+        data[:, -4] = betrag(data, 8, 9)
+        data[:, -3] = betrag(data, 10, 11)
+        data[:, -2] = betrag(data, 12, 13)
+        data[:, -1] = betrag(data, 14, 15)
 
+        m.use_contours = True
+        m.plot_prior = False
+        m.fixed_1D_binning = True;
+        m.use_histogram = False; m.kde_bandwidth = 0.03; m.one_dim_n_bins = 500
+        # m.use_histogram = True; m.one_dim_n_bins = 50
+
+        for i in range(1, 5):
+            m.out.par_defs[-i].nuisance = False
+            m.out.par_defs[-i].min = 0.0
+            m.out.par_defs[-i].max = 1
+            P.clf()
+            m.one_dimensional(data.shape[1] - i)
+            P.savefig(marg.out(s + '_Betrag_%d' % i))
+        return
+        '''
         # 1D intervals for table
[…]

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added to sec. IV.C and figure captions

--- 2015-07-08 tensor/draft/draft-tensor-op.tex
@@
 
-\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-??}
+\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-107}
 
@@
     at 68\% (darker) and 95\% (lighter) probability. The constraints on
-    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$,
-    apart from a small shift of the contours by $(+0.2,\, +0.15)$.
+    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
+    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
+    by the black diamond.
   }
@@
     (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
+    The SM is indicated by the black diamond.
   }
@@
 is numerically of the order ${\cal O}(10^{-7})$ in the SM
-\todo{check large SM uncertainty of 30\% at low-$q^2$}
 \begin{equation}
@@
 \end{equation}
-when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
+when integrated over low- and high-$q^2$ regions. \todo{Elaborate on larger
+theory uncertainties at low-$q^2$, due to subleading corrections.
+Form factor uncertainties are small due to correlations, would be larger
+when neglecting them.}
+
+The angular observable $J_{6c}$
 is strictly zero for the approximation adopted here. Non-zero contributions
@@
 
-We find that the experimental measurement of $F_H^\mu$
+We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
 \begin{enumerate}
-\item imposes by itself constraints on tensor couplings $|{\cal C}_{T,\,T5}|
+\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
   < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
   In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}| < 0.33\,
+  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
   (0.43)$, even in the presence of non-standard contributions in vector
   couplings.
-\item allows for the first time to bound all four scalar and pseudo-scalar
-  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
-  Even when taking into account destructive interference with vector couplings
-  $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| <
-  0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
-  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
-  by about a factor four. In the future, measurements at LHCb and Belle II will
-  further tighten the bounds.
+\item allows for the first time to bound all four scalar couplings $\wilson{i}$ 
+  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s 
+  \to \bar\mu\mu)$. Even when taking into account destructive interference with
+  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and 
+  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) 
+  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
+  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
+  future, measurements at LHCb and Belle II will further tighten the bounds.
 
@@
   the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
-\item SM-EFT $\ldots$
 \end{enumerate}
-
-In all cases these \eos{constraints are weakened only slightly} in the presence
-of new physics in vector couplings from destructive interference.
-
-In the future this might change once measurements start to probe the SM expectation,
-as in this case constraints on the tensor and scalar couplings become so
-stringent that the formal suppression of vector couplings by $m_\ell / \sqrt{q^2}$
-is overcome. Our study of angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
-and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ shows that
+Our updated bounds on complex-valued tensor and scalar couplings are summarised
+in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
+interference effects with vector couplings. These bounds hold even in the most 
+general scenario of complex-valued tensor, scalar and vector couplings, showing
+also that the data is able to bound the real and imaginary parts of all Wilson
+coefficients simultaneously.
+
+As a special case, we considered also the scenario arising from the SM augmented
+by dimension 6 operators generalising existing studies to the case of complex-valued
+couplings. In this scenario tensor couplings are absent and additional
+relations between scalar couplings are enforced by the linear realisation of the
+$SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
+
+Our study of yet not measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
+and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see 
+\reftab{tab:postdictions}) shows that despite the current bounds on tensor couplings,
+enhancements of two orders of magnitude over the SM predictions are allowed for
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. On the other hand, current bounds
+on scalar couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$ are already quite 
+restrictive allowing only for small deviations from SM predictions in 
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry 
+$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by non-vanishing width of the 
+$B_s$ meson can still take any value in the range $[-1,\, 1]$.
 
@@
   $B\to K^*$ form factors \cite{Straub:2015ica}.
-  C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR''
+  C.B. was supported by the ERC Advanced Grant project ``FLAVOUR''
   (267104).

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[tensor/draft] review content in sec. III and IV

@@
 
-With the first run of data taking by the LHCb Collaboration at the Large Hadron
-Collider (LHC), $B$ physics has now also access to rather large samples of
-rare $B$-meson decays with branching ratios below the $10^{-5}$. In consequence,
-angular analyses of three- and four-body final states can be used to measure
-a larger number of additional observables. Namely rare $B$ decays that are driven
-at parton level by flavor-changing neutral current (FCNC) transitions $b\to s
-\bar\ell\ell$ constitute valuable probes of the standard model (SM) and provide
-constraints on its extensions, especially $B\to K^*(\to K\pi) \bar\ell\ell$, but
-also $B\to K \bar\ell\ell$.
-
-The angular distribution of $B\to K \bar\ell\ell$ in the angle $\theta_\ell$
-between the $B$ and $\ell^-$ as measured in the dilepton rest frame
+With the analysis of the data collected by the LHCb Collaboration
+during phase I at the Large Hadron Collider (LHC), we now have access
+to rather large samples of rare $B$ meson decays with branching ratios
+below $10^{-5}$. As a consequence, angular analyses of three- and
+four-body final states can be used to measure a larger number of
+observables than previously possible at the B factories BaBar and
+Belle. In this work we focus on rare $B$ decays driven at the parton
+level by the flavor-changing neutral-current (FCNC) transition $b\to s
+\bar\ell\ell$ that constitutes a valuable probe of the standard model
+(SM) and provides constraints on its extensions.
+
+The angular distribution of $B\to K \bar\ell\ell$---normalized to the
+width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
+$\ell^-$ as measured in the dilepton rest frame is
 \begin{align}
@@
   + \frac{1}{2} F_H^\ell
-  + A_{\rm FB}^\ell \cos\theta_\ell \,,
+  + A_{\rm FB}^\ell \cos\theta_\ell \,.
 \end{align}
-normalised to the width $\Gamma_\ell$, has been recently updated with 3 fb$^{-1}$
-by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,
-with unprecedented precision, and the first analysis of $B^0\to K_{S} \bar\mu\mu$
-has been reported as well. It provides the lepton-forward-backward asymmetry
-$A_{\rm FB}^\mu$ and the flat term $F_H^\mu$ in CP-averaged form and integrated
-over several bins in the dilepton invariant mass $q^2$. Similarly, the CP-averaged
-branching ratios, ${\cal B}_\mu = \tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli}
-and the rate CP asymmetry $A_{\rm CP}^\mu$ \cite{Aaij:2014bsa} are also
-available from 3 fb$^{-1}$.
-
-Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
-factors for vector and dipole
-couplings present in the SM, thereby enhancing their sensitivity to tensor and
-scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
-scalar couplings compared to helicity-suppressed vector couplings of the SM
-is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
-$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
-allow to perform current angular analysis without the assumption of vanishing
-scalar and tensor couplings in this decay mode. In the future also certain
-angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
-on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
-and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
-\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
-test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.
+LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the
+angular distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
+\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
+lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term
+$F_H^\mu$ in CP-averaged form and integrated over several bins in the
+dilepton invariant mass $q^2$\fred{sent. too long}. Similarly, the
+CP-averaged branching ratios, ${\cal B}_\mu = \tau_{B}
+\Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
+  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.
+
+Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong
+suppression factors for vector and dipole couplings present in the SM,
+thereby enhancing their sensitivity to tensor and scalar couplings
+\cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of scalar
+couplings compared to helicity-suppressed vector couplings of the SM
+is well-known from $B_s\to \bar\mu\mu$. \fred{Which model gives rise
+  to tensor contributions?} Unfortunately the limited data set of
+$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still
+does not allow to perform current angular analysis without the
+assumption of vanishing scalar and tensor couplings in this decay
+mode. In the future also certain angular observables in $B\to K^*
+\bar\ell\ell$ will provide additional constraints on such couplings,
+as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the linear
+combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
+\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the
+experimental test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 =
+0$~\cite{Bobeth:2012vn}.
 
@@
 
-This picture does not change in the presence of new physics contributions to
-vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
-non-vanishing tensor or scalar contributions are enhanced unless the
-dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
-for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
-$F_H^\ell$ is very sensitive to tensor couplings whereas $A_{\rm FB}^\ell$ to
-the interference of tensor and scalar couplings.
+This picture does not change in the presence of new physics
+contributions to vector and dipole operators $i =
+7,7',9,9',10,10'$. On the other hand, non-vanishing tensor or scalar
+contributions are enhanced unless the dynamics of NP implies similar
+suppression factors, i.e., lepton-Yukawa couplings for $F_H^\ell$ or
+$\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular, $F_H^\ell$
+is very sensitive to tensor couplings $A_{\rm FB}^\ell$ is sensitive
+to the interference of tensor and scalar couplings.
 
@@
       is available.
-      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$
-            or even $\in [-0.5, +0.5]$?}}
+      }
   \label{fig:FHvsCT}
@@
 There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
-\bar\ell\ell$ with the same properties, i.e. tensor and scalar contributions
-are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones
-present in the SM or their respective interference terms. These are $J_{6c}$
-and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
-with explicit formulas given in \refapp{app:BKstarellell}.
-In the limit of vanishing lepton mass one obtains that
+\bar\ell\ell$ with the same properties, i.e. tensor and scalar
+contributions are kinematically enhanced by a factor
+$\sqrt{q^2}/m_\ell$ over vector ones present in the SM or their
+respective interference terms. These are $J_{6c}$ and the two linear
+combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with
+explicit formulas given in \refapp{app:BKstarellell}. In our fits and
+predictions we include all kinematically suppressed terms. But for the
+purpose of illustration, we now consider the analytical dependence for
+vanishing lepton mass. In this limit,
 \begin{align}
@@
 
-To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we compare
-it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
-\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
-input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
-In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
-$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
-Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
-$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
-the sensitivity to tensor couplings is highest for $F_H^\ell$ at high $q^2$,
-also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
-whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
-the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
-stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
-and has some impact on the constraints on tensor couplings as will be
-discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
-high $q^2$ provides currently the most stringent constraints on the size of
-tensor couplings. Moreover, the dependence on vector couplings is such that
-$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
-$\wilson[NP]{9} \approx 0$.
-
-Important additional constraints on scalar couplings come from the branching
-ratio of $B_s \to \bar\mu\mu$ as given in \refeq{eq:Br-Bsmumu}. It provides
-the most stringent constraints on the moduli $|\wilson{S} - \wilson{S'}|$
-and $|\wilson{P} - \wilson{P'}|$ that are complementary to \refeq{eq:FH-dependence}
-in $B\to K \bar\ell\ell$ and depends only on the further combination
-$(\wilson{10} - \wilson{10'})$.
-
-Eventually we also explore the behaviour of derived constraints with respect to
-destructive interference with vector couplings $\wilson{9,\,9',\,10,\,10'}$.
-For this purpose we include also the branching ratio, the lepton forward-backward
-asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
-additional constraints on the real and imaginary parts of vector couplings.
-
-In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
-kinematically suppressed terms in predictions of measured observables as well
-as when predicting not yet measured observables. The experimental input of these
-observables is listed in \reftab{tab:observables} together with input for the
-$B\to K^{(*)}$ form factors. More details on the latter can be found in
+To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we
+compare it in \reffig{fig:FHvsCT} to the one of the branching ratios
+of $B\to K^{(*)} \bar\ell\ell$ for {$\ell = \mu$}, integrated over low
+and high $q^2$. The details of the numerical input and the treatment
+of uncertainty propagation can be found in \refapp{app:theory:inputs}.
+In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent
+global analysis of $b\to s (\gamma,\, \bar\ell\ell)$ data
+\cite{Descotes-Genon:2013wba, Altmannshofer:2013foa, Beaujean:2013soa,
+  Hurth:2014vma, Altmannshofer:2014rta} we show besides
+$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.1$. As
+can be seen, the sensitivity to tensor couplings is highest for
+$F_H^\ell$ at high $q^2$, also due to a partial cancellation of form
+factors \cite{Bobeth:2012vn}, whereas the one on $\wilson[NP]{9} < 0$
+is rather mild, in contrast to that of the branching ratios. For the
+latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows stronger dependence on
+$\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$ and has some
+impact on the constraints on tensor couplings as will be discussed in
+\refsec{sec:results}. In consequence, the data on $F_H^\ell$ at high
+$q^2$ provides currently the most stringent constraints on the size of
+tensor couplings. Moreover, the dependence on vector couplings is such
+that $\wilson[NP]{9} < 0$ leads to stronger constraints on
+$\wilson{T}$ than $\wilson[NP]{9} \approx 0$. \fred{Stress that
+  $J_{1c}+J_{2c}$ and $J_{1s}-3J_{2s}$ robust against changes in
+  $\wilson{9}$ but sensitive to $\wilson{T}$. $F_H$ sensitive to
+  $\wilson[NP]{9}$ only if $\wilson{T} \ne 0$. Mention prior predictive}
+
+Important additional constraints on scalar couplings come from the
+branching ratio of $B_s \to \bar\mu\mu$ as given in
+\refeq{eq:Br-Bsmumu}. It provides the most stringent constraints on
+the moduli $|\wilson{S} - \wilson{S'}|$ and $|\wilson{P} -
+\wilson{P'}|$ and further depends only on $(\wilson{10} -
+\wilson{10'})$. Thus it is complementary to $F_H^{\ell}$ in $B\to K
+\bar\ell\ell$; see Eq. \refeq{eq:FH-dependence}.
+
+Eventually we also explore the effect of interference with NP in the
+vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor
+and scalar couplings.  For this purpose we include also the branching
+ratio, the lepton forward-backward asymmetry and the rate CP asymmetry
+of $B\to K^* \bar\mu\mu$ as they provide additional constraints on the
+real and imaginary parts of $\wilson{9,\,9',\,10,\,10'}$.
+
+The experimental inputs of all observables entering our fits is listed
+in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
+form factors. More details on the latter can be found in
 \refapp{app:theory:inputs}.
@@
 
-In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$,
-the experimental measurement of $F_H^\mu$ constrains the combination
-$|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
-$\wilson{T}$ with vector couplings $\wilson{7,\,7',\,9,\,9'}$.
-The according 68\% (95\%) 1D-marginalized probability intervals are listed in
-\reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
-the constraints become tighter when utilising all observables in
-\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio of $B\to K^{*}
-\bar\mu\mu$ to tensor couplings (see also \reffig{fig:FHvsCT}). The latter
-stronger bounds are driven by the new lattice
-results of $B\to K^*$ form factors that yield too high predictions compared
-to the measurements~\cite{Horgan:2013pva}. Since tensor couplings contribute
-constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
-constrained. In this scenario, the measurements of $A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$
-does not pose constraints due to vanishing scalar couplings.
-
-Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
-by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$,
-($i = 9,10$) in order to access the stability of the bounds
-against destructive interference. In this case, $F_H^\mu$ by itself still provides
-bounds on $|\wilson{T,\,T5}|$ that are
-weakened by a factor of two since $F_H^\mu$ does not pose constraints on
-$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
-measurements of \reftab{tab:observables}
-are taken into account, the potential destructive effects of new physics
-in $\wilson{9,\,10}$ become reduced and almost the same constraints on $\wilson{T,\,T5}$
-are recovered, as shown in \reftab{tab:cTT5:1-dimCLs}.
-In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
-3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$
-by a \eos{factor of two}.
+In a scenario with only tensor complex-valued couplings $\wilson{T,\,
+  T5}$, the experimental measurement of $F_H^\mu$ constrains the
+combination $|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small
+interference of $\wilson{T}$ with vector couplings
+$\wilson{7,\,7',\,9,\,9'}$.  The according 68\% (95\%) 1D-marginalized
+probability intervals are listed in the first column of
+\reftab{tab:cTT5:1-dimCLs}. As can be seen further in the second
+column, the constraints become tighter when utilising all observables
+in \reftab{tab:observables}, mainly due to the sensitivity of the
+branching ratio of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see
+also \reffig{fig:FHvsCT}). The latter stronger bounds are driven by
+the new lattice results of $B\to K^*$ form factors that yield too high
+predictions compared to the measurements~\cite{Horgan:2013pva}. Since
+tensor couplings contribute constructively to ${\cal B}(B\to
+K^{*}\bar\mu\mu)$ large values are stronger constrained. In this
+scenario with vanishing scalar couplings, current measurements of
+$A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
+cf.~\refeq{eq:AFB-dependence}.
+
+We also perform a fit with non-zero complex-valued $\wilson{9,\,10}$
+by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\,
+7]$, ($i = 9,10$) in order to access the stability of the bounds
+against interference. Note that $\wilson{7,7'}$ appears in linear
+combinations with $\wilson{9,9'}$ such that its interference with
+tensor and scalar couplings is captured implicitly by allowing new
+physics in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM
+value without loss of generality. In this case, $F_H^\mu$ by itself
+still provides bounds on $|\wilson{T,\,T5}|$ that are weakened by a
+factor of two since $F_H^\mu$ does not pose constraints on
+$\wilson{9,\,10}$ (in the chosen prior range). Once additional
+experimental measurements of \reftab{tab:observables} are taken into
+account, the potential destructive effects of new physics in
+$\wilson{9,\,10}$ become reduced and almost the same constraints on
+$\wilson{T,\,T5}$ are recovered, as shown in the third column in
+\reftab{tab:cTT5:1-dimCLs}.  In consequence, the $F_H^\mu$
+measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the
+previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by 50\%.
+
+\fred{comment on last row: SM in all cartesian intervals but not in polar!}
 
@@
 
-Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
-kinematic suppression --- see \refeq{eq:FH-dependence} --- in the complementary
-manner $(\wilson{i} + \wilson{i'})$ to the branching ratio
-$\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only $(\wilson{i} - \wilson{i'})$,
-where $i = S,\, P$.
-Most notably, we find that the current measurement of $F_H^\mu$ does constrain
-the orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of $F_H^\mu$ and
-$\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound for the first time the moduli of
-all four couplings.
-
-The according four-parameter fit for complex-valued scalar couplings to the data of
-$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
-regions in the $\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
-\reffig{fig:scalar} and similarly for $\mbox{Im}(\wilson{i} \pm \wilson{i'})$. These
-bounds do not change when including all other data in \reftab{tab:observables}, since
-the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
-couplings and other observables are not very sensitive to scalar
-couplings. Quantitatively, the constraint from $\overline{\cal B}
-(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor four to five}
-stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
-
-Interference terms of $\wilson{P,\,P'}$ with vector couplings might weaken
-these bounds. Most important for $\overline{\cal B}(B_s \to \bar\mu\mu)$ are
-$(\wilson{10} - \wilson{10'})$ --- compare \refeq{eq:Br-Bsmumu:time0} --- and
-for $F_H^\ell$ similarly $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw},
-which are suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
-respectively. However, due to the large SM contribution of $\wilson[SM]{10}
-\simeq -4.2$, these terms are important for small pseudo-scalar couplings.
-We compile constraints on complex-valued scalar couplings from $i)$ only
-$F_H^\mu$, $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$
-their combination with all the other observables in \reftab{tab:observables},
-even allowing new physics in vector couplings
-$\wilson{9,\ 9',\, 10,\, 10'}$ in \reftab{tab:cSP:1-dimCLs}, utilising
-uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$.
-Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\mu\mu)$
-alone can bound all four complex-valued scalar couplings, however their
-combination is capable to do so and moreover, the bounds are stable against
-destructive interference with vector couplings. In the general case
-of complex-valued couplings, $\overline{\cal B}(B_s \to \bar\mu\mu)$ does
-not provide anymore constraints on sub-intervals in contrast to the
-case of real-valued couplings. In consequence, for example the ring-like
-structure in the $(\wilson{S}-\wilson{S'}) - (\wilson{P}-\wilson{P'}) $-plane
-of \reffig{fig:scalar} would turn into a filled circle.
-
-Our results improve and extend previous constraints in the literature to
-the most general case of complex-valued couplings. For example they are
-a factor \eos{two to three} more stringent then \cite{Becirevic:2012fy} and
-\eos{comparable} to \cite{Altmannshofer:2012az} once restricting to scenarios
-considered there.
+Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$
+without kinematic suppression --- see \refeq{eq:FH-dependence} --- in
+the complementary manner $(\wilson{i} + \wilson{i'})$ to the branching
+ratio $\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only
+$(\wilson{i} - \wilson{i'})$, where $i = S,\, P$.  Most notably, we
+find that the current measurement of $F_H^\mu$ does constrain the
+orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of
+$F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound
+for the first time the real and imaginary parts of all four couplings.
+
+The according four-parameter fit for complex-valued scalar couplings
+to the data of $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$
+results in the (2D-marginalized) regions in the $\mbox{Re}(\wilson{i}
+\pm \wilson{i'})$ ($i = S, P$) planes shown in
+\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i}
+\pm \wilson{i'})$ are very similar to those shown and thus
+omitted. These bounds do not change when including all other data in
+\reftab{tab:observables}, since the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$
+requires interference of scalar with tensor couplings and other
+observables are not very sensitive to scalar
+couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s
+\to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor
+four to five stronger than the one of $F_H^\mu$ on $(\wilson{i} +
+\wilson{i'})$.
+
+Interference terms of $\wilson{P,\,P'}$ with vector couplings might
+weaken these bounds. Most important for $\overline{\cal B}(B_s \to
+\bar\mu\mu)$ are $(\wilson{10} - \wilson{10'})$ --- compare
+\refeq{eq:Br-Bsmumu:time0} --- and for $F_H^\ell$ similarly
+$(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}, which are
+suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
+respectively \fred{hard to read}. However, these terms become
+important for small $\wilson{P,\,P'}$ due to the large SM contribution
+of $\wilson[SM]{10} \simeq -4.2$. We compile bounds on complex-valued
+scalar couplings in \reftab{tab:cSP:1-dimCLs} for only $F_H^\mu$, only
+$\overline{\cal B}(B_s \to \bar\mu\mu)$, and their combination with
+all the other observables in \reftab{tab:observables}. In the last
+case, we allow new physics in vector couplings $\wilson{9,\ 9',\,
+  10,\, 10'}$ assuming uniform priors for $\mbox{Re, Im}(\wilson{i})
+\in[-7,\, 7]$.  Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to
+\bar\ell\ell)$ alone can bound all four complex-valued scalar
+couplings, however their combination is capable to do so and moreover,
+the bounds are stable against destructive interference with vector
+couplings. In the special case of real-valued couplings,
+$\overline{\cal B}(B_s \to \bar\ell\ell)$ would lead to
+rings~\cite{Alonso:2014csa} instead of circles. In the most general
+scenario, we find the following bounds with 68\% (95\%) probability:
+\begin{equation}
+  \begin{aligned}
+    \left| \wilson{S} \right| & \in [0.06,\, 0.25]\; ([0.01,\, 0.36]),\\
+    \left| \wilson{S'} \right| & \in [0.09,\, 0.46]\; ([0.02,\, 0.73]),\\
+    \left| \wilson{P} \right| & \in [0.05,\, 0.21]\; ([0.01,\, 0.32]),\\
+    \left| \wilson{P'} \right| & \in [0.11,\, 0.42]\; ([0.02,\, 0.63]).
+  \end{aligned}
+\end{equation}
+
+Our results improve and extend previous bounds in the literature to
+the most general case of complex-valued couplings. For example they
+are a factor two to five more stringent than \cite{Becirevic:2012fy}
+and comparable to \cite{Altmannshofer:2012az} once restricting to the
+much simpler scenarios considered there.
 
@@
 
+\todo{Describe how we do prior/posterior predictive}
 %

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[tensor] Complete review of section IV

--- 2015-07-09 tensor/draft/draft-tensor-op.tex
@@
 and the steadily rising lower bounds on new particle masses towards higher energies
-from ATLAS and CMS such a scenario becomes more and more viable.
-
-A non-redundant set of dimension six operators of
-this effective theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
-matching to the effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the
-scale $\mu \sim m_W$ of the order of the $W$-boson mass in~\cite{D'Ambrosio:2002ex}
-for vector couplings $\wilson{7,\,9,\,10}$. The matching for tensor
-\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
-\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the linear
-representation impose the relations
+from ATLAS and CMS such a scenario becomes more and more viable \fred{hard to read}.
+
+A non-redundant set of dimension-six operators of this effective
+theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
+matching to the effective theory of $\Delta B = 1$ decays
+\refeq{eq:Heff} at the scale $\mu \sim m_W$ of the order of the
+$W$-boson mass in~\cite{D'Ambrosio:2002ex} for vector couplings
+$\wilson{7,\,9,\,10}$. The matching for tensor \refeq{eq:tensor:ops}
+and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows
+that SM gauge groups in conjunction with the linear representation
+\todo{Ask Martin, Oscar how to correctly phrase this} impose the
+relations
 \begin{align}
@@
 
-The SM gauge groups do not impose constraints on the operators of the SM-EFT that
-imply relations among $\wilson{10}$ and $\wilson{10'}$, so they
-are in general additional independent parameters. Here we find that destructive
-interference with contributions involving $\wilson{10,\, 10'}$ do not change
-much upper bounds on $|\wilson{S,\, S'}|$ found in \cite{Alonso:2014csa}. Since we
-consider here complex-valued couplings the allowed regions are circles rather
-than rings as for the case of real-valued couplings. The result of the simultaneous
-fit of complex-valued $\wilson{S,\,S',\,10,\,10'}$ is shown in
-\reffig{fig:scalar:SM-EFT}.
+The SM gauge group does not imply any relation between $\wilson{10}$
+and $\wilson{10'}$, so they are in general additional independent
+parameters. Here we find that destructive interference with
+contributions involving $\wilson{10,\, 10'}$ does not significantly
+alter the bounds on $\wilson{S,\, S'}$.  Since we consider here
+complex-valued couplings the allowed regions are circles rather than
+rings as for the case of real-valued
+couplings~\cite{Alonso:2014csa}. The result of the simultaneous fit of
+complex-valued $\wilson{S,\,S',\,10,\,10'}$ is shown in
+\reffig{fig:scalar:SM-EFT}. \fred{Circle smaller, prob. moves to
+  center compared to Alonso}
 
@@
 The most general fit of complex-valued tensor and scalar couplings
-$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vector couplings
-$\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
-and \refsec{sec:scalar} with same prior ranges --- does not yield very different
-bounds. The changes are only small and in fact the bounds tend to be even more
-stringent, because tensor and scalar couplings can contribute to $F_H^{\mu}$
-only constructively --- see \refeq{eq:FH-dependence}.
-As before branching-ratio measurements of $B\to K^{*}\bar\mu\mu$ help to strengthen
-the constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
-of complex-valued couplings the data is able to constrain all real and imaginary
-parts.
+$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vector
+couplings $\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of
+\refsec{sec:tensor} and \refsec{sec:scalar} with same prior ranges ---
+yields bounds very similar to those in tables \ref{tab:cTT5:1-dimCLs}
+and \ref{tab:cSP:1-dimCLs} . The changes are only small and in fact
+the bounds tend to be even more stringent because tensor and scalar
+couplings can contribute to $F_H^{\mu}$ only constructively --- see
+\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
+$B\to K^{*}\bar\mu\mu$ help to strengthen the constraints on
+$\wilson{T,\, T5}$. This demonstrates that even in the case of
+complex-valued couplings the data are able to constrain all real and
+imaginary parts.
 
@@
 
-Eventually, we present the yet allowed ranges due to non-standard tensor
-and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
-$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$
-in order to explore the potential of their future measurements in fits of the kind
-pursued in this work.
-The 68\% probability intervals are collected in \reftab{tab:postdictions}
-for the various model-independent scenarios, allowing for interference with
-non-zero vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
-and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities
-in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$
-GeV$^2$, respectively. Their posterior distributions have been obtained from the
-final posterior samples as explained in~\cite{Beaujean:2012uj}.
+Now we present the yet allowed ranges due to non-standard tensor and
+scalar couplings of the so far unmeasured angular observables
+$J_{6c}$, $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to
+K^*(\to K\pi)\bar\ell\ell$ in order to explore the potential of their
+future measurements in fits of the kind pursued in this work.  The
+68\% probability intervals are collected in \reftab{tab:postdictions}
+for the various model-independent scenarios, allowing for interference
+with non-zero vector couplings, in \refsec{sec:tensor},
+\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for
+$q^2$-integrated quantities in the low- and high-$q^2$ bins $q^2\in
+[1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ GeV$^2$,
+respectively. Their posterior distributions have been obtained from
+the final posterior samples as explained in~\cite{Beaujean:2012uj}
+\todo{check uncertainty propagation there}.
 
@@
 \end{align}
-is numerically of the order ${\cal O}(10^{-7})$ in the SM
-\begin{equation}
-\begin{aligned}
-  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
-  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
-\\
-  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
-  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
-\end{aligned}
-\end{equation}
-when integrated over low- and high-$q^2$ regions. \todo{Elaborate on larger
-theory uncertainties at low-$q^2$, due to subleading corrections.
-Form factor uncertainties are small due to correlations, would be larger
-when neglecting them.}
-
-The angular observable $J_{6c}$
-is strictly zero for the approximation adopted here. Non-zero contributions
-can be generated by QED corrections or potentially from higher-dimensional
-($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
-suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
-suppression must be compared to potential suppression present for tensor
-and scalar contributions in particular NP models in order to decide their
-relevance. Our model-independent fits are still in a realm where such
-considerations are insignificant since current experimental measurements, in
-combination with theory uncertainties, do not impose yet too stringent
-constraints on tensor and scalar couplings.
-
-Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in scenarios
-involving tensor couplings and only ${\cal O}(10^{-10})$ in their absence.
-Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
-deviations from the SM prediction are possible only in the presence of non-zero
-tensor couplings. In this case enhancement by two orders of magnitude are
-possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
-the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
-experimental constraints in \reftab{tab:observables}. In view of current
-experimental precision of $20\%$ of the branching ratio measurements at LHCb
-\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal O}(10^{-8})$, one can
-indeed hope for some sensitivity to such large effects in $(J_{1c} + J_{2c})$
-and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3 fb$^{-1}$ data set.
-\todo{Would be a nice place to cite method of moments paper?}
+is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
+$q^2 \in [1,\, 6]$ and $[15,\, 19]$ GeV$^2$ bins.
+
+The angular observable $J_{6c}$ is strictly zero in the absence of
+tensor and scalar couplings. Non-zero contributions can be generated
+in the SM by QED corrections or potentially from higher-dimensional
+($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to
+parametrical suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$,
+respectively. Such a suppression must be compared to potential
+suppression present for tensor and scalar contributions in particular
+NP models in order to decide their relevance. Our model-independent
+fits are still in a realm where such considerations are insignificant
+since current experimental measurements, in combination with theory
+uncertainties, do not impose yet too stringent constraints on tensor
+and scalar couplings.
+
+Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in
+scenarios involving tensor couplings only and about ${\cal
+  O}(10^{-10})$ in the presence of scalar couplings only. Both effects
+are due to interference with vector couplings. Due to the strong
+suppression of scalar couplings, the direct interference of scalar and
+tensor contributions the allowed region in the most general scenario
+\todo{schematic formula from notes}
+
+Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again
+substantial deviations from the SM prediction are possible only in the
+presence of non-zero tensor couplings. In this case enhancement by two
+orders of magnitude are possible up to the ${\cal O}(10^{-8})$ at
+high-$q^2$ and also at low-$q^2$ in the case of $(J_{1s} - 3\,
+J_{2s})$, always being consistent with all included experimental
+constraints in \reftab{tab:observables}. In view of current
+experimental precision of $20\%$ of the branching ratio measurements
+at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to
+the ${\cal O}(10^{-8})$, one can indeed hope for some sensitivity to
+such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$
+for the not yet published 3 fb$^{-1}$ data set.  \todo{Would be a nice
+  place to cite method of moments paper?}
+
+The CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
+non-vanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell})
+can still take any value in the range $[-1,\, 1]$ in scenarios with
+nonzero scalar couplings.
 

### 2015-07-10 tensor/paper_plots.py
[tensor] Recreate all plots with times font

@@ -776,7 +776,7 @@ class Spring2015(object):
                 m.one_dimensional(data.shape[1] - 1)
                 P.savefig(marg.out(s + '_Betrag_' + name))
 
-    def fig_pred(self, scen_obs, measurement, ylabel, xlabel=r'$C_{T}$', yrange=None,
+    def fig_pred(self, scen_obs, measurement, ylabel, xlabel=r'$\wilson{T}$', yrange=None,
                  legendpos='upper center', rescale=None):
         '''Plot predictions/postdictions with uncertainty varying one parameter over a fixed range.'''
 
@@ -829,7 +829,7 @@ class Spring2015(object):
         P.savefig(marg.out(scenario_names[0]))
 
     def np_label(self, value):
-        return r'$\mathcal{C}_9^{\rm NP} = ' + str(value) + '$'
+        return r'$\wilson[NP]{9} = ' + str(value) + '$'
 
     def scenario_comparison(self, obs, s_min, s_max, scen=('ct', 'ct_c9_1dot1'), delta_c9=(0, -1.1)):
         return [dict(name=scen[i] + '_' + obs + '%gto%g' % (s_min, s_max), unc_label=self.np_label(delta_c9[i])) for i
@@ -1000,8 +1000,8 @@ if __name__ == '__main__':
     matplotlib.rcParams['text.latex.unicode'] = True
     matplotlib.rcParams['font.size'] = 28
     matplotlib.rcParams['text.latex.preamble'] = r'''
-    \usepackage[proportional]{libertine}
-    \usepackage[libertine]{newtxmath}
+    \usepackage{mathptmx}
+    \newcommand{\wilson}[2][{}]{\mathcal{C}_{#2}^{\mathrm{#1}}}
     '''
 
     # enlarge ticks
@@ -1015,7 +1015,6 @@ if __name__ == '__main__':
 
     f = Spring2015()
     f.figSP()
-    # f.figTT5()
-    # f.fig_1()
-    # f.fig_constrained()
-    # f.all()
+    f.figTT5()
+    f.fig_1()
+    f.fig_constrained()

### 2015-07-10 tensor/draft/draft-tensor-op.tex
[tensor] Reformat draft to EPJC

@@
-\documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
+% \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
+\documentclass[twocolumn,epjc3]{svjour3}
+
+\RequirePackage[T1]{fontenc}
+\RequirePackage{mathptmx}      % use Times fonts if available on your TeX system
+\RequirePackage{flushend}
+\RequirePackage[numbers,sort&compress]{natbib}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}
+
+\journalname{Eur. Phys. J. C}
 
@@
 \usepackage{graphicx}
-\usepackage{hyperref}
 \usepackage{listings}
@@
 \def \refeq#1{(\ref{#1})}
-\def \refsec#1{sec.~\ref{#1}}
-\def \refSec#1{Sec.~\ref{#1}}
-\def \refapp#1{app.~\ref{#1}}
-\def \reffig#1{fig.~\ref{#1}}
-\def \reftab#1{tab.~\ref{#1}}
+\def \refsec#1{Section \ref{#1}}
+\def \refapp#1{\ref{#1}}
+\def \reffig#1{Figure \ref{#1}}
+\def \reftab#1{Table \ref{#1}}
 
@@
 %%
-\newcommand{\danny}[1]{{\color{purple}{#1}}}
 \newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
 \newcommand{\fred}[1]{{\color{green}{#1}}}
-\newcommand{\todo}[1]{{\color{blue}{ {\bf ToDo: }{#1}}}}
+\newcommand{\todo}[1]{{\color{purple}{ {\bf ToDo: }{#1}}}}
 \newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}
@@
 
+% better line breaks, http://tex.stackexchange.com/questions/32062
+\sloppy
+
 \title{Constraints on tensor and scalar couplings from
@@
 }
-
-\author{Frederik Beaujean}
-\affiliation{
-  C2PAP, Excellence Cluster Universe,\\
+\author{Frederik Beaujean\thanksref{e1,addr1}
+  \and
+  Christoph Bobeth\thanksref{e2,addr2}
+  \and
+  Stephan Jahn\thanksref{e3,addr3,addr4}
+}
+\institute{
+  C2PAP, Excellence Cluster Universe,
   Ludwig-Maximilians-Universit\"at M\"unchen,
-  Garching, Germany
-}
-
-\author{Christoph Bobeth}
-\affiliation{
+  Garching, Germany\label{addr1}
+  \and
   Institute for Advanced Study,
   Technische Universit\"at M\"unchen,
-  Garching, Germany
-}
-
-\author{Stephan Jahn}
-\affiliation{
-  Max Planck institute for physics, Munich.\\
+  Garching, Germany\label{addr2}
+  \and
   Excellence Cluster Universe,
   Technische Universit\"at M\"unchen,
-  Garching, Germany
-}
+  Garching, Germany\label{addr3}
+  \and
+  \emph{Present Address:}
+  Max Planck institute for physics, Munich, Germany\label{addr4}
+}
+
+\thankstext[$\star$]{t1}{\todo{EOS-2015-??}, FLAVOUR(267104)-ERC-107}
+\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
+\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
+\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}
 
 \date{\today}
-
-\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-107}
+\maketitle
 
@@
 \end{abstract}
-
-%
-%
-%
-
-\maketitle
 
@@
   \setlength{\relwidth}{0.33\textwidth}
+  \begin{center}
     \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
@@
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
-  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
+    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
@@
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
+  \end{center}
 \caption{ The sensitivity to the tensor coupling
@@
 \\
-\hline \hline
+\hline
 ${B\to K}$ form factors
@@
   \renewcommand{\arraystretch}{1.3}
-  %\resizebox{\textwidth}{!}{
-  \begin{tabular}{c|ccc}
+  \begin{center}
+  \begin{tabular}{cccc}
   \hline
@@
   \\
-  \hline \hline
+  \hline
   $\mbox{Re}\,\wilson{T}$
@@
   \end{tabular}
-%}
+
+  \end{center}
+
   \renewcommand{\arraystretch}{1.0}
@@
 \begin{figure*}
+  \begin{center}
     \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
@@
     \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
+  \end{center}
   \caption{
@@
   \renewcommand{\arraystretch}{1.3}
-%\resizebox{\textwidth}{!}{
-  \begin{tabular}{c|ccc}
+  \begin{center}
+  \begin{tabular}{cccc}
   \hline
@@
   \\
-  \hline \hline
+  \hline
   $\mbox{Re}(\wilson{S} - \wilson{S'})$
@@
   \end{tabular}
-%}
+  \end{center}
+
   \renewcommand{\arraystretch}{1.0}
@@
 \begin{figure*}
+  \begin{center}
       \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
       \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
+    \end{center}
     \caption{
@@
   \renewcommand{\arraystretch}{1.5}
-  %\resizebox{\textwidth}{!}{
-  \begin{tabular}{cc|c|ccc}
+  \begin{center}
+  \begin{tabular}{cccccc}
   \hline
@@
   \\
-  \hline \hline
+  \hline
   \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
@@
   \\
-  \hline \hline
-  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
+  \hline
+  \multicolumn{2}{c}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
   & 1
@@
   \end{tabular}
-%}
+  \end{center}
   \renewcommand{\arraystretch}{1.0}
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\begin{acknowledgments}
+\begin{acknowledgements}
   We are grateful to Danny van Dyk for helpful discussions and his support on
@@
   (267104).
-\end{acknowledgments}
+\end{acknowledgements}
 
@@
 The interesting combinations are
-
-\begin{widetext}
 \begin{align}
-  \frac{4}{3} J_{6c} & =
-  4\, \beta_\ell\, \mbox{Re} \bigg[ 2\, (A_{t0}^{} A_S^* - A_{\parallel\perp}^{} A_P^*) +
-      \frac{m_\ell}{\sqrt{q^2}} \big[(A_0^L + A_0^R) A_S^*
+  \frac{4}{3} J_{6c}  =
+  4\, \beta_\ell\, \mbox{Re} \bigg[ &2\, (A_{t0}^{} A_S^* - A_{\parallel\perp}^{} A_P^*) \nonumber\\
+  &+ \frac{m_\ell}{\sqrt{q^2}} \big[(A_0^L + A_0^R) A_S^*
            + 4\, A_{\parallel\perp}^{} \tilde{A}_t^* \big] \bigg],
-\\
-  \frac{4}{3}\(J_{1c} + J_{2c}\) & =
-    \Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2
-   + \Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2 + \beta_\ell^2\, |A_S|^2
+\end{align}
+\begin{align}
+  \frac{4}{3}\(J_{1c} + J_{2c}\)  = \;
+    &\Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2 + \beta_\ell^2\, |A_S|^2 \nonumber\\
+   + &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
    + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2,
-\\[0.2cm]
-  \frac{4}{3}\(J_{1s} - 3\, J_{2s}\) &  =
-    \Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\perp^L + A_\perp^R) + 4\, A_{t\perp} \Bigg|^2
-  + \Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\parallel^L + A_\parallel^R) + 4\, A_{t\parallel} \Bigg|^2.
  \end{align}
-\end{widetext}
-Above $\beta_\ell^2 = 1 - 4 m_\ell^2/q^2 \to 1$ for $m_\ell \ll \sqrt{q^2}$.
-The condition is well fulfilled for $\ell = e$ and $1\, \mbox{GeV}^2\lesssim q^2$,
-provided that tensor and scalar Wilson coefficients do not receive additional
-suppression factors. For $\ell = \mu$ the value of $q^2$ should not be too low,
-whereas in the case $\ell = \tau$, these observables are not anymore dominated by
-tensor and/or scalar contributions alone, and the full lepton-mass dependence has
-to be taken into account.
-
-Finally, we note that the term
-\begin{widetext}
  \begin{align}
-  \Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
-  + \beta_\ell^2\, |A_S|^2  & =
-  4 N^2 \lambda A_0^2 \Bigg\{
-    \beta_\ell^2 \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2
-  + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
+ \frac{4}{3}\(J_{1s} - 3\, J_{2s}\) = \;
+    &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\perp^L + A_\perp^R) + 4\, A_{t\perp} \Bigg|^2 \nonumber\\
+  + &\Bigg| \frac{\sqrt{2}\, m_\ell}{\sqrt{q^2}} (A_\parallel^L + A_\parallel^R) + 4\, A_{t\parallel} \Bigg|^2.
+\end{align}
+Above $\beta_\ell^2 = 1 - 4 m_\ell^2/q^2 \to 1$ for $m_\ell \ll
+\sqrt{q^2}$.  The condition is well fulfilled for $\ell = e$ and $1\,
+\mbox{GeV}^2\lesssim q^2$, provided that tensor and scalar Wilson
+coefficients do not receive additional suppression factors. For $\ell
+= \mu$ the value of $q^2$ should not be too low, whereas in the case
+$\ell = \tau$, these observables are not anymore dominated by tensor
+and/or scalar contributions alone, and the full lepton-mass dependence
+has to be taken into account.  Finally, we note that the term
+\begin{align}
+  &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
+   + \beta_\ell^2\, |A_S|^2   =  4 N^2 \lambda A_0^2 \Bigg\{
+    \beta_\ell^2 \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2\nonumber\\
+  &\hskip1cm + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
      + \frac{2 m_\ell}{q^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
@@
 decays $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
-\begin{equation}
+\begin{align}
 \label{eq:Br-Bsmumu:time0}
-\begin{aligned}
-  {\cal B}(B_s \to \bar\ell\ell) & =
+  {\cal B}(B_s \to \bar\ell\ell) &=
     \frac{G_F^2 \alpha_e^2 |V_{tb}^{} V_{ts}^*|^2}{64\, \pi^3}
     M_{B_s}^5 f_{B_s}^2 \tau_{B_s} \beta_\ell(q^2 = M_{B_s}^2)
-\\
-   & \hskip0.5cm \times \Bigg\{
-    \beta_\ell^2(q^2 = M_{B_s}^2) \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2
-  + \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
+\nonumber\\
+    & \times \Bigg\{
+    \beta_\ell^2(q^2 = M_{B_s}^2) \Bigg|\frac{\wilson[]{S} - \wilson[']{S}}{m_b + m_s}\Bigg|^2 \nonumber\\
+    &+ \Bigg|\frac{\wilson[]{P} - \wilson[']{P}}{m_b + m_s}
      + \frac{2 m_\ell}{M_{B_s}^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
     \Bigg\}\,.
-\end{aligned}
-\end{equation}
-\end{widetext}
+  \end{align}
 Hence there is some complementarity among $(J_{1c} + J_{2c})$ in $B \to K^*
@@
 \hline
+\todo{fill in}\\
+\hline
 \end{tabular}
@@
 
-\begin{table}
+\begin{table*}
+  \begin{center}
     \renewcommand{\arraystretch}{1.3}
-    \begin{tabular}{c|ccc}
+    \begin{tabular}{cccc}
         \hline
@@
     \renewcommand{\arraystretch}{1.3}
-    \begin{tabular}{c|ccccccccc}
+    \begin{tabular}{cccccccccc}
         \hline
@@
     \end{tabular}
+
+  \end{center}
+
     \renewcommand{\arraystretch}{1.0}
@@
       }
-\end{table}
+\end{table*}
 

### 2015-07-13 tensor/draft/draft-tensor-op.tex
[draft] proofread appendix A

@@
 
-Here we present those angular observables $J_i$ in $B\to K^* \bar\ell\ell$
-in which tensor and scalar contributions are kinematically enhanced by a factor
-$\sqrt{q^2}/m_\ell$ over vector once present in the SM or their respective
-interference terms using results and notation from \cite{Bobeth:2012vn}.
-
-For convenience, we split the time-like transversity amplitude into
+Here we focus on those angular observables $J_i$ in $B\to K^* \bar\ell\ell$ in
+which tensor and scalar contributions are kinematically enhanced by a factor
+$\sqrt{q^2}/m_\ell$ compared to the vector contributions of the SM or the
+respective interference terms. The results and the notation follow
+\cite{Bobeth:2012vn}.
+
+For convenience, we split the time-like transversity amplitude $A_t$ into two
+parts as
 \begin{align}
   A_t &
-  = \tilde{A}_t - \frac{1}{2} \frac{\sqrt{q^2}}{m_\ell} A_P
+  = \tilde{A}_t - \frac{1}{2} \frac{\sqrt{q^2}}{m_\ell} A_P \, .
 \end{align}
-that depend on the Wilson coefficients $i = 10, 10', P, P'$ and the scalar
-$B\to K^*$ form factor $A_0(q^2)$, a normalisation factor $N$ and the
-K{\"a}ll{\'e}n-function $\lambda$ (see \cite{Bobeth:2012vn})
+Both terms depend on the scalar $B\to K^*$ form factor $A_0(q^2)$, a
+normalization factor $N$, and the K{\"a}ll{\'e}n-function $\lambda$ (see
+\cite{Bobeth:2012vn}) but have a different dependence on the Wilson coefficients
+$i = 10, 10', P, P'$:
 \begin{equation}
@@
 \end{equation}
-The lepton-flavor index $\ell$ at Wilson coefficients is omitted for
-brevity throughout this section.
-
-In full generality angular observables in $B\to K^* \bar\ell\ell$ depend on
-seven transversity amplitudes with vector and dipole contributions
-$A_{0,\,\perp,\,\parallel}^{L,R}$, and $\tilde{A}_t$, one scalar and one
-pseudoscalar amplitude $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$,
-and six tensor amplitudes: $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
-\wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$.
-The interesting combinations are
+The lepton-flavor index $\ell$ of Wilson coefficients is omitted for brevity
+throughout.
+
+In full generality, the angular observables in $B\to K^* \bar\ell\ell$ depend on
+seven transversity amplitudes with vector and dipole contributions,
+$A_{0,\,\perp,\,\parallel}^{L,R}$ and $\tilde{A}_t$, one scalar and one
+pseudoscalar amplitude, $A_{S,\,P} \propto (\wilson[]{S,P} - \wilson[]{S',P'})$,
+and six tensor amplitudes, $A_{\parallel\perp,\,t\perp,\,0\parallel} \propto
+\wilson[]{T}$ and $A_{t0,\,t\parallel,\,0\perp} \propto \wilson[]{T5}$.  The
+interesting combinations are
 \begin{align}
@@
 \begin{align}
+  \label{eq:j1c-j2c}
   \frac{4}{3}\(J_{1c} + J_{2c}\) = \;
-    &\Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2 + \beta_\ell^2\, |A_S|^2 \nonumber\\
-   + &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2
-   + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2,
+  &\Bigg| \frac{2\, m_\ell}{\sqrt{q^2}} (A_0^L + A_0^R) + 4\, A_{t0} \Bigg|^2    + 16\, \beta_\ell^2\, |A_{\parallel\perp}|^2 \nonumber\\
+  + &\Bigg|\frac{2\, m_\ell}{\sqrt{q^2}}\, \tilde{A}_t - A_P\Bigg|^2 +
+  \beta_\ell^2\, |A_S|^2,
  \end{align}
@@
 \end{align}
-Above $\beta_\ell^2 = 1 - 4 m_\ell^2/q^2 \to 1$ for $m_\ell \ll
-\sqrt{q^2}$.  The condition is well fulfilled for $\ell = e$ and $1\,
-\mbox{GeV}^2\lesssim q^2$, provided that tensor and scalar Wilson
-coefficients do not receive additional suppression factors. For $\ell
-= \mu$ the value of $q^2$ should not be too low, whereas in the case
-$\ell = \tau$, these observables are not anymore dominated by tensor
-and/or scalar contributions alone, and the full lepton-mass dependence
-has to be taken into account.  Finally, we note that the term
+The function $\beta_\ell^2(q^2) \equiv 1 - 4 m_\ell^2/q^2$ tends to 1 for $m_\ell \ll
+\sqrt{q^2}$.  This condition is well fulfilled for $\ell = e$ and $q^2 \gtrsim
+1\, \mbox{GeV}^2$, provided that tensor and scalar Wilson coefficients do not
+receive additional suppression factors. For $\ell = \mu$, the value of $q^2$
+should not be too low, whereas in the case $\ell = \tau$, these observables are
+not anymore dominated by tensor and scalar contributions alone, and the full
+lepton-mass dependence has to be taken into account.  Finally, we note that the
+second part of $(J_{1c} + J_{2c})$ in \refeq{eq:j1c-j2c},
 \begin{align}
@@
      + \frac{2 m_\ell}{q^2} \big(\wilson[]{10} - \wilson[']{10}\big) \Bigg|^2
-    \Bigg\}
+    \Bigg\}\,,
 \end{align}
-entering $(J_{1c} + J_{2c})$, resembles very much the branching ratio of the rare
-decays $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
+ resembles very much the branching ratio of the rare
+decay $B_s \to \bar\ell\ell$ in the limit $q^2 \to M_{B_s}^2$
 \begin{align}
@@
   \end{align}
-Hence there is some complementarity among $(J_{1c} + J_{2c})$ in $B \to K^*
-\bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$, however former depends also
-on tensor couplings and vector couplings. The helicity suppression
-factor $4\,m_\ell^2/q^2$ of vector couplings is weaker in
-$B \to K^* \bar\ell\ell$ decays than the corresponding factor
-$4\,m_\ell^2/M_{B_s}^2$ in $B_s \to \bar\ell\ell$.
+  Hence there is some similarity between $(J_{1c} + J_{2c})$ in $B \to K^*
+  \bar\ell\ell$ and ${\cal B}(B_s \to \bar\ell\ell)$ in their dependence on the
+  couplings but the former has additional dependence on tensor and vector
+  couplings through the other transversity amplitudes.  In $B \to K^*
+  \bar\ell\ell$, the helicity suppression factor $4\,m_\ell^2/q^2$ of vector
+  couplings is weaker than the corresponding factor $4\,m_\ell^2/M_{B_s}^2$ in
+  $B_s \to \bar\ell\ell$.
 
   Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
-corresponds to the unintegrated branching ratio at time $t=0$. Due to the non-vanishing
-decay width $\Delta\Gamma_s$, experiments measure the average
-time-integrated branching ratio --- denoted by $\overline{\cal B}$ ---
-and both are related as \cite{DeBruyn:2012wk}
+  corresponds to the unintegrated branching ratio at time $t=0$. Due to the
+  non-vanishing decay width $\Delta\Gamma_s$, experiments measure the average
+  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
+  are related as \cite{DeBruyn:2012wk}
 \begin{align}
@@
 $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
-optimised observables. For this purpose we use form factor relations at leading
+optimized observables. For this purpose we use form-factor relations at leading
 order in $1/m_b$ and neglect terms suppressed by $m_\ell/\sqrt{q^2}$. With the
@@
 Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalisations,
-unless chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ vanish, because then
-$\rho_1^+ = \rho_1^-$ holds. There are three potential normalisations
+unless the chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ because then
+$\rho_1^+ = \rho_1^-$ holds. There are three potential normalizations
 \begin{equation}
@@
 \end{equation}
-where the last one depends only on vector couplings, i.e., is free of
-tensor and scalar ones. In the $J_{1s}$ and $J_{2s}$, tensor couplings
-contribute either cumulative or destructive to vector couplings in
-$\rho_1^\pm$.
+where the last one depends only on vector couplings; i.e., is free of tensor and
+scalar ones. In $J_{1s}$ and $J_{2s}$, tensor couplings contribute either
+cumulatively or destructively to vector couplings in $\rho_1^\pm$.
 
 A similar situation arises for $(J_{1c} + J_{2c})$, where no appropriate
-normalisation exists, unless scalar couplings vanish. In this special
-case, either $J_{1c}$ and also $J_{2c} = -3/2 (\rho_1^- - \rho_1^T) f_0^2$ will
-depend only on $f_0$ and can be used as normalisation. In the general case,
-$J_{2c}$ still depends only on tensor couplings and was used at low $q^2$
-\cite{Matias:2012xw}. Finally we note that
+normalization exists, unless scalar couplings vanish. In this special case, both
+$J_{1c}$ and $J_{2c} = -3/2 (\rho_1^- - \rho_1^T) f_0^2$ depend only on $f_0$
+and can be used as normalization. In the general case, $J_{2c}$ still depends
+only on tensor couplings and was used at low $q^2$ \cite{Matias:2012xw}. Finally
+we note that
 \begin{equation}

### 2015-07-13 tensor/draft/draft-tensor-op.tex
[draft] add appendix on MC methods

@@
 
-Here we describe the theoretical treatment of observables and collect
-numerical input of the most relevant parameters. The software package
-{\tt EOS} \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for
-predictions of observables in $B_s\to \bar\mu\mu$ and $B\to
-K^{(*)}\bar\ell\ell$. The fit is performed with the package {\tt
-  pypmc}, which incorporates the algorithm presented in
-\cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an
-implementation of the variational Bayes algorithm. \fred{Add, get DOI
-  for pypmc version}
+Here we describe the theoretical treatment of observables and collect numerical
+input of the most relevant parameters. The software package {\tt EOS}
+\cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for the calculation of
+observables in $B_s\to \bar\mu\mu$ and $B\to K^{(*)}\bar\ell\ell$ and associated
+constraints. Both the likelihood and the prior are defined entirely within EOS.
 
@@
 
-\todo{Describe how we do prior/posterior predictive}
+\section{Monte Carlo sampling}
+\label{app:mc}
+\todo{reference in main text}
+The marginalization of the posterior is performed with the package {\tt
+  pypmc}~\cite{beaujean_2015_20045}, which incorporates the algorithm presented
+in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an implementation
+of the variational Bayes algorithm. In every analysis we first run multiple
+adaptive Markov chains (MCMC) in parallel through \texttt{pypmc}. If necessary,
+chains are seeded at the SM point to exclude solutions in which multiple
+nuisance parameters simultaneously deviate strongly from prior expectations.
+
+In total, there are 19 parameters $\alpha^i_j$ to describe $B\to K^*$ form
+factors and most of them are strongly correlated. But it is well known that
+strong correlation leads to poor sampling as it can cause the random-walk Markov
+chains to spend significant time in regions of low probability and thus produce
+spurious peaks. To mitigate this issue, we perform a fit to form-factor
+constraints without any experimental data and use the resulting covariance
+matrix to transform parameters such that the new parameters are uncorrelated. \todo{Why no Jacobian involved?}
+
+In all but three cases, the Markov chains then give reliable results. But when
+we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
+strong correlations appear again. As a final solution, we then use importance
+sampling with the initial proposal function determined by a fit of a Gaussian
+mixture to the MCMC samples within the variational Bayes approximation. As the
+posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
+components are need; i.e., 3 components proved optimal by the variational
+approximation to the model evidence. In the most challenging run with 62
+parameters, we obtain a relative effective sample size of only 0.038\%. We want
+to have enough samples such that the 68\% region is determined with a relative
+precision of about 1\%. As a rule of thumb, we consider the ``relative error of
+the error'' given by $1/\sqrt{2 N_{\rm eff}}$~\cite[ch. 37]{Agashe:2014kda}.
+
+% consider the binomial model with flat
+% prior. Then the standard deviation over the mean of the posterior on the
+% binomial parameter $p$ is $\sqrt{ \frac{1-p}{N_{\rm eff} p}}$ where $N_{\rm
+%   eff}$ is the number of independent samples.
+
+In the 62D case, we compute $1.1\cdot10^6$ importance samples such that $N_{\rm
+  eff} \approx 3500$ and the estimated relative error of the error is 1.2\% and
+thus good enough for our purposes.
+
+To create the smooth marginal plots in Figures
+\ref{fig:FHvsCT}--\ref{fig:scalar:SM-EFT}, we apply kernel density estimation
+for MCMC and importance samples using the fast \texttt{figtree}
+library~\cite{morariu08figtree}. In the latter case, we additionally crop 500
+outliers.
+
 %

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft, mcmc] clarify jacobian issue

@@
 strong correlation leads to poor sampling as it can cause the random-walk Markov
-chains to spend significant time in regions of low probability and thus produce
-spurious peaks. To mitigate this issue, we perform a fit to form-factor
-constraints without any experimental data and use the resulting covariance
-matrix to transform parameters such that the new parameters are uncorrelated. \todo{Why no Jacobian involved?}
+chains to spend an excessive amount of time in regions of low probability and
+thus produce spurious peaks. To mitigate this issue, we perform a fit to
+form-factor constraints without any experimental data and use the resulting
+covariance matrix to transform parameters such that the new parameters are
+uncorrelated.
 

### 2015-07-14 py-eos/mcmc.py

@@ -16,7 +16,13 @@ hdf5_subdirectory = '/chain #0'
 
 class Target(object):
     """Transform parameters with a linear transformation so pypmc samples
-     *uncorrelated* parameters but eos sees the correlated parameters."""
+    *uncorrelated* parameters but eos sees the correlated parameters. We
+    don't have to include a Jacobian determinant because the
+    transformation matrix is a constant triangular matrix, so the
+    determinant is just a constant that modifies the anyway arbitray
+    normalization of the likelihood.
+
+    """
     def __init__(self, analysis, filename=None):
 
         self.analysis = analysis

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] finish MC appendix

@@
 
-Now we present the yet allowed ranges due to non-standard tensor and
-scalar couplings of the so far unmeasured angular observables
-$J_{6c}$, $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to
-K^*(\to K\pi)\bar\ell\ell$ in order to explore the potential of their
-future measurements in fits of the kind pursued in this work.  The
-68\% probability intervals are collected in \reftab{tab:postdictions}
-for the various model-independent scenarios, allowing for interference
-with non-zero vector couplings, in \refsec{sec:tensor},
-\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for
-$q^2$-integrated quantities in the low- and high-$q^2$ bins $q^2\in
-[1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ GeV$^2$,
-respectively. Their posterior distributions have been obtained from
-the final posterior samples as explained in~\cite{Beaujean:2012uj}
-\todo{check uncertainty propagation there}.
+Now we present the yet allowed ranges due to non-standard tensor and scalar
+couplings of the so far unmeasured angular observables $J_{6c}$, $(J_{1s} - 3\,
+J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$ in order to
+explore the potential of their future measurements in fits of the kind pursued
+in this work.  The 68\% probability intervals are collected in
+\reftab{tab:postdictions} for the various model-independent scenarios, allowing
+for interference with non-zero vector couplings, in \refsec{sec:tensor},
+\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for $q^2$-integrated
+quantities in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and
+$q^2\in [15,\, 19]$ GeV$^2$, respectively. Their posterior distributions have
+been obtained from the posterior samples as explained in~\ref{app:mc}.
 
@@
 \label{app:mc}
-\todo{reference in main text}
-The marginalization of the posterior is performed with the package {\tt
-  pypmc}~\cite{beaujean_2015_20045}, which incorporates the algorithm presented
-in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition an implementation
-of the variational Bayes algorithm. In every analysis we first run multiple
-adaptive Markov chains (MCMC) in parallel through \texttt{pypmc}. If necessary,
-chains are seeded at the SM point to exclude solutions in which multiple
-nuisance parameters simultaneously deviate strongly from prior expectations.
+\todo{reference in main text} The marginalization of the posterior is performed
+with the package {\tt pypmc}~\cite{beaujean_2015_20045}, which incorporates the
+algorithm presented in \cite{Beaujean:2013:PMC, Beaujean:2012uj} and in addition
+an implementation of the variational Bayes algorithm. In every analysis we first
+run multiple adaptive Markov chains (MCMC) in parallel through
+\texttt{pypmc}. If necessary, chains are seeded at the SM point to exclude
+solutions in which multiple nuisance parameters---mostly for hadronic
+corrections---simultaneously deviate strongly from prior expectations.
 
@@
 posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
-components are need; i.e., 3 components proved optimal by the variational
-approximation to the model evidence. In the most challenging run with 62
-parameters, we obtain a relative effective sample size of only 0.038\%. We want
-to have enough samples such that the 68\% region is determined with a relative
-precision of about 1\%. As a rule of thumb, we consider the ``relative error of
-the error'' given by $1/\sqrt{2 N_{\rm eff}}$~\cite[ch. 37]{Agashe:2014kda}.
-
-% consider the binomial model with flat
-% prior. Then the standard deviation over the mean of the posterior on the
-% binomial parameter $p$ is $\sqrt{ \frac{1-p}{N_{\rm eff} p}}$ where $N_{\rm
-%   eff}$ is the number of independent samples.
-
-In the 62D case, we compute $1.1\cdot10^6$ importance samples such that $N_{\rm
-  eff} \approx 3500$ and the estimated relative error of the error is 1.2\% and
-thus good enough for our purposes.
+components are needed; i.e., 3 components proved optimal by the variational
+approximation to the model evidence.
+
+In the most challenging run with 62 parameters, we obtain a relative effective
+sample size of only 0.038\%. We want to have enough independent samples $N$ such
+that the 68\% region is determined with a relative precision of about 1\%. As a
+rule of thumb, we consider the ``relative error of the error'' given by
+$1/\sqrt{2 N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute
+$1.1\cdot10^6$ importance samples such that $N \approx 3500$ and the estimated
+relative error of the error is 1.2\% and thus good enough for our purposes.
 
@@
 \ref{fig:FHvsCT}--\ref{fig:scalar:SM-EFT}, we apply kernel density estimation
-for MCMC and importance samples using the fast \texttt{figtree}
+for both MCMC and importance samples using the fast \texttt{figtree}
 library~\cite{morariu08figtree}. In the latter case, we additionally crop 500
 outliers.
+
+The prior or posterior predictive distribution of an observable $X$ within a
+model $M$ in which $X=f(\vecth)$ is a definite function of the
+parameters $\vecth$ is given as
+\begin{align}
+  \label{eq:predictive}
+  P(X | M) &= \int \rmdx{\vecth} P(X|\vecth,M) P(\vecth|M)\nn
+  &= \int \rmdx{\vecth} \delta(X - f(\vecth)) P(\vecth|M) \,.
+\end{align}
+We estimate $P(X|M)$ by computing $f(\vecth_i)$ for every sample $\vecth_i \sim
+P(\vecth|M)$, then smooth as above.
 

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] Proofread intro, add MoM citation

@@
 \section{
-  Introduction
+ \checked{ Introduction}
 }
@@
 \end{align}
-LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the
-angular distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
+LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the angular
+distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
 \mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
-lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term
-$F_H^\mu$ in CP-averaged form and integrated over several bins in the
-dilepton invariant mass $q^2$\fred{sent. too long}. Similarly, the
-CP-averaged branching ratios, ${\cal B}_\mu = \tau_{B}
-\Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
+lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term $F_H^\mu$
+in CP-averaged form and integrated over several bins in the dilepton invariant
+mass $q^2$. Similarly, the CP-averaged branching ratios, ${\cal B}_\mu =
+\tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
   CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.
 
-Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong
-suppression factors for vector and dipole couplings present in the SM,
-thereby enhancing their sensitivity to tensor and scalar couplings
-\cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of scalar
-couplings compared to helicity-suppressed vector couplings of the SM
-is well-known from $B_s\to \bar\mu\mu$. \fred{Which model gives rise
-  to tensor contributions?} Unfortunately the limited data set of
-$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still
-does not allow to perform current angular analysis without the
-assumption of vanishing scalar and tensor couplings in this decay
-mode. In the future also certain angular observables in $B\to K^*
-\bar\ell\ell$ will provide additional constraints on such couplings,
-as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the linear
-combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
-\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the
-experimental test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 =
-0$~\cite{Bobeth:2012vn}.
-
-Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
-to derive stronger constraints then before on tensor and scalar couplings in
-various model-independent scenarios and study their impact on the yet not
-measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
-we specify the effective theory of $|\Delta B| = 1$ decays, on which our
-model-independent fits are based on. We discuss the dependence of observables
-in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensor and scalar
-couplings in \refsec{sec:observables} and specify also the experimental input
-used in the fits. The constraints on tensor and scalar couplings from the data
-are presented for several model-independent scenarios in \refsec{sec:results}.
-Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
-branching fraction of $B_s\to \bar\mu\mu$ and the
-treatment of theory uncertainties are relegated to appendices.
+Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
+factors for vector and dipole couplings present in the SM, thereby enhancing
+their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
+  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
+helicity-suppressed vector couplings of the SM is well-known from $B_s\to
+\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
+\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} did not allow to perform a full
+angular analysis without the assumption of vanishing scalar and tensor couplings
+in this decay mode. In the future with more data or special-purpose analysis
+techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
+observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
+such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
+linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
+\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
+relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
+hadronic recoil.
+
+Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to
+\bar\mu\mu$ to derive stronger constraints than before on tensor and scalar
+couplings in various model-independent scenarios and study their impact on the
+not yet measured sensitive observables in $B\to K^* \bar\ell\ell$. In
+\refsec{sec:EFT}, we specify the effective theory of $|\Delta B| = 1$ decays on
+which our model-independent fits are based. Within this theory, we discuss the
+dependence of observables in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$
+on the tensor and scalar couplings in \refsec{sec:observables} and specify also
+the experimental input used in the fits. The constraints on tensor and scalar
+couplings from the data are presented for several model-independent scenarios in
+\refsec{sec:results}.  Technical details of the angular observables in $B\to K^*
+\bar\ell\ell$, the branching fraction of $B_s\to \bar\mu\mu$, the treatment of
+theory uncertainties, and the Monte Carlo methods used are relegated to
+appendices.
 
@@
 
-Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again
-substantial deviations from the SM prediction are possible only in the
-presence of non-zero tensor couplings. In this case enhancement by two
-orders of magnitude are possible up to the ${\cal O}(10^{-8})$ at
-high-$q^2$ and also at low-$q^2$ in the case of $(J_{1s} - 3\,
-J_{2s})$, always being consistent with all included experimental
-constraints in \reftab{tab:observables}. In view of current
-experimental precision of $20\%$ of the branching ratio measurements
-at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to
-the ${\cal O}(10^{-8})$, one can indeed hope for some sensitivity to
-such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$
-for the not yet published 3 fb$^{-1}$ data set.  \todo{Would be a nice
-  place to cite method of moments paper?}
+Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
+deviations from the SM prediction are possible only in the presence of non-zero
+tensor couplings. In this case enhancement by two orders of magnitude are
+possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
+the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
+experimental constraints in \reftab{tab:observables}. In view of current
+experimental precision of $20\%$ of the branching ratio measurements at LHCb
+\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal
+  O}(10^{-8})$, one can indeed hope for some sensitivity to such large effects
+in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3
+fb$^{-1}$ data set at least with the method of moments~\cite{beaujean:2015mom}.
 

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] check section on exp. inputs

@@
 \newcommand{\fred}[1]{{\color{green}{#1}}}
-\newcommand{\todo}[1]{{\color{purple}{ {\bf ToDo: }{#1}}}}
-\newcommand{\checked}[1]{{\color{magenta}{ {\bf Checked: }{#1}}}}
+\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
+\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
 
@@
 \begin{abstract}
+  \todo{check}
   The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
@@
     observables''. There could be a bit of summary of outcome here, too}
+  \todo{check captions of figures and tables}
 \end{abstract}
@@
 \section{
-  Effective Theory
+  \checked{Effective Theory}
   \label{sec:EFT}
@@
 \end{equation}
-the most general dimension-six flavor-changing operators $\Op_i$ mediating
-$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
-chiral structure. There are dipole ($i = 7,7')$ and vector ($i = 9,9',10,10'$)
-operators
+the most general dimension-six flavor-changing operators $\Op_i$ mediating $b\to
+s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
+structure. There are dipole ($i = 7,7'$ \fred{so there is no $\mu, \tau$ version
+  of $\wilson{7}$? I guess it should also depend on $\mu_b$}) and vector ($i =
+9,9',10,10'$) operators
 \begin{equation}
@@
 \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
-also used frequently in the literature. Their respective short-distance couplings,
+also used frequently in the literature. The respective short-distance couplings,
 the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
@@
 %from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
-
 The Wilson coefficients of the four-quark current-current and QCD-penguin
@@
 \section{
-  Observables and experimental input
+  \checked{Observables and experimental input}
   \label{sec:observables}
@@
 \end{align}
-Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
-The $F_H^\ell(q^2)|_{\rm SM}$
-is strongly suppressed away from both kinematical endpoints in $q^2$,
-except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
-Non-zero values
-of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
-which will modify the simple $\cos\theta_\ell$ dependence
-of the angular distribution~\refeq{eq:ang-distr}, however, currently there is
-no solid estimate available for this source of SM background\footnote{The leading
-QED corrections to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
+Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.  The flat
+term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed away from both \fred{Why
+  both? At $q^2_{\rm max}$ it is strongly suppressed according to the formula
+  given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
+\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Non-zero values of
+$A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
+which will modify the simple $\cos\theta_\ell$ dependence of the angular
+distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
+available for this source of SM background\footnote{The leading QED corrections
+  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
   corresponding effects in $B\to K \bar\ell\ell$.}.
 
-This picture does not change in the presence of new physics
-contributions to vector and dipole operators $i =
-7,7',9,9',10,10'$. On the other hand, non-vanishing tensor or scalar
-contributions are enhanced unless the dynamics of NP implies similar
-suppression factors, i.e., lepton-Yukawa couplings for $F_H^\ell$ or
-$\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular, $F_H^\ell$
-is very sensitive to tensor couplings $A_{\rm FB}^\ell$ is sensitive
-to the interference of tensor and scalar couplings.
+This picture does not change in the presence of new physics contributions to
+vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
+non-vanishing tensor or scalar contributions are enhanced unless the dynamics of
+NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
+$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
+$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
+below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
+scalar couplings (see \refeq{eq:FH-dependence} below).
 
@@
 
-There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
-\bar\ell\ell$ with the same properties, i.e. tensor and scalar
-contributions are kinematically enhanced by a factor
-$\sqrt{q^2}/m_\ell$ over vector ones present in the SM or their
-respective interference terms. These are $J_{6c}$ and the two linear
-combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with
-explicit formulas given in \refapp{app:BKstarellell}. In our fits and
-predictions we include all kinematically suppressed terms. But for the
-purpose of illustration, we now consider the analytical dependence for
-vanishing lepton mass. In this limit,
+There are some angular observables $J_i$ in $B\to K^*(\to K\pi)\, \bar\ell\ell$
+with the same properties; i.e. tensor and scalar contributions are kinematically
+enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones present in the SM or
+their respective interference terms. These are $J_{6c}$ and the two linear
+combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with explicit
+formulas given in \refapp{app:BKstarellell}. In our fits and predictions we
+include all kinematically suppressed terms. But for the purpose of illustration,
+we now consider the analytical dependence for vanishing lepton mass. In this
+limit,
 \begin{align}
@@
 \intertext{is sensitive to the interference of tensor and scalar operators,
-  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
+  complementary to $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
   \label{eq:AFB-dependence}
@@
 \end{align}
-i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.
-We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
-of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
-it has to compete with $J_{6s}$ in this observable, a separate measurement of
-$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensor contributions enter
+i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.  We
+note also that $J_{6c}$ contributes to the lepton forward-backward asymmetry of
+$B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since it has to
+compete with $J_{6s}$ in this observable, a separate measurement of $J_{6s}$ and
+$J_{6c}$ is necessary.
+
+Only tensor contributions enter
 \begin{align}
@@
 \end{align}
-where the dots indicate different kinematical and form factor dependences.
-On the other hand, tensor and scalar contributions enter
+where the dots indicate different kinematic and form-factor dependencies.  But
+tensor \emph{and} scalar contributions enter
 \begin{equation}
@@
 \end{equation}
-Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
-Bobeth:2012vn} --- are such that tensor and scalar couplings contribute only
-constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
-Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
-\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
-by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
-and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
-respectively.
-
-The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
-\refeq{eq:AFB-dependence} are measured in the angular distribution \refeq{eq:ang-distr}
-of $B\to K \bar\ell\ell$ being normalised to the decay width $\Gamma_\ell$, such
-that uncertainties due to form factors can cancel in part \cite{Bobeth:2007dw,
-Bobeth:2012vn}. On the other hand, $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and
-$(J_{1c} + J_{2c})$ appear in the unnormalised angular distribution of
-$B\to K^* \bar\ell\ell$ and so-called ``optimised'' versions $S_1$, $M_1$ and
-$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw},
-respectively, where form factors cancel in the limit of $m_b \to \infty$.
-For the high-$q^2$ region potential normalisations are discussed in
-\refapp{app:BKstarellell}, which could serve to form optimised observables for
-special scenarios of either vanishing chirality-flipped vector or tensor
-or scalar couplings. In the most general case, however, there are no optimised
-observables at high-$q^2$. Although form factors do not cancel in this case, it
-might be still advantageous to use normalisations, for example when the overall
-normalisation of $B\to K^*$ form factors constitutes a major theoretical
+Concerning $F_H^\ell$, the involved kinematic factors---see \cite{Bobeth:2007dw,
+  Bobeth:2012vn}---are such that tensor and scalar couplings contribute only
+constructively/cumulatively, apart from cancellations among $\wilson{S(P)}$ and
+$\wilson{S'(P')}$.  Interference terms in the numerator of $F_H^\ell$ of the
+form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
+\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. They can only become
+relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
+\ll\wilson{10,10'}$.
+
+On the one hand, the observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm
+  FB}^\ell$ \refeq{eq:AFB-dependence} are measured in the angular distribution
+\refeq{eq:ang-distr} of $B\to K \bar\ell\ell$ normalized to the decay width
+$\Gamma_\ell$ such that uncertainties due to form factors can cancel in part
+\cite{Bobeth:2007dw, Bobeth:2012vn}. On the other hand, $J_{6c}$, $(J_{1s} - 3\,
+J_{2s})$, and $(J_{1c} + J_{2c})$ appear in the unnormalized angular
+distribution of $B\to K^* \bar\ell\ell$. ``Optimized'' versions $S_1$, $M_1$,
+and $M_2$ for the low-$q^2$ region for which form factors cancel in the limit of
+$m_b \to \infty$ have been identified in~\cite{Matias:2012xw}.  For the
+high-$q^2$ region, potential normalizations are discussed in
+\refapp{app:BKstarellell}, which could serve to form optimized observables for
+special scenarios of either vanishing chirality-flipped vector or tensor or
+scalar couplings. In the most general case, however, there are no optimized
+observables at high $q^2$. Although form factors do not cancel in this case, it
+might still be preferable to use normalizations, for example when the overall
+normalization of $B\to K^*$ form factors constitutes a major theoretical
 uncertainty.
@@
 
-To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we
-compare it in \reffig{fig:FHvsCT} to the one of the branching ratios
-of $B\to K^{(*)} \bar\ell\ell$ for {$\ell = \mu$}, integrated over low
-and high $q^2$. The details of the numerical input and the treatment
-of uncertainty propagation can be found in \refapp{app:theory:inputs}.
-In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent
-global analysis of $b\to s (\gamma,\, \bar\ell\ell)$ data
-\cite{Descotes-Genon:2013wba, Altmannshofer:2013foa, Beaujean:2013soa,
-  Hurth:2014vma, Altmannshofer:2014rta} we show besides
-$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.1$. As
-can be seen, the sensitivity to tensor couplings is highest for
-$F_H^\ell$ at high $q^2$, also due to a partial cancellation of form
-factors \cite{Bobeth:2012vn}, whereas the one on $\wilson[NP]{9} < 0$
-is rather mild, in contrast to that of the branching ratios. For the
-latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows stronger dependence on
-$\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$ and has some
-impact on the constraints on tensor couplings as will be discussed in
-\refsec{sec:results}. In consequence, the data on $F_H^\ell$ at high
-$q^2$ provides currently the most stringent constraints on the size of
-tensor couplings. Moreover, the dependence on vector couplings is such
-that $\wilson[NP]{9} < 0$ leads to stronger constraints on
-$\wilson{T}$ than $\wilson[NP]{9} \approx 0$. \fred{Stress that
-  $J_{1c}+J_{2c}$ and $J_{1s}-3J_{2s}$ robust against changes in
-  $\wilson{9}$ but sensitive to $\wilson{T}$. $F_H$ sensitive to
-  $\wilson[NP]{9}$ only if $\wilson{T} \ne 0$. Mention prior predictive}
+To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we compare it
+in \reffig{fig:FHvsCT} to the branching ratios of $B\to K^{(*)} \bar\ell\ell$
+for {$\ell = \mu$}, integrated over one low-$q^2$ and one high-$q^2$ bin. The
+details of the numerical input and the uncertainty propagation can be found in
+\refapp{app:theory:inputs} and \refapp{app:mc}.  In light of the hint of new
+physics in $\wilson{9}$ from recent global analyses of $b\to s (\gamma,\,
+\bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
+  Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta}, we show predictions
+for $\wilson[NP]{9} = -1.1$ in addition to $\wilson[NP]{9} = 0$.
+
+From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
+\to K$ observable is attained by $F_H^\ell$ at high $q^2$ due to a partial
+cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
+uncertainty could be reduced further, $F_H^\ell$ would give a very strong
+constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
+$\wilson[NP]{T}$. The prediction of ${\cal B}(B\to K \bar\ell\ell)$ is
+essentially insensitive to $\wilson{T}$ but sensitive to $\wilson{NP}[9]$. A
+stronger impact on global fits, however, would required reduced theory
+uncertainty.
+
+The observable ${\cal B}(B\to K^* \bar\ell\ell)$ shows moderate dependence on
+$\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
+tensor couplings as will be discussed in \refsec{sec:results}. At the moment,
+theory and experimental uncertainty are of similar size.
+
+$J_{1c}+J_{2c}$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low
+$q^2$, it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
+unaffected. Regarding $J_{1s}-3J_{2s}$, the situation is reversed: here the
+strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, $F_H^\ell$,
+$J_{1c}+J_{2c}$ at large $q^2$, and $J_{1s}-3J_{2s}$ are sensitive to
+$\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.
+
+From the available measurements, $F_H^\ell$ at high $q^2$ currently provides the
+most stringent constraints on the size of tensor couplings. Moreover, the
+dependence on vector couplings is such that $\wilson[NP]{9} < 0$ leads to
+stronger constraints on $\wilson{T}$ than $\wilson[NP]{9} \approx
+0$.
 
@@
 
-Eventually we also explore the effect of interference with NP in the
-vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor
-and scalar couplings.  For this purpose we include also the branching
-ratio, the lepton forward-backward asymmetry and the rate CP asymmetry
-of $B\to K^* \bar\mu\mu$ as they provide additional constraints on the
-real and imaginary parts of $\wilson{9,\,9',\,10,\,10'}$.
+Eventually we also explore the effect of interference with NP in the vector
+couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor and scalar
+couplings.  For this purpose we include also the branching ratio, the lepton
+forward-backward asymmetry, and the rate CP asymmetry of $B\to K^* \bar\mu\mu$
+as they provide additional constraints on the real and imaginary parts of
+$\wilson{9,\,9',\,10,\,10'}$.
 
@@
 
-Finally we discuss the possibility of suitable normalisations of $J_{6c}$,
+Finally we discuss the possibility of suitable normalizations of $J_{6c}$,
 $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ at high $q^2$ that would provide
@@
 
-Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalisations,
+Concerning $(J_{1s} - 3\, J_{2s})$, there are no appropriate normalizations,
 unless the chirality-flipped $\wilson[NP]{7',\,9',\,10'} = 0$ because then
@@
 $z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters
-(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematical relation
+(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematic relation
 $f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft] correct section 4 except for last subsection

@@
   on tensor and scalar effective couplings and determine their impact
-  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
+  on not-yet-measured angular observables in $B\to K^*\bar\mu\mu$,
   which feature the same suppression of vector couplings.  Most
@@
 couplings in various model-independent scenarios and study their impact on the
-not yet measured sensitive observables in $B\to K^* \bar\ell\ell$. In
+not-yet-measured sensitive observables in $B\to K^* \bar\ell\ell$. In
 \refsec{sec:EFT}, we specify the effective theory of $|\Delta B| = 1$ decays on
@@
 \hline
-\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
+\multirow{5}{*}{${B^+\to K^+ \bar\mu\mu}$}
     & \multirow{2}{*}{$\BR_\mu$}
@@
 \hline
-    ${B^0\to K^{\ast 0} \bar\mu\mu}$
+    \multirow{3}{*}{${B^0\to K^{\ast 0} \bar\mu\mu}$}
     & $\BR_\mu$
@@
 \renewcommand{\arraystretch}{1.0}
-\caption{\label{tab:observables} List of all observables of the various
-  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
-  and experiments that provide the measurements. LCSR and lattice results of
-  $B\to K^{(*)}$ form factors are used to constrain parameters of their
-  $q^2$-dependence.
-  For more details see the text and \refapp{app:theory:inputs}.
-}
+\caption{\label{tab:observables} List of all observables of the various $b\to s
+  \bar\mu\mu$ decays entering the fits with the respective kinematics and
+  experiments that provide the measurements. LCSR and lattice results of $B\to
+  K^{(*)}$ form factors are used to constrain a $q^2$-dependent form-factor
+  parametrization.  For more details see \refsec{sec:observables} and
+  \refapp{app:theory:inputs}. \checked{} }
 \end{center}
@@
 as they provide additional constraints on the real and imaginary parts of
-$\wilson{9,\,9',\,10,\,10'}$.
-
-The experimental inputs of all observables entering our fits is listed
-in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
-form factors. More details on the latter can be found in
+$\wilson{9,\,9',\,10,\,10'}$. The experimental inputs of all observables
+entering our fits is listed in \reftab{tab:observables} together with input for
+the $B\to K^{(*)}$ form factors. More details on the latter can be found in
 \refapp{app:theory:inputs}.
@@
 
-As a matter of the fact there are no discrepancies between the latest measurements
-for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in
-$B^+ \to K^+ \bar\mu\mu$ and
-their tiny SM predictions. Thus our main objective is the derivation of stronger
-constraints on tensor and scalar couplings, taking advantage of their enhancement
-in both observables over vector ones. For this purpose, we will consider several
-model-independent scenarios, starting from rather restricted to more general ones,
-in order to asses the effect of cancellations due to interference of various
-contributions.
-
-We will start with the scenario of only tensor couplings and see that they are
-well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
-couplings in order to investigate the complementarity of $F_H^\mu$ and
-$B_s \to \bar\mu\mu$. Here we find that for the first time all scalar couplings
-can be bounded simultaneously by the combination of both measurements. Eventually
-we will consider as a special scenario the SM
-augmented by dimension six operators as an effective theory of new physics below
-some high scale $\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
-symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
-as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
-also interference effects with new physics in vector couplings. Finally, we
-conclude this section with postirior predictions of the allowed ranges of the yet
-not measured angular observables in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in
-$B_s\to\bar\mu\mu$ given all other experimental constraints.
-
-\todo{Explain special initialisation of Markov chains at fixed point in parameter
-space in order to avoid other local modes in subspace of nuisance parameters.
-What would be appropriate place to do so?}
+There are no discrepancies between the latest measurements for $\ell = \mu$
+(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
+\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
+main objective is to derive constraints on tensor and scalar couplings through
+the enhanced sensitivity of both observables to those couplings compared to
+vector couplings. For this purpose, we will consider several model-independent
+scenarios, progressing from rather restricted to more general ones in order to
+asses the effect of cancellations due to interference of various contributions.
+
+For each coupling we vary in a fit, we remain as general as possible, treat it
+as a complex number and use the cartesian parametrization assuming uniform
+priors for ease of comparison with previous studies. Specifically, we set
+\begin{align}
+  \label{eq:wilson-prior}
+  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
+\end{align}
+and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.
+
+We start with the scenario of only tensor couplings and see that they are well
+constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
+couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
+\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
+couplings can be bounded simultaneously by the combination of both
+measurements. Finally we consider as a special scenario the SM augmented by
+dimension six operators as an effective theory of new physics below some high
+scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
+electroweak symmetry breaking. In addition, the model contains one scalar
+doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
+interference effects with new physics in vector couplings. Finally, we conclude
+this section with posterior predictions---conditional on all experimental
+constraints---of the probable ranges of the not-yet-measured angular observables
+in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.
 
@@
   \\
+  credibility level
+  & 68\%, 95\%
+  & 68\%, 95\%
+  & 68\%, 95\%
+  \\
   \hline
   $\mbox{Re}\,\wilson{T}$
-  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
-  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
-  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
+  & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
+  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
+  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
   \\
   $\mbox{Im}\,\wilson{T}$
-  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
-  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
-  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
+  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
+  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
+  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
   \\[0.1cm]
   $\mbox{Re}\,\wilson{T5}$
-  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
-  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
-  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
+  & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
+  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
+  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
   \\
   $\mbox{Im}\,\wilson{T5}$
-  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
-  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
-  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
+  & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
+  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
+  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
   \\
@@
   $|\wilson{T}|$, $|\wilson{T5}|$
-  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
-  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
-  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
+  & $[0.13,\, 0.43]$, $[0.03,\, 0.57]$
+  & $[0.09,\, 0.33]$, $[0.02,\, 0.44]$
+  & $[0.10,\, 0.33]$, $[0.02,\, 0.43]$
   \\
@@
      \label{tab:cTT5:1-dimCLs}
-     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
-     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
-     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
-     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
-     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
+     The constraints on complex-valued $\wilson{T,\,T5}$ when using
+     measurements of only $F_H^\mu$, $F_H^\mu$ and other data in
+     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and finally allowing
+     complex-valued new physics contributions to $\wilson{9,\,10}$. \checked{} %\fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
    }
@@
 
-In a scenario with only tensor complex-valued couplings $\wilson{T,\,
-  T5}$, the experimental measurement of $F_H^\mu$ constrains the
-combination $|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small
-interference of $\wilson{T}$ with vector couplings
-$\wilson{7,\,7',\,9,\,9'}$.  The according 68\% (95\%) 1D-marginalized
-probability intervals are listed in the first column of
-\reftab{tab:cTT5:1-dimCLs}. As can be seen further in the second
-column, the constraints become tighter when utilising all observables
-in \reftab{tab:observables}, mainly due to the sensitivity of the
-branching ratio of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see
-also \reffig{fig:FHvsCT}). The latter stronger bounds are driven by
-the new lattice results of $B\to K^*$ form factors that yield too high
-predictions compared to the measurements~\cite{Horgan:2013pva}. Since
-tensor couplings contribute constructively to ${\cal B}(B\to
-K^{*}\bar\mu\mu)$ large values are stronger constrained. In this
-scenario with vanishing scalar couplings, current measurements of
-$A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
+In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$, the
+experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
++ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
+couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
+according 68\% (95\%) 1D-marginalized probability intervals are listed in the
+second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
+that the constraints become tighter when utilising all observables in
+\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
+of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
+\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
+results of $B\to K^*$ form factors that predict values above the measured
+values~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
+to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
+this scenario with vanishing scalar couplings, current measurements of $A_{\rm
+  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
 cf.~\refeq{eq:AFB-dependence}.
 
-We also perform a fit with non-zero complex-valued $\wilson{9,\,10}$
-by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\,
-7]$, ($i = 9,10$) in order to access the stability of the bounds
-against interference. Note that $\wilson{7,7'}$ appears in linear
-combinations with $\wilson{9,9'}$ such that its interference with
-tensor and scalar couplings is captured implicitly by allowing new
-physics in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM
-value without loss of generality. In this case, $F_H^\mu$ by itself
-still provides bounds on $|\wilson{T,\,T5}|$ that are weakened by a
-factor of two since $F_H^\mu$ does not pose constraints on
-$\wilson{9,\,10}$ (in the chosen prior range). Once additional
-experimental measurements of \reftab{tab:observables} are taken into
-account, the potential destructive effects of new physics in
-$\wilson{9,\,10}$ become reduced and almost the same constraints on
-$\wilson{T,\,T5}$ are recovered, as shown in the third column in
-\reftab{tab:cTT5:1-dimCLs}.  In consequence, the $F_H^\mu$
-measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the
-previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by 50\%.
-
-\fred{comment on last row: SM in all cartesian intervals but not in polar!}
+We also perform a fit with non-zero $\wilson[NP]{9,\,10}$ \fred{Is this
+  $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
+bounds with respect to interference. Note that $\wilson{7,7'}$ appears in linear
+combinations with $\wilson{9,9'}$ such that its interference with tensor and
+scalar couplings is captured implicitly by allowing new physics in
+$\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
+generality. In this case, $F_H^\mu$ by itself still provides bounds on
+$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
+not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
+additional experimental measurements of \reftab{tab:observables} are taken into
+account, the potential destructive effects of new physics in $\wilson{9,\,10}$
+become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
+recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
+addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
+\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%
+which we attribute to cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
+$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
+measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
+bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.
+
+A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
+$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
+coordinates but never in even the 95\% region in polar coordinates. This is a
+consequence of the general \emph{concentration of measure}. Another way to look
+at it is to transform the uniform prior density from cartesian to polar
+coordinates. For the example of the single Wilson coefficient, say $\wilson{T}$,
+the transformed density is proportional to the determinant of the Jacobian which
+is $|\wilson{T}|$. In words, the uniform prior on $\mbox{Re}(\wilson{T})$ and
+$\mbox{Im}(\wilson{T})$ favors larger values of $|\wilson{T}|$ even though we
+consider it consensus in the community that smaller rather than larger values
+are held reasonable because in the SM, $\wilson{T} = 0$. We suggest therefore
+that the default prior be changed in the future.
 
@@
   \end{center}
-  \caption{
-    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
-    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
-    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
-    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
-    at 68\% (darker) and 95\% (lighter) probability. The constraints on
-    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
-    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
-    by the black diamond.
-  }
+  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
+    only $F_H^\mu$~[grey dotted, left panel], only $\overline{\cal B}(B_s \to
+    \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
+    data in \reftab{tab:observables} as well as non-zero
+    $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
+    and 95\% (lighter) probability. The constraints on Re$(\wilson{P}Ê\pm
+    \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$, apart from
+    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
+    indicated by the black diamond. \checked{} }
   \label{fig:scalar}
@@
   \\
+  credibility level
+  & 68\%, 95\%
+  & 68\%, 95\%
+  & 68\%, 95\%
+  \\
   \hline
@@
   & $\quad$ $-$ $\quad$
-  & $\quad$ $[-0.10,\, 0.08]$ ($[-0.14,\, 0.13]$) $\quad$
-  & $\quad$ $[-0.08,\, 0.07]$ ($[-0.13,\, 0.13]$) $\quad$
+  & $\quad$ $[-0.10,\, 0.08]$, $[-0.14,\, 0.13]$ $\quad$
+  & $\quad$ $[-0.08,\, 0.07]$, $[-0.13,\, 0.13]$ $\quad$
   \\
@@
   & $\quad$ $-$ $\quad$
-  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.11,\, 0.12]$) $\quad$
-  & $\quad$ $[-0.07,\, 0.07]$ ($[-0.12,\, 0.11]$) $\quad$
+  & $\quad$ $[-0.07,\, 0.07]$, $[-0.11,\, 0.12]$ $\quad$
+  & $\quad$ $[-0.07,\, 0.07]$, $[-0.12,\, 0.11]$ $\quad$
   \\[0.1cm]
   $\mbox{Re}(\wilson{S} + \wilson{S'})$
-  & $[-0.36,\, 0.39]$ ($[-0.69,\, 0.68]$)
+  & $[-0.36,\, 0.39]$, $[-0.69,\, 0.68]$
   & $-$
-  & $[-0.32,\, 0.32]$ ($[-0.59,\, 0.62]$)
+  & $[-0.32,\, 0.32]$, $[-0.59,\, 0.62]$
   \\
   $\mbox{Im}(\wilson{S} + \wilson{S'})$
-  & $[-0.37,\, 0.35]$ ($[-0.68,\, 0.66]$)
+  & $[-0.37,\, 0.35]$, $[-0.68,\, 0.66]$
   & $-$
-  & $[-0.25,\, 0.41]$ ($[-0.57,\, 0.64]$)
+  & $[-0.25,\, 0.41]$, $[-0.57,\, 0.64]$
   \\[0.1cm]
@@
   & $-$
-  & $[ 0.05,\, 0.20]$ ($[ 0.01,\, 0.26]$)
-  & $[ 0.00,\, 0.16]$ ($[-0.07,\, 0.22]$)
+  & $[ 0.05,\, 0.20]$, $[ 0.01,\, 0.26]$
+  & $[ 0.00,\, 0.16]$, $[-0.07,\, 0.22]$ \hspace{-3mm}
   \\
@@
   & $-$
-  & $[-0.07,\, 0.08]$ ($[-0.12,\, 0.12]$)
-  & $[-0.07,\, 0.09]$ ($[-0.14,\, 0.16]$)
+  & $[-0.07,\, 0.08]$, $[-0.12,\, 0.12]$
+  & $[-0.07,\, 0.09]$, $[-0.14,\, 0.16]$
   \\[0.1cm]
   $\mbox{Re}(\wilson{P} + \wilson{P'})$
-  & $[-0.24,\, 0.51]$ ($[-0.51,\, 0.82]$)
+  & $[-0.24,\, 0.51]$, $[-0.51,\, 0.82]$
   & $-$
-  & $[-0.12,\, 0.52]$ ($[-0.42,\, 0.78]$)
+  & $[-0.12,\, 0.52]$, $[-0.42,\, 0.78]$
   \\
   $\mbox{Im}(\wilson{P} + \wilson{P'})$
-  & $[-0.36,\, 0.37]$ ($[-0.67,\, 0.67]$)
+  & $[-0.36,\, 0.37]$, $[-0.67,\, 0.67]$
   & $-$
-  & $[-0.37,\, 0.29]$ ($[-0.68,\, 0.57]$)
+  & $[-0.37,\, 0.29]$, $[-0.68,\, 0.57]$
   \\
@@
      The 1D-marginalized constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
-     at 68\% (95\%) probability from measurements of $i)$ only $F_H^\mu$,
-     $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $iii)$ all the data in
+     at 68\% (95\%) probability from measurements of only $F_H^\mu$,
+     only $\overline{\cal B}(B_s \to \bar\mu\mu)$, and all the data in
      \reftab{tab:observables} and additional new physics contributions to
-     $\wilson{9,\, 9',\, 10,\,10'}$.
+     $\wilson{9,\, 9',\, 10,\,10'}$. \checked{}
    }
@@
 
-Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$
-without kinematic suppression --- see \refeq{eq:FH-dependence} --- in
-the complementary manner $(\wilson{i} + \wilson{i'})$ to the branching
-ratio $\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only
-$(\wilson{i} - \wilson{i'})$, where $i = S,\, P$.  Most notably, we
-find that the current measurement of $F_H^\mu$ does constrain the
-orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of
-$F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound
-for the first time the real and imaginary parts of all four couplings.
-
-The according four-parameter fit for complex-valued scalar couplings
-to the data of $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$
-results in the (2D-marginalized) regions in the $\mbox{Re}(\wilson{i}
-\pm \wilson{i'})$ ($i = S, P$) planes shown in
-\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i}
-\pm \wilson{i'})$ are very similar to those shown and thus
-omitted. These bounds do not change when including all other data in
-\reftab{tab:observables}, since the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$
-requires interference of scalar with tensor couplings and other
-observables are not very sensitive to scalar
-couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s
-\to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor
-four to five stronger than the one of $F_H^\mu$ on $(\wilson{i} +
-\wilson{i'})$.
-
-Interference terms of $\wilson{P,\,P'}$ with vector couplings might
-weaken these bounds. Most important for $\overline{\cal B}(B_s \to
-\bar\mu\mu)$ are $(\wilson{10} - \wilson{10'})$ --- compare
-\refeq{eq:Br-Bsmumu:time0} --- and for $F_H^\ell$ similarly
-$(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}, which are
-suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
-respectively \fred{hard to read}. However, these terms become
-important for small $\wilson{P,\,P'}$ due to the large SM contribution
-of $\wilson[SM]{10} \simeq -4.2$. We compile bounds on complex-valued
-scalar couplings in \reftab{tab:cSP:1-dimCLs} for only $F_H^\mu$, only
-$\overline{\cal B}(B_s \to \bar\mu\mu)$, and their combination with
-all the other observables in \reftab{tab:observables}. In the last
-case, we allow new physics in vector couplings $\wilson{9,\ 9',\,
-  10,\, 10'}$ assuming uniform priors for $\mbox{Re, Im}(\wilson{i})
-\in[-7,\, 7]$.  Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to
-\bar\ell\ell)$ alone can bound all four complex-valued scalar
-couplings, however their combination is capable to do so and moreover,
-the bounds are stable against destructive interference with vector
-couplings. In the special case of real-valued couplings,
-$\overline{\cal B}(B_s \to \bar\ell\ell)$ would lead to
-rings~\cite{Alonso:2014csa} instead of circles. In the most general
-scenario, we find the following bounds with 68\% (95\%) probability:
+Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
+kinematic suppression---see \refeq{eq:FH-dependence}---as the sum $(\wilson{i} +
+\wilson{i'})$ whereas in the branching ratio $\overline{\cal B}(B_s\to
+\bar\ell\ell)$ they appear as the difference $(\wilson{i} - \wilson{i'}), i =
+S,\, P$.  Since the existing measurement of $F_H^\mu$ constrains the sum, the
+combination of $F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows
+us---for the first time---to bound the real and imaginary parts of all four
+couplings.  The corresponding 2D-marginalized regions in the
+$\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$) planes are shown in
+\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i} \pm
+\wilson{i'})$ are very similar to those shown and thus omitted. These bounds do
+not change when including all other data in \reftab{tab:observables}, since the
+$A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
+couplings and other observables are not very sensitive to scalar
+couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s \to
+\bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor four to five
+stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
+
+Interference terms of $\wilson{P,\,P'}$ with vector couplings might weaken these
+bounds. For $\overline{\cal B}(B_s \to \bar\mu\mu)$, the relevant term is
+$(\wilson{10} - \wilson{10'})$ (see \refeq{eq:Br-Bsmumu:time0}) and for
+$F_H^\ell$ it is $(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}; both are
+suppressed by the factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
+respectively. Nevertheless, these terms become important for small
+$\wilson{P,\,P'}$ due to the large SM value of $\wilson[SM]{10} \simeq -4.2$. We
+compile bounds on complex-valued scalar couplings in \reftab{tab:cSP:1-dimCLs}
+for only $F_H^\mu$, only $\overline{\cal B}(B_s \to \bar\mu\mu)$, and their
+combination with all the other observables in \reftab{tab:observables}. Neither
+$F_H^\ell$ nor $\overline{\cal B}(B_s \to \bar\ell\ell)$ alone can bound all
+four complex-valued scalar couplings, however their combination is capable to do
+so and moreover, the bounds are stable against destructive interference with
+vector couplings. In the case of $\wilson[NP]{9,9',10,10'} \ne 0$, we find the
+following bounds with 68\% (95\%) probability:
 \begin{equation}
+  \label{eq:SP-bounds}
   \begin{aligned}
@@
 \end{equation}
-
-Our results improve and extend previous bounds in the literature to
-the most general case of complex-valued couplings. For example they
-are a factor two to five more stringent than \cite{Becirevic:2012fy}
-and comparable to \cite{Altmannshofer:2012az} once restricting to the
-much simpler scenarios considered there.
-
-\begin{figure*}
-  \begin{center}
-      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
-      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
-    \end{center}
-    \caption{
-    Constraints (2D-marginalized) on complex-valued scalar couplings
-    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in
-    \reftab{tab:observables} (red) at 68\% (darker) and 95\%
-    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
-    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
-    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
-    and $F_H^\mu$ \todo{What else?}
-    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
-    The SM is indicated by the black diamond.
-  }
-  \label{fig:scalar:SM-EFT}
-\end{figure*}
-
+Allowing in addition $\wilson{T,T5} \ne 0$, the intervals of
+\refeq{eq:SP-bounds} are quite similar but in general (10--20)\% narrower and
+shifted by that amount towards zero. Again, this can be explained by the
+cumulative effect of $\wilson{S,S',P,P'}$ and $\wilson{T,T5}$ in $F_H^\ell$
+shown in \refeq{eq:FH-dependence}.
+
+In the special case of real-valued couplings, $\overline{\cal B}(B_s \to
+\bar\ell\ell)$ would lead to rings~\cite{Alonso:2014csa} instead of circles in \reffig{fig:scalar}.
+Our results improve and extend previous bounds in the literature to the most
+general case of complex-valued couplings. For example they are a factor two to
+five more stringent than \cite{Becirevic:2012fy} and comparable to
+\cite{Altmannshofer:2012az} once restricting to the simpler scenarios considered
+there.
 %
@@
 
-In the following we consider a model-independent scenario as predicted by the SM
+In the following we consider a model-independent scenario as given by the SM but
 augmented by dimension six operators that respect the SM gauge group and are
-composed out of SM fields only. After the discovery of a scalar resonance at the LHC
-that complies currently with all requirements of the Higgs particle in the SM
-and the steadily rising lower bounds on new particle masses towards higher energies
-from ATLAS and CMS such a scenario becomes more and more viable \fred{hard to read}.
-
-A non-redundant set of dimension-six operators of this effective
-theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
-matching to the effective theory of $\Delta B = 1$ decays
-\refeq{eq:Heff} at the scale $\mu \sim m_W$ of the order of the
-$W$-boson mass in~\cite{D'Ambrosio:2002ex} for vector couplings
-$\wilson{7,\,9,\,10}$. The matching for tensor \refeq{eq:tensor:ops}
-and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows
-that SM gauge groups in conjunction with the linear representation
-\todo{Ask Martin, Oscar how to correctly phrase this} impose the
-relations
+composed of SM fields only. Such a scenario becomes more and more viable for two
+reasons. The first is the discovery of a scalar resonance at the LHC in
+agreement with all requirements of the Higgs particle in the SM. The second are
+the steadily rising lower bounds on the mass of new particles reported by ATLAS
+and CMS in various more or less specific models.
+
+A non-redundant set of dimension-six operators of this effective theory (SM-EFT)
+was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
+of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
+order of the $W$-boson mass is presented in~\cite{D'Ambrosio:2002ex} for vector
+couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
+and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
+gauge groups in conjunction with the linear representation \todo{Ask Martin,
+  Oscar how to correctly phrase this} impose the relations
 \begin{align}
@@
 on scalar and pseudo-scalar couplings and require tensor couplings to be
-suppressed to the level of dimension eight operators. In consequence only two
-scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm NP} \ll 1$
-where $v^2$ denotes the scale of electroweak symmetry breaking and $\Lambda_{\rm NP}$
-a high energy scale at which new physics generates these operators.
-
-The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (omitting
-for the sake of the argument terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$)
+suppressed to the level of dimension-eight operators. In consequence only two
+scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
+  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
+$\Lambda_{\rm NP}$ is the high-energy scale at which new physics generates these
+operators.
+
+Omitting for the sake of simplicity terms of order $m_\ell^2/M_{B_s}^2$ and
+$m_s/m_b$, the couplings $\wilson{S,\, S'}$ can be bound quite reliably from
 \cite{Alonso:2014csa}
@@
   - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re}
-  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right]
+  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right] \,.
 \end{aligned}
 \end{equation}
-and almost similarly (omitting terms of order $m_\ell^2/q^2$
-and $m_s/m_b$)
+In similar spirit, dropping terms of order $m_\ell^2/q^2$ and
+$m_s/m_b$ gives
 \begin{equation}
@@
 
-The SM gauge group does not imply any relation between $\wilson{10}$
-and $\wilson{10'}$, so they are in general additional independent
-parameters. Here we find that destructive interference with
-contributions involving $\wilson{10,\, 10'}$ does not significantly
-alter the bounds on $\wilson{S,\, S'}$.  Since we consider here
-complex-valued couplings the allowed regions are circles rather than
-rings as for the case of real-valued
-couplings~\cite{Alonso:2014csa}. The result of the simultaneous fit of
-complex-valued $\wilson{S,\,S',\,10,\,10'}$ is shown in
-\reffig{fig:scalar:SM-EFT}. \fred{Circle smaller, prob. moves to
-  center compared to Alonso}
-
-It must be noted that relations \refeq{eq:mEFT-constraints} are a consequence
-of embedding the Higgs in a weak doublet along with the Goldstone bosons.
-For example choosing a non-linear representation of the scalar sector allows
-for additional dimension six operators in the SM-EFT, such that $\wilson{S,S',P,P'}$
-are all independent and tensor operators have non-vanishing couplings already
-at dimension six \cite{Cata:2015lta}.
-
-%
-%
-%--------+---------+---------+---------+---------+---------+---------+---------+
-\subsection{Tensor, scalar and vector couplings \label{sec:tensor:scalar}}
+The SM gauge group does not imply any relation between $\wilson{10}$ and
+$\wilson{10'}$, so they are in general additional independent parameters. Here
+we find that destructive interference with contributions involving
+$\wilson{10,\, 10'}$ does not significantly alter the bounds on $\wilson{S,\,
+  S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
+first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on $B
+\to K \mu \bar{\mu}$ and $B_s \to \mu \bar{\mu}$. In the second fit, we allow
+$\wilson[NP]{10, 10'} \ne 0$ and further include all $B \to K^*\mu \bar{\mu}$
+constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
+of real and imaginary parts of $\wilson{S}$ vs. $\wilson{S'}$ have nearly
+circular contours of equal size that contain the SM point at the 68\% level
+except for $\mbox{Re}(\wilson{S})$ vs. $\mbox{Re}(\wilson{S'})$ where it is
+within the 95\% credible region. The regions hardly vary between the two fits.
+
+\begin{figure*}
+  \begin{center}
+      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
+      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
+    \end{center}
+    \caption{ 68\% and 95\% contours of the 2D-marginalized distributions of
+      scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
+      constraints in \reftab{tab:observables} (red) when marginalising over
+      non-zero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
+      superimpose the corresponding contours from using only $\overline{\cal
+        B}(B_s\to \bar\mu\mu)$ and all $B \to K \mu \bar{\mu}$ constraints
+      (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
+      indicated by the black diamond.  \checked{}}
+  \label{fig:scalar:SM-EFT}
+\end{figure*}
+
+Since we consider here complex-valued couplings the allowed regions are circles
+rather than rings as for the case of real-valued
+couplings~\cite{Alonso:2014csa}. Compared to those rings, the circles are
+smaller because the probability moves from the ring towards the center of the
+circle.
+
+It must be noted that the relations \refeq{eq:mEFT-constraints} are a
+consequence of embedding the Higgs in a weak doublet along with the Goldstone
+bosons.  For example choosing a non-linear representation of the scalar sector
+allows additional dimension-six operators in the SM-EFT, such that the couplings
+$\wilson{S,S',P,P'}$ are all independent and tensor operators have nonvanishing
+couplings already at dimension six \cite{Cata:2015lta}.
+
+%
+%
+%--------+---------+---------+---------+---------+---------+---------+---------+
+\subsection{Tensor, scalar, and vector couplings \label{sec:tensor:scalar}}
 
 The most general fit of complex-valued tensor and scalar couplings
-$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vector
-couplings $\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of
-\refsec{sec:tensor} and \refsec{sec:scalar} with same prior ranges ---
-yields bounds very similar to those in tables \ref{tab:cTT5:1-dimCLs}
-and \ref{tab:cSP:1-dimCLs} . The changes are only small and in fact
-the bounds tend to be even more stringent because tensor and scalar
-couplings can contribute to $F_H^{\mu}$ only constructively --- see
-\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
-$B\to K^{*}\bar\mu\mu$ help to strengthen the constraints on
-$\wilson{T,\, T5}$. This demonstrates that even in the case of
-complex-valued couplings the data are able to constrain all real and
-imaginary parts.
+$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
+$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor} and
+\refsec{sec:scalar}---yields bounds very similar to those in tables
+\ref{tab:cTT5:1-dimCLs} and \ref{tab:cSP:1-dimCLs} . The changes are only small
+and in fact the bounds tend to be even more stringent because tensor and scalar
+couplings can contribute to $F_H^{\mu}$ only constructively---see
+\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of $B\to
+K^{*}\bar\mu\mu$ help to improve the constraints on $\wilson{T,\, T5}$. This
+demonstrates that even in the case of complex-valued couplings there is enough
+information in the data to bound all 20 real and imaginary parts.
 
@@
      \label{tab:postdictions}
-     The 68\% probability intervals of not yet measured angular observables in
+     The 68\% probability intervals of not-yet-measured angular observables in
      $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
@@
   O}(10^{-8})$, one can indeed hope for some sensitivity to such large effects
-in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3
+in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not-yet-published 3
 fb$^{-1}$ data set at least with the method of moments~\cite{beaujean:2015mom}.
@@
 \sqrt{q^2}$) w.r.t tensor and scalar couplings. We provide predictions for
-analogous but not yet measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
+analogous but not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
 and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$.
@@
 
-Our study of yet not measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
+Our study of yet-not-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
 and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
@@
   respectively. We thank also David Straub for his support with LCSR results of
-  $B\to K^*$ form factors \cite{Straub:2015ica}.
-  C.B. was supported by the ERC Advanced Grant project ``FLAVOUR''
-  (267104).
+  $B\to K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
+  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
+  DFG Cluster of Excellence "Origin and Structure of the Universe". The
+  computations have been carried out on the computing facilities of the
+  Computational Center for Particle and Astrophysics (C2PAP).
 \end{acknowledgements}
@@
 \section{
-  Angular observables in $B\to K^* \bar\ell\ell$
+  \checked{Angular observables in $B\to K^* \bar\ell\ell$}
   \label{app:BKstarellell}
@@
 \cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
-see \reftab{tab:btokstar-lattice}.}
+see \reftab{tab:btok-lattice}.}
 
@@
 
-\section{Monte Carlo sampling}
-\label{app:mc}
-\todo{reference in main text} The marginalization of the posterior is performed
+\section{\checked{Monte Carlo sampling} \label{app:mc}}
+
+The marginalization of the posterior is performed
 with the package {\tt pypmc}~\cite{beaujean_2015_20045}, which incorporates the

### 2015-07-15 tensor/draft/draft-tensor-op.tex
[draft] correct subsection on posterior predictive

@@
   given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
-\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Non-zero values of
+\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Nonzero values of
 $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
@@
 vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
-non-vanishing tensor or scalar contributions are enhanced unless the dynamics of
+nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
 NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
@@
 
-We also perform a fit with non-zero $\wilson[NP]{9,\,10}$ \fred{Is this
+We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ \fred{Is this
   $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
@@
     \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
-    data in \reftab{tab:observables} as well as non-zero
+    data in \reftab{tab:observables} as well as nonzero
     $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
@@
 
-A non-redundant set of dimension-six operators of this effective theory (SM-EFT)
+A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
 was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
@@
       constraints in \reftab{tab:observables} (red) when marginalising over
-      non-zero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
+      nonzero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
       superimpose the corresponding contours from using only $\overline{\cal
@@
 consequence of embedding the Higgs in a weak doublet along with the Goldstone
-bosons.  For example choosing a non-linear representation of the scalar sector
+bosons.  For example choosing a nonlinear representation of the scalar sector
 allows additional dimension-six operators in the SM-EFT, such that the couplings
@@
   & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
-  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-\todo{10}}$
+  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
   & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
@@
   \hline
-  \multicolumn{2}{c}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
+  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
+  & --
   & 1
-  & SM
+  & 1
   & $[-1,\, 1]$
@@
      \label{tab:postdictions}
-     The 68\% probability intervals of not-yet-measured angular observables in
-     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
-     for several new physics scenarios respecting all the considered experimental
-     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
+     The posterior predictive 68\% probability intervals of not-yet-measured angular observables in
+%     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
+     for several new-physics scenarios given all the considered experimental
+     constraints. The corresponding values for the SM (prior predictive) are given, too, where ``$\simeq 0$''
      indicates zero in the considered
-     approximation, see text for more explanations.
+     approximation, see text for details. \checked{}
    }
@@
 
-Now we present the yet allowed ranges due to non-standard tensor and scalar
-couplings of the so far unmeasured angular observables $J_{6c}$, $(J_{1s} - 3\,
-J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$ in order to
-explore the potential of their future measurements in fits of the kind pursued
-in this work.  The 68\% probability intervals are collected in
-\reftab{tab:postdictions} for the various model-independent scenarios, allowing
-for interference with non-zero vector couplings, in \refsec{sec:tensor},
-\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for $q^2$-integrated
-quantities in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and
-$q^2\in [15,\, 19]$ GeV$^2$, respectively. Their posterior distributions have
-been obtained from the posterior samples as explained in~\ref{app:mc}.
-
-For comparison, the SM estimates are also given in \reftab{tab:postdictions}
-multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
-At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
-$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
-due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
-magnitude of vector couplings, note that for example the branching ratio of
-$B\to K^*\bar\ell\ell$
+Now we discuss what the fits tells us about likely values of observables that
+have not been measured yet but have sensitivity to tensor and scalar couplings.
+In the $B\to K^*(\to K\pi)\bar\ell\ell$ decay, we again consider $(J_{1s} - 3\,
+J_{2s})$ and $(J_{1c} + J_{2c})$ as in \refsec{sec:observables} and additionally
+$J_{6c}$. We compute the posterior predictive distribution (see ~\ref{app:mc})
+for each observable integrated over the low-$q^2$ bin $[1.1,\, 6]$~GeV$^2$ and
+high-$q^2$ bin $[15,\, 19]$~GeV$^2$ matching LHCb's range. The distributions
+resemble Gaussians, thus we summarize them by their modes and smallest 68\%
+intervals in \reftab{tab:postdictions} comparing the SM (prior predictive,
+$\wilson[NP]{i}=0$) to three NP scenarios. In each, we allow for interference
+with the vector couplings and additionally vary only $\wilson{T,T5}$
+(\refsec{sec:tensor}), only $\wilson{S^{(')},P^{(')}}$ (\refsec{sec:scalar}),
+and finally both tensor and scalar couplings (\refsec{sec:tensor:scalar}).
+
+We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
+1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
+them in the near future.  At low $q^2$ the posterior predictive ranges are
+${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
+suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
+$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
+of vector couplings, note that for example the branching ratio of $B\to
+K^*\bar\ell\ell$
 \begin{align}
@@
 
-The angular observable $J_{6c}$ is strictly zero in the absence of
-tensor and scalar couplings. Non-zero contributions can be generated
-in the SM by QED corrections or potentially from higher-dimensional
-($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to
-parametrical suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$,
-respectively. Such a suppression must be compared to potential
-suppression present for tensor and scalar contributions in particular
-NP models in order to decide their relevance. Our model-independent
-fits are still in a realm where such considerations are insignificant
-since current experimental measurements, in combination with theory
-uncertainties, do not impose yet too stringent constraints on tensor
-and scalar couplings.
-
-Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in
-scenarios involving tensor couplings only and about ${\cal
-  O}(10^{-10})$ in the presence of scalar couplings only. Both effects
-are due to interference with vector couplings. Due to the strong
-suppression of scalar couplings, the direct interference of scalar and
-tensor contributions the allowed region in the most general scenario
-\todo{schematic formula from notes}
-
-Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
-deviations from the SM prediction are possible only in the presence of non-zero
-tensor couplings. In this case enhancement by two orders of magnitude are
-possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
-the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
-experimental constraints in \reftab{tab:observables}. In view of current
-experimental precision of $20\%$ of the branching ratio measurements at LHCb
-\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal
-  O}(10^{-8})$, one can indeed hope for some sensitivity to such large effects
-in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not-yet-published 3
-fb$^{-1}$ data set at least with the method of moments~\cite{beaujean:2015mom}.
-
-The CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
-non-vanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell})
-can still take any value in the range $[-1,\, 1]$ in scenarios with
-nonzero scalar couplings.
+The angular observable $J_{6c}$ is strictly zero in the absence of tensor and
+scalar couplings. Nonzero contributions can be generated in the SM by QED
+corrections or potentially from higher-dimensional ($d \geq 8$) $|\Delta B| =
+|\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
+\pi)$ or $(m_b/m_W)^2$. These factors should be compared to the potential
+suppression present for tensor and scalar contributions in particular NP models
+in order to gauge their relevance. Our model-independent fits are still in a
+regime where such considerations are insignificant since current experimental
+measurements, in combination with theory uncertainties, do not yet impose too
+stringent constraints on tensor and scalar couplings.
+
+Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in scenarios
+involving tensor couplings only and about ${\cal O}(10^{-10})$ in the presence
+of scalar couplings only. Both effects are due to interference with vector
+couplings.  Schematically, $J_{6c}$ is a function of $\wilson{T} \times
+\wilson{P} + \wilson{S} \times \wilson{T5}$, $\frac{m_{\ell}}{\sqrt{q^2}}
+(\mbox{scalar}) \times (\mbox{vector})$, and $\frac{m_{\ell}}{\sqrt{q^2}}
+(\mbox{tensor}) \times (\mbox{vector})$. The largest interval is obtained for
+the scenario without scalar couplings because then the uncertainty on the
+(tensor) couplings is largest. But even then, it seems the experimental
+sensitivity will not be high enough to have an impact in global fits.
+
+Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, substantial
+deviations from the SM prediction are again only possible in the presence of
+nonzero tensor couplings. In this case, an enhancement by two orders of
+magnitude is possible up to ${\cal O}(10^{-8})$ at high $q^2$ and also at low
+$q^2$ in the case of $(J_{1s} - 3\, J_{2s})$. We want to stress again that we
+make these statements conditional on all included experimental constraints, the
+scenario, and our prior. In view of the current experimental precision of $20\%$
+on the branching ratio at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$,
+corresponding to the ${\cal O}(10^{-8})$, one can indeed hope for some
+sensitivity to such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\,
+J_{2s})$ for the not-yet-published 3 fb$^{-1}$ data set. At least, we can hope
+for some measurement if the method of moments~\cite{beaujean:2015mom} is
+applied.
+
+For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by the
+nonvanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell}), we find a
+rather uniform distribution in scenarios with nonzero scalar couplings. So any
+value in the range $[-1,\, 1]$ is OK whereas we predict precisely one in the SM
+and the scenario with only tensor couplings; cf.  the last row in
+\reftab{tab:postdictions}. Hence any deviation from one would unambiguously hint
+at the presence of scalar operators.
 
@@
   $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
-  (0.43)$, even in the presence of non-standard contributions in vector
+  (0.43)$, even in the presence of nonstandard contributions in vector
   couplings.
@@
 $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
-$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by non-vanishing width of the
+$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by nonvanishing width of the
 $B_s$ meson can still take any value in the range $[-1,\, 1]$.
@@
   corresponds to the unintegrated branching ratio at time $t=0$. Due to the
-  non-vanishing decay width $\Delta\Gamma_s$, experiments measure the average
+  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
   time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
@@
 This parameterization allows us to combine consistently available results
-of form factors from different non-perturbative approaches, namely LCSR's at
+of form factors from different nonperturbative approaches, namely LCSR's at
 large recoil and lattice at low recoil and implement simultaneously the

### 2015-07-15 tensor/draft/draft-tensor-op.tex
[draft] revise conclusions and acknowledgements

@@
   \end{center}
-\caption{ The sensitivity to the tensor coupling
-      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
-      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
-      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
-      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
-      last two rows, the observables are normalized by the lifetime of
-      the $B$ meson for easier comparison with the branching
-      ratios. The bands represent the theory uncertainties at 68\%
-      and 95\% probability.  For comparison, two sets of bands are
-      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
-      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
-      latest 68\% uncertainty reported by LHCb (grey) if a measurement
-      is available.
-      }
+  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
+    $F_H$ (first row) and ${\cal B}$ (second row) in $B^+ \to K^+ \bar\mu\mu$
+    and ${\cal B}$ (third row), $J_{1c} + J_{2c}$ (fourth row), and $J_{1s}-3
+    J_{2s}$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ integrated over low- and
+    high-$q^2$ bins. In the last two rows, the observables are rescaled by the
+    lifetime of the $B$ meson for easier comparison with the branching
+    ratios. The bands represent the theory uncertainties at 68\% and 95\%
+    probability of the prior predictive distribution.  For comparison, two sets
+    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
+    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
+    confidence interval reported by LHCb (grey) if a measurement is
+    available. \checked{} }
   \label{fig:FHvsCT}
@@
 \section{
-  Fits and constraints
+  \checked{Fits and constraints}
   \label{sec:results}
@@
 $\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
-coordinates but never in even the 95\% region in polar coordinates. This is a
-consequence of the general \emph{concentration of measure}. Another way to look
-at it is to transform the uniform prior density from cartesian to polar
-coordinates. For the example of the single Wilson coefficient, say $\wilson{T}$,
-the transformed density is proportional to the determinant of the Jacobian which
-is $|\wilson{T}|$. In words, the uniform prior on $\mbox{Re}(\wilson{T})$ and
-$\mbox{Im}(\wilson{T})$ favors larger values of $|\wilson{T}|$ even though we
-consider it consensus in the community that smaller rather than larger values
-are held reasonable because in the SM, $\wilson{T} = 0$. We suggest therefore
-that the default prior be changed in the future.
+coordinates but never in even the 95\% region in polar coordinates\footnote{But
+  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
+  region.}. This is a consequence of the general \emph{concentration of
+  measure}. Another way to look at it is to transform the uniform prior density
+from cartesian to polar coordinates. For the example of a single Wilson
+coefficient, say $\wilson{T}$, the transformed density is proportional to the
+determinant of the Jacobian which is $|\wilson{T}|$. Since the cartesian prior
+boundaries are much larger than the regions of high likelihood, one could think
+the value of the boundary is irrelevant but in fact it determines the peak of
+the prior in polar coordinates. In other words, the uniform prior on
+$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
+$|\wilson{T}|$ even though we consider it consensus in the community that
+smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
+SM. We suggest therefore that the default treatment be revised in the future to
+include available prior knowledge.
 
@@
 %--------+---------+---------+---------+---------+---------+---------+---------+
-\section{Conclusions}
-
-We have derived to date most stringent constraints on tensor and scalar
-couplings that mediate $b\to s\bar\mu\mu$ utilising the latest measurements
-of angular observables $F_H^\mu$ and the lepton forward-backward asymmetry
-$A_{\rm FB}^\mu$ in $B^+\to K^+ \bar\mu\mu$ from LHCb \cite{Aaij:2014tfa},
-supplemented by measurements of the branching ratios of $B_s\to \bar\mu\mu$ and
-$B\to K^{(*)} \bar\mu\mu$. Both observables, $F_H^\mu$ and $A_{\rm FB}^\mu$,
-belong to a class in which vector and dipole couplings that arise also in
-the standard model (SM) are suppressed (mostly kinematically by $m_\ell /
-\sqrt{q^2}$) w.r.t tensor and scalar couplings. We provide predictions for
-analogous but not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
-and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$.
-
-We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
+\section{\checked{Conclusions}}
+
+We have derived the most stringent constraints to date on tensor and scalar
+couplings that mediate $b\to s\bar\mu\mu$ transitions using the latest
+measurements of angular observables $F_H^\mu$ and the lepton forward-backward
+asymmetry $A_{\rm FB}^\mu$ in $B^+\to K^+ \bar\mu\mu$ from LHCb
+\cite{Aaij:2014tfa}, supplemented by measurements of the branching ratios of
+$B_s\to \bar\mu\mu$ and $B\to K^{(*)} \bar\mu\mu$. Both $F_H^\mu$ and $A_{\rm
+  FB}^\mu$ belong to a class of observables in which vector and dipole
+couplings---present in the standard model (SM)---are suppressed (mostly
+kinematically by $m_\ell / \sqrt{q^2}$) with respect to tensor and scalar
+couplings. We provide predictions for the equivalent but not-yet-measured
+angular observables $J_{6c}$, $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$ in
+$B\to K^* (\to K\pi) \bar\mu\mu$.
+
+In a Bayesian analysis of the complex-valued couplings of the effective theory,
+we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
 \begin{enumerate}
-\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
-  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
-  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
-  (0.43)$, even in the presence of nonstandard contributions in vector
-  couplings.
-\item allows for the first time to bound all four scalar couplings $\wilson{i}$
-  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s
-  \to \bar\mu\mu)$. Even when taking into account destructive interference with
-  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and
-  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%)
-  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
-  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
-  future, measurements at LHCb and Belle II will further tighten the bounds.
-
-  Moreover, measurements of $F_H^e$ ($\ell = e$)
-  will provide constraints on scalar couplings in the electron channel in
-  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
+  \item imposes by itself bounds on tensor couplings $|\wilson{T,\,T5}|$ such
+  that the upper bound of the smallest 68\% (95\%) credibility interval is
+  $0.43\, (0.57)$, superseding previous bounds.  In combination with current
+  data from $B\to K^* \bar\mu\mu$ and lattice $B\to K^*$ form factors, the
+  bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
+  contributions in vector couplings.
+  \item for the first time allows to bound all four scalar couplings
+  $\wilson{i}$ with $i = S,\,S',\,P,\,P'$ due to it's complementarity to
+  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
+  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
+  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
+  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
+  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
+  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
+  further tighten the bounds.
+
+  Moreover, measurements of $F_H^e$ ($\ell = e$) will provide constraints on
+  scalar couplings in the electron channel in the absence of a direct
+  determination of the branching ratio of $B_s \to \bar{e}e$.
 \end{enumerate}
@@
 interference effects with vector couplings. These bounds hold even in the most
-general scenario of complex-valued tensor, scalar and vector couplings, showing
-also that the data is able to bound the real and imaginary parts of all Wilson
-coefficients simultaneously.
-
-As a special case, we considered also the scenario arising from the SM augmented
-by dimension 6 operators generalising existing studies to the case of complex-valued
-couplings. In this scenario tensor couplings are absent and additional
-relations between scalar couplings are enforced by the linear realisation of the
-$SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
-
-Our study of yet-not-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
+general scenario of complex-valued tensor, scalar, and vector couplings, showing
+that the data are good enough to bound the real and imaginary parts of all
+Wilson coefficients simultaneously.
+
+As a special case, we considered the scenario arising from the SM augmented by
+dimension-6 operators generalising existing studies to the case of
+complex-valued couplings. In this scenario, tensor couplings are absent and
+additional relations between scalar couplings are enforced by the linear
+realisation of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
+
+Our study of not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$,
 and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
-\reftab{tab:postdictions}) shows that despite the current bounds on tensor couplings,
-enhancements of two orders of magnitude over the SM predictions are allowed for
-$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. On the other hand, current bounds
-on scalar couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$ are already quite
-restrictive allowing only for small deviations from SM predictions in
-$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
-$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by nonvanishing width of the
-$B_s$ meson can still take any value in the range $[-1,\, 1]$.
+\reftab{tab:postdictions}) shows that despite the current bounds on tensor
+couplings, enhancements of up to two orders of magnitude over the SM predictions
+are allowed for $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in
+reach of the LHCb analysis of the full phase I data set. Our bounds on scalar
+couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
+restrictive permitting only small deviations from SM predictions in $(J_{1c} +
+J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
+$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ is a sensitive probe to distinguish tensor
+from scalar couplings; it can take on any value in the range $[-1,\, 1]$ for
+nonzero scalar couplings but is fixed to one if the scalar couplings vanish.
 
@@
   We are grateful to Danny van Dyk for helpful discussions and his support on
-  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
-  Bouchard and Matthew Wingate for communications on their results of $B\to K$
-  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
-  respectively. We thank also David Straub for his support with LCSR results of
-  $B\to K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
+  EOS \cite{EOS}. Concerning form factor results from lattice QCD, we thank
+  Chris Bouchard and Matthew Wingate for communications on their results of
+  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
+  factors. We thank also David Straub for his support with LCSR results of $B\to
+  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
   Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the

### 2015-07-16 tensor/draft/draft-tensor-op.tex
[draft] Revise abstract and theory appendix

@@
-% \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
 \documentclass[twocolumn,epjc3]{svjour3}
@@
 %%
-\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
 \newcommand{\fred}[1]{{\color{green}{#1}}}
@@
 \newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
+\renewcommand{\checked}[1]{#1}
 
@@
 \newlength{\relwidth}
+
+%
+% codes
+%
+\def \eos{\texttt{EOS}}
 %--------+---------+---------+---------+---------+---------+---------+---------+
@@
 \begin{abstract}
-  \todo{check}
-  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
-  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
-  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
-  suppressed in the standard model. In both, nonstandard tensor and
-  scalar contributions are enhanced with respect to vector ones. We
-  use latest experimental results for $\ell = \mu$ in combination with
-  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
-  on tensor and scalar effective couplings and determine their impact
-  on not-yet-measured angular observables in $B\to K^*\bar\mu\mu$,
-  which feature the same suppression of vector couplings.  Most
-  notably, the measurement of $F_H^\mu$ provides constraints on
-  (pseudo-)scalar couplings and their chirality-flipped counterparts
-  that are complementary to the ones from the branching ratio $B_s\to
-  \bar\mu\mu$, which allows to put for the first time simultaneously
-  upper bounds on all four couplings. \fred{Try to shorten, add
-    sentence ``independent of deviations in vector-coupling dominated
-    observables''. There could be a bit of summary of outcome here, too}
-  \todo{check captions of figures and tables}
+  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
+  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
+    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
+  the standard model and constitute sensitive probes of tensor and scalar
+  contributions. We use the latest experimental results for $\ell = \mu$ in
+  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
+  bounds on tensor and scalar effective couplings to date. The measurement of
+  $F_H^\mu$ is complementary to that of the branching ratio of $B_s\to
+  \bar\mu\mu$ and allows us---for the first time---to constrain all
+  complex-valued (pseudo-)scalar couplings and their chirality-flipped
+  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
+  that our bounds even become tighter when vector couplings are allowed to
+  deviate from the standard model and that specific combinations of angular
+  observables in $B \to K^*$ are still allowed to be up to two orders of
+  magnitude larger than in the standard model, which would place them in the
+  region of LHCb's sensitivity.
+%   \todo{check captions of figures and tables}
 \end{abstract}
@@
   We are grateful to Danny van Dyk for helpful discussions and his support on
-  EOS \cite{EOS}. Concerning form factor results from lattice QCD, we thank
+  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
   Chris Bouchard and Matthew Wingate for communications on their results of
@@
 \section{
-  Theoretical Inputs
+  \checked{Theoretical Inputs}
   \label{app:theory:inputs}
@@
 
-Here we describe the theoretical treatment of observables and collect numerical
-input of the most relevant parameters. The software package {\tt EOS}
+Here we describe the theoretical treatment of observables and collect the
+numerical input for the relevant parameters. The software package \eos{}
 \cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for the calculation of
 observables in $B_s\to \bar\mu\mu$ and $B\to K^{(*)}\bar\ell\ell$ and associated
-constraints. Both the likelihood and the prior are defined entirely within EOS.
+constraints. Both the likelihood and the prior are defined entirely within \eos.
 
 Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
-the compilation of nuisance parameters and according values, whose uncertainties
-are negligible. Further, we adopt the same values for common nuisance parameters of
-$i)$ the CKM quark-mixing matrix, $ii)$ the charm and bottom quark masses in the
-$\overline{\rm MS}$ scheme, and $iii)$ the parameterisation of subleading corrections
+the compilation of nuisance parameters relevant to this work. We adopt the same
+values for fixed parameters and the same priors unless noted otherwise
+below. Specifically, we use identical priors for for common nuisance parameters
+of the CKM quark-mixing matrix, the charm and bottom quark masses in the
+$\overline{\rm MS}$ scheme, and the parameterisation of subleading corrections
 in $1/m_b$ as given in \cite{Beaujean:2013soa}.
@@
 FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
-averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.
-More recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and
-$N_f = 2$ \cite{Carrasco:2013zta} are consistent with these averages.
-
-The tensor and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
-i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
-are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
-given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively and we refrain from
-using respective form factor relations at large and low recoil for the tensor and scalar
-$B\to K$ and $B\to K^*$ form factors.
+averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.  More
+recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and $N_f = 2$
+\cite{Carrasco:2013zta} flavors are consistent with these averages.
+
+The tensor and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize
+naively, i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form
+factors. These amplitudes are implemented in \eos{} for $B\to K \bar\ell\ell$
+and $B\to K^* \bar\ell\ell$ as given in \cite{Bobeth:2007dw} and
+\cite{Bobeth:2012vn}, respectively and we refrain from using form-factor
+relations at large and low recoil for the tensor and scalar $B\to K$ and $B\to
+K^*$ form factors.  Therefore, we need additional nuisance parameters for the
+complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
+$z$ parameterization \cite{Khodjamirian:2010vf} and the kinematic relation
+$f_0(0) = f_+(0)$, five nuisance parameters (listed in
+\reftab{tab:hadronic:nuisance}) are needed. As prior information, we average the
+LCSR results~\cite{Khodjamirian:2010vf} and \cite{Ball:2004ye} (see
+\reftab{tab:hadronic:nuisance} and cf. \cite{Beaujean:2013soa}) supplement them
+with lattice determinations~\cite{Bouchard:2013eph}.
+
+Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma distribution
+for the asymmetric uncertainties in priors anymore but rather a continuous yet
+asymmetric Gaussian distribution. In a unifying spirit, we now use the
+continuous rather than discontinuous asymmetric Gaussian to approximate
+asymmetric experimental intervals in our likelihood.
+
+The lattice results are given in a slightly different parametrization
+necessitating a conversion to the parametrization used here. For this purpose,
+we generate the form factors from the parametrization
+of~\cite{Bouchard:2013eph}, including full correlations, at three values of $q^2
+= 17,\, 20,\, 23$ GeV$^2$.  Subsequently, these ``data'' are included in the
+prior by means of a multivariate Gaussian whose mean and covariance is given in
+\reftab{tab:btok-lattice}. The $q^2$ values and number of points are chosen such
+that the correlation of neighboring points is small enough to keep the
+covariance nonsingular.
 
@@
 \hline
-  Quantity & Prior & Unit & Reference\\
-\hline \hline
-  \multicolumn{4}{c}{$B_s$ decay constant}
-\\
-\hline
-  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
-\hline \hline
-  \multicolumn{4}{c}{$B\to K$ form factors}\\
-\hline
-  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
-  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
-  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
-  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
-  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
-\hline \hline
-\multicolumn{4}{c}{$B\to K^*$ form factors}\\
-\hline
-\todo{fill in}\\
+  Quantity & Prior & Reference\\
+\hline
+  \multicolumn{3}{c}{$B_s$ decay constant}
+\\
+\hline
+  $f_{B_s}$   &  ($227.7 \pm 4.5$) MeV &  \cite{Aoki:2013ldr}\\
+\hline
+  \multicolumn{3}{c}{$B\to K$ form factors}\\
+\hline
+  $f_+(0)=f_0(0)$    &  $0.34 \pm 0.05$       &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
+  $f_T(0)$    &  $0.38 \pm 0.06$      &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
+  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  \cite{Khodjamirian:2010vf}\\
+  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  \cite{Khodjamirian:2010vf}\\
+  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  \cite{Khodjamirian:2010vf}\\
+\hline
+\multicolumn{3}{c}{$B\to K^*$ form factors}\\
+\hline
+$\alpha_{0}^{A_0}$     & $0.35^{+0.02}_{-0.03}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{A_0}$     & $-1.21^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{A_0}$     & $0.77^{+0.45}_{-0.48}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{0}^{A_1}$     & $0.2625^{+0.015}_{-0.015}$  & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{A_1}$     & $0.07^{+0.08}_{-0.08}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{A_1}$     & $0.045^{+0.12}_{-0.15}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{A_{12}}$  & $0.53^{+0.10}_{-0.14}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{A_{12}}$  & $0.32^{+0.33}_{-0.39}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{0}^{V}$       & $0.35^{+0.02}_{-0.03}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{V}$       & $-1.19^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{V}$       & $1.55^{+0.33}_{-0.33}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{0}^{T_1}$     & $0.31^{+0.02}_{-0.02}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{T_1}$     & $-1.07^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{T_1}$     & $1.40^{+0.30}_{-0.30}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{T_2}$     & $0.33^{+0.08}_{-0.10}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{T_2}$     & $0.26^{+0.21}_{-0.24}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{0}^{T_{23}}$  & $0.67^{+0.04}_{-0.05}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{1}^{T_{23}}$  & $0.93^{+0.28}_{-0.22}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
+$\alpha_{2}^{T_{23}}$  & $-0.15^{+0.86}_{-0.71}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
 \hline
@@
 \renewcommand{\arraystretch}{1.0}
-\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
-   for hadronic quantities entering inclusive and exclusive decays. Note that
-   $f_0(0) = f_+(0)$.
-}
+\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance
+  parameters for hadronic quantities. \checked{} }
 \end{center}
 \end{table}
-
-As we do not make use of form factor relations for tensor and scalar amplitudes
-in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
-set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
-$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters
-(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematic relation
-$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
-and \cite{Ball:2004ye} have been averaged (see \reftab{tab:hadronic:nuisance} and
-cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}.
-Contrary to \cite{Beaujean:2013soa}, we do not adapt anymore a log-gamma prior for
-the asymmetric uncertainties but rather a continuous, but asymmetric gaussian distribution.
-The lattice results are given within a slightly different parameterisation necessitating
-a conversion to the parameterisation used here. For this purpose, we generate the
-form factors from the parameterisation \cite{Bouchard:2013eph}, including full
-correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
-compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
-such that the correlation of neighboring points does not exceed $80\%$.)
-Subsequently, these ``data'' of the form factors is included in the likelihood
-by means of a multivariate Gaussian in addition to experimental measurements.
 
@@
     \renewcommand{\arraystretch}{1.0}
-    \caption{Mean values, uncertainties (top) and correlation
-        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
-        $B\to K$ form factors $f_{0,+,T}(q^2)$.
+    \caption{Mean values, standard deviations (top) and correlation
+        coefficients (bottom) of lattice points \cite{Bouchard:2013eph} for the
+        $B\to K$ form factors $f_{0,+,T}(q^2)$. \checked{}
         \label{tab:btok-lattice}
@@
 We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
-work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
-(SSE) \cite{Bharucha:2010im}
+work \cite{Beaujean:2013soa} slightly and now use the simplified series
+expansion (SSE) \cite{Bharucha:2010im}
 \begin{align}
@@
 \end{align}
-with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1},
-T_{1,23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
+with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_0,A_1,
+T_1,T_{23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
 correspond to $F_i(q^2 = 0)$ and the kinematic constraints
@@
   A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,, &
-  T_1(0) & = T_2(0)
+  T_1(0) & = T_2(0) \,,
 \end{align}
@@
 
-This parameterization allows us to combine consistently available results
-of form factors from different nonperturbative approaches, namely LCSR's at
-large recoil and lattice at low recoil and implement simultaneously the
-kinematic constraints. We determine the parameters $\alpha_i^k$
-in a combined fit to form factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the
-LCSR \cite{Straub:2015ica} and of $V, A_{0,1,12},T_{1,2,23}$ from the lattice
-\cite{Horgan:2013hoa, Horgan:2015vla} calculations,
-including their correlations. Further, we implement the second kinematic constraint
+This parameterization allows us to consistently combine available results of
+form factors from different nonperturbative approaches, namely LCSR's at large
+recoil and lattice at low recoil and to simultaneously implement the kinematic
+constraints. We determine the parameters $\alpha_i^k$ in a combined fit to
+form-factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the LCSR
+\cite{Straub:2015ica} and of $V, A_0,A_1,A_{12},T_1,T_2,T_{23}$ from the lattice
+\cite{Horgan:2013hoa, Horgan:2015vla} calculations, including their
+correlations. We verified that the  constraint
 \begin{align}
@@
 \end{align}
-at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
-are chosen for all $\alpha_k^i$
+at the kinematic endpoint $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$ is satisfied
+to high accuracy by the above constraints and thus need not be imposed
+explicitly. Uninformative flat priors are chosen for all $\alpha_k^i$ with
+ranges
 \begin{align}
@@
   \alpha_{2}^i & \in [-3,\, 3] \,.
-\end{align}
-The results of the LCSR predictions of the form factors have been provided to us
+t\end{align}
+The results of the LCSR form-factor predictions have been provided to us
 directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
-12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12},\, T_{1,2,3}$, including their $28\times 28$
-covariance matrix. \todo{In the case of lattice predictions, we proceed as in our
-previous work \cite{Beaujean:2013soa} by generating form factor values of
-$V,\, A_{0,1,12},\, T_{1,2,3}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
-\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
-see \reftab{tab:btok-lattice}.}
-
-\todo{We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
-versus two parameters only and found that in the latter case lattice form factor
-results influence the fit such that form factors tend to be higher than LCSR
-predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
-setup as it accommodates better LCSR and lattice results.}
+12.1)\, \mbox{GeV}^2$ for $V, A_0,A_1,A_{12},T_1,T_2,T_{3}$ including the
+$28\times 28$ covariance matrix. Similar results could have been obtained by
+``drawing'' form factors from the correlated parameters given in
+\cite{Straub:2015ica} and ancillary files just as for $B \to K$ lattice form
+factors.
+
+But for the $B \to K^*$ lattice form factors this approach is not good enough as
+we were not even able to select just two $q^2$ values and obtain a nonsingular
+covariance. We then contacted the authors of~\cite{Horgan:2015vla} and obtained
+the original values of the form factors (including correlation) at various
+values in the interval $q^2 \in [11.9,\, 17.8]$ to which Horgan et al. fit the
+SSE. The covariance has a block-diagonal structure with a 48$\times$48 block for
+$V, A_0, A_1, A_{12}$ and a 36$\times$36 block for $T_1, T_2, T_{23}$. Having
+the ``raw'' information on form-factor values is much more reliable and future
+proof as there are no issues with artificial correlation and we could one day
+decide to use yet another form-factor parametrization and fit it easily to these
+data points.
+
+We have compared the SSE fit \refeq{eq:SSE-FF-parameterization} with two versus
+three parameters and found that in the former case lattice form factors
+influence the fit such that form factors tend to be higher than LCSR predictions
+at low $q^2$ leading to a poor fit. Hence we prefer the three-parameter setup as
+it provides the flexibility needed to accomodate LCSR and lattice results. Means
+and standard abbreviations of that three-parameter fit are given in
+\reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
+but are happy to provide them.
 
@@
 
+\todo{this is just filler text to avoid ``pdfendlink ended up in different
+  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
+}
+
 %

### 2015-08-03 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] christoph's corrections to finalize draft for arxiv v1 submission

@@
 \def \refeq#1{(\ref{#1})}
-\def \refsec#1{Section \ref{#1}}
+\def \refsec#1{Section~\ref{#1}}
 \def \refapp#1{\ref{#1}}
-\def \reffig#1{Figure \ref{#1}}
-\def \reftab#1{Table \ref{#1}}
+\def \reffig#1{Figure~\ref{#1}}
+\def \reftab#1{Table~\ref{#1}}
 
@@
 %%
+\newcommand{\christoph}[1]{{\color{red}{#1}}}
 \newcommand{\fred}[1]{{\color{green}{#1}}}
@@
 
-\thankstext[$\star$]{t1}{\todo{EOS-2015-??}, FLAVOUR(267104)-ERC-107}
+\thankstext[$\star$]{t1}{\christoph{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
 \thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
@@
   bounds on tensor and scalar effective couplings to date. The measurement of
-  $F_H^\mu$ is complementary to that of the branching ratio of $B_s\to
+  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
   \bar\mu\mu$ and allows us---for the first time---to constrain all
@@
   region of LHCb's sensitivity.
-%   \todo{check captions of figures and tables}
 \end{abstract}
@@
 With the analysis of the data collected by the LHCb Collaboration
-during phase I at the Large Hadron Collider (LHC), we now have access
-to rather large samples of rare $B$ meson decays with branching ratios
+during \christoph{Run} I at the Large Hadron Collider (LHC), we now have access
+to rather large samples of rare \christoph{$B$-meson} decays with branching ratios
 below $10^{-5}$. As a consequence, angular analyses of three- and
@@
 \bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
-\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} did not allow to perform a full
+\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
 angular analysis without the assumption of vanishing scalar and tensor couplings
@@
    \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
-      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
+      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
  \\ & +
        \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
+   \christoph{\,,}
 \end{aligned}
@@
 s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
-structure. There are dipole ($i = 7,7'$ \fred{so there is no $\mu, \tau$ version
-  of $\wilson{7}$? I guess it should also depend on $\mu_b$}) and vector ($i =
-9,9',10,10'$) operators
+structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
 \begin{equation}
@@
 also used frequently in the literature. The respective short-distance couplings,
-the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
+the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
 the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
@@
 
+\christoph{For the rest of this article we will suppress the lepton-flavor index
+on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$. In \refsec{sec:results}
+we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
+principle only to the muonic case, but can be carried over to other lepton
+species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
+flavor. In general the Wilson coefficients are decomposed into SM and NP
+contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
+will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
+contributions synonymously for $\wilson[NP]{i}$. }
+
 %
@@
 the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
-with $\mbox{dim} > 6$. These results imply that for SM values of the effective
+with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
 couplings
 \begin{align}
-  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
+  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
+    \christoph{\bigg/ \Gamma_\ell} \,, &
   A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
 \end{align}
-Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.  The flat
-term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed away from both \fred{Why
-  both? At $q^2_{\rm max}$ it is strongly suppressed according to the formula
-  given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
-\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Nonzero values of
-$A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
-which will modify the simple $\cos\theta_\ell$ dependence of the angular
+Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
+The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
+lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
+\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
+Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
+corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
 distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
 available for this source of SM background\footnote{The leading QED corrections
-  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
-  corresponding effects in $B\to K \bar\ell\ell$.}.
+  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} \todo{(update ref. with published)} might provide an estimate of
+  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}
 
@@
   \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
-    $F_H$ (first row) and ${\cal B}$ (second row) in $B^+ \to K^+ \bar\mu\mu$
-    and ${\cal B}$ (third row), $J_{1c} + J_{2c}$ (fourth row), and $J_{1s}-3
-    J_{2s}$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ integrated over low- and
-    high-$q^2$ bins. In the last two rows, the observables are rescaled by the
+    \christoph{$F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
+    in $B^+ \to K^+ \bar\mu\mu$
+    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$ 
+    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ 
+    integrated over low- and high-$q^2$ bins. In the last two rows, the observables 
+    are rescaled by the
     lifetime of the $B$ meson for easier comparison with the branching
@@
 From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
-\to K$ observable is attained by $F_H^\ell$ at high $q^2$ due to a partial
+\to K$ observable is attained by \christoph{$F_H^\mu$} at high $q^2$ due to a partial
 cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
-uncertainty could be reduced further, $F_H^\ell$ would give a very strong
+uncertainty could be reduced further, \christoph{$F_H^\mu$} would give a very strong
 constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
-$\wilson[NP]{T}$. The prediction of ${\cal B}(B\to K \bar\ell\ell)$ is
-essentially insensitive to $\wilson{T}$ but sensitive to $\wilson{NP}[9]$. A
-stronger impact on global fits, however, would required reduced theory
+\christoph{$\wilson{T}$}. The prediction of \christoph{${\cal B}(B\to K \bar\mu\mu)$} is
+essentially insensitive to $\wilson{T}$ but sensitive to \christoph{$\wilson[NP]{9}$}. A
+stronger impact on global fits, however, would \christoph{require a} reduced theory
 uncertainty.
 
-The observable ${\cal B}(B\to K^* \bar\ell\ell)$ shows moderate dependence on
+The observable \christoph{${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
 $\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
@@
 
-$J_{1c}+J_{2c}$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low
-$q^2$, it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
-unaffected. Regarding $J_{1s}-3J_{2s}$, the situation is reversed: here the
-strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, $F_H^\ell$,
-$J_{1c}+J_{2c}$ at large $q^2$, and $J_{1s}-3J_{2s}$ are sensitive to
-$\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.
-
-From the available measurements, $F_H^\ell$ at high $q^2$ currently provides the
+$(J_{1c}+J_{2c})$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low~$q^2$, 
+it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
+unaffected. Regarding $(J_{1s}-3J_{2s})$, the situation is reversed: here the
+strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, \christoph{$F_H^\mu$},
+$(J_{1c}+J_{2c})$ at \christoph{high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
+to $\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.
+
+From the available measurements, \christoph{$F_H^\mu$} at high $q^2$ currently provides the
 most stringent constraints on the size of tensor couplings. Moreover, the
-dependence on vector couplings is such that $\wilson[NP]{9} < 0$ leads to
-stronger constraints on $\wilson{T}$ than $\wilson[NP]{9} \approx
+dependence on vector couplings is such that $\wilson[NP]{9} \lesssim 0$ leads to
+stronger constraints on~$\wilson{T}$ than $\wilson[NP]{9} \approx
 0$.
@@
 
-Eventually we also explore the effect of interference with NP in the vector
-couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor and scalar
-couplings.  For this purpose we include also the branching ratio, the lepton
-forward-backward asymmetry, and the rate CP asymmetry of $B\to K^* \bar\mu\mu$
-as they provide additional constraints on the real and imaginary parts of
-$\wilson{9,\,9',\,10,\,10'}$. The experimental inputs of all observables
-entering our fits is listed in \reftab{tab:observables} together with input for
+Eventually we also explore the effect of interference with \christoph{NP contributions}
+in the vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds 
+on tensor and scalar couplings.  For this purpose we include also the branching 
+ratio, the lepton forward-backward asymmetry, and the rate CP asymmetry of 
+$B\to K^* \bar\mu\mu$ as they provide additional constraints on the real and 
+imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental \christoph{input} of all 
+observables entering our fits is listed in \reftab{tab:observables} together with input for
 the $B\to K^{(*)}$ form factors. More details on the latter can be found in
@@
 main objective is to derive constraints on tensor and scalar couplings through
-the enhanced sensitivity of both observables to those couplings compared to
+the enhanced sensitivity of both observables to \christoph{these} couplings compared to
 vector couplings. For this purpose, we will consider several model-independent
@@
 
-For each coupling we vary in a fit, we remain as general as possible, treat it
+For each coupling \christoph{that} we vary in a fit, we remain as general as possible, treat it
 as a complex number and use the cartesian parametrization assuming uniform
@@
 doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
-interference effects with new physics in vector couplings. Finally, we conclude
+interference effects with new physics in vector couplings \christoph{$\wilson{9,9',10,10'}$}. Finally, we conclude
 this section with posterior predictions---conditional on all experimental
 constraints---of the probable ranges of the not-yet-measured angular observables
+\christoph{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
 in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.
@@
 
-In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$, the
+In a scenario with only \christoph{complex-valued tensor couplings} $\wilson{T,\, T5}$, the
 experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
@@
 results of $B\to K^*$ form factors that predict values above the measured
-values~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
+\christoph{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
 to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
@@
 
-We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ \fred{Is this
-  $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
-bounds with respect to interference. Note that $\wilson{7,7'}$ appears in linear
-combinations with $\wilson{9,9'}$ such that its interference with tensor and
-scalar couplings is captured implicitly by allowing new physics in
-$\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
+We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ in order to assess the 
+robustness of the bounds with respect to interference. Note that $\wilson{7,7'}$
+appears in linear combinations with $\wilson{9,9'}$ such that its interference 
+with tensor and scalar couplings is captured implicitly by allowing new physics
+in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
 generality. In this case, $F_H^\mu$ by itself still provides bounds on
@@
 addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
-\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%
-which we attribute to cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
+\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%,
+which we attribute to \christoph{the} cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
 $F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
@@
 boundaries are much larger than the regions of high likelihood, one could think
-the value of the boundary is irrelevant but in fact it determines the peak of
+the value of the boundary is irrelevant, but in fact it determines the peak of
 the prior in polar coordinates. In other words, the uniform prior on
@@
   \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
-    only $F_H^\mu$~[grey dotted, left panel], only $\overline{\cal B}(B_s \to
-    \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
+    only $F_H^\mu$~\christoph{[grey dotted]}, only $\overline{\cal B}(B_s \to
+    \bar\mu\mu)$ \christoph{[blue dashed]}, and the combination with all other
     data in \reftab{tab:observables} as well as nonzero
-    $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
-    and 95\% (lighter) probability. The constraints on Re$(\wilson{P}Ê\pm
-    \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$, apart from
+    $\wilson[]{9,\,9',\,10,\, 10'}$ \christoph{[red solid]} at 68\% (darker)
+    and 95\% (lighter) probability. The constraints on Re$(\wilson{P} \pm
+    \wilson{P'})$ are identical to Re$(\wilson{S} \pm \wilson{S'})$, apart from
     a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
@@
 general case of complex-valued couplings. For example they are a factor two to
-five more stringent than \cite{Becirevic:2012fy} and comparable to
+five more stringent than~\cite{Becirevic:2012fy} and comparable to
 \cite{Altmannshofer:2012az} once restricting to the simpler scenarios considered
@@
 
-In the following we consider a model-independent scenario as given by the SM but
-augmented by dimension six operators that respect the SM gauge group and are
+In the following we consider a model-independent scenario \christoph{consisting
+of the SM augmented} by dimension six operators that respect the SM gauge group and are
 composed of SM fields only. Such a scenario becomes more and more viable for two
@@
 of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
-order of the $W$-boson mass is presented in~\cite{D'Ambrosio:2002ex} for vector
+order of the $W$-boson \christoph{mass in~\cite{D'Ambrosio:2002ex}} for vector
 couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
@@
   NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
-$\Lambda_{\rm NP}$ is the high-energy scale at which new physics generates these
-operators.
+$\Lambda_{\rm NP}$ is the high-energy scale at which new physics \christoph{
+is decoupled}.
 
@@
   S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
-first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on $B
-\to K \mu \bar{\mu}$ and $B_s \to \mu \bar{\mu}$. In the second fit, we allow
-$\wilson[NP]{10, 10'} \ne 0$ and further include all $B \to K^*\mu \bar{\mu}$
+first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on 
+\christoph{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
+$\wilson[NP]{10, 10'} \ne 0$ and further include all \christoph{$B \to K^* \bar\mu\mu$}
 constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
@@
       superimpose the corresponding contours from using only $\overline{\cal
-        B}(B_s\to \bar\mu\mu)$ and all $B \to K \mu \bar{\mu}$ constraints
+        B}(B_s\to \bar\mu\mu)$ and all \christoph{$B \to K \bar\mu\mu$} constraints
       (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
@@
 \refsec{sec:scalar}---yields bounds very similar to those in tables
-\ref{tab:cTT5:1-dimCLs} and \ref{tab:cSP:1-dimCLs} . The changes are only small
+\ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes are only small
 and in fact the bounds tend to be even more stringent because tensor and scalar
@@
      \label{tab:postdictions}
-     The posterior predictive 68\% probability intervals of not-yet-measured angular observables in
-%     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
-     for several new-physics scenarios given all the considered experimental
-     constraints. The corresponding values for the SM (prior predictive) are given, too, where ``$\simeq 0$''
-     indicates zero in the considered
-     approximation, see text for details. \checked{}
+     The posterior predictive 68\% probability intervals of not-yet-measured 
+     angular observables for several new-physics scenarios given all the
+     considered experimental constraints. The corresponding values for the
+     SM (prior predictive) are given, too, where ``$\simeq 0$'' indicates
+     zero in the considered approximation, see text for details.
    }
@@
 
-Now we discuss what the fits tells us about likely values of observables that
+Now we discuss what the \christoph{fits tell} us about likely values of observables that
 have not been measured yet but have sensitivity to tensor and scalar couplings.
@@
 with the vector couplings and additionally vary only $\wilson{T,T5}$
-(\refsec{sec:tensor}), only $\wilson{S^{(')},P^{(')}}$ (\refsec{sec:scalar}),
+(\refsec{sec:tensor}), only $\wilson{S,S',P,P'}$ (\refsec{sec:scalar}),
 and finally both tensor and scalar couplings (\refsec{sec:tensor:scalar}).
@@
 \begin{align}
-  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
+  \BR &
+  = \frac{\tau_{B^0}}{3} \big[
     2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
-  \right]
+  \big]
 \end{align}
 is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
-$q^2 \in [1,\, 6]$ and $[15,\, 19]$ GeV$^2$ bins.
+\christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$ bins.
 
@@
 couplings.  Schematically, $J_{6c}$ is a function of $\wilson{T} \times
-\wilson{P} + \wilson{S} \times \wilson{T5}$, $\frac{m_{\ell}}{\sqrt{q^2}}
-(\mbox{scalar}) \times (\mbox{vector})$, and $\frac{m_{\ell}}{\sqrt{q^2}}
-(\mbox{tensor}) \times (\mbox{vector})$. The largest interval is obtained for
+\wilson{P} + \wilson{S} \times \wilson{T5}$, \christoph{$m_{\ell}/\sqrt{q^2} \times
+(\mbox{scalar}) \times (\mbox{vector})$, and $m_{\ell}/\sqrt{q^2} \times
+(\mbox{tensor}) \times (\mbox{vector})$}. The largest interval is obtained for
 the scenario without scalar couplings because then the uncertainty on the
-(tensor) couplings is largest. But even then, it seems the experimental
+(tensor) couplings is largest. But even then, it \christoph{seems that the} experimental
 sensitivity will not be high enough to have an impact in global fits.
@@
 scenario, and our prior. In view of the current experimental precision of $20\%$
-on the branching ratio at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$,
+on the branching ratio at LHCb~\cite{Aaij:2013iag} with only 1 fb$^{-1}$,
 corresponding to the ${\cal O}(10^{-8})$, one can indeed hope for some
@@
 rather uniform distribution in scenarios with nonzero scalar couplings. So any
-value in the range $[-1,\, 1]$ is OK whereas we predict precisely one in the SM
-and the scenario with only tensor couplings; cf.  the last row in
-\reftab{tab:postdictions}. Hence any deviation from one would unambiguously hint
-at the presence of scalar operators.
+value in the range $[-1,\, 1]$ is \christoph{allowed} whereas \christoph{the SM 
+and the scenario with only tensor couplings predicts precisely one \cite{DeBruyn:2012wk}}; 
+cf. the last row in \reftab{tab:postdictions}. Hence any deviation from one would
+unambiguously hint at the presence of scalar operators.
 
@@
 We have derived the most stringent constraints to date on tensor and scalar
-couplings that mediate $b\to s\bar\mu\mu$ transitions using the latest
+couplings that mediate $b\to s\bar\mu\mu$ transitions\christoph{. They are based on}
+the latest
 measurements of angular observables $F_H^\mu$ and the lepton forward-backward
@@
 \cite{Aaij:2014tfa}, supplemented by measurements of the branching ratios of
-$B_s\to \bar\mu\mu$ and $B\to K^{(*)} \bar\mu\mu$. Both $F_H^\mu$ and $A_{\rm
+$B_s\to \bar\mu\mu$ and $B\to K^{(*)} \bar\mu\mu$.
+
+\christoph{Both,} $F_H^\mu$ and $A_{\rm
   FB}^\mu$ belong to a class of observables in which vector and dipole
@@
 \begin{enumerate}
-  \item imposes by itself bounds on tensor couplings $|\wilson{T,\,T5}|$ such
+  \item imposes by itself \christoph{constraints} on tensor couplings $|\wilson{T,\,T5}|$ such
   that the upper bound of the smallest 68\% (95\%) credibility interval is
   $0.43\, (0.57)$, superseding previous bounds.  In combination with current
-  data from $B\to K^* \bar\mu\mu$ and lattice $B\to K^*$ form factors, the
+  data from $B\to K^* \bar\mu\mu$ and lattice \christoph{predictions of} $B\to K^*$ form factors, the
   bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
@@
   \item for the first time allows to bound all four scalar couplings
-  $\wilson{i}$ with $i = S,\,S',\,P,\,P'$ due to it's complementarity to
+  \christoph{$\wilson{i = S,S',P,P'}$} due to it's complementarity to
   $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
@@
 additional relations between scalar couplings are enforced by the linear
-realisation of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
+realization of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
 
@@
 are allowed for $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in
-reach of the LHCb analysis of the full phase I data set. Our bounds on scalar
+reach of the LHCb analysis of the full \christoph{Run} I data set. Our bounds on scalar
 couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
@@
 J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
-$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ is a sensitive probe to distinguish tensor
-from scalar couplings; it can take on any value in the range $[-1,\, 1]$ for
-nonzero scalar couplings but is fixed to one if the scalar couplings vanish.
+$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ of \christoph{nonzero scalar couplings. 
+Currently, it can take on any value in the range $[-1,\, 1]$.}
 
@@
 Both terms depend on the scalar $B\to K^*$ form factor $A_0(q^2)$, a
-normalization factor $N$, and the K{\"a}ll{\'e}n-function $\lambda$ (see
-\cite{Bobeth:2012vn}) but have a different dependence on the Wilson coefficients
-$i = 10, 10', P, P'$:
+normalization factor $N$, and the K{\"a}ll{\'e}n-function $\lambda$
+(see~\cite{Bobeth:2012vn}), but have a different dependence on the
+Wilson coefficients $i = 10, 10', P, P'$:
 \begin{equation}
@@
 of the CKM quark-mixing matrix, the charm and bottom quark masses in the
-$\overline{\rm MS}$ scheme, and the parameterisation of subleading corrections
+$\overline{\rm MS}$ scheme, and the parameterization of subleading corrections
 in $1/m_b$ as given in \cite{Beaujean:2013soa}.
+
+\christoph{Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma distribution
+for the asymmetric uncertainties in priors anymore but rather a continuous yet
+asymmetric Gaussian distribution. In a unifying spirit, we now use the
+continuous rather than discontinuous asymmetric Gaussian to approximate
+asymmetric experimental intervals in our likelihood.}
 
@@
 \cite{Bobeth:2012vn}, respectively and we refrain from using form-factor
-relations at large and low recoil for the tensor and scalar $B\to K$ and $B\to
-K^*$ form factors.  Therefore, we need additional nuisance parameters for the
+relations at \christoph{low and high $q^2$} for the tensor and scalar $B\to K$ and $B\to
+K^*$ form factors.
+
+\christoph{Therefore, we need} additional nuisance parameters for the
 complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
@@
 with lattice determinations~\cite{Bouchard:2013eph}.
-
-Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma distribution
-for the asymmetric uncertainties in priors anymore but rather a continuous yet
-asymmetric Gaussian distribution. In a unifying spirit, we now use the
-continuous rather than discontinuous asymmetric Gaussian to approximate
-asymmetric experimental intervals in our likelihood.
-
 The lattice results are given in a slightly different parametrization
@@
   \alpha_{2}^i & \in [-3,\, 3] \,.
-t\end{align}
+\end{align}
 The results of the LCSR form-factor predictions have been provided to us
@@
 we were not even able to select just two $q^2$ values and obtain a nonsingular
-covariance. We then contacted the authors of~\cite{Horgan:2015vla} and obtained
+covariance. \todo{Really? We managed with 2, but not with 3?!} We then contacted the authors of~\cite{Horgan:2015vla} and obtained
 the original values of the form factors (including correlation) at various
@@
 it provides the flexibility needed to accomodate LCSR and lattice results. Means
-and standard abbreviations of that three-parameter fit are given in
+and standard \christoph{deviations} of that three-parameter fit are given in
 \reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
@@
 model $M$ in which $X=f(\vecth)$ is a definite function of the
-parameters $\vecth$ is given as
+parameters $\vecth$ \christoph{and} given as
 \begin{align}
@@
 
-\todo{this is just filler text to avoid ``pdfendlink ended up in different
-  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
-}
+%\todo{this is just filler text to avoid ``pdfendlink ended up in different
+%  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
+%}
 

### 2015-08-03 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added Danny's comments to draft

@@
   contributions. We use the latest experimental results for $\ell = \mu$ in
-  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
+  combination with \christoph{branching ratio of} $B_s\to \bar\mu\mu$ to derive the strongest model-independent
   bounds on tensor and scalar effective couplings to date. The measurement of
@@
 
-Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
+Both \christoph{angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
 factors for vector and dipole couplings present in the SM, thereby enhancing
@@
  \\ & +
-       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
+       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)
+       \christoph{\Op_i^\ell} \Big] + \text{h.c.}
    \christoph{\,,}
@@
 \end{equation}
-the most general dimension-six flavor-changing operators $\Op_i$ mediating $b\to
+the most general dimension-six flavor-changing operators \christoph{$\Op_i^{(\ell)}$} mediating $b\to
 s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
@@
 \\
-  \Op_{9(9')} &
+  \christoph{\Op_{9(9')}^\ell} &
   = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
 \\[0.1cm]
-  \Op_{10(10')} &
+  \christoph{\Op_{10(10')}^\ell} &
   = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
@@
 \begin{aligned}
-  \Op_{S(S')} &
+  \christoph{\Op_{S(S')}^\ell} &
   = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
 \\[0.1cm]
-  \Op_{P(P')} &
+  \christoph{\Op_{P(P')}^\ell} &
   = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
@@
 \begin{aligned}
-  \Op_{T} &
+  \christoph{\Op_{T}^\ell} &
   = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
 \\[0.1cm]
-  \Op_{T5} &
+  \christoph{\Op_{T5}^\ell} &
   = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
@@
 \end{equation}
-where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
+where the notation $\christoph{\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
 \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
@@
 $\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
-{\cal O}(m_b^2/m_W^2)$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
+\christoph{m_b m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
 %Beyond the SM,
@@
 \christoph{For the rest of this article we will suppress the lepton-flavor index
-on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$. In \refsec{sec:results}
+on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$ and 
+operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results}
 we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
@@
 available for this source of SM background\footnote{The leading QED corrections
-  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} \todo{(update ref. with published)} might provide an estimate of
+  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
   corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}
@@
   \end{center}
-  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
-    \christoph{$F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
+  \caption{ The sensitivity of to the tensor coupling $\mbox{Re}(\wilson{T})$
+    of\christoph{: $F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
     in $B^+ \to K^+ \bar\mu\mu$
@@
     confidence interval reported by LHCb (grey) if a measurement is
-    available. \checked{} }
+    available. }
   \label{fig:FHvsCT}
@@
 form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
-\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. They can only become
-relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
-\ll\wilson{10,10'}$.
+\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. \christoph{They become numerically
+relevant in cases $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
+\ll\wilson{10,10'}$, where the smallness of Wilson coefficient is of the
+same level as the suppression factor $m_\ell/\sqrt{q^2}$ of the large vectorial
+SM Wilson coefficients $\wilson[SM]{9,10}$, which implies however no large
+enhancement of $F_H^\ell$ over the SM prediction.}
 
@@
 
-In the following we consider a model-independent scenario \christoph{consisting
+In the following we consider a \christoph{scenario consisting
 of the SM augmented} by dimension six operators that respect the SM gauge group and are
@@
 
+\todo{Fred should clarify with Danny on their paper.}
 We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
@@
 \begin{align}
-  \BR &
+  \christoph{\BR} &
   = \frac{\tau_{B^0}}{3} \big[
@@
 |\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
-\pi)$ or $(m_b/m_W)^2$. These factors should be compared to the potential
+\pi)$ or \christoph{$m_b m_\ell/m_W^2$}. These factors should be compared to the potential
 suppression present for tensor and scalar contributions in particular NP models
@@
 regime where such considerations are insignificant since current experimental
-measurements, in combination with theory uncertainties, do not yet impose too
+measurements, in combination with theory uncertainties, do not yet impose 
+\christoph{sufficiently}
 stringent constraints on tensor and scalar couplings.
@@
   contributions in vector couplings.
-  \item for the first time allows to bound all four scalar couplings
+  \item for the first time allows to \christoph{simultaneously} bound all four scalar couplings
   \christoph{$\wilson{i = S,S',P,P'}$} due to it's complementarity to
@@
 
-Our study of not-yet-measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$,
+Our study of \christoph{yet unmeasured} angular observables $J_{6c}$, $(J_{1c} + J_{2c})$,
 and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
@@
 ${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
-$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
-given in \cite{Straub:2015ica}.
+$B$- and $K^*$-meson masses. The \christoph{pole} masses $M_{R,i}$ are set to
+the values given in \cite{Straub:2015ica}.
 
@@
 
-%\todo{this is just filler text to avoid ``pdfendlink ended up in different
-%  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
-%}
-
 %

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] updated journal version in one reference + revision of footnote 1

@@
 distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
-available for this source of SM background\footnote{The leading QED corrections
+available for this source of SM background\footnote{The \christoph{logarithmically
+enhanced NLO QED corrections}
   to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Discuss comments in section 1 and 2

--- 2015-08-03 tensor/draft/draft-tensor-op.tex
@@
 
-\thankstext[$\star$]{t1}{\christoph{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
+\thankstext[$\star$]{t1}{{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
 \thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
@@
 \begin{abstract}
-  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
-  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
-    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
-  the standard model and constitute sensitive probes of tensor and scalar
-  contributions. We use the latest experimental results for $\ell = \mu$ in
-  combination with \christoph{branching ratio of} $B_s\to \bar\mu\mu$ to derive the strongest model-independent
-  bounds on tensor and scalar effective couplings to date. The measurement of
-  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
+  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
+  e,\,\mu,\,\tau$) depends on two parameters, the lepton
+  forward-backward asymmetry, $A_{\rm FB}^\ell$, and the flat term,
+  $F_H^\ell$. Both are strongly suppressed in the standard model and
+  constitute sensitive probes of tensor and scalar contributions. We
+  use the latest experimental results for $\ell = \mu$ in combination
+  with the branching ratio of $B_s\to \bar\mu\mu$ to derive the
+  strongest model-independent bounds on tensor and scalar effective
+  couplings to date. The measurement of $F_H^\mu$ provides a
+  complementary constraint to that of the branching ratio of $B_s\to
   \bar\mu\mu$ and allows us---for the first time---to constrain all
   complex-valued (pseudo-)scalar couplings and their chirality-flipped
-  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
-  that our bounds even become tighter when vector couplings are allowed to
-  deviate from the standard model and that specific combinations of angular
-  observables in $B \to K^*$ are still allowed to be up to two orders of
-  magnitude larger than in the standard model, which would place them in the
-  region of LHCb's sensitivity.
+  counterparts in one fit. Based on Bayesian fits of various
+  scenarios, we find that our bounds even become tighter when vector
+  couplings are allowed to deviate from the standard model and that
+  specific combinations of angular observables in $B \to K^*$ are
+  still allowed to be up to two orders of magnitude larger than in the
+  standard model, which would place them in the region of LHCb's
+  sensitivity.
 \end{abstract}
@@
 With the analysis of the data collected by the LHCb Collaboration
-during \christoph{Run} I at the Large Hadron Collider (LHC), we now have access
-to rather large samples of rare \christoph{$B$-meson} decays with branching ratios
+during run I at the Large Hadron Collider (LHC), we now have access to
+rather large samples of rare $B$-meson decays with branching ratios
 below $10^{-5}$. As a consequence, angular analyses of three- and
@@
 
-Both \christoph{angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
+Both {angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
 factors for vector and dipole couplings present in the SM, thereby enhancing
@@
 \bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
-\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
+\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} {did not yet} allow to perform a full
 angular analysis without the assumption of vanishing scalar and tensor couplings
@@
    \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
-      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
+      \, \Big[ {C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
  \\ & +
        \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)
-       \christoph{\Op_i^\ell} \Big] + \text{h.c.}
-   \christoph{\,,}
+       {\Op_i^\ell} \Big] + \text{h.c.}
+   {\,,}
 \end{aligned}
 \end{equation}
-the most general dimension-six flavor-changing operators \christoph{$\Op_i^{(\ell)}$} mediating $b\to
+the most general dimension-six flavor-changing operators {$\Op_i^{(\ell)}$} mediating $b\to
 s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
@@
 \\
-  \christoph{\Op_{9(9')}^\ell} &
+  {\Op_{9(9')}^\ell} &
   = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
 \\[0.1cm]
-  \christoph{\Op_{10(10')}^\ell} &
+  {\Op_{10(10')}^\ell} &
   = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
@@
 \begin{aligned}
-  \christoph{\Op_{S(S')}^\ell} &
+  {\Op_{S(S')}^\ell} &
   = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
 \\[0.1cm]
-  \christoph{\Op_{P(P')}^\ell} &
+  {\Op_{P(P')}^\ell} &
   = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
@@
 \begin{aligned}
-  \christoph{\Op_{T}^\ell} &
+  {\Op_{T}^\ell} &
   = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
 \\[0.1cm]
-  \christoph{\Op_{T5}^\ell} &
+  {\Op_{T5}^\ell} &
   = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
@@
 \end{equation}
-where the notation $\christoph{\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
+where the notation ${\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
 \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
@@
 
-The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
-(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
-of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
-Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
-All other Wilson coefficients are numerically suppressed or zero:
-$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
-\christoph{m_b m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
-%Beyond the SM,
-%lepton-flavor non-universal effects are possible in principle and have been
-%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
-%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
-%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
-%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
-%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
-The Wilson coefficients of the four-quark current-current and QCD-penguin
-operators as well as of the chromomagnetic dipole operators are set to their
-NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$ \cite{Bobeth:2003at, Huber:2005ig}.
-
-\christoph{For the rest of this article we will suppress the lepton-flavor index
-on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$ and 
-operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results}
-we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
-principle only to the muonic case, but can be carried over to other lepton
-species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
-flavor. In general the Wilson coefficients are decomposed into SM and NP
-contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
-will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
-contributions synonymously for $\wilson[NP]{i}$. }
+The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at
+next-to-next-to leading order (NNLO) \cite{Bobeth:2003at,
+  Huber:2005ig} and depend on the fundamental parameters of the
+top-quark and $W$-boson masses, as well as on the sine of the weak
+mixing angle.  Moreover, they are universal for the three lepton
+flavors $\ell = e,\, \mu,\, \tau$.  All other Wilson coefficients are
+numerically suppressed or zero: $\wilson[SM]{7'} = m_s/m_b\,
+\wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim {m_b
+  m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.  The
+Wilson coefficients of the four-quark current-current and QCD-penguin
+operators as well as of the chromomagnetic dipole operators are set to
+their NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$
+\cite{Bobeth:2003at, Huber:2005ig}.
+
+For the rest of this article, we will suppress the lepton-flavor index
+on the Wilson coefficients $\wilson[\ell]{i} \to \wilson[]{i}$ and
+operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results} we exploit
+data with $\ell =\mu$ only, hence all derived constraints apply in
+principle only to the muonic case but can be carried over to the other
+lepton flavors $\ell = e,\, \tau$ for NP models that do not violate
+lepton flavor. In general, the Wilson coefficients are decomposed into
+SM and NP contributions $\wilson[]{i} = \wilson[SM]{i} +
+\wilson[NP]{i}$ but often we will use $\wilson[]{i}$ for Wilson
+coefficients with zero (or suppressed) SM contributions synonymously
+with $\wilson[NP]{i}$.
 
@@
 
-The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
-couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
-the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
-with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
+The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
+scalar couplings has been presented in \cite{Bobeth:2007dw,
+  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
+i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
+  8$}. These results imply that for SM values of the effective
 couplings
@@
   F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
-    \christoph{\bigg/ \Gamma_\ell} \,, &
+    {\bigg/ \Gamma_\ell} \,, &
   A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
@@
 Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
-The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
+The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by small
 lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
 \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
-Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
+Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher-order QED
 corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
 distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
-available for this source of SM background\footnote{The leading QED corrections
+available for this source of SM background\footnote{The \christoph{logarithmically
+enhanced NLO QED corrections}
   to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
@@
 $B_s\to \bar\mu\mu$
-& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
+& $\overline{\cal B} \equiv \int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
 \\
@@
 
-Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
-kinematic suppression---see \refeq{eq:FH-dependence}---as the sum $(\wilson{i} +
-\wilson{i'})$ whereas in the branching ratio $\overline{\cal B}(B_s\to
-\bar\ell\ell)$ they appear as the difference $(\wilson{i} - \wilson{i'}), i =
-S,\, P$.  Since the existing measurement of $F_H^\mu$ constrains the sum, the
-combination of $F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows
-us---for the first time---to bound the real and imaginary parts of all four
-couplings.  The corresponding 2D-marginalized regions in the
-$\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$) planes are shown in
-\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i} \pm
-\wilson{i'})$ are very similar to those shown and thus omitted. These bounds do
-not change when including all other data in \reftab{tab:observables}, since the
-$A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
-couplings and other observables are not very sensitive to scalar
-couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s \to
-\bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor four to five
-stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.
+Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$
+without kinematic suppression---see \refeq{eq:FH-dependence}---as the
+sum $(\wilson{i} + \wilson{i'})$ whereas in the time-integrated
+branching ratio $\overline{\cal B}(B_s\to \bar\ell\ell)$ they appear
+as the difference $(\wilson{i} - \wilson{i'}), i = S,\, P$.  Since the
+existing measurement of $F_H^\mu$ constrains the sum, the combination
+of $F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows
+us---for the first time---to bound the real and imaginary parts of all
+four couplings.  The corresponding 2D-marginalized regions in the
+$\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$) planes are shown
+in \reffig{fig:scalar}. The corresponding plots for
+$\mbox{Im}(\wilson{i} \pm \wilson{i'})$ are very similar to those
+shown and thus omitted. These bounds do not change when including all
+other data in \reftab{tab:observables}, since the $A_{\rm FB}^\mu(B\to
+K\bar\mu\mu)$ requires interference of scalar with tensor couplings
+and other observables are not very sensitive to scalar
+couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s
+\to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor
+four to five stronger than the one of $F_H^\mu$ on $(\wilson{i} +
+\wilson{i'})$.
 
@@
 
-\todo{Fred should clarify with Danny on their paper.}
-We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
-1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
-them in the near future.  At low $q^2$ the posterior predictive ranges are
-${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
-suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
-$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
-of vector couplings, note that for example the branching ratio of $B\to
-K^*\bar\ell\ell$
+We rescale $J_i$ and combinations by the $B^0$-meson life time
+$\tau_{B^0} = 1.519$~ps~\cite{Agashe:2014kda} to judge the
+experimental sensitivity in the near future by comparing to current
+measurements of the branching ratio
 \begin{align}
@@
     2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
-  \big]
+  \big] \,.
 \end{align}
-is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
-\christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$ bins.
+In the SM, the typical magnitude of the branching ratio of $B\to
+K^*\bar\ell\ell$ is approximately equal to $2 \cdot 10^{-7}$ for both
+the \christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$
+bins. For comparison, the predicted ranges for $\tau_{B^0}(J_{1s} -
+3\, J_{2s})$ and $\tau_{B^0}(J_{1c} + J_{2c})$ in the SM are
+suppressed by $2-3$ orders of magnitude down to ${\cal O}(10^{-10})$;
+cf. \reftab{tab:postdictions}.
 
@@
 
-As a special case, we considered the scenario arising from the SM augmented by
-dimension-6 operators generalising existing studies to the case of
-complex-valued couplings. In this scenario, tensor couplings are absent and
-additional relations between scalar couplings are enforced by the linear
-realization of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.
+As a special case, we consider the scenario arising from the SM
+augmented by dimension-6 operators generalizing existing studies to
+the case of complex-valued couplings. In this scenario, tensor
+couplings are absent and additional relations between scalar couplings
+are enforced by the linear realization of the $SU(2)_L \otimes U(1)_Y$
+electroweak symmetry group.
 

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Finish comment, one last todo remains, eos with doi

@@
 Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
-The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by small
-lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
-\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
-Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher-order QED
-corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
-distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
-available for this source of SM background\footnote{The \christoph{logarithmically
-enhanced NLO QED corrections}
-  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
-  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}
+The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
+  small lepton masses for the considered kinematical region $1 \leq
+  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
+  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
+can be induced by higher-order QED corrections, which will modify the
+simple $\cos\theta_\ell$ dependence of the angular
+distribution~\refeq{eq:ang-distr}, however, currently there is no
+solid estimate available for this source of SM background\footnote{The
+  {logarithmically enhanced NLO QED corrections} to $B\to
+  X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
+  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's
+  comment?!}
 
@@
   \end{center}
-  \caption{ The sensitivity of to the tensor coupling $\mbox{Re}(\wilson{T})$
-    of\christoph{: $F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row)
-    in $B^+ \to K^+ \bar\mu\mu$
-    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$
-    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$
-    integrated over low- and high-$q^2$ bins. In the last two rows, the observables
-    are rescaled by the
-    lifetime of the $B$ meson for easier comparison with the branching
-    ratios. The bands represent the theory uncertainties at 68\% and 95\%
-    probability of the prior predictive distribution.  For comparison, two sets
-    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
-    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
-    confidence interval reported by LHCb (grey) if a measurement is
-    available. }
+  \caption{ The sensitivity to the tensor coupling
+    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
+    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
+    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
+    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
+    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
+    observables are rescaled by the lifetime of the $B$ meson,
+    $\tau_B$. The bands represent the theory uncertainties at 68\% and
+    95\% probability of the prior predictive.  Two sets of bands are
+    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
+    (red). If available, the grey band indicates the latest 68\%
+    confidence interval reported by LHCb.}
   \label{fig:FHvsCT}
@@
 \end{equation}
-Concerning $F_H^\ell$, the involved kinematic factors---see \cite{Bobeth:2007dw,
-  Bobeth:2012vn}---are such that tensor and scalar couplings contribute only
-constructively/cumulatively, apart from cancellations among $\wilson{S(P)}$ and
-$\wilson{S'(P')}$.  Interference terms in the numerator of $F_H^\ell$ of the
-form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
-\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. \christoph{They become numerically
-relevant in cases $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
-\ll\wilson{10,10'}$, where the smallness of Wilson coefficient is of the
-same level as the suppression factor $m_\ell/\sqrt{q^2}$ of the large vectorial
-SM Wilson coefficients $\wilson[SM]{9,10}$, which implies however no large
-enhancement of $F_H^\ell$ over the SM prediction.}
+Concerning $F_H^\ell$, the involved kinematic factors---see
+\cite{Bobeth:2007dw, Bobeth:2012vn}---are such that tensor and scalar
+couplings contribute only constructively/cumulatively, apart from
+cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
+Interference terms in the numerator of $F_H^\ell$ of the form
+$(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
+\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. They become
+numerically relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$ or
+$\wilson{P,P'} \ll\wilson{10,10'}$ where the smallness of
+$\wilson{T,P,P'}$ is of the same level as the suppression factor
+$m_\ell/\sqrt{q^2}$ accompanying the large vectorial SM Wilson
+coefficients $\wilson[SM]{9,10} \sim \pm 4$. This implies, however, no
+large enhancement of $F_H^\ell$ over the SM prediction.
 
@@
 From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
-\to K$ observable is attained by \christoph{$F_H^\mu$} at high $q^2$ due to a partial
+\to K$ observable is attained by {$F_H^\mu$} at high $q^2$ due to a partial
 cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
-uncertainty could be reduced further, \christoph{$F_H^\mu$} would give a very strong
+uncertainty could be reduced further, {$F_H^\mu$} would give a very strong
 constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
-\christoph{$\wilson{T}$}. The prediction of \christoph{${\cal B}(B\to K \bar\mu\mu)$} is
-essentially insensitive to $\wilson{T}$ but sensitive to \christoph{$\wilson[NP]{9}$}. A
-stronger impact on global fits, however, would \christoph{require a} reduced theory
+{$\wilson{T}$}. The prediction of {${\cal B}(B\to K \bar\mu\mu)$} is
+essentially insensitive to $\wilson{T}$ but sensitive to {$\wilson[NP]{9}$}. A
+stronger impact on global fits, however, would {require a} reduced theory
 uncertainty.
 
-The observable \christoph{${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
+The observable {${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
 $\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
@@
 unaffected. Regarding $(J_{1s}-3J_{2s})$, the situation is reversed: here the
-strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, \christoph{$F_H^\mu$},
-$(J_{1c}+J_{2c})$ at \christoph{high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
+strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, {$F_H^\mu$},
+$(J_{1c}+J_{2c})$ at {high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
 to $\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.
 
-From the available measurements, \christoph{$F_H^\mu$} at high $q^2$ currently provides the
+From the available measurements, {$F_H^\mu$} at high $q^2$ currently provides the
 most stringent constraints on the size of tensor couplings. Moreover, the
@@
 
-Eventually we also explore the effect of interference with \christoph{NP contributions}
+Eventually we also explore the effect of interference with {NP contributions}
 in the vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds
@@
 $B\to K^* \bar\mu\mu$ as they provide additional constraints on the real and
-imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental \christoph{input} of all
+imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental {input} of all
 observables entering our fits is listed in \reftab{tab:observables} together with input for
@@
 main objective is to derive constraints on tensor and scalar couplings through
-the enhanced sensitivity of both observables to \christoph{these} couplings compared to
+the enhanced sensitivity of both observables to {these} couplings compared to
 vector couplings. For this purpose, we will consider several model-independent
@@
 
-For each coupling \christoph{that} we vary in a fit, we remain as general as possible, treat it
+For each coupling {that} we vary in a fit, we remain as general as possible, treat it
 as a complex number and use the cartesian parametrization assuming uniform
@@
 doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
-interference effects with new physics in vector couplings \christoph{$\wilson{9,9',10,10'}$}. Finally, we conclude
+interference effects with new physics in vector couplings {$\wilson{9,9',10,10'}$}. Finally, we conclude
 this section with posterior predictions---conditional on all experimental
 constraints---of the probable ranges of the not-yet-measured angular observables
-\christoph{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
+{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
 in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.
@@
 
-In a scenario with only \christoph{complex-valued tensor couplings} $\wilson{T,\, T5}$, the
+In a scenario with only {complex-valued tensor couplings} $\wilson{T,\, T5}$, the
 experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
@@
 results of $B\to K^*$ form factors that predict values above the measured
-\christoph{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
+{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
 to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
@@
 \reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%,
-which we attribute to \christoph{the} cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
+which we attribute to {the} cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
 $F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
@@
   \end{center}
-  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
-    only $F_H^\mu$~\christoph{[grey dotted]}, only $\overline{\cal B}(B_s \to
-    \bar\mu\mu)$ \christoph{[blue dashed]}, and the combination with all other
-    data in \reftab{tab:observables} as well as nonzero
-    $\wilson[]{9,\,9',\,10,\, 10'}$ \christoph{[red solid]} at 68\% (darker)
-    and 95\% (lighter) probability. The constraints on Re$(\wilson{P} \pm
-    \wilson{P'})$ are identical to Re$(\wilson{S} \pm \wilson{S'})$, apart from
-    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
-    indicated by the black diamond. \checked{} }
+  \caption{ The constraints on complex-valued
+    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(grey dotted), only
+    $\overline{\cal B}(B_s \to \bar\mu\mu)$ (blue dashed), and the
+    combination with all other data in \reftab{tab:observables} as
+    well as nonzero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid) at
+    68\% (darker) and 95\% (lighter) probability. The constraints on
+    Re$(\wilson{P} \pm \wilson{P'})$ are identical to Re$(\wilson{S}
+    \pm \wilson{S'})$, apart from a small translation of the contours
+    by $(+0.2,\, +0.15)$. The SM prediction is indicated by the black
+    diamond. }
   \label{fig:scalar}
@@
 
-In the following we consider a \christoph{scenario consisting
-of the SM augmented} by dimension six operators that respect the SM gauge group and are
-composed of SM fields only. Such a scenario becomes more and more viable for two
-reasons. The first is the discovery of a scalar resonance at the LHC in
-agreement with all requirements of the Higgs particle in the SM. The second are
-the steadily rising lower bounds on the mass of new particles reported by ATLAS
-and CMS in various more or less specific models.
+In the following we consider a {scenario consisting of the
+  SM augmented} by dimension-six operators that respect the SM gauge
+group and are composed of SM fields only. Such a scenario becomes more
+and more viable for two reasons. The first is the discovery of a
+scalar resonance at the LHC in agreement with all requirements of the
+Higgs particle in the SM. The second are the steadily rising lower
+bounds on the mass of new particles reported by ATLAS and CMS in
+various more or less specific models.
 
@@
 of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
-order of the $W$-boson \christoph{mass in~\cite{D'Ambrosio:2002ex}} for vector
+order of the $W$-boson {mass in~\cite{D'Ambrosio:2002ex}} for vector
 couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
@@
   NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
-$\Lambda_{\rm NP}$ is the high-energy scale at which new physics \christoph{
+$\Lambda_{\rm NP}$ is the high-energy scale at which new physics {
 is decoupled}.
@@
 first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on
-\christoph{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
-$\wilson[NP]{10, 10'} \ne 0$ and further include all \christoph{$B \to K^* \bar\mu\mu$}
+{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
+$\wilson[NP]{10, 10'} \ne 0$ and further include all {$B \to K^* \bar\mu\mu$}
 constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
@@
       superimpose the corresponding contours from using only $\overline{\cal
-        B}(B_s\to \bar\mu\mu)$ and all \christoph{$B \to K \bar\mu\mu$} constraints
+        B}(B_s\to \bar\mu\mu)$ and all {$B \to K \bar\mu\mu$} constraints
       (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
@@
 
-Now we discuss what the \christoph{fits tell} us about likely values of observables that
+Now we discuss what the {fits tell} us about likely values of observables that
 have not been measured yet but have sensitivity to tensor and scalar couplings.
@@
 \begin{align}
-  \christoph{\BR} &
+  {\BR} &
   = \frac{\tau_{B^0}}{3} \big[
@@
 K^*\bar\ell\ell$ is approximately equal to $2 \cdot 10^{-7}$ for both
-the \christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$
+the {$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$
 bins. For comparison, the predicted ranges for $\tau_{B^0}(J_{1s} -
@@
 |\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
-\pi)$ or \christoph{$m_b m_\ell/m_W^2$}. These factors should be compared to the potential
+\pi)$ or {$m_b m_\ell/m_W^2$}. These factors should be compared to the potential
 suppression present for tensor and scalar contributions in particular NP models
@@
 measurements, in combination with theory uncertainties, do not yet impose
-\christoph{sufficiently}
+{sufficiently}
 stringent constraints on tensor and scalar couplings.
@@
 couplings.  Schematically, $J_{6c}$ is a function of $\wilson{T} \times
-\wilson{P} + \wilson{S} \times \wilson{T5}$, \christoph{$m_{\ell}/\sqrt{q^2} \times
-(\mbox{scalar}) \times (\mbox{vector})$, and $m_{\ell}/\sqrt{q^2} \times
-(\mbox{tensor}) \times (\mbox{vector})$}. The largest interval is obtained for
+\wilson{P} + \wilson{S} \times \wilson{T5}$, {$m_{\ell}/\sqrt{q^2} \times
+\mbox{scalar} \times \mbox{vector}$, and $m_{\ell}/\sqrt{q^2} \times
+\mbox{tensor} \times \mbox{vector}$}. The largest interval is obtained for
 the scenario without scalar couplings because then the uncertainty on the
-(tensor) couplings is largest. But even then, it \christoph{seems that the} experimental
+(tensor) couplings is largest. But even then, it {seems that the} experimental
 sensitivity will not be high enough to have an impact in global fits.
@@
 
-For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by the
-nonvanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell}), we find a
-rather uniform distribution in scenarios with nonzero scalar couplings. So any
-value in the range $[-1,\, 1]$ is \christoph{allowed} whereas \christoph{the SM
-and the scenario with only tensor couplings predicts precisely one \cite{DeBruyn:2012wk}};
-cf. the last row in \reftab{tab:postdictions}. Hence any deviation from one would
+For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
+the nonvanishing width of the $B_s$ meson
+(cf. \refapp{app:BKstarellell}), we find a rather uniform distribution
+in scenarios with nonzero scalar couplings. So any value in the range
+$[-1,\, 1]$ is plausible whereas {the SM and the scenario
+  with only tensor couplings predict a value of precisely one
+  \cite{DeBruyn:2012wk}}; cf. the last row in
+\reftab{tab:postdictions}. Hence any deviation from one would
 unambiguously hint at the presence of scalar operators.
@@
 We have derived the most stringent constraints to date on tensor and scalar
-couplings that mediate $b\to s\bar\mu\mu$ transitions\christoph{. They are based on}
+couplings that mediate $b\to s\bar\mu\mu$ transitions{. They are based on}
 the latest
@@
 
-\christoph{Both,} $F_H^\mu$ and $A_{\rm
-  FB}^\mu$ belong to a class of observables in which vector and dipole
-couplings---present in the standard model (SM)---are suppressed (mostly
-kinematically by $m_\ell / \sqrt{q^2}$) with respect to tensor and scalar
-couplings. We provide predictions for the equivalent but not-yet-measured
-angular observables $J_{6c}$, $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$ in
-$B\to K^* (\to K\pi) \bar\mu\mu$.
+Both $F_H^\mu$ and $A_{\rm FB}^\mu$ belong to a class of observables
+in which vector and dipole couplings---present in the standard model
+(SM)---are suppressed (mostly kinematically by $m_\ell / \sqrt{q^2}$)
+with respect to tensor and scalar couplings. We provide predictions
+for the equivalent but not-yet-measured angular observables $J_{6c}$,
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
+\bar\mu\mu$.
 
@@
 \begin{enumerate}
-  \item imposes by itself \christoph{constraints} on tensor couplings $|\wilson{T,\,T5}|$ such
-  that the upper bound of the smallest 68\% (95\%) credibility interval is
-  $0.43\, (0.57)$, superseding previous bounds.  In combination with current
-  data from $B\to K^* \bar\mu\mu$ and lattice \christoph{predictions of} $B\to K^*$ form factors, the
-  bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
-  contributions in vector couplings.
-  \item for the first time allows to \christoph{simultaneously} bound all four scalar couplings
-  \christoph{$\wilson{i = S,S',P,P'}$} due to it's complementarity to
+\item imposes by itself {constraints} on tensor couplings
+  $|\wilson{T,\,T5}|$ such that the upper bound of the smallest 68\%
+  (95\%) credibility interval is $0.43\, (0.57)$, superseding previous
+  bounds.  In combination with current data from $B\to K^* \bar\mu\mu$
+  and lattice {predictions of} $B\to K^*$ form factors, the
+  bounds are lowered to 0.33 (0.43), even in the presence of
+  nonstandard contributions in vector couplings.
+  \item for the first time allows to {simultaneously} bound all four scalar couplings
+  {$\wilson{S,S',P,P'}$} due to its complementarity to
   $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
@@
 
-Our study of \christoph{yet unmeasured} angular observables $J_{6c}$, $(J_{1c} + J_{2c})$,
-and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see
-\reftab{tab:postdictions}) shows that despite the current bounds on tensor
-couplings, enhancements of up to two orders of magnitude over the SM predictions
-are allowed for $(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in
-reach of the LHCb analysis of the full \christoph{Run} I data set. Our bounds on scalar
-couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
-restrictive permitting only small deviations from SM predictions in $(J_{1c} +
-J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry
-$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ of \christoph{nonzero scalar couplings.
-Currently, it can take on any value in the range $[-1,\, 1]$.}
+Our study of the {yet unmeasured} angular observables $J_{6c}$,
+$(J_{1c} + J_{2c})$, and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
+\bar\mu\mu$ (see \reftab{tab:postdictions}) shows that despite the
+current bounds on tensor couplings, enhancements of up to two orders
+of magnitude over the SM predictions are allowed for $(J_{1c} +
+J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in reach of the LHCb
+analysis of the full run~I data set. Our bounds on scalar couplings
+from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
+restrictive permitting only small deviations from SM predictions in
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP
+asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
+couplings can take on any value in the range $[-1,\, 1]$.
 
@@
 
-\christoph{Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma distribution
-for the asymmetric uncertainties in priors anymore but rather a continuous yet
-asymmetric Gaussian distribution. In a unifying spirit, we now use the
-continuous rather than discontinuous asymmetric Gaussian to approximate
-asymmetric experimental intervals in our likelihood.}
+Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma
+distribution for the asymmetric uncertainties in priors anymore but
+rather a continuous yet asymmetric Gaussian distribution. This avoids
+a poor fit because the log-gamma distribution falls off too rapidly in
+the ``short'' tail. In a unifying spirit, we now use the continuous rather
+than discontinuous asymmetric Gaussian to approximate asymmetric
+experimental intervals in our likelihood.
 
@@
 \cite{Bobeth:2012vn}, respectively and we refrain from using form-factor
-relations at \christoph{low and high $q^2$} for the tensor and scalar $B\to K$ and $B\to
+relations at {low and high $q^2$} for the tensor and scalar $B\to K$ and $B\to
 K^*$ form factors.
 
-\christoph{Therefore, we need} additional nuisance parameters for the
+{Therefore, we need} additional nuisance parameters for the
 complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
@@
 ${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
-$B$- and $K^*$-meson masses. The \christoph{pole} masses $M_{R,i}$ are set to
+$B$- and $K^*$-meson masses. The {pole} masses $M_{R,i}$ are set to
 the values given in \cite{Straub:2015ica}.
@@
 
-But for the $B \to K^*$ lattice form factors this approach is not good enough as
-we were not even able to select just two $q^2$ values and obtain a nonsingular
-covariance. \todo{Really? We managed with 2, but not with 3?!} We then contacted the authors of~\cite{Horgan:2015vla} and obtained
-the original values of the form factors (including correlation) at various
-values in the interval $q^2 \in [11.9,\, 17.8]$ to which Horgan et al. fit the
-SSE. The covariance has a block-diagonal structure with a 48$\times$48 block for
-$V, A_0, A_1, A_{12}$ and a 36$\times$36 block for $T_1, T_2, T_{23}$. Having
-the ``raw'' information on form-factor values is much more reliable and future
-proof as there are no issues with artificial correlation and we could one day
-decide to use yet another form-factor parametrization and fit it easily to these
-data points.
+For the $B \to K^*$ lattice form factors this approach is not good
+enough as we were not able to select more than two $q^2$ values
+without obtaining a singular covariance. In order to fully the exploit
+the available information, we then contacted the authors
+of~\cite{Horgan:2015vla} and obtained the original values of the form
+factors (including correlation) at various values in the interval $q^2
+\in [11.9,\, 17.8]$ to which Horgan et al. fit the SSE. The covariance
+has a block-diagonal structure with a 48$\times$48 block for $V, A_0,
+A_1, A_{12}$ and a 36$\times$36 block for $T_1, T_2, T_{23}$. Having
+the ``raw'' information on form-factor values is much more reliable
+and future proof as there are no issues with artificial correlation
+and we could one day decide to use yet another form-factor
+parametrization and fit it easily to these data points.
 
@@
 it provides the flexibility needed to accomodate LCSR and lattice results. Means
-and standard \christoph{deviations} of that three-parameter fit are given in
+and standard {deviations} of that three-parameter fit are given in
 \reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
@@
 model $M$ in which $X=f(\vecth)$ is a definite function of the
-parameters $\vecth$ \christoph{and} given as
+parameters $\vecth$ {and} given as
 \begin{align}

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Cite Stephan's thesis

@@
 
-In all but three cases, the Markov chains then give reliable results. But when
-we analyze scenarios with $\wilson[NP]{S,P} \ne 0$ and all exp.  constraints,
-strong correlations appear again. As a final solution, we then use importance
-sampling with the initial proposal function determined by a fit of a Gaussian
-mixture to the MCMC samples within the variational Bayes approximation. As the
-posterior is unimodal and closely resembles a Gaussian, only a few Gaussian
-components are needed; i.e., 3 components proved optimal by the variational
+In all but three cases, the Markov chains then give reliable
+results. But when we analyze scenarios with $\wilson{S,P} \ne 0$ and
+all experimental constraints, strong correlations appear again. As a
+final solution, we then use importance sampling with the initial
+proposal function determined by a fit of a Gaussian mixture to the
+MCMC samples within the variational Bayes
+approximation~\cite{Jahn:2015}. As the posterior is unimodal and
+closely resembles a Gaussian, only a few Gaussian components are
+needed; i.e., 3 components proved optimal by the variational
 approximation to the model evidence.
 
-In the most challenging run with 62 parameters, we obtain a relative effective
-sample size of only 0.038\%. We want to have enough independent samples $N$ such
-that the 68\% region is determined with a relative precision of about 1\%. As a
-rule of thumb, we consider the ``relative error of the error'' given by
-$1/\sqrt{2 N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute
-$1.1\cdot10^6$ importance samples such that $N \approx 3500$ and the estimated
-relative error of the error is 1.2\% and thus good enough for our purposes.
+In the most challenging run with 62 parameters, we obtain a relative
+effective sample size of only 0.038\%. We want to have enough
+independent samples $N$ such that the 68\% region is determined with a
+relative precision of about 1\%. As a rule of thumb, we consider the
+``relative error of the error'' given by $1/\sqrt{2
+  N}$~\cite[ch. 37]{Agashe:2014kda}.  In the 62D case, we compute a
+total of $1.1\cdot10^6$ importance samples, update the proposal after
+every $10^5$ samples, and combine all samples~\cite{Jahn:2015} such
+that $N \approx 3500$ and the estimated relative error of the error is
+1.2\% and thus good enough for our purposes.
 

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] changed footnote 1

@@
 distribution~\refeq{eq:ang-distr}, however, currently there is no
-solid estimate available for this source of SM background\footnote{The
-  {logarithmically enhanced NLO QED corrections} to $B\to
-  X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
-  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's
-  comment?!}
-
+solid estimate available for this source of SM background\footnote{
+  Logarithmically enhanced NLO QED corrections to $B\to X_s
+  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
+  for angular observables,
+  however, analogous corrections to $B\to K \bar\ell\ell$ are partially 
+  included in the event simulation of the experimental 
+  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}. 
+  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
+  moments of the decay distribution~\refeq{eq:ang-distr} could give an 
+  estimate of the size of higher-order QED corrections, but still
+  admixed with contributions of $\mbox{dim} \geq 8$ operators.}. 
 This picture does not change in the presence of new physics contributions to

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added Martin Jungs comments to section 4.3, extended acknowledgement

@@
 
-In the following we consider a {scenario consisting of the
-  SM augmented} by dimension-six operators that respect the SM gauge
+In the following we consider a scenario in which it is assumed that there is
+a sizeable hierarchy between the electroweak scale and the new-physics 
+scale, $\Lambda_{\rm NP}$, and that the SM gauge symmetries $SU(2)_L \times
+U(1)_Y$ are only broken at the electroweak scale. This results in the
+augmentation of the SM by dimension-six operators that respect the SM gauge
 group and are composed of SM fields only. Such a scenario becomes more
@@
 scalar resonance at the LHC in agreement with all requirements of the
-Higgs particle in the SM. The second are the steadily rising lower
+Higgs particle in the SM. The second is the steadily rising lower
 bounds on the mass of new particles reported by ATLAS and CMS in
@@
 
-A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
-was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
-of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
-order of the $W$-boson {mass in~\cite{D'Ambrosio:2002ex}} for vector
-couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
-and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
-gauge groups in conjunction with the linear representation \todo{Ask Martin,
-  Oscar how to correctly phrase this} impose the relations
+A nonredundant set of dimension-six operators of this effective theory (SM-EFT),
+requiring additionally the electroweak symmetry to be linearly realized,
+was given in \cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the
+effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale
+$\mu \sim m_W$ of the order of the $W$-boson mass was performed for vector
+couplings $\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching
+of tensor \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators 
+\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the 
+linear representation impose the relations
 \begin{align}
@@
 \end{align}
-on scalar and pseudo-scalar couplings and require tensor couplings to be
+on scalar couplings and require tensor couplings to be
 suppressed to the level of dimension-eight operators. In consequence only two
-scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
-  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
-$\Lambda_{\rm NP}$ is the high-energy scale at which new physics {
-is decoupled}.
+scalar couplings $\wilson{S,\, S'}$ arise that scale as $(\sim v/\Lambda_{\rm
+  NP})^2 \ll 1$ where $v \propto m_W$ denotes the scale of electroweak symmetry breaking.
+
+It must be noted that the relations \refeq{eq:mEFT-constraints} are a
+consequence of embedding the Higgs in a weak doublet along with the Goldstone
+bosons.  For example choosing a nonlinear representation of the scalar sector
+allows additional dimension-six operators in the according effective theory, 
+such that the couplings $\wilson{S,S',P,P'}$ are all independent and tensor
+operators have nonvanishing couplings already at dimension six 
+\cite{Cata:2015lta}.
 
 Omitting for the sake of simplicity terms of order $m_\ell^2/M_{B_s}^2$ and
-$m_s/m_b$, the couplings $\wilson{S,\, S'}$ can be bound quite reliably from
-\cite{Alonso:2014csa}
+$m_s/m_b$, the couplings $\wilson{S,\, S'}$ can be bound from~\cite{Alonso:2014csa}
 \begin{equation}
@@
 
-The SM gauge group does not imply any relation between $\wilson{10}$ and
-$\wilson{10'}$, so they are in general additional independent parameters. Here
+In the SM-EFT no relations between $\wilson{10}$ and$\wilson{10'}$ arise, 
+so they are in general additional independent parameters. Here
 we find that destructive interference with contributions involving
@@
 circle.
-
-It must be noted that the relations \refeq{eq:mEFT-constraints} are a
-consequence of embedding the Higgs in a weak doublet along with the Goldstone
-bosons.  For example choosing a nonlinear representation of the scalar sector
-allows additional dimension-six operators in the SM-EFT, such that the couplings
-$\wilson{S,S',P,P'}$ are all independent and tensor operators have nonvanishing
-couplings already at dimension six \cite{Cata:2015lta}.
 
@@
   factors. We thank also David Straub for his support with LCSR results of $B\to
-  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
+  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub
+  and Danny van Dyk for comments on the manuscript. C.B. was supported by the ERC
   Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft] run spellchecker, proof read sec. 4.3

@@
 The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
-  small lepton masses for the considered kinematical region $1 \leq
+  small lepton masses for the considered kinematic region $1 \leq
   q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
@@
     shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
-    (red). If available, the grey band indicates the latest 68\%
+    (red). If available, the gray band indicates the latest 68\%
     confidence interval reported by LHCb.}
@@
 For each coupling {that} we vary in a fit, we remain as general as possible, treat it
-as a complex number and use the cartesian parametrization assuming uniform
+as a complex number and use the Cartesian parametrization assuming uniform
 priors for ease of comparison with previous studies. Specifically, we set
@@
 second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
-that the constraints become tighter when utilising all observables in
+that the constraints become tighter when utilizing all observables in
 \reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
@@
 A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
-$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
+$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in Cartesian
 coordinates but never in even the 95\% region in polar coordinates\footnote{But
@@
   measure}. Another way to look at it is to transform the uniform prior density
-from cartesian to polar coordinates. For the example of a single Wilson
+from Cartesian to polar coordinates. For the example of a single Wilson
 coefficient, say $\wilson{T}$, the transformed density is proportional to the
-determinant of the Jacobian which is $|\wilson{T}|$. Since the cartesian prior
+determinant of the Jacobian which is $|\wilson{T}|$. Since the Cartesian prior
 boundaries are much larger than the regions of high likelihood, one could think
@@
   \caption{ The constraints on complex-valued
-    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(grey dotted), only
+    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(gray dotted), only
     $\overline{\cal B}(B_s \to \bar\mu\mu)$ (blue dashed), and the
@@
 In the following we consider a scenario in which it is assumed that there is
-a sizeable hierarchy between the electroweak scale and the new-physics 
+a sizable hierarchy between the electroweak scale and the new-physics
 scale, $\Lambda_{\rm NP}$, and that the SM gauge symmetries $SU(2)_L \times
@@
 Higgs particle in the SM. The second is the steadily rising lower
-bounds on the mass of new particles reported by ATLAS and CMS in
+bound on the mass of new particles reported by ATLAS and CMS in
 various more or less specific models.
 
-A nonredundant set of dimension-six operators of this effective theory (SM-EFT),
-requiring additionally the electroweak symmetry to be linearly realized,
-was given in \cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the
-effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale
-$\mu \sim m_W$ of the order of the $W$-boson mass was performed for vector
-couplings $\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching
-of tensor \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators 
-\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the 
-linear representation impose the relations
+A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
+that requires a linear realization of the electroweak symmetry was given in
+\cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the effective theory
+of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
+order of the $W$-boson mass was performed for vector couplings
+$\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching of tensor
+\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
+\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the linear
+representation impose the relations
 \begin{align}
@@
 consequence of embedding the Higgs in a weak doublet along with the Goldstone
-bosons.  For example choosing a nonlinear representation of the scalar sector
+bosons.  For example, choosing a nonlinear representation of the scalar sector
 allows additional dimension-six operators in the according effective theory,
@@
       scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
-      constraints in \reftab{tab:observables} (red) when marginalising over
+      constraints in \reftab{tab:observables} (red) when marginalizing over
       nonzero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
@@
 \end{enumerate}
-Our updated bounds on complex-valued tensor and scalar couplings are summarised
+Our updated bounds on complex-valued tensor and scalar couplings are summarized
 in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
@@
   factors. We thank also David Straub for his support with LCSR results of $B\to
-  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub
+  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub,
   and Danny van Dyk for comments on the manuscript. C.B. was supported by the ERC
@@
   Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
-  corresponds to the unintegrated branching ratio at time $t=0$. Due to the
+  corresponds to the plain branching ratio at time $t=0$. Due to the
   nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
@@
 of the CKM quark-mixing matrix, the charm and bottom quark masses in the
-$\overline{\rm MS}$ scheme, and the parameterization of subleading corrections
+$\overline{\rm MS}$ scheme, and the parametrization of subleading corrections
 in $1/m_b$ as given in \cite{Beaujean:2013soa}.
@@
 complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
-$z$ parameterization \cite{Khodjamirian:2010vf} and the kinematic relation
+$z$ parametrization \cite{Khodjamirian:2010vf} and the kinematic relation
 $f_0(0) = f_+(0)$, five nuisance parameters (listed in
@@
 
-We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
+We change the parametrization of $B\to K^*$ form factors w.r.t. our previous
 work \cite{Beaujean:2013soa} slightly and now use the simplified series
@@
 \begin{align}
-  \label{eq:SSE-FF-parameterization}
+  \label{eq:SSE-FF-parametrization}
   F_i(q^2) & =
@@
 
-This parameterization allows us to consistently combine available results of
+This parametrization allows us to consistently combine available results of
 form factors from different nonperturbative approaches, namely LCSR's at large
@@
 
-We have compared the SSE fit \refeq{eq:SSE-FF-parameterization} with two versus
+We have compared the SSE fit \refeq{eq:SSE-FF-parametrization} with two versus
 three parameters and found that in the former case lattice form factors
@@
 at low $q^2$ leading to a poor fit. Hence we prefer the three-parameter setup as
-it provides the flexibility needed to accomodate LCSR and lattice results. Means
+it provides the flexibility needed to accommodate LCSR and lattice results. Means
 and standard {deviations} of that three-parameter fit are given in

### 2015-08-05 py-eos/unc.py
[tensor,py-eos] Save kinematics in unc*.hdf5
Rerun all predictions for the low q^2 region on [1.1, 6] GeV^2

@@ -60,6 +60,7 @@ class Unc(object):
         with h5py.File(args.output, 'a') as output_file:
             ds_obs = output_file.create_dataset('/observable', data=self.results)
             ds_obs.attrs['name'] = self.args.observable
+            ds_obs.attrs['kinematics'] = repr(self.args.kinematics)
 
             # fixed values always the same, only use from last output
             ds_fixed = output_file.create_dataset('/descriptions/fixed parameter', data=arr.T[0])

### 2015-08-06 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] bug fix for low-q^2 predictions in Table 4, lower q^2-boundary now 1.1 GeV^2 (before 1)
[draft-tensor-op] minor modifications Intro and Fig 1 caption

@@
 \end{align}
-LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the angular
+LHCb analyzed their full run 1 data set of 3 fb$^{-1}$ and measured the angular
 distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
-\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
+\mu$~\cite{Aaij:2014tfa}, with unprecedented precision. They provide the
 lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term $F_H^\mu$
@@
     $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
-    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
-    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
+    \bar\mu\mu$. All observables are integrated over $q^2 \in [q_1^2,\,q_2^2]$
+    bins denoted as
+    $\langle \dots \rangle_{[q^2_1,\, q^2_2]}$. Angular
     observables are rescaled by the lifetime of the $B$ meson,
@@
   & $\simeq 0$
-  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
-  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
-  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
+  & $(0.6_{-1.9}^{+1.8}) \cdot 10^{-9\;}$
+  & $(-0.1_{-1.9}^{+2.3}) \cdot 10^{-10}$
+  & $(0.2_{-1.1}^{+1.1}) \cdot 10^{-9}$
   \\
@@
   & $[1.1,\, 6]$
-  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
-  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
-  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
-  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
+  & $(3.30_{-0.56}^{+0.65}) \cdot 10^{-9\;}$
+  & $(4.8_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
+  & $(2.6_{-0.4}^{+0.5}) \cdot 10^{-9\;}$
+  & $(2.8_{-1.1}^{+1.5}) \cdot 10^{-9}$
   \\
@@
   & $[1.1,\, 6]$
-  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
+  & $(2.44_{-0.48}^{+0.46}) \cdot 10^{-10}$
   & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
-  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
-  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
+  & $(4.0_{-1.2}^{+1.6}) \cdot 10^{-10}$
+  & $(1.5_{-1.1}^{+1.0}) \cdot 10^{-8}$
   \\

### 2015-08-06 tensor/draft/draft-tensor-op.tex
[plots] Update predictions at low q^2

@@
   \begin{center}
-    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
+    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1dot1to6}
     \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
     \\
-    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
+    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1dot1to6}
     \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
@@
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
-    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
     \\
-    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
+    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1dot1to6}
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
     \\
-    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
+    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1dot1to6}
     \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
@@
     $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
-    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
-    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
-    \bar\mu\mu$. All observables are integrated over $q^2 \in [q_1^2,\,q_2^2]$
-    bins denoted as
-    $\langle \dots \rangle_{[q^2_1,\, q^2_2]}$. Angular
-    observables are rescaled by the lifetime of the $B$ meson,
-    $\tau_B$. The bands represent the theory uncertainties at 68\% and
-    95\% probability of the prior predictive.  Two sets of bands are
-    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
-    (red). If available, the gray band indicates the latest 68\%
-    confidence interval reported by LHCb.}
+    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$}, $(J_{1c} +
+    J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
+    \bar\mu\mu$. Angular observables are rescaled by the lifetime of
+    the $B$ meson, $\tau_B$. The bands represent the theory
+    uncertainties at 68\% and 95\% probability of the prior
+    predictive.  Two sets of bands are shown for $\wilson[NP]{9} = 0$
+    (blue) and $\wilson[NP]{9} = -1.1$ (red). If available, the gray
+    band indicates the latest 68\% confidence interval reported by
+    LHCb. All observables are integrated over $q^2 \in
+    [q_1^2,\,q_2^2]$ bins denoted as $\langle \dots \rangle_{[q^2_1,\,
+      q^2_2]}$ to match LHCb. }
   \label{fig:FHvsCT}

### 2015-08-06 tensor/paper_plots.py

@@ -832,7 +832,14 @@ class Spring2015(object):
         return r'$\wilson[NP]{9} = ' + str(value) + '$'
 
     def scenario_comparison(self, obs, s_min, s_max, scen=('ct', 'ct_c9_1dot1'), delta_c9=(0, -1.1)):
-        return [dict(name=scen[i] + '_' + obs + '%gto%g' % (s_min, s_max), unc_label=self.np_label(delta_c9[i])) for i
+        # if s_min not integer, truncate to first decimal digit
+        kin = list(range(2))
+        for i, x in enumerate((s_min, s_max)):
+            kin[i] = repr(int(np.floor(x)))
+            if np.floor(x) != float(x):
+                kin[i] += 'dot' + repr(int(np.floor((x - np.floor(x)) * 10)))
+
+        return [dict(name=scen[i] + '_' + obs + '%sto%s' % tuple(kin), unc_label=self.np_label(delta_c9[i])) for i
                 in range(len(scen))]
 
     def fig_1(self):
@@ -842,7 +849,7 @@ class Spring2015(object):
         ylabel = r'$\langle F_H \rangle'
         yrange = (-0.02, 0.3)
 
-        s_min, s_max = 1, 6
+        s_min, s_max = 1.1, 6
         self.fig_pred(scen_obs=self.scenario_comparison(obs, s_min, s_max),
                       measurement=dict(central=0.03, sigma_upper=0.036),
                       ylabel=ylabel + '_{[%g,%g]}$' % (s_min, s_max), yrange=yrange)
@@ -856,7 +863,7 @@ class Spring2015(object):
         yrange = (0.5e-7, 2.75e-7)
         ylabel = r'$\langle \mathcal{B}(K) \rangle'
 
-        s_min, s_max = 1, 6
+        s_min, s_max = 1.1, 6
         self.fig_pred(scen_obs=self.scenario_comparison(obs, s_min, s_max),
                       measurement=dict(central=2.42e-8 * 4.9, sigma_upper=6.8072975548304046e-09),
                       ylabel=ylabel + '_{[%g,%g]}$' % (s_min, s_max), yrange=yrange)
@@ -893,7 +900,7 @@ class Spring2015(object):
         ylabel = r'$\tau_B \, \times \, \langle J_{1c} + J_{2c} \rangle'
 
         s_min, s_max = 1.1, 6
[…]

### 2015-08-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] modified eq.(3.1), final version arXiv v1
[draft-tensor-op.tex] changed name of A_\Delta\Gamma(B_s -> mu mu) to mass-eigenstate rate asymmetry as suggested by referee and unified symbol {\cal A} -> A around eq.(A.8)

@@
 
-\date{\today}
+%\date{\today}
 \maketitle
@@
   F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
-    {\bigg/ \Gamma_\ell} \,, &
-  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
+    \bigg/ \Gamma_\ell(q^2) \,, &
+  A_{\rm FB}^\ell(q^2) \big|_{\rm SM} & = 0 \,.
 \end{align}
@@
 
-For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
+For the \christoph{mass-eigenstate rate} asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
 the nonvanishing width of the $B_s$ meson
@@
 restrictive permitting only small deviations from SM predictions in
-$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the \christoph{
+mass-eigenstate rate}
 asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
@@
   \overline{\cal B} (B_s \to \bar\ell\ell) &
-  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
+  = \frac{1 + y_s \christoph{\, A_{\Delta\Gamma}}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
 \end{align}
 Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
-\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
-due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
-in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
-Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
+\cite{Beaujean:2013soa}. \christoph{$A_{\Delta\Gamma}$ is the mass-eigenstate rate} asymmetry
+due to nonvanishing width difference, which is \christoph{$A_{\Delta\Gamma} = 1$}
+in the SM, but in general can be \christoph{$A_{\Delta\Gamma} \in [-1,\, 1]$}.
+Since \christoph{$A_{\Delta\Gamma}$} can depart from it's SM value in scenarios of
 new physics considered in this work, we take this effect into account

### 2015-08-27 tensor/draft/draft-tensor-op.tex
[draft] Remove references to polar coordinates and absolute values

@@
   \hline
-  $|\wilson{T}|$, $|\wilson{T5}|$
-  & $[0.13,\, 0.43]$, $[0.03,\, 0.57]$
-  & $[0.09,\, 0.33]$, $[0.02,\, 0.44]$
-  & $[0.10,\, 0.33]$, $[0.02,\, 0.43]$
-  \\
-  \hline
   \end{tabular}
@@
 bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.
-
-A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
-$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in Cartesian
-coordinates but never in even the 95\% region in polar coordinates\footnote{But
-  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
-  region.}. This is a consequence of the general \emph{concentration of
-  measure}. Another way to look at it is to transform the uniform prior density
-from Cartesian to polar coordinates. For the example of a single Wilson
-coefficient, say $\wilson{T}$, the transformed density is proportional to the
-determinant of the Jacobian which is $|\wilson{T}|$. Since the Cartesian prior
-boundaries are much larger than the regions of high likelihood, one could think
-the value of the boundary is irrelevant, but in fact it determines the peak of
-the prior in polar coordinates. In other words, the uniform prior on
-$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
-$|\wilson{T}|$ even though we consider it consensus in the community that
-smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
-SM. We suggest therefore that the default treatment be revised in the future to
-include available prior knowledge.
 
@@
 so and moreover, the bounds are stable against destructive interference with
-vector couplings. In the case of $\wilson[NP]{9,9',10,10'} \ne 0$, we find the
-following bounds with 68\% (95\%) probability:
-\begin{equation}
-  \label{eq:SP-bounds}
-  \begin{aligned}
-    \left| \wilson{S} \right| & \in [0.06,\, 0.25]\; ([0.01,\, 0.36]),\\
-    \left| \wilson{S'} \right| & \in [0.09,\, 0.46]\; ([0.02,\, 0.73]),\\
-    \left| \wilson{P} \right| & \in [0.05,\, 0.21]\; ([0.01,\, 0.32]),\\
-    \left| \wilson{P'} \right| & \in [0.11,\, 0.42]\; ([0.02,\, 0.63]).
-  \end{aligned}
-\end{equation}
-Allowing in addition $\wilson{T,T5} \ne 0$, the intervals of
-\refeq{eq:SP-bounds} are quite similar but in general (10--20)\% narrower and
-shifted by that amount towards zero. Again, this can be explained by the
-cumulative effect of $\wilson{S,S',P,P'}$ and $\wilson{T,T5}$ in $F_H^\ell$
-shown in \refeq{eq:FH-dependence}.
+vector couplings.
 
@@
 $\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
-$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor} and
-\refsec{sec:scalar}---yields bounds very similar to those in tables
-\ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes are only small
-and in fact the bounds tend to be even more stringent because tensor and scalar
-couplings can contribute to $F_H^{\mu}$ only constructively---see
-\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of $B\to
-K^{*}\bar\mu\mu$ help to improve the constraints on $\wilson{T,\, T5}$. This
-demonstrates that even in the case of complex-valued couplings there is enough
-information in the data to bound all 20 real and imaginary parts.
+$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
+and \refsec{sec:scalar}---yields bounds very similar to those in
+tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
+are only small and in fact the bounds tend to be even more stringent
+\fred{by $\sim (10 - 20) \%$} because tensor and scalar couplings can
+contribute to $F_H^{\mu}$ only constructively---see
+\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
+$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
+$\wilson{T,\, T5}$. This demonstrates that even in the case of
+complex-valued couplings there is enough information in the data to
+bound all 20 real and imaginary parts.
 
@@
 \begin{enumerate}
-\item imposes by itself {constraints} on tensor couplings
-  $|\wilson{T,\,T5}|$ such that the upper bound of the smallest 68\%
-  (95\%) credibility interval is $0.43\, (0.57)$, superseding previous
-  bounds.  In combination with current data from $B\to K^* \bar\mu\mu$
-  and lattice {predictions of} $B\to K^*$ form factors, the
-  bounds are lowered to 0.33 (0.43), even in the presence of
-  nonstandard contributions in vector couplings.
-  \item for the first time allows to {simultaneously} bound all four scalar couplings
-  {$\wilson{S,S',P,P'}$} due to its complementarity to
-  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
-  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
-  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
-  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
-  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
-  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
-  further tighten the bounds.
+\item imposes by itself {constraints} on \fred{real and imaginary
+    parts of the} tensor couplings \fred{$\wilson{T,\,T5}$} such that the
+  upper bound of the smallest 68\% (95\%) credibility interval is
+  \fred{$ \lesssim 0.25\, (0.45)$}, superseding previous bounds.  In
+  combination with current data from $B\to K^* \bar\mu\mu$ and lattice
+  {predictions of} $B\to K^*$ form factors, the bounds are lowered to
+  \fred{$\lesssim 0.23\, (0.39)$}, even in the presence of nonstandard
+  contributions in vector couplings.
+\item for the first time allows to {simultaneously} bound all four
+  scalar couplings {$\wilson{S,S',P,P'}$} due to its complementarity
+  to $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into
+  account destructive interference with vector couplings, \fred{all
+  credibility intervals contain the SM. The corresponding 1D intervals
+  of real and imaginary parts have widths of $\sim 0.6\, (1.2)
+  $ for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
+  $\wilson{i} - \wilson{i'}$} for $i = S,P$. Currently, the bounds from
+  $F_H^\mu$ are weaker than those from $\overline{\cal B}(B_s \to
+  \bar\mu\mu)$ by about a factor of four. Future measurements of
+  $F_H^\mu$ at LHCb and Belle II will further tighten the bounds.
 

### 2015-08-28 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] removed all \christoph{...} and \fred{...} tags -> version for referee reply EPJC v2

@@
      \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and finally allowing
-     complex-valued new physics contributions to $\wilson{9,\,10}$. \checked{} %\fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
+     complex-valued new physics contributions to $\wilson{9,\,10}$.
   }
@@
 are only small and in fact the bounds tend to be even more stringent
-\fred{by $\sim (10 - 20) \%$} because tensor and scalar couplings can
+by $\sim (10 - 20) \%$ because tensor and scalar couplings can
 contribute to $F_H^{\mu}$ only constructively---see
@@
 
-For the \christoph{mass-eigenstate rate} asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
+For the mass-eigenstate rate asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
 the nonvanishing width of the $B_s$ meson
@@
 \begin{enumerate}
-\item imposes by itself {constraints} on \fred{real and imaginary
-    parts of the} tensor couplings \fred{$\wilson{T,\,T5}$} such that the
+\item imposes by itself {constraints} on real and imaginary
+  parts of the tensor couplings $\wilson{T,\,T5}$ such that the
   upper bound of the smallest 68\% (95\%) credibility interval is
-  \fred{$ \lesssim 0.25\, (0.45)$}, superseding previous bounds.  In
+  $\lesssim 0.25\, (0.45)$, superseding previous bounds.  In
   combination with current data from $B\to K^* \bar\mu\mu$ and lattice
-  {predictions of} $B\to K^*$ form factors, the bounds are lowered to
-  \fred{$\lesssim 0.23\, (0.39)$}, even in the presence of nonstandard
+  predictions of $B\to K^*$ form factors, the bounds are lowered to
+  $\lesssim 0.23\, (0.39)$, even in the presence of nonstandard
   contributions in vector couplings.
-\item for the first time allows to {simultaneously} bound all four
-  scalar couplings {$\wilson{S,S',P,P'}$} due to its complementarity
+\item for the first time allows to simultaneously bound all four
+  scalar couplings $\wilson{S,S',P,P'}$ due to its complementarity
   to $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into
-  account destructive interference with vector couplings, \fred{all
+  account destructive interference with vector couplings, all
   credibility intervals contain the SM. The corresponding 1D intervals
   of real and imaginary parts have widths of $\sim 0.6\, (1.2)
-  $ for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
-  $\wilson{i} - \wilson{i'}$} for $i = S,P$. Currently, the bounds from
+  $for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
+  $\wilson{i} - \wilson{i'}$ for $i = S,P$. Currently, the bounds from
   $F_H^\mu$ are weaker than those from $\overline{\cal B}(B_s \to
@@
 restrictive permitting only small deviations from SM predictions in
-$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the \christoph{
-mass-eigenstate rate}
-asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
+$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the mass-eigenstate
+rate asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
 couplings can take on any value in the range $[-1,\, 1]$.
@@
   \overline{\cal B} (B_s \to \bar\ell\ell) &
-  = \frac{1 + y_s \christoph{\, A_{\Delta\Gamma}}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
+  = \frac{1 + y_s \, A_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
 \end{align}
 Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
-\cite{Beaujean:2013soa}. \christoph{$A_{\Delta\Gamma}$ is the mass-eigenstate rate} asymmetry
-due to nonvanishing width difference, which is \christoph{$A_{\Delta\Gamma} = 1$}
-in the SM, but in general can be \christoph{$A_{\Delta\Gamma} \in [-1,\, 1]$}.
-Since \christoph{$A_{\Delta\Gamma}$} can depart from it's SM value in scenarios of
+\cite{Beaujean:2013soa}. $A_{\Delta\Gamma}$ is the mass-eigenstate rate asymmetry
+due to nonvanishing width difference, which is $A_{\Delta\Gamma} = 1$
+in the SM, but in general can be $A_{\Delta\Gamma} \in [-1,\, 1]$.
+Since $A_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
 new physics considered in this work, we take this effect into account

### 2015-10-27 tensor/draft/draft-tensor-op.tex
[tensor] Update intervals on marginals and post. predictive for some T5 fits
[tensor-draft] corrected sign in eq.(3.2) for C_T5 -> - C_T5
[draft-tensor-op.tex] updated predictions for most general scenario

@@
 \newcommand{\fred}[1]{{\color{green}{#1}}}
+\newcommand{\update}[1]{{\color{red}{#1}}}
 \newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
@@
     \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
-                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
+                \update{+ (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}}\big]
 \intertext{is sensitive to the interference of tensor and scalar operators,
@@
   & $\quad$ $[-0.32,\, 0.16]$, $[-0.52,\, 0.35]$ $\quad$
-  & $\quad$ $[-0.29,\, 0.09]$, $[-0.43,\, 0.27]$ $\quad$
-  & $\quad$ $[-0.23,\, 0.14]$, $[-0.39,\, 0.30]$ $\quad$
+  & $\quad$ \update{$[-0.26,\, 0.10]$, $[-0.40,\, 0.26]$} $\quad$
+  & $\quad$ \update{$[-0.24,\, 0.14]$, $[-0.38,\, 0.30]$} $\quad$
   \\
@@
   & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
-  & $[-0.19,\, 0.21]$, $[-0.37,\, 0.35]$
-  & $[-0.17,\, 0.22]$, $[-0.33,\, 0.37]$
+  & \update{$[-0.18,\, 0.20]$, $[-0.34,\, 0.36]$}
+  & \update{$[-0.16,\, 0.22]$, $[-0.34,\, 0.36]$}
   \\[0.1cm]
@@
   & $[-0.25,\, 0.24]$, $[-0.44,\, 0.44]$
-  & $[-0.19,\, 0.17]$, $[-0.33,\, 0.33]$
-  & $[-0.18,\, 0.16]$, $[-0.32,\, 0.32]$
+  & \update{$[-0.24,\, 0.08]$, $[-0.38,\, 0.24]$}
+  & \update{$[-0.24,\, 0.10]$, $[-0.38,\, 0.26]$}
   \\
@@
   & $[-0.24,\, 0.25]$, $[-0.44,\, 0.45]$
-  & $[-0.21,\, 0.19]$, $[-0.37,\, 0.35]$
-  & $[-0.20,\, 0.18]$, $[-0.36,\, 0.35]$
+  & \update{$[-0.20,\, 0.18]$, $[-0.36,\, 0.34]$}
+  & \update{$[-0.18,\, 0.20]$, $[-0.34,\, 0.36]$}
   \\
@@
 are only small and in fact the bounds tend to be even more stringent
-by $\sim (10 - 20) \%$ because tensor and scalar couplings can
+\update{by $\sim (10 - 30) \%$} because tensor and scalar couplings can
 contribute to $F_H^{\mu}$ only constructively---see
@@
   & $\simeq 0$
-  & $(0.6_{-1.9}^{+1.8}) \cdot 10^{-9\;}$
+  & \update{$(0.6_{-1.9}^{+1.7}) \cdot 10^{-9\;}$}
   & $(-0.1_{-1.9}^{+2.3}) \cdot 10^{-10}$
-  & $(0.2_{-1.1}^{+1.1}) \cdot 10^{-9}$
+  & \update{$(0.0_{-0.9}^{+1.1}) \cdot 10^{-9}$}
   \\
@@
   & $\simeq 0$
-  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
+  & \update{$(1.7_{-5.6}^{+5.3}) \cdot 10^{-10}$}
   & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
-  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
+  & \update{$(-0.1_{-3.0}^{+3.5}) \cdot 10^{-10}$}
   \\
@@
   & $(3.30_{-0.56}^{+0.65}) \cdot 10^{-9\;}$
-  & $(4.8_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
+  & \update{$(3.6_{-1.1}^{+2.1}) \cdot 10^{-9\;}$}
   & $(2.6_{-0.4}^{+0.5}) \cdot 10^{-9\;}$
-  & $(2.8_{-1.1}^{+1.5}) \cdot 10^{-9}$
+  & \update{$(3.3_{-1.2}^{+2.5}) \cdot 10^{-9}$}
   \\
@@
   & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
-  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
+  & \update{$(4.3_{-2.5}^{+3.1}) \cdot 10^{-9\;}$}
   & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
-  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
+  & \update{$(2.8_{-2.2}^{+3.0}) \cdot 10^{-9}$}
   \\
@@
   & $(2.44_{-0.48}^{+0.46}) \cdot 10^{-10}$
-  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
+  &  \update{$(2.0_{-1.3}^{+1.3}) \cdot 10^{-8\;}$}
   & $(4.0_{-1.2}^{+1.6}) \cdot 10^{-10}$
-  & $(1.5_{-1.1}^{+1.0}) \cdot 10^{-8}$
+  & \update{$(1.0_{-0.7}^{+1.2}) \cdot 10^{-8}$}
   \\
@@
   & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
-  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
+  &  \update{$(7.8_{-4.9}^{+4.2}) \cdot 10^{-9\;}$}
   & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
-  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
+  & \update{$(4.6_{-3.6}^{+4.3}) \cdot 10^{-9}$}
   \\
